### 2016-09-28 2016.9.28 Jason.tex
docs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass{beamer}
\usepackage{mathtools}
\usepackage{graphicx}
\mode<presentation> {

% The Beamer class comes with a number of default slide themes
% which change the colors and layouts of slides. Below this is a list
% of all the themes, uncomment each in turn to see what they look like.

%\usetheme{default}
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Dresden}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

% As well as themes, the Beamer class has a number of color themes
% for any slide theme. Uncomment each of these in turn to see how it
% changes the colors of your current slide theme.

%\usecolortheme{albatross}
%\usecolortheme{beaver}
%\usecolortheme{beetle}
%\usecolortheme{crane}
%\usecolortheme{dolphin}
%\usecolortheme{dove}
%\usecolortheme{fly}
%\usecolortheme{lily}
%\usecolortheme{orchid}
%\usecolortheme{rose}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
%\usecolortheme{whale}
%\usecolortheme{wolverine}

%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line

%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[]{Optimized synthesized spectrum} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{Jason Cao} % Your name
\institute[NYU] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
New York University \\ % Your institution for the title page
\medskip
\textit{jc6933@nyu.edu} % Your email address
}
\date{\today} % Date, can be changed to a custom date

\begin{document}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

\begin{frame}
\frametitle{Overview} % Table of contents slide, comment this block out to remove it
\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

%------------------------------------------------
\section{Optimizing method} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\subsection{The Cannon 2 model by Casey} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}
\frametitle{Details}

The model we adopt
 \[y_{jn} = v(l_n) * \theta_{jn} + e_j \]

 Where \(y_{jn}\) is the data for star n at wavelength pixel j.

And \(v(l_n)\) is the vectorizing function. 
The input \(l_n\) is the label list of length K for star n and the  output 
\(v(l_n)\) is a vector of length D (D is bigger than K).

\( \theta_{jn}\) is a vector of length D of parameters which controlling the model at wavelength pixel j

\( e_{jn}\) is a noise draw or residual at pixel j for star n.

\end{frame}

%------------------------------------------------

%------------------------------------------------
\section{Optimizing method} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\subsection{Optimize the spectrum} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}
\frametitle{Details}

After training the model, \(v(l_n)\) and \(\theta_{jn}\) are available.

\(y_{jn}^synthesized\) is the synthesized spectrum data for star n at pixel j by Casey's 
Cannon 2.

\(y_{jn}^synthesized=v(l_n^inferred)*\theta_{jn}\) and \(l_n^inferred\) is the 
inferred labels from Casey's Cannon 2.

Get \(y_{j,n-1}^synthesized\) and \(y_{j,n+1}^synthesized\) by moving the synthesized spectrum one pixel left and one pixel right.

Fit the spectrum linearly by using 
\[y_{j,n}^optimized = a*y_{j,n-1}^synthesized + b*y_{j,n}^synthesized+c*y_{j,n+1}^synthesized\]
And a+b+c should be 1

\end{frame}

%------------------------------------------------
\section{Plot}
%------------------------------------------------

\begin{frame}
\frametitle{Table}
\begin{table}
\begin{tabular}{l l l}
\toprule
\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
\midrule
Treatment 1 & 0.0003262 & 0.562 \\
Treatment 2 & 0.0015681 & 0.910 \\
Treatment 3 & 0.0009271 & 0.296 \\
\bottomrule
\end{tabular}
\caption{Table caption}
\end{table}
\end{frame}

%------------------------------------------------

%------------------------------------------------

%------------------------------------------------
\section{Plot} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\subsection{Labels} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}
\frametitle{Details}

After training the model, \(v(l_n)\) and \(\theta_{jn}\) are available.

\(y_{jn}^observed\) is blue

\(y_{jn}^inferred\) is green

\(y_{jn}^synthesized\) is red

\end{frame}

%------------------------------------------------

%------------------------------------------------
\section{Plot} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\subsection{Compare spectrum} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}
\frametitle{Details}

Compare the spectrum: a+b+c=0.984  (a,b,c)=(0.537,0.114,0.333 )

\includegraphics[width=100mm]{/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/compare spectrum.png}

\end{frame}

%------------------------------------------------

%------------------------------------------------
\section{Plot} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\subsection{Compare Chi-Square} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}
\frametitle{Details}

The chi-squared plot

\includegraphics[width=110mm]{/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/parameter.png}

\end{frame}

\begin{frame}
\Huge{\centerline{The End}}
\end{frame}

%----------------------------------------------------------------------------------------

\end{document}

### 2016-10-01 2016.10.3 Jason_v1.tex
opts

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{Optimized Synthesized Spectrum}% Force line breaks with \\
\thanks{A footnote to the article title}%

\author{Jason Cao}
 \altaffiliation[Also at ]{Physics Department, New York University.}%Lines break automatically or can be forced with \\

\affiliation{%
 Physics Department, New York University
}%

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
The Cannon 2 is a powerful tool, which can infer labels from the spectrum after it's trained. Also, it can generate the spectrum. Here we start at the point that the model is trained. First, infer the spectrum by using the Cannon 2. Then optimize the method and generate a better spectrum. Finally, compare the synthesized spectrum with the real spectrum and check whether the optimization works.
\begin{description}

\item[Structure]
The first part describes how to synthesize the spectrum from the Cannon 2. The second part talks about how to optimize the method and generate a better synthesized spectrum. Finally, we compare the results .
\end{description}
\end{abstract}

\pacs{}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

\section{\label{sec:level1}Infer spectrum by using the Cannon 2}

Suppose we have a trained model. The training set contains 548 stellar and each stellar spectrum has 8575 pixels.

The model we adopt
 \[y_{jn} = v(l_n) \cdot \theta_{j} + e_{jn} (1)\]

 Where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. 
 And \(v(l_n)\) is the vectorizing function. 
The input \(l_n\) is the label list of length K for star n and the  output 
\(v(l_n)\) is a vector of length D (D is bigger than K).
\( \theta_{j}\) is a vector of length D of parameters which controlling the model at wavelength pixel j.
\( e_{jn}\) is a noise draw or residual at pixel j for star n.

The inferred label for stellar n \(l_n^{inferred}\) and \( \theta_{j}\) are available after the training step.
Then infer spectrum by using:
 \[y_{jn}^{inferred} = v(l_n^{inferred}) \cdot \theta_{j}  \]

 This is how to obtain the synthesized spectrum by using the Cannon 2.

 \bigskip
 The code is as followed:

 \bigskip
inferred\_labels = model.fit\_labelled\_set()

 \bigskip
v = model.vectorizer.get\_label\_vector(inferred\_labels)

 \bigskip
inferred\_flux = np.dot(v,model.theta.T)

 %% second paragraph

 \section{\label{sec:level1}optimize the inferred spectrum}

The Cannon 2 can predict the spectrum pretty well. But we can still improve it.
\bigskip

From the inferred spectrum \(y_{jn}^{inferred}\), we optimize it and generate a better synthesized spectrum, which we call \(y_{jn}^{optimized}\).
\bigskip

The method we use is to represent the spectrum at pixel j by using the inferred spectrum at pixel j-1,pixel j and pixel j+1.(If the pixel is out of range, set the flux as 1).

\[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]
\bigskip

Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. 
a+b+c should be equal to 1.
\bigskip

The code is as followed:
\bigskip

\bigskip

popt, pcov= optimization.curve\_fit(func, (x\_data, y\_data, z\_data),nor\_r, x0)
\bigskip

\bigskip

parameters = popt
\bigskip

x\_data, y\_data and z\_data are \(y_{j-1,n}^{inferred},y_{j,n}^{inferred} \)

and \( y_{j+1,n}^{inferred}\)
\bigskip

parameters are a, b and c
\bigskip

The result is \(a+b+c = 0.983661295269\). To make a+b+c=1, set a = a/(a+b+c)

b = b/(a+b+c) c = c/(a+b+c)

Calculate the optimized spectrum \( y_{j,n}^{optimized}\) by using (2)

%% Third paragraph

 \section{\label{sec:level1}Compare the two methods.}

 The blue line "Observed" is the observed spectrum from the data  \(y_{jn}\).
 The green line "inferred" is \( y_{j,n}^{inferred}\) , which is generated by the Cannon 2.
 The red line "optimized" is \( y_{j,n}^{optimized}\), which is generated by (2)

\includegraphics[width=70mm]{figure_1.png}

 Then compare the chi-square for a random stellar of the two methods:
 chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 145.84 and 145.89
 They are similar to each other.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2016-10-01 all_in_one.py
Delete all_in_one.py

@@ -1,206 +1,0 @@
-# import
-import matplotlib
-import scipy.optimize as optimization
-import numpy as np
-from astropy.table import Table
-import matplotlib.pyplot as plt
-import pickle
-import AnniesLasso as tc
-from scipy.stats import chisquare
-
-#import the data
-
-training_set = Table.read("reference_labels.csv")
-
-pkl_file = open('training_set_flux.pkl', 'rb')
-training_set_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('training_set_ivar.pkl', 'rb')
-training_set_ivar = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('wl.pkl', 'rb')
-wl = pickle.load(pkl_file)
-pkl_file.close()
-
-
-
-
-# train the model
-model = tc.L1RegularizedCannonModel(
-    training_set, training_set_flux, training_set_ivar,threads=8)
-
-model.s2 = 0
-model.regularization = 0
-model.vectorizer = tc.vectorizer.NormalizedPolynomialVectorizer(training_set,
-    tc.vectorizer.polynomial.terminator(("Teff_{corr}", "logg_{corr}", "[M/H]_{corr}"), 2))
-
-model.train()
-
-# obtain the spectrum data
-norm_tr_flux = training_set_flux
-
-inferred_labels = model.fit_labelled_set()
-v = model.vectorizer.get_label_vector(inferred_labels)
-inferred_flux = np.dot(v,model.theta.T)
-
-
-
-# fit a b c for a single pixel/wave length
-
-# define a function for fitting
-def func(m, a, b, c):
-    (x,y,z) = m
-    return a * x + b * y + c * z
-
-# define the class for fitting spectrum by nearby spectrum
-class fit_neighborhood:
-
-    def __init__(self,n,i):
-        self.n = np.array(n)
-        self.i = np.array(i)
-
-
-    def fitting_spectrum_parameters(self):
-        nor = self.n
-        inf = self.i
-        n_pixel = nor[0, :].size
-        n_star = inf[:, 0].size
-        nor = norm_tr_flux
-        inf = inferred_flux
-        n_pixel = nor[0, :].size
-        n_star = inf[:, 0].size
-
-        x_data = inf
-        y_data = inf
-        z_data = inf
-
-        one = np.ones(n_star)
-        x_data = np.delete(x_data, (0), axis=1)
[…]

### 2016-10-01 Plot_spectrum_compare.py
Delete Plot_spectrum_compare.py

@@ -1,43 +1,0 @@
-from numpy import genfromtxt
-import matplotlib.pyplot as plt
-import random
-import matplotlib
-import numpy as np
-import pickle
-
-
-# read data
-pkl_file = open('normalized_flux.pkl', 'rb')
-nor = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('inferred_spectrum.pkl', 'rb')
-inf_old = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('optimized_spectrum.pkl', 'rb')
-inf_opt = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('wl.pkl', 'rb')
-wl = pickle.load(pkl_file)
-pkl_file.close()
-
-
-p = np.random.randint(0,547)
-
-# plot
-font = {'weight': 'bold','size': 30}
-matplotlib.rc('font', **font)
-fig = plt.figure()
-
-plt.plot(wl,nor[p,:],"b",wl,inf_old[p,:],"g",wl,inf_opt[p,:],"r",linewidth =3.0)
-fig.suptitle('Comparison of the spectrum', fontsize=40)
-plt.xlabel('wave length', fontsize=38)
-plt.ylabel('Spectrum', fontsize=36)
-
-axes = plt.gca()
-axes.set_xlim([15660,15780])
-axes.set_ylim([0.8,1.1])
-
-plt.show()

### 2016-10-01 Plot_chi_square.py
Delete Plot_chi_square.py

@@ -1,68 +1,0 @@
-import numpy as np
-from scipy.stats import chisquare
-import matplotlib.pyplot as plt
-import pickle
-import matplotlib
-
-# read data
-
-pkl_file = open('normalized_flux.pkl', 'rb')
-nor = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('inferred_spectrum.pkl', 'rb')
-inf_old = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('optimized_spectrum.pkl', 'rb')
-inf_opt = pickle.load(pkl_file)
-pkl_file.close()
-
-
-chi_old = np.array([])
-p_old = np.array([])
-
-chi_opt = np.array([])
-p_opt = np.array([])
-
-for p in range(0,nor[:,0].size):
-    nor_i = nor[p,:]
-    inf_old_i = inf_old[p,:]
-    inf_opt_i = inf_opt[p,:]
-    a_old, b_old = chisquare(nor_i, inf_old_i)
-    a_opt, b_opt = chisquare(nor_i, inf_opt_i)
-    chi_old = np.append(chi_old,a_old)
-    #p_old.append(b_old)
-    chi_opt = np.append(chi_opt,a_opt)
-    #p_old.append(b_opt)
-
-
-# plot
-
-
-font = {'weight': 'bold','size': 30}
-matplotlib.rc('font', **font)
-fig = plt.figure()
-
-plt.plot(chi_old,"r",chi_opt,"g",linewidth =5.0)
-
-fig.suptitle('compare chi-square', fontsize=40)
-plt.xlabel('stellar', fontsize=38)
-plt.ylabel('chi-square', fontsize=36)
-
-#axes = plt.gca()
-#axes.set_xlim([15660,15780])
-#axes.set_xlim([16160,16280])
-#axes.set_ylim([0.8,1.1])
-#axes.set_ylim([0.8,1.1])
-plt.show()
-
-
-
-
-
-
-
-
-
-

### 2016-10-01 fitting_spectrum_optimized_v4.py
Update fitting_spectrum_optimized_v4.py

@@ -125,9 +125,8 @@ class fit_neighborhood:
 
         # infer flux from the parameters
         # add scale factor
-        scale = parameters[0] + parameters[1] + parameters[2]
 
-        opt_flux = (parameters[0]*x_data+parameters[1]*y_data+parameters[2]*z_data)/scale
+        opt_flux = (parameters[0]*x_data+parameters[1]*y_data+parameters[2]*z_data)
 
         self.optimized_spectrum = opt_flux
 

### 2016-10-01 2016.10.3 Jason_v2.tex
Add files via upload

--- 2016-10-01 2016.10.3 Jason_v1.tex
@@
 \title{Optimized Synthesized Spectrum}% Force line breaks with \\
-\thanks{A footnote to the article title}%
 
 \author{Jason Cao}
- \altaffiliation[Also at ]{Physics Department, New York University.}%Lines break automatically or can be forced with \\
 
@@
 \item[Structure]
-The first part describes how to synthesize the spectrum from the Cannon 2.
-The second part talks about how to optimize the method and generate a better synthesized spectrum.
-Finally, we compare the results .
+There are four sections.
+The first part is the introduction part, which describes the background of the method.
+Then in the assumptions and method part, we show the detail of our method.
+The next section is the experiment, where the experiment results are showed.
+Finally, we discuss our results?
 \end{description}
@@
 
-\section{\label{sec:level1}Infer spectrum by using the Cannon 2}
+\section{\label{sec:level1}Introduction}
+
+Coming soon...
+
+ %% second paragraph
+
+ \section{\label{sec:level1}Assumption and method}
 
@@
  This is how to obtain the synthesized spectrum by using the Cannon 2.
-
- \bigskip
  The code is as followed:
@@
 v = model.vectorizer.get\_label\_vector(inferred\_labels)
+\bigskip
 
+inferred\_flux = np.dot(v,model.theta.T)
  \bigskip
-inferred\_flux = np.dot(v,model.theta.T)
-
- %% second paragraph
-
- \section{\label{sec:level1}optimize the inferred spectrum}
 
@@
 \[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]
-\bigskip
 
-Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. 
+Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. The optimization method we use is Levenberg - Marquardt algorithm.
 a+b+c should be equal to 1.
-\bigskip
 
@@
 
-\bigskip
-
 popt, pcov= optimization.curve\_fit(func, (x\_data, y\_data, z\_data),nor\_r, x0)
-\bigskip
-
 \bigskip
@@
 parameters are a, b and c
+
+The result is \(a+b+c = 0.983661295269\). (a,b,c) = (0.338, 0.110, 0.536)
+
+Calculate the optimized spectrum \( y_{j,n}^{optimized}\) by using (2)
 \bigskip
 
-The result is \(a+b+c = 0.983661295269\). To make a+b+c=1, set a = a/(a+b+c)
-
-b = b/(a+b+c) c = c/(a+b+c)
-
-Calculate the optimized spectrum \( y_{j,n}^{optimized}\) by using (2)
+If the optimization works, we will optimized \(\theta_{j}\) besides a,b and c, which will come soon.
 
@@
 
- \section{\label{sec:level1}Compare the two methods.}
+ \section{\label{sec:level1}Experiment}
+ \subsection{\label{sec:level2}Experiment 1}
+
+ Choose stellar aspcapStar-v304-2M16421116+361822
+ 5. Then plot the spectrum
 
@@
 
-\includegraphics[width=70mm]{figure_1.png}
+%\includegraphics[width=70mm]{figure_1.png}
 
- Then compare the chi-square for a random stellar of the two methods:
+ Then compare the chi-square for aspcapStar-v304-2M16421116+3618225 of the two methods:
  chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 145.84 and 145.89
  They are similar to each other.
+
+ %% Fourth paragraph
+
+ \section{\label{sec:level1}Discussion}
+
+ Coming soon.
 

### 2016-10-02 2016.10.3 Jason_v2.tex
Update 2016.10.3 Jason_v2.tex

@@
 a+b+c should be equal to 1.
+\bigskip
+
+There are some tricks in the fitting.
+Because the fitting module is very sensitive to the outliers in the spectrum data, we add a constant to the flux and subtract it after the fitting.
+The result is better because a+b+c is closer to 1, which is 0.996 compared to 0.983.
+\bigskip
+Also, we add a bound to the parameters to make b is bigger than a or c. set the range of b as (0.8,1.2)
 
@@
 
-The result is \(a+b+c = 0.983661295269\). (a,b,c) = (0.338, 0.110, 0.536)
+The result is \(a+b+c = 0.997\). (a,b,c) = (-0.005,0.810, 0.192)
 
@@
  Then compare the chi-square for aspcapStar-v304-2M16421116+3618225 of the two methods:
- chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 145.84 and 145.89
+ chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 302.41 and 304.21
  They are similar to each other.

### 2016-10-02 fitting_spectrum_optimized_v4.py
Update fitting_spectrum_optimized_v4.py

@@ -91,7 +91,7 @@ class fit_neighborhood:
 
 
 
-        """
+
 
         output = open('x_data.pkl', 'wb')
         pickle.dump(x_data, output)
@@ -105,21 +105,24 @@ class fit_neighborhood:
         pickle.dump(z_data, output)
         output.close()
 
-        """
+        # add a value to minimize the influence of outlier
+        scale = 4
+        trial = np.ones((548, 8575)) * scale
 
-
-
-
-        x_data_r = x_data.ravel()
-        y_data_r = y_data.ravel()
-        z_data_r = z_data.ravel()
-        print(x_data.shape,y_data.shape,z_data.shape,nor.shape)
-        nor_r = nor.ravel()
-
-        # The trick is here. give x,y,z equal positions
-        x0 = np.array([0, 0, 0])
         # fit
-        popt, pcov= optimization.curve_fit(func, (x_data_r, y_data_r, z_data_r),nor_r, x0)
+        x_data_r = (trial + x_data).ravel()
+        y_data_r = (trial + y_data).ravel()
+        z_data_r = (trial + z_data).ravel()
+        # print(x_data.shape, y_data.shape, z_data.shape, nor.shape)
+        nor_r = (nor + trial).ravel()
+
+        # set bounds
+        para_bounds = ([-np.inf, 0.81, -np.inf], [np.inf, 1, np.inf])
+
+        x0 = np.array([0,1,0])
+
+        popt, pcov = optimization.curve_fit(func, (x_data_r, y_data_r, z_data_r),
+                                            nor_r, x0, bounds=para_bounds)
         parameters = popt
 
 
@@ -133,7 +136,7 @@ class fit_neighborhood:
         print(parameters[0],parameters[1],parameters[2],parameters[0]+parameters[1]+parameters[2])
         #save the optimized spectrum
 
-        output = open('optimized_spectrum_v4.pkl', 'wb')
+        output = open('optimized_spectrum_v5.pkl', 'wb')
         pickle.dump(opt_flux, output)
         output.close()
 
@@ -229,5 +232,5 @@ print(trial.fitting_spectrum_parameters().shape)
 
 trial.plot_spectrum()
 trial.plot_chi_square()
-# trial.plot_chi_square_single()
+#trial.plot_chi_square_single()
 print(trial.optimized_spectrum.shape)

### 2016-10-02 2016.10.3 Jason_v2.tex
Update 2016.10.3 Jason_v2.tex

@@
 
-There are some tricks in the fitting.
-Because the fitting module is very sensitive to the outliers in the spectrum data, we add a constant to the flux and subtract it after the fitting.
-The result is better because a+b+c is closer to 1, which is 0.996 compared to 0.983.
-\bigskip
-Also, we add a bound to the parameters to make b is bigger than a or c. set the range of b as (0.8,1.2)
-
 The code is as followed:
@@
 
-The result is \(a+b+c = 0.997\). (a,b,c) = (-0.005,0.810, 0.192)
+The result is \(a+b+c = 0.982\). (a,b,c) = ()
 

### 2016-10-02 fitting_spectrum_optimized_v4.py
Update fitting_spectrum_optimized_v4.py

@@ -105,24 +105,19 @@ class fit_neighborhood:
         pickle.dump(z_data, output)
         output.close()
 
-        # add a value to minimize the influence of outlier
-        scale = 4
-        trial = np.ones((548, 8575)) * scale
-
         # fit
-        x_data_r = (trial + x_data).ravel()
-        y_data_r = (trial + y_data).ravel()
-        z_data_r = (trial + z_data).ravel()
+        x_data_r = x_data.ravel()
+        y_data_r = y_data.ravel()
+        z_data_r = z_data.ravel()
         # print(x_data.shape, y_data.shape, z_data.shape, nor.shape)
-        nor_r = (nor + trial).ravel()
+        nor_r = nor.ravel()
 
-        # set bounds
-        para_bounds = ([-np.inf, 0.81, -np.inf], [np.inf, 1, np.inf])
+
 
         x0 = np.array([0,1,0])
 
         popt, pcov = optimization.curve_fit(func, (x_data_r, y_data_r, z_data_r),
-                                            nor_r, x0, bounds=para_bounds)
+                                            nor_r, x0)
         parameters = popt
 
 

### 2016-10-08 fitting_spectrum_optimized_v6.py
Cut the matrix

@@ -1,0 +1,283 @@
+# In this version, we choose another objective function and improve the fitting by using a better optimization method.
+
+
+
+# import
+import matplotlib
+import scipy.optimize as optimization
+import numpy as np
+from astropy.table import Table
+import matplotlib.pyplot as plt
+import pickle
+import AnniesLasso as tc
+from scipy.stats import chisquare
+from numpy.linalg import inv
+
+#import the data
+
+training_set = Table.read("reference_labels.csv")
+
+pkl_file = open('training_set_flux.pkl', 'rb')
+training_set_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('training_set_ivar.pkl', 'rb')
+training_set_ivar = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('training_set_error.pkl', 'rb')
+error = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+
+
+# train the model
+model = tc.L1RegularizedCannonModel(
+    training_set, training_set_flux, training_set_ivar,threads=8)
+
+model.s2 = 0
+model.regularization = 0
+model.vectorizer = tc.vectorizer.NormalizedPolynomialVectorizer(training_set,
+    tc.vectorizer.polynomial.terminator(("Teff_{corr}", "logg_{corr}", "[M/H]_{corr}"), 2))
+
+model.train()
+
+# obtain the spectrum data
+norm_tr_flux = training_set_flux
+
+inferred_labels = model.fit_labelled_set()
+v = model.vectorizer.get_label_vector(inferred_labels)
+inferred_flux = np.dot(v,model.theta.T)
+print(v.shape)
+
+
+
+# fit a b c for a single pixel/wave length
+
+# define a function for fitting
+def func(m, a, b, c):
+    (x,y,z) = m
+    return a * x + b * y + c * z
+
+# define the class for fitting spectrum by nearby spectrum
+class fit_neighborhood:
+
+    def __init__(self,n,i):
+        self.n = np.array(n)
+        self.i = np.array(i)
+
+
+    def fitting_spectrum_parameters(self,ivar):
+        nor = self.n
+        inf = self.i
+        n_pixel = nor[0, :].size
+        n_star = inf[:, 0].size
+        nor = norm_tr_flux
+        inf = inferred_flux
[…]

### 2016-10-08 paper/ms.tex
Update ms.tex

--- 2016-10-02 2016.10.3 Jason_v2.tex
@@
 The next section is the experiment, where the experiment results are showed.
-Finally, we discuss our results?
+Finally, we discuss our results.
 \end{description}
@@
 The method we use is to represent the spectrum at pixel j by using the inferred spectrum at pixel j-1,pixel j and pixel j+1.(If the pixel is out of range, set the flux as 1). 
+\bigskip
 
+Because linear regression is sensitive to bad data points, extra parameters need to be added to describe the bad data points. Here we introduce \(\big\{q_n\big\}_{n=1}^{N}\), \(P\), \(Y\) and \(V\).
+
+We need to find a correct objective function! 
 \[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]
+\bigskip
 
@@
 
-popt, pcov= optimization.curve\_fit(func, (x\_data, y\_data, z\_data),nor\_r, x0)
+popt, pcov= optimization.curve\_fit(func, (x\_data, y\_data, z\_data),nor\_r, x0, sigma=error)
 \bigskip
@@
 
-parameters are a, b and c
+parameters are a, b and c. b should be much bigger than both a and c. And a+b+c should be equal to 1.
 
-The result is \(a+b+c = 0.982\). (a,b,c) = ()
+The result is \(a+b+c = 0.9996\).
+
+(a,b,c) = (0.0423 ,0.9173 ,0.0404 ).
 
@@
 
-If the optimization works, we will optimized \(\theta_{j}\) besides a,b and c, which will come soon.
+If the optimization works, we will optimized \(\theta_{j}\) besides a, b and c, which will come soon.
 
@@
 %\includegraphics[width=70mm]{figure_1.png}
+%\includegraphics[width=70mm]{figure_2.png}
 
  Then compare the chi-square for aspcapStar-v304-2M16421116+3618225 of the two methods:
- chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 302.41 and 304.21
- They are similar to each other.
+ chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are  9431.78 and 9360.95 .
+ The optimized flux has a 1\% smaller chi-squared, which means our optimization works.
 

### 2016-10-09 paper/ms.tex
Update ms.tex

@@
 
-Suppose we have a trained model. The training set contains 548 stellar and each stellar spectrum has 8575 pixels.
+Suppose we have a trained model.
+The training set contains 548 stellar and each stellar spectrum has 8575 pixels.
+Every pixel is related to a specific wave length.
+It belongs to APOGEE release 10 and has a good quality.
+These stellar are the very same objects as used by the APOGEE survey for the calibration of DR10.
+Each of them has at least nine stellar labels.
+But in the training step, we only use three labels: $T_{eff}$, $log$ g  and $\left[Fe/H\right]$.
+They span the range of $3500K <T_{eff}< 5300K$, $0 <log$ $g< 5$ and $-2.5 <\left[Fe/H\right]< 0.45$.
 
@@
 The method we use is to represent the spectrum at pixel j by using the inferred spectrum at pixel j-1,pixel j and pixel j+1.(If the pixel is out of range, set the flux as 1).
+The data we use is the same as the training step.
 \bigskip
 
-Because linear regression is sensitive to bad data points, extra parameters need to be added to describe the bad data points. Here we introduce \(\big\{q_n\big\}_{n=1}^{N}\), \(P\), \(Y\) and \(V\).
+The objective function is linear :
+\[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]
 
-We need to find a correct objective function! 
-\[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]
+And the Jacobian Matrix of the objective function with respect to parameters 
+\[J = \left[y_{j-1,n}^{inferred}/\sigma_{j-1,n}, y_{j,n}^{inferred}/\sigma_{j,n},, y_{j+1,n}^{inferred}/\sigma_{j+1,n},\right]\]
+Where $\sigma{j,n}$ is the uncertainty for pixel j of stellar n.
 \bigskip
 
-Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. The optimization method we use is Levenberg - Marquardt algorithm.
-a+b+c should be equal to 1.
+Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. The optimization method we use is the least chi-squared method.
 \bigskip
 
-The code is as followed:
+To obtain a,b and c, we introduce several matrix: Y, A and C. Here the numbers of stellar and pixel each star are $n-star$ and $n-pixel$
+
+% insert matrix
+
+\[
+Y
+=
+\begin{bmatrix}
+    Y_1&Y_2 &\dots&Y_{n-star}\\
+
+\end{bmatrix}
+\]
+
+where
+\[
+ Y_n
+=
+\begin{bmatrix}
+    y_{1,n} \\
+    y_{2,n} \\
+    \vdots  \\
+    y_{j,n}  \\
+
+\end{bmatrix}
+\]
+
+% A
+\[
+A
+=
+\begin{bmatrix}
+    A_1&A_2 &\dots&A_{n-star}\\
+
+\end{bmatrix}
+\]
+
+where
+\[
+A_n
+=
+\begin{bmatrix}
+
+    1 & y_{1,n} ^{inferred} & y_{2,n} ^{inferred}\\
+    y_{1,n}^{inferred}&y_{2,n}^{inferred}& y_{3,n}^{inferred}  \\
+    \vdots & \vdots & \vdots \\
+    y_{j-1,n}^{inferred}&y_{j,n}^{inferred}& 1  \\
+
+\end{bmatrix}
+\]
+
+% sigma-C
+
+\[
+C
+=
+\begin{bmatrix}
+    C_1&C_2 &\dots&C_{n-star}\\
+
+\end{bmatrix}
+\]
+
+where
+\[
+C_n
+=
+\begin{bmatrix}
+
+    \sigma_{1,n}&0&\dots&0\\
+    0& \sigma_{2,n}&\dots&0 \\
+    \vdots & \vdots & \vdots \\
+    0&\dots&0&\sigma_{j,n}  \\
+
+\end{bmatrix}
+\]
+
+$\sigma_{j,n} $is the uncertainty for pixel j of star n. 
 \bigskip
 
-popt, pcov= optimization.curve\_fit(func, (x\_data, y\_data, z\_data),nor\_r, x0, sigma=error)
-\bigskip
+We cut the matrix Y,A and C into n-star smaller matrix so the calculation speed is higher. To calculate a,b and c.
 
-parameters = popt
-\bigskip
+ \(X = 
+ \begin{bmatrix}
 
-x\_data, y\_data and z\_data are \(y_{j-1,n}^{inferred},y_{j,n}^{inferred} \)
+    a\\
+    b \\
+    c \\
 
-and \( y_{j+1,n}^{inferred}\)
-\bigskip
+\end{bmatrix}
+\)=$\sum_{n=1}^{n-star} X_n \over{n-star}$
+
+where
+\[
+X_n = 
+\begin{bmatrix}
+
+    a_n\\
+    b_n \\
+    c_n \\
+
+\end{bmatrix}
+=\left[A_n^TC^{-1}_nA_n\right]^{-1}\left[A_n^TC^{-1}_nY_n\right]
+\]
 

### 2016-10-16 paper/ms.tex
Add fitting spectrum

--- 2016-10-02 2016.10.3 Jason_v2.tex
@@
-% ****** Start of file apssamp.tex ******
-%
-%   This file is part of the APS files in the REVTeX 4.1 distribution.
-%   Version 4.1r of REVTeX, August 2010
-%
-%   Copyright (c) 2009, 2010 The American Physical Society.
-%
-%   See the REVTeX 4 README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.1
-%
-% See the REVTeX 4 README file
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex apssamp.tex
-%  2)  bibtex apssamp
-%  3)  latex apssamp.tex
-%  4)  latex apssamp.tex
-%
-\documentclass[%
- reprint,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-%preprint,
-%showpacs,preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
- amsmath,amssymb,
- aps,
-%pra,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-1}
+\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
+\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
 
-\usepackage{graphicx}% Include figure files
+\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
+%\geometry{landscape}                		% Activate for rotated page geometry
+%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
+\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
+								% TeX will automatically convert eps --> pdf in pdflatex		
+\usepackage{amssymb}
+\usepackage{amsmath, amsthm, amssymb, amsfonts}
+
 \usepackage{dcolumn}% Align table columns on decimal point
 \usepackage{bm}% bold math
-%\usepackage{hyperref}% add hypertext capabilities
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
 
-%\usepackage[showframe,%Uncomment any one of the following lines to test 
-%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
-%%text={7in,10in},centering,
-%%margin=1.5in,
-%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
-%%height=10in,a5paper,hmargin={3cm,0.8in},
-%]{geometry}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{authblk}
+
+%SetFonts
+
+%SetFonts
+
+\title{Optimize the Cannon 2}
+\author[1]{Jason Cao\thanks{jc6933@nyu.edu}}
+\author[2]{David W. hogg\thanks{david.hogg@nyu.edu}}
+
+\affil[1]{Department of Physics,  New York University}
+\affil[2]{NYU Physics - Center for Cosmology and Particle Physics
+NYU Center for Data Science
+Max-Planck-Institut fuer Astronomie }
+
+\renewcommand\Authands{ and }
+
+\date{\today}						% Activate to display a given date or no date
 
 \begin{document}
-
-\preprint{APS/123-QED}
-
-\title{Optimized Synthesized Spectrum}% Force line breaks with \\
-
-\author{Jason Cao}
-
-\affiliation{%
- Physics Department, New York University
-}%
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
-
-\begin{abstract}
-The Cannon 2 is a powerful tool, which can infer labels from the spectrum after it's trained.
-Also, it can generate the spectrum.
-Here we start at the point that the model is trained.
-First, infer the spectrum by using the Cannon 2.
-Then optimize the method and generate a better spectrum.
-Finally, compare the synthesized spectrum with the real spectrum and check whether the optimization works.
-\begin{description}
-
-\item[Structure]
-There are four sections.
-The first part is the introduction part, which describes the background of the method.
-Then in the assumptions and method part, we show the detail of our method.
-The next section is the experiment, where the experiment results are showed.
-Finally, we discuss our results?
-\end{description}
-\end{abstract}
-
-\pacs{}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
 \maketitle
-
-%\tableofcontents
 
@@
  \section{\label{sec:level1}Assumption and method}
+ \subsection{\label{sec:level2}Optimize the spectrum}
 
-Suppose we have a trained model. The training set contains 548 stellar and each stellar spectrum has 8575 pixels.
+Suppose we have a trained model.
+The training set contains 548 stellar and each stellar spectrum has 8575 pixels.
+Every pixel is related to a specific wave length.
+It belongs to APOGEE data release 10 and has a good quality.
+These stellar are the very same objects as used by the APOGEE survey for the calibration of DR10.
+Each of them has at least nine stellar labels.
+But in the training step, we only use three of them $T_{eff}$, $log$ g  and $\left[Fe/H\right]$.
+They span the range of $3500K <T_{eff}< 5300K$, $0 <log$ $g< 5$ and $-2.5 <\left[Fe/H\right]< 0.45$.
+]
 
@@
  Where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. 
- And \(v(l_n)\) is the vectorizing function. 
+ \(v(l_n)\) is the vectorizing function. 
 The input \(l_n\) is the label list of length K for star n and the  output 
@@
 
-The inferred label for stellar n \(l_n^{inferred}\) and \( \theta_{j}\) are available after the training step.
-Then infer spectrum by using:
- \[y_{jn}^{inferred} = v(l_n^{inferred}) \cdot \theta_{j}  \]
+\(l_n^{inf}\) and \( \theta_{j}\) are available after the training step.
+Infer spectrum by using:
+ \[y_{jn}^{inf} = v(l_n^{inf}) \cdot \theta_{j}  (2)\]
 
- This is how to obtain the synthesized spectrum by using the Cannon 2.
- The code is as followed:
-
- \bigskip
-inferred\_labels = model.fit\_labelled\_set()
-
- \bigskip
-v = model.vectorizer.get\_label\_vector(inferred\_labels)
-\bigskip
-
-inferred\_flux = np.dot(v,model.theta.T)
- \bigskip
+ This is how to obtain the synthesized spectrum by using the Cannon 2. We also call it inferred flux(spectrum).
 
@@
 
-From the inferred spectrum \(y_{jn}^{inferred}\), we optimize it and generate a better synthesized spectrum, which we call \(y_{jn}^{optimized}\).
+From the inferred spectrum \(y_{jn}^{inf}\), we optimize it and generate a better synthesized spectrum, which we call \(y_{jn}^{opt}\).
 \bigskip
@@
 The method we use is to represent the spectrum at pixel j by using the inferred spectrum at pixel j-1,pixel j and pixel j+1.(If the pixel is out of range, set the flux as 1).
-
-\[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]
-
-Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. The optimization method we use is Levenberg - Marquardt algorithm.
-a+b+c should be equal to 1.
+The data we use is the same as the training step.
 \bigskip
 
-The code is as followed:
+The new spectrum, which is the optimized spectrum, is represented by:
+\[y_{j,n}^{opt}=a\cdot y_{j-1,n}^{inf}+b\cdot y_{j,n}^{inf}+c\cdot y_{j+1,n}^{inf}(3)\]
 \bigskip
 
-popt, pcov= optimization.curve\_fit(func, (x\_data, y\_data, z\_data),nor\_r, x0)
+We use the least chi-squared method. So our objective function is the chi-squared between the optimized spectrum and the spectrum data. 
 \bigskip
 
-parameters = popt
+$F_{obj} (a,b,c)$= \[\sum_{n=1,j=1}^{n=N,j=J} {(y_{jn} - y_{jn}^{opt})^2 \over{\sigma_{jn}^2}} \]  (4)
 \bigskip
 
-x\_data, y\_data and z\_data are \(y_{j-1,n}^{inferred},y_{j,n}^{inferred} \)
+$\sigma_{jn}^2$ is the data uncertainty for star n at pixel j.
+The number of stellar and pixel each star are N and J.
+Here N=548 and J = 8575.
+Write the objective function in the form of matrix can make it simpler.
+So we introduce several matrix: Y, A, C and X, which are defined as followed:
 
-and \( y_{j+1,n}^{inferred}\)
+% insert matrix
+
+\[
+Y
+=
+\begin{bmatrix}
+    Y_1&Y_2 &\dots&Y_{N}\\
+
+\end{bmatrix}
+\]
+
+where
+\[
+ Y_n
+=
+\begin{bmatrix}
+    y_{1,n} \\
+    y_{2,n} \\
+    \vdots  \\
+    y_{J,n}  \\
+
+\end{bmatrix}
+\]
+
+% A
+\[
+A
+=
+\begin{bmatrix}
+    A_1&A_2 &\dots&A_{N}\\
+
+\end{bmatrix}
+\]
+
+where
+\[
+A_n
+=
+\begin{bmatrix}
+
+    1 & y_{1,n} ^{inf} & y_{2,n} ^{inf}\\
+    y_{1,n}^{inf}&y_{2,n}^{inf}& y_{3,n}^{inf}  \\
+    \vdots & \vdots & \vdots \\
+    y_{J-1,n}^{inf}&y_{J,n}^{inf}& 1  \\
+
+\end{bmatrix}
+\]
+
+% sigma-C
+
+\[
+C
+=
+\begin{bmatrix}
+    C_1&C_2 &\dots&C_{N}\\
+
+\end{bmatrix}
+\]
+
+where
+\[
+C_n
+=
+\begin{bmatrix}
+
+    \sigma_{1,n}^2&0&\dots&0\\
+    0& \sigma_{2,n}^2&\dots&0 \\
+    \vdots & \vdots & \vdots \\
+    0&\dots&0&\sigma_{J,n}^2  \\
+
+\end{bmatrix}
+\]
+
 \bigskip
 
-parameters are a, b and c
+\(X = 
+ \begin{bmatrix}
 
-The result is \(a+b+c = 0.982\). (a,b,c) = ()
+    a\\
+    b \\
+    c \\
 
-Calculate the optimized spectrum \( y_{j,n}^{optimized}\) by using (2)
+\end{bmatrix}
+\)
+
+We cut matrix Y, A and C into N smaller matrix so the calculation speed is higher. 
 \bigskip
 
-If the optimization works, we will optimized \(\theta_{j}\) besides a,b and c, which will come soon.
+Now the objective function can be described as:
+$F_{obj} (a,b,c)$= \[\sum_{n=1}^{N} (Y_n-A_n X)^TC^{-1}(Y_n-A_n X) (5)\]  
+\bigskip
+
+And the Jacobian Matrix of the objective function with respect to parameters is
+
+J = $\partial F_{obj}\over \partial X$ \[=\sum_{n=1}^{n=N}2\cdot [(Y_n-A_nX)^TC^{-1}]\cdot (-A_n) (6)\]   
+\bigskip
+
+The dimension of the Jacobian Matrix is 1*3. To minimize the objective function, let the Jacobian Matrix be 0 and we have:
+
+\[X = [\sum_{n=1}^{n=N}A_n^TC_n^{-1}A]^{-1} \cdot [\sum_{n=1}^{n=N}A^TC_n^{-1}Y_n](7)\]
+\bigskip
+
+By using (7) we can calculate a,b and c. b should be much bigger than both a and c. And a+b+c should be equal to 1.
+
+The result is \(a+b+c = 0.99990\).
+
+(a,b,c) = (-0.00215, 1.00462, -0.00258 ).
+
+Calculate the optimized spectrum \( y_{j,n}^{opt}\) by using (3). The Experiment 1 shows that the optimization works.
+\bigskip
+
+%If the optimization works, we will optimized \(\theta_{j}\) besides a, b and c, which will come soon.
+%It works!
+
+ \subsection{\label{sec:level2}Optimized $\theta_{j}$ and inferred labels}
+ After optimizing the inferred spectrum, we can modify $\theta_{j}$ and get a better result.
+The method is to represent $\theta_j$ by using $\theta_{j-1}$ , $\theta_j$ and $\theta_{j+1}$.
+If $\theta_j$ is out of range, set it as zero.
+So the optimized $\theta$ is:
+ \[\theta_{j}^{opt}=a\cdot \theta_{j-1}+b\cdot \theta_{j}+c\cdot \theta_{j+1}(8)\]
+ \bigskip
+
+ Here a,b and c are the parameters obtained from spectrum optimization.
+Then we infer stellar labels by using $\theta_{j}^{opt}$ and generate optimized inferred labels.
+The data we use is the training set, which includes 548 stellar with 8575 pixel each.
+ Finally, compare the chi-squared to check whether the optimization works.
 
@@
 
- Choose stellar aspcapStar-v304-2M16421116+361822
- 5. Then plot the spectrum
+ Choose four stellar, which are not in the training set:
 
- The blue line "Observed" is the observed spectrum from the data  \(y_{jn}\).
- The green line "inferred" is \( y_{j,n}^{inferred}\) , which is generated by the Cannon 2.
- The red line "optimized" is \( y_{j,n}^{optimized}\), which is generated by (2)
+ Star A  $T_{eff} =4750$  log g =3.0 $\left[Fe/h\right] =0.15$
 
-%\includegraphics[width=70mm]{figure_1.png}
+ Star B  $T_{eff} =4849$  log g =2.2 $\left[Fe/h\right] =-1.0$
 
- Then compare the chi-square for aspcapStar-v304-2M16421116+3618225 of the two methods:
- chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 302.41 and 304.21
- They are similar to each other.
+ Star C  $T_{eff} =3614$  log g =0.4 $\left[Fe/h\right] =-0.68$
+
+ Star D  $T_{eff} =5003$  log g =2.8 $\left[Fe/h\right] =-0.71$
+
+ Then plot the spectrum
+
+ The black line "Observed" is the observed spectrum from the data  \(y_{jn}\).
+ The green line "inferred" is \( y_{j,n}^{inf}\) , which is generated by the Cannon 2.
+ The red line "optimized" is \( y_{j,n}^{opt}\), which is generated by (3)
+\bigskip
+
+%\includegraphics[width=170mm]{figure_1.png}
+ \centerline{Fig.1 The optimized spectrum and the data spectrum}
+\bigskip
+
+%\includegraphics[width=170mm]{figure_2.png}
+ \centerline{Fig.2 The inferred spectrum and the data spectrum}
+
+ Finally compare the chi-square for these four stars of the two methods:
+ The optimized spectrum has a 1\% smaller chi-squared so our optimization works.
+
+ \subsection{\label{sec:level2}Experiment 2}
+ Optimize $\theta_j$ and generate optimized inferred labels. Then plot the inferred labels and the optimized inferred labels.
+ \bigskip
+
+ %\includegraphics[width=170mm]{figure_3.png}
+ \centerline{Fig.3 Inferred labels and the reference labels}
+ \bigskip
+
+ Finally compare the chi-square.
+
+The chi-squared becomes 1\% bigger after the optimization. We need to do bigger optimization before inferring the labels!
 
@@
 \end{document}
-%
-% ****** End of file apssamp.tex ******

### 2016-10-16 AnniesLasso_2/__init__.py

@@ -1,0 +1,90 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+__version__ = "0.1.0"
+
+import logging
+from numpy import RankWarning
+from warnings import simplefilter
+from sys import version_info
+
+from .cannon import *
+from .regularized import *
+from . import (censoring, continuum, diagnostics, utils, vectorizer)
+
+logger = logging.getLogger(__name__)
+logger.setLevel(logging.INFO) # TODO: Remove this when stable.
+
+handler = logging.StreamHandler()
+handler.setFormatter(logging.Formatter(
+    "%(asctime)s [%(levelname)-8s] %(message)s"))
+logger.addHandler(handler)
+
+# For debugging:
+#handler.setFormatter(logging.Formatter(
+#    "%(asctime)s [%(levelname)-8s] (%(name)s/%(lineno)d): %(message)s"))
+
+simplefilter("ignore", RankWarning)
+simplefilter("ignore", RuntimeWarning)
+
+
+def load_model(filename, **kwargs):
+    """
+    Load a Cannon model from an existing filename, regardless of the kind of
+    Cannon model sub-class.
+
+    :param filename:
+        The path where the model has been saved. This saved model must include
+        a labelled data set.
+    """
+    from six.moves import cPickle as pickle # I know.
+
+    encodings = ("utf-8", "latin-1")
+    for encoding in encodings:
+        kwds = {"encoding": encoding} if version_info[0] >= 3 else {}
+        try:
+            with open(filename, "rb") as fp:        
+                contents = pickle.load(fp, **kwds)
+
+        except UnicodeDecodeError:
+            if encoding == encodings:
+                raise
+
+    class_factory = contents["metadata"]["model_name"]
+    if not class_factory.endswith("CannonModel"):
+        raise TypeError("Cannon model factory class '{}' not recognised".format(
+            class_factory))
+
+    _class = eval(class_factory)
+    has_data = (contents["metadata"]["data_attributes"][0] in contents)
+    if not has_data:
+        contents.update({
+            "labelled_set": {},
+            "normalized_flux": [],
+            "normalized_ivar": []
+        })
+
+    # Initiate the class.
+    kwds = { "verify": False }
+    kwds.update(**kwargs)
+
+    model = _class(
+        *[contents.get(attr, None) for attr in contents["metadata"]["data_attributes"]],
+        **kwds)
+
+    # Update information.
+    model._metadata.update(contents["metadata"].get("metadata", {}))
[…]

### 2016-10-16 AnniesLasso_2/__main__.py

@@ -1,0 +1,525 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+A basic command line interface for The Cannon.
+"""
+
+import argparse
+import logging
+import os
+from collections import OrderedDict
+from numpy import ceil, loadtxt, zeros, nan, diag, ones
+from subprocess import check_output
+from six.moves import cPickle as pickle
+from tempfile import mkstemp
+from time import sleep
+
+condor_code = """
+executable     = /opt/ioa/software/python/2.7/bin/python 
+universe       = vanilla
+output         = {logging_dir}/condor-{prefix}-out.log
+error          = {logging_dir}/condor-{prefix}-err.log
+log            = {logging_dir}/condor-{prefix}.log
+request_cpus   = {cpus}
+request_memory = {memory}
+Notification   = never
+# maybe arguments?
+## arguments = <arguments your script would typically take >
+arguments      = {executable} train {model_filename}
+queue
+"""
+
+def _condorlock_filename(path):
+    return "{0}/.{1}.condorlock".format(
+        os.path.dirname(path), os.path.basename(path))
+
+
+def fit(model_filename, spectrum_filenames, threads, clobber, from_filename,
+    **kwargs):
+    """
+    Fit a series of spectra.
+    """
+
+    import AnniesLasso_2 as tc
+
+    model = tc.load_model(model_filename, threads=threads)
+    logger = logging.getLogger("AnniesLasso_2")
+    assert model.is_trained
+
+    chunk_size = kwargs.pop("parallel_chunks", 1000) if threads > 1 else 1
+    fluxes = []
+    ivars = []
+    output_filenames = []
+    failures = 0
+
+    fit_velocity = kwargs.pop("fit_velocity", False)
+
+    # MAGIC HACK
+    delete_meta_keys = ("fjac", ) # To save space...
+    initial_labels = loadtxt("initial_labels.txt")
+
+    if from_filename:
+        with open(spectrum_filenames[0], "r") as fp:
+            _ = list(map(str.strip, fp.readlines()))
+        spectrum_filenames = _
+
+    output_suffix = kwargs.get("output_suffix", "result")
+    N = len(spectrum_filenames)
+    for i, filename in enumerate(spectrum_filenames):
+        logger.info("At spectrum {0}/{1}: {2}".format(i + 1, N, filename))
+
+        basename, _ = os.path.splitext(filename)
+        output_filename = "-".join([basename, output_suffix]) + ".pkl"
+        
[…]

### 2016-10-16 AnniesLasso_2/cannon.py

@@ -1,0 +1,823 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+A pedestrian version of The Cannon.
+"""
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = ["CannonModel"]
+
+import logging
+from numpy.linalg import inv
+import numpy as np
+import scipy.optimize as op
+import os
+from scipy.ndimage import gaussian_filter
+
+from . import (model, utils)
+
+logger = logging.getLogger(__name__)
+
+
+class CannonModel(model.BaseCannonModel):
+    """
+    A generalised Cannon model for the estimation of arbitrary stellar labels.
+
+    :param labelled_set:
+        A set of labelled objects. The most common input form is a table with
+        columns as labels, and stars/objects as rows.
+
+    :type labelled_set:
+        :class:`~astropy.table.Table` or a numpy structured array
+
+    :param normalized_flux:
+        An array of normalized fluxes for stars in the labelled set, given as
+        shape `(num_stars, num_pixels)`. The `num_stars` should match the number
+        of rows in `labelled_set`.
+
+    :type normalized_flux:
+        :class:`np.ndarray`
+
+    :param normalized_ivar:
+        An array of inverse variances on the normalized fluxes for stars in the
+        labelled set. The shape of the `normalized_ivar` array should match that
+        of `normalized_flux`.
+
+    :type normalized_ivar:
+        :class:`np.ndarray`
+
+    :param dispersion: [optional]
+        The dispersion values corresponding to the given pixels. If provided, 
+        this should have length `num_pixels`.
+
+    :type dispersion:
+        :class:`np.array`
+
+    :param threads: [optional]
+        Specify the number of parallel threads to use. If `threads > 1`, the
+        training and prediction phases will be automagically parallelised.
+
+    :type threads:
+        int
+
+    :param pool: [optional]
+        Specify an optional multiprocessing pool to map jobs onto.
+        This argument is only used if specified and if `threads > 1`.
+    
+    :type pool:
+        bool
+    """
+    def __init__(self, *args, **kwargs):
+        super(CannonModel, self).__init__(*args, **kwargs)
+
+
+    @model.requires_model_description
+    def train(self, fixed_scatter=True, **kwargs):
+        """
+        Train the model based on the labelled set.
+        """
+        
+        # Experimental/asthetic keywords:
[…]

### 2016-10-16 AnniesLasso_2/censoring.py

@@ -1,0 +1,89 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+A dictionary sub-class to deal with wavelength censoring.
+"""
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = ["CensorsDict"]
+
+import logging
+import numpy as np
+
+logger = logging.getLogger(__name__)
+
+class CensorsDict(dict):
+
+    def __init__(self, model, *args, **kwargs):
+        """
+        A dictionary sub-class that allows for wavelength censoring masks to be
+        applied to Cannon models.
+
+        :param model:
+            The Cannon model for which this censored dictionary will be applied.
+
+        Note:   This custom class is necessary because if you have a dictionary
+                attribute that is a `@property` of a class then it can be
+                updated directly by `model.censors["label"] = ...` which will
+                bypass the `@property.setter` method of the model class.
+        """
+        super(CensorsDict, self).__init__(*args, **kwargs)
+        self.model = model
+        return None
+
+
+    def __setitem__(self, label_name, value):
+        """
+        Update one of the entries of the wavelength censoring dictionary.
+
+        :param label_name:
+            The name of the label to apply the censoring onto.
+
+        :param value:
+            A boolean mask the same length as the `model.dispersion`, or a set
+            of (start, end) ranges to censor (*exclude*).
+        """
+
+        if  self.model.vectorizer is not None \
+        and label_name not in self.model.vectorizer.label_names:
+            logger.warn(
+                "Ignoring unrecognized label name '{}' in the wavelength "
+                "censoring description".format(label_name))
+
+        value = np.atleast_2d(value)
+        if value.size == self.model.dispersion.size:
+            # A mask was given. Ensure it is boolean.
+            if not np.all(np.isfinite(value)):
+                raise ValueError("non-finite values given as a boolean mask")
+
+            value = value.flatten().astype(bool)
+
+        elif len(value.shape) == 2 and value.shape[1] == 2:
+            # Ranges specified. Generate boolean mask.
+            mask = np.zeros(self.model.dispersion.size, dtype=bool)
+            for start, end in value:
+
+                # Allow 'None' to automatically specify edges.
+                start = start or -np.inf
+                end = end or +np.inf
+
+                censored = (end >= self.model.dispersion) \
+                         * (self.model.dispersion >= start)
+                mask[censored] = True
+
+            value = mask
+
+        else:
[…]

### 2016-10-16 AnniesLasso_2/continuum.py

@@ -1,0 +1,158 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+Continuum-normalization.
+"""
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = ["fit", "fit_sines_and_cosines"]
+
+import numpy as np
+
+
+def _continuum_design_matrix(dispersion, L, order):
+    """
+    Build a design matrix for the continuum determination, using sines and
+    cosines.
+
+    :param dispersion:
+        An array of dispersion points.
+
+    :param L:
+        The length-scale for the sine and cosine functions.
+
+    :param order:
+        The number of sines and cosines to use in the fit.
+    """
+
+    L, dispersion = float(L), np.array(dispersion)
+    scale = 2 * (np.pi / L)
+    return np.vstack([
+        np.ones_like(dispersion).reshape((1, -1)), 
+        np.array([
+            [np.cos(o * scale * dispersion), np.sin(o * scale * dispersion)] \
+            for o in range(1, order + 1)]).reshape((2 * order, dispersion.size))
+        ])
+
+
+def fit_sines_and_cosines(dispersion, flux, ivar, continuum_pixels,
+    L=1400, order=3, regions=None, fill_value=1.0, full_output=False, **kwargs):
+    """
+    Fit the flux values of pre-defined continuum pixels using a sum of sine and
+    cosine functions.
+
+    :param dispersion:
+        The dispersion values.
+
+    :param flux:
+        The flux values for all pixels, as they correspond to the `dispersion`
+        array.
+
+    :param ivar:
+        The inverse variances for all pixels, as they correspond to the
+        `dispersion` array.
+
+    :param continuum_pixels:
+        A mask that selects pixels that should be considered as 'continuum'.
+
+    :param L: [optional]
+        The length scale for the sines and cosines.
+
+    :param order: [optional]
+        The number of sine/cosine functions to use in the fit.
+
+    :param regions: [optional]
+        Specify sections of the spectra that should be fitted separately in each
+        star. This may be due to gaps between CCDs, or some other physically-
+        motivated reason. These values should be specified in the same units as
+        the `dispersion`, and should be given as a list of `[(start, end), ...]`
+        values. For example, APOGEE spectra have gaps near the following
+        wavelengths which could be used as `regions`:
+
[…]

### 2016-10-16 AnniesLasso_2/diagnostics.py

@@ -1,0 +1,585 @@
+
+import numpy as np
+import matplotlib
+#matplotlib.rcParams["text.usetex"] = True
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MaxNLocator
+
+from . import L1RegularizedCannonModel
+from . import model, regularized
+
+def _get_pixel_mask(model, wavelengths=None, pixels=None):
+
+    if pixels is None:
+        pixels = []
+
+    if wavelengths is not None:
+        pixels.extend(np.searchsorted(model.dispersion, wavelengths))
+
+    pixel_mask = np.zeros_like(model.dispersion, dtype=bool)
+    for pixel in pixels:
+        pixel_mask[pixel] = True
+
+    return pixels, pixel_mask
+
+
+def compare_derivatives(models, model_names, latex_labels=None, **kwargs):
+    """
+    Compare the model derivatives (theta coefficients) for multiple models.
+    """
+
+    if not all(m.is_trained for m in models):
+        raise ValueError("not all models are trained")
+
+
+    axes_per_page = 10.
+    N_axes = 1.0 + len(models[0].vectorizer.terms) 
+    N_figs = int(np.ceil(N_axes/axes_per_page))
+
+    figs = []
+    for i in range(N_figs):
+        fig, _ = plt.subplots(min([axes_per_page, N_axes]))
+        figs.append(fig)
+
+    axes = np.hstack([fig.axes for fig in figs])
+    colours = ("#4C72B0", "#55A868", "#C44E52", "#8172B2", "#64B5CD")
+    
+    if latex_labels is not None:
+        label_names = models[0].vectorizer.get_human_readable_label_vector(
+            latex_labels, mul=kwargs.pop("mul", "\cdot"))
+    else:
+        label_names = models[0].vectorizer.get_human_readable_label_vector()
+
+
+    for i, ax in enumerate(axes):
+        
+        if 1 + i == N_axes:
+            # Scatter plot
+            break
+
+        for m, name in zip(models, model_names):
+            ax.plot(m.dispersion, m.theta[:, i], c=c, lw=2, label=name)
+
+        ax.set_xlim(m.dispersion[0], m.dispersion[-1])
+        if ax.is_last_row():
+            ax.set_xlabel("Lambda")
+
+        else:
+            ax.set_xticklabels([])
+
+        ax.set_ylabel(r"$\theta_{{{0}}}$".format(i))
+        ax_twin = ax.twinx()
[…]

### 2016-10-16 AnniesLasso_2/local_cannon.py

@@ -1,0 +1,507 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+A basic command line interface for a local version of The Cannon.
+"""
+
+import argparse
+import logging
+import multiprocessing as mp
+import numpy as np
+import os
+from random import shuffle
+from six.moves import cPickle as pickle
+from six import string_types
+
+from astropy.table import Table
+
+import AnniesLasso_2 as tc
+
+
+logger = logging.getLogger("AnniesLasso_2")
+
+_DEFAULT_FILENAME_COLUMN = "FILENAME"
+_DEFAULT_OUTPUT_SUFFIX = "result"
+
+
+def get_neighbours(labelled_set, star, label_names, K, exclude=None):
+    """
+    Return `K` indices of the nearest neighbours of `star` in the `labelled_set`.
+
+    :param labelled_set:
+        A table containing high fidelity labels for all stars.
+
+    :param star:
+        The star to determine neighbours to.
+
+    :param label_names:
+        A list of label names that will be used in the model, and which will be
+        used to gauge proximity in label space.
+
+    :param K:
+        The number of neighbours to return.
+
+    :param exclude: [optional]
+        A list-like of indices to exclude from the list of neighbouring indices.
+        For example, this may be the index that corresponds to `star`.
+
+    :returns:
+        An array of indices of length `K`.
+    """
+
+    # Pivot and rescale the labels.
+    D = np.sum(np.abs([(labelled_set[_] - star[_])/np.ptp(labelled_set[_]) \
+        for _ in label_names]), axis=0)
+
+    assert np.all(np.isfinite(D))
+
+    if exclude is not None:
+        if isinstance(exclude, int): exclude = [exclude]
+        max_D = 1 + np.max(D)
+        for index in exclude:
+            D[index] = max_D
+
+    return np.argsort(D)[:K]
+
+
+def loocv(labelled_set, label_names, K=None, model_order=1, 
+    filename_column=None, output_suffix=None, overwrite=False, **kwargs):
+    """
+    Perform leave-one-out cross-validation using a local Cannon model at every
+    point in the labelled set.
+
+    :param labelled_set:
+        The path of a table containing labels of stars, and a column including
+        the path of a spectrum for that star.
+
+    :param label_names:
+        A list of label names to include in the model.
+
+    :param K: [optional]
+        The number of K nearby training set stars to train a model with. If
+        `None` is specified, then `K = 2 * N_labels`
+
[…]

### 2016-10-16 AnniesLasso_2/model.py

@@ -1,0 +1,819 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+An abstract model class for The Cannon.
+"""
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = [
+    "BaseCannonModel", "requires_training_wheels", "requires_model_description"]
+
+
+import logging
+import numpy as np
+from collections import OrderedDict
+from copy import deepcopy
+from datetime import datetime
+from os import path
+from six.moves import cPickle as pickle
+from six import string_types
+from scipy.spatial import Delaunay
+
+from .vectorizer.base import BaseVectorizer
+from . import (censoring, utils, __version__ as code_version)
+
+logger = logging.getLogger(__name__)
+
+
+def requires_training_wheels(method):
+    """
+    A decorator for model methods that require training before being run.
+
+    :param method:
+        A method belonging to a sub-class of BaseCannonModel.
+    """
+    def wrapper(model, *args, **kwargs):
+        if not model.is_trained:
+            raise TypeError("the model needs training first")
+        return method(model, *args, **kwargs)
+    return wrapper
+
+
+def requires_model_description(*args):
+    """
+    A decorator for model methods that require some part of a model description.
+
+    :param args: [optional]
+        If specified, only these descriptors will be required. If set as None,
+        then all model descriptors will be required.
+    """
+
+    def decorator(method):
+        """
+        A decorator for model methods that require a full model description.
+
+        :param method:
+            A method belonging to a sub-class of BaseCannonModel.
+        """
+    
+        def wrapper(model, *args, **kwargs):
+            for attr in descriptors or model._descriptive_attributes:
+                if getattr(model, attr) is None:
+                    raise TypeError("the model requires a {} term".format(
+                        attr.lstrip("_")))
+            return method(model, *args, **kwargs)
+        return wrapper
+
+    # This decorator can have optional descriptors.
+    descriptors = None if len(args) == 1 and callable(args[0]) else args[1:]
+    if descriptors is None:
+        return decorator(args[0])
+    return decorator
+
+
+
+class BaseCannonModel(object):
+    """
+    An abstract Cannon model object that implements convenience functions.
+
+    :param labelled_set:
+        A set of labelled objects. The most common input form is a table with
+        columns as labels, and stars/objects as rows.
+
+    :type labelled_set:
[…]

### 2016-10-16 AnniesLasso_2/regularized.py

@@ -1,0 +1,326 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+A regularized (compressed sensing) version of The Cannon.
+"""
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = ["L1RegularizedCannonModel"]
+
+import logging
+import numpy as np
+import scipy.optimize as op
+
+from . import (cannon, utils)
+
+logger = logging.getLogger(__name__)
+
+
+class L1RegularizedCannonModel(cannon.CannonModel):
+    """
+    A L1-regularized edition of The Cannon model for the estimation of arbitrary
+    stellar labels.
+
+    :param labelled_set:
+        A set of labelled objects. The most common input form is a table with
+        columns as labels, and stars/objects as rows.
+
+    :type labelled_set:
+        :class:`~astropy.table.Table`, numpy structured array
+
+    :param normalized_flux:
+        An array of normalized fluxes for stars in the labelled set, given as
+        shape `(num_stars, num_pixels)`. The `num_stars` should match the number
+        of rows in `labelled_set`.
+
+    :type normalized_flux:
+        :class:`np.ndarray`
+
+    :param normalized_ivar:
+        An array of inverse variances on the normalized fluxes for stars in the
+        labelled set. The shape of the `normalized_ivar` array should match that
+        of `normalized_flux`.
+
+    :type normalized_ivar:
+        :class:`np.ndarray`
+
+    :param dispersion: [optional]
+        The dispersion values corresponding to the given pixels. If provided, 
+        this should have length `num_pixels`.
+
+    :param threads: [optional]
+        Specify the number of parallel threads to use. If `threads > 1`, the
+        training and prediction phases will be automagically parallelised.
+
+    :param pool: [optional]
+        Specify an optional multiprocessing pool to map jobs onto.
+        This argument is only used if specified and if `threads > 1`.
+    """
+
+    _descriptive_attributes \
+        = ["_dispersion", "_vectorizer", "_censors", "_regularization"]
+        
+    def __init__(self, *args, **kwargs):
+        super(L1RegularizedCannonModel, self).__init__(*args, **kwargs)
+
+
+    @property
+    def regularization(self):
+        """
+        Return the regularization term for this model.
+        """
+        return self._regularization
+
+
+    @regularization.setter
[…]

### 2016-10-16 AnniesLasso_2/tests/test_base_vectorizer.py

@@ -1,0 +1,147 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+Unit tests for the base vectorizer.
+"""
+
+import numpy as np
+import os
+import tempfile
+import unittest
+from six.moves import cPickle as pickle
+
+from AnniesLasso_2.vectorizer import base
+
+
+class TestBaseVectorizerInitialization(unittest.TestCase):
+
+    label_names = ("a", "b", "c", "d", "e")
+
+    def test_incompatible_scale_length(self):
+        with self.assertRaises(ValueError):
+            base.BaseVectorizer(self.label_names,
+                np.random.uniform(size=len(self.label_names)),
+                np.random.uniform(size=len(self.label_names) + 1),
+                [])
+
+    def test_incompatible_fiducial_length_1(self):
+        with self.assertRaises(ValueError):
+            base.BaseVectorizer(self.label_names,
+                np.random.uniform(size=len(self.label_names) - 1),
+                np.random.uniform(size=len(self.label_names)),
+                [])
+
+
+    def test_non_finite_fiducials(self):
+        with self.assertRaises(ValueError):
+            base.BaseVectorizer(self.label_names,
+                ([0] * (len(self.label_names) - 1)) + [np.nan],
+                np.random.uniform(size=len(self.label_names)),
+                [])
+
+
+    def test_infinite_fiducials(self):
+        with self.assertRaises(ValueError):
+            base.BaseVectorizer(self.label_names,
+                ([0] * (len(self.label_names) - 1)) + [+np.inf],
+                np.random.uniform(size=len(self.label_names)),
+                [])
+
+        with self.assertRaises(ValueError):
+            base.BaseVectorizer(self.label_names,
+                ([0] * (len(self.label_names) - 1)) + [-np.inf],
+                np.random.uniform(size=len(self.label_names)),
+                [])
+
+
+    def test_non_finite_scales(self):
+        with self.assertRaises(ValueError):
+            base.BaseVectorizer(self.label_names,
+                np.random.uniform(size=len(self.label_names)),
+                ([0] * (len(self.label_names) - 1)) + [np.nan],
+                [])
+
+
+    def test_infinite_scales(self):
+        with self.assertRaises(ValueError):
+            base.BaseVectorizer(self.label_names,
+                np.random.uniform(size=len(self.label_names)),
+                ([0] * (len(self.label_names) - 1)) + [+np.inf],
+                [])
+
[…]

### 2016-10-16 AnniesLasso_2/tests/test_censoring.py

@@ -1,0 +1,134 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+Unit tests for the censoring dictionary.
+"""
+
+import numpy as np
+import unittest
+from collections import namedtuple
+
+from AnniesLasso_2.censoring import CensorsDict
+
+
+class fake_model(object):
+
+    def __init__(self, N=1000, label_names="abcde"):
+
+        self.dispersion = np.arange(N)
+        v = namedtuple('foo', ['label_names'])
+        self.vectorizer = v(label_names=label_names)
+        self.censors = CensorsDict(self)
+
+
+class TestCensorsDict(unittest.TestCase):
+
+    def test_boolean_mask(self):
+
+        N = 1000
+        f = fake_model(N, label_names=["a"])
+
+        mask = np.round(np.random.uniform(size=N)).reshape(-1, 5)
+        f.censors["a"] = mask
+        
+        self.assertTrue(np.all(f.censors["a"] == mask.flatten().astype(bool)))
+
+
+    def test_non_finite_boolean_masks(self):
+
+        N = 1000
+        f = fake_model(N, label_names=["a"])
+
+        mask = np.round(np.random.uniform(size=N)).reshape(-1, 5)
+        
+        bad = (-np.inf, +np.inf, np.nan)
+        for each in bad:
+            mask[100, 2] = each
+            with self.assertRaises(ValueError):
+                f.censors["a"] = mask
+
+
+    def test_incompatible_mask(self):
+
+        N = 1000
+        f = fake_model(N, label_names=["a"])
+
+        mask = np.round(np.random.uniform(size=N/2))
+        with self.assertRaises(ValueError):
+            f.censors["a"] = mask
+
+
+    def test_range_mask(self):
+
+        f = fake_model()
+
+        censored_ranges = [
+            [100, 200],
+            [300, 400],
+            [500, 600],
+            [700, 800],
+            [900, 1000]
+        ]
+
+        f.censors["a"] = censored_ranges
+
+        # The first pixels should not be censored.
+        self.assertFalse(f.censors["a"][0])
+
+        # The mid-pixel between each range should be censored.
+        for start, end in censored_ranges:
+            mid = start + (end - start)/2
+            index = f.dispersion.searchsorted(mid)
+            self.assertTrue(f.censors["a"][index])
+
+
+    def test_range_mask_with_non_finites(self):
+    
+        f = fake_model()
+
+        censored_ranges = [
+            [-np.inf, 200],
[…]

### 2016-10-16 AnniesLasso_2/tests/test_utils.py

@@ -1,0 +1,20 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+Unit tests for general utility functions.
+"""
+
+import unittest
+from AnniesLasso_2 import utils
+
+
+class TestShortHash(unittest.TestCase):
+
+    def test_different(self):
+        self.assertNotEqual(utils.short_hash(True), utils.short_hash(False))
+
+    def test_hashing(self):
+        # So that it does not change with time and break old hashes.
+        self.assertEqual("7fc56270e79d5ed678fe0d61f8370cf623e75af33a3ea00cfc",
+            utils.short_hash("ABCDE"))

### 2016-10-16 AnniesLasso_2/utils.py

@@ -1,0 +1,259 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+General utility functions.
+"""
+
+__all__ = ["InterruptiblePool", "short_hash", "wrapper"]
+
+import functools
+import logging
+import os
+import signal
+import sys
+from six import string_types
+from six.moves import cPickle as pickle
+from tempfile import mkstemp
+from time import time
+from collections import Iterable
+from hashlib import md5
+from multiprocessing.pool import Pool
+from multiprocessing import Lock, TimeoutError, Value
+
+logger = logging.getLogger(__name__)
+
+
+# Initialize global counter for incrementing between threads.
+_counter = Value('i', 0)
+_counter_lock = Lock()
+
+def _init_pool(args):
+    global _counter
+    _counter = args
+
+class wrapper(object):
+    """
+    A generic wrapper with a progressbar, which can be used either in serial or
+    in parallel.
+
+    :param f:
+        The function to apply.
+
+    :param args:
+        Additional arguments to supply to the function `f`.
+
+    :param kwds:
+        Keyword arguments to supply to the function `f`.
+
+    :param N:
+        The number of items that will be iterated over.
+
+    :param message: [optional]
+        An information message to log before showing the progressbar.
+
+    :param size: [optional]
+        The width of the progressbar in characters.
+    """
+    def __init__(self, f, args, kwds, N, message=None, size=100):
+        self.f = f
+        self.args = list(args if args is not None else [])
+        self.kwds = kwds if kwds is not None else {}
+        self._init_progressbar(N, message)
+        
+
+    def _init_progressbar(self, N, message=None):
+        """
+        Initialise a progressbar.
+
+        :param N:
+            The number of items that will be iterated over.
+        
+        :param message: [optional]
+            An information message to log before showing the progressbar.
+        """
+        self.N = N
+        self.t_init = time()
+        self.message = message
+        if 0 >= self.N:
+            return None
+
+        if message is not None:
+            logger.info(message.rstrip())
+        
+        sys.stdout.flush()
+        with _counter_lock:
+            _counter.value = 0
+            
+
+    def _update_progressbar(self):
+        """
+        Increment the progressbar by one iteration.
+        """
+        if 0 >= self.N:
+            return None
+
+        global _counter, _counter_lock
+        with _counter_lock:
+            _counter.value += 1
+
+        index = _counter.value
+        
[…]

### 2016-10-16 AnniesLasso_2/vectorizer/base.py

@@ -1,0 +1,211 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+A base vectorizer for use in The Cannon.
+"""
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = ["BaseVectorizer"]
+
+import numpy as np
+
+
+class BaseVectorizer(object):
+    """
+    A vectorizer class that models spectral fluxes, allows for offsets and
+    scaling of different labels, and computes the derivatives for the underlying
+    spectral model.
+
+    :param label_names:
+        The names of the labels that will be used by the vectorizer.
+
+    :param fiducials:
+        The fiducial offsets for the `label_names` provided.
+
+    :param scales:
+        The scaling values for the `label_names` provided.
+
+    :param terms:
+        The terms that constitute the label vector.
+    """
+
+    def __init__(self, label_names, fiducials, scales, terms):
+
+        N = len(label_names)        
+        fiducials = np.array(fiducials)
+        scales = np.array(scales)
+
+        if N != fiducials.size:
+            raise ValueError("the number of fiducials does not match "
+                             "the number of label_names ({0} != {1})".format(
+                                N, fiducials.size))
+
+        if N != scales.size:
+            raise ValueError("the number of fiducials does not match "
+                             "the number of scales {0} != {1}".format(
+                                N, scales.size))
+
+        # Fiducials can be any finite value, but scales must be finite values
+        # and be positive.
+        if not all(np.isfinite(fiducials)):
+            raise ValueError("fiducials must be finite values")
+
+        if not all(np.isfinite(scales)) or not all(scales > 0):
+            raise ValueError("scales must be finite and positive values")
+
+        # Set the state of the vectorizer.
+        self.__setstate__((label_names, fiducials, scales, terms))
+        return None
+
+
+    # These can be over-written by sub-classes, but it is useful to have some
+    # basic information if the sub-classes do not overwrite it.
+    def __str__(self):
+        return "<{module}.{name} object consisting of {K} labels and {D} terms>"\
+            .format(module=self.__module__, name=type(self).__name__,
+                K=len(self.label_names), D=len(self.terms))
+
+    def __repr__(self):
+        return "<{0}.{1} object at {2}>".format(
+            self.__module__, type(self).__name__, hex(id(self)))
+
+
+    # I/O (Serializable) functionality.
+    def __getstate__(self):
+        """
[…]

### 2016-10-16 AnniesLasso_2/vectorizer/polynomial.py

@@ -1,0 +1,443 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+A polynomial vectorizer for use in The Cannon.
+"""
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = ["BasePolynomialVectorizer", "NormalizedPolynomialVectorizer",
+    "terminator", "get_label_names"]
+
+import numpy as np
+from collections import (Counter, OrderedDict)
+from itertools import combinations_with_replacement
+from six import string_types
+
+from AnniesLasso_2.vectorizer.base import BaseVectorizer
+
+
+class BasePolynomialVectorizer(BaseVectorizer):
+    """
+    A base vectorizer class that models spectral fluxes as a linear combination
+    of label terms in a polynomial fashion.
+
+    :param label_names:
+        The names of the labels that will be used by the vectorizer.
+
+    :param fiducials:
+        The fiducial offsets for the labels.
+
+    :param scales:
+        The scaling values for the labels.
+
+    :param terms:
+        The terms that constitute the label vector.
+    """
+
+    def __init__(self, *args, **kwargs):
+        super(BasePolynomialVectorizer, self).__init__(*args, **kwargs)
+
+        # Check that the terms are OK, and parse them into a useful format.
+        self._terms = parse_label_vector_description(
+            self._terms, columns=self.label_names)
+        return None
+
+
+    def get_label_vector(self, labels):
+        """
+        Return the values of the label vector, given the labels.
+
+        :param labels:
+            The labels to calculate the label vector for. This can be a 
+            one-dimensional vector of `K` labels (using the same order and
+            length provided by self.label_names), or a two-dimensional array of
+            `N` by `K` values. The returning array will be of shape `(N, D)`,
+            where `D` is the number of terms in the label vector description.
+        """
+
+        labels = np.atleast_2d(labels)
+        if labels.ndim > 2:
+            raise ValueError("labels must be a 1-d or 2-d array")
+
+        # Offset and scale the labels before building the vector.
+        scaled_labels = self._transform(labels)
+
+        columns = [np.ones(labels.shape[0], dtype=float)]
+        for term in self.terms:
+            column = 1. # This works; don't use np.multiply/np.product.
+            for index, order in term:
+                column *= scaled_labels[:, index]**order
+            columns.append(column)
+        return np.vstack(columns).T
+
+
+    def get_label_vector_derivative(self, labels):
+        """
[…]

### 2016-10-16 AnniesLasso_2/vectorizer/tests/test_polynomial.py

@@ -1,0 +1,223 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+Unit tests for the polynomial vectorizer.
+"""
+
+import unittest
+from AnniesLasso_2.vectorizer import polynomial
+
+class TestIsStructuredLabelVector(unittest.TestCase):
+
+    def test_fail_input_string(self):
+        self.assertFalse(polynomial._is_structured_label_vector(""))
+
+    def test_fail_input_none(self):
+        self.assertFalse(polynomial._is_structured_label_vector(None))
+
+    def test_fail_input_bool(self):
+        self.assertFalse(polynomial._is_structured_label_vector(True))
+        self.assertFalse(polynomial._is_structured_label_vector(False))
+
+    def test_fail_input_int(self):
+        self.assertFalse(polynomial._is_structured_label_vector(1))
+
+    def test_fail_input_float(self):
+        self.assertFalse(polynomial._is_structured_label_vector(0.0))
+        
+    def test_fail_input_empty_iterables(self):
+        self.assertFalse(polynomial._is_structured_label_vector(()))
+        self.assertFalse(polynomial._is_structured_label_vector(set()))
+        self.assertFalse(polynomial._is_structured_label_vector([]))
+        self.assertFalse(polynomial._is_structured_label_vector({}))
+
+    def test_fail_input_nested_empty_iterables(self):
+        self.assertFalse(polynomial._is_structured_label_vector([{}]))
+        self.assertFalse(polynomial._is_structured_label_vector([()]))
+        self.assertFalse(polynomial._is_structured_label_vector([[()]]))
+
+    def test_failed_input_term_lengths(self):
+        self.assertFalse(
+            polynomial._is_structured_label_vector([[("A", 0, 1)]]))
+        self.assertFalse(polynomial._is_structured_label_vector(
+            [[("A", 1)], [("B", 0, 1)]]))
+    
+    def test_valid_input_term_int_power(self):
+        self.assertTrue(polynomial._is_structured_label_vector([[("A", 1)]]))
+
+    def test_valid_input_term_float_power(self):
+        self.assertTrue(polynomial._is_structured_label_vector([[("A", 1.0)]]))
+
+    def test_valid_input_term_form(self):
+        self.assertFalse(polynomial._is_structured_label_vector([[(1, "A")]]))
+
+
+
[…]

### 2016-10-16 example.py

@@ -1,0 +1,147 @@
+
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import pickle
+
+import AnniesLasso_2 as tc
+
+
+training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
+training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
+
+
+training_set = Table.read("reference_labels.csv")
+
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+N = len(training_set)
+keep = np.ones(N, dtype=bool)
+
+training_set_flux = []
+training_set_ivar = []
+training_set_error = []
+for i, row in enumerate(training_set):
+
+    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
+    if not os.path.exists(image_path):
+        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+        keep[i] = False
+        continue
+
+    print("{}/{}: {}".format(i + 1, N, image_path))
+
+    image = fits.open(image_path)
+
+    flux = image[1].data
+    flux_err = image[2].data
+
+    badpix = get_pixmask(flux, flux_err)
+    ivar = 1.0/flux_err**2
+    error = flux_err
+    # badpix is a array and the length is 8575
+    flux[badpix] = 1.0
+    ivar[badpix] = 0.0
+
+    training_set_flux.append(flux)
+    training_set_ivar.append(ivar)
+    training_set_error.append(error)
+
+training_set_flux = np.array(training_set_flux)
+training_set_ivar = np.array(training_set_ivar)
+training_set_error = np.array(training_set_error)
+
+# save training_set_flux, ivar and error
+"""
+output = open('training_set_flux.pkl', 'wb')
+pickle.dump(training_set_flux, output)
+output.close()
+
+output = open('training_set_ivar.pkl', 'wb')
+pickle.dump(training_set_ivar, output)
+output.close()
+
[…]

### 2016-10-16 fitting_spectrum_optimized_v6.py

@@ -1,283 +1,0 @@
-# In this version, we choose another objective function and improve the fitting by using a better optimization method.
-
-
-
-# import
-import matplotlib
-import scipy.optimize as optimization
-import numpy as np
-from astropy.table import Table
-import matplotlib.pyplot as plt
-import pickle
-import AnniesLasso as tc
-from scipy.stats import chisquare
-from numpy.linalg import inv
-
-#import the data
-
-training_set = Table.read("reference_labels.csv")
-
-pkl_file = open('training_set_flux.pkl', 'rb')
-training_set_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('training_set_ivar.pkl', 'rb')
-training_set_ivar = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('wl.pkl', 'rb')
-wl = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('training_set_error.pkl', 'rb')
-error = pickle.load(pkl_file)
-pkl_file.close()
-
-
-
-
-
-# train the model
-model = tc.L1RegularizedCannonModel(
-    training_set, training_set_flux, training_set_ivar,threads=8)
-
-model.s2 = 0
-model.regularization = 0
-model.vectorizer = tc.vectorizer.NormalizedPolynomialVectorizer(training_set,
-    tc.vectorizer.polynomial.terminator(("Teff_{corr}", "logg_{corr}", "[M/H]_{corr}"), 2))
-
-model.train()
-
-# obtain the spectrum data
-norm_tr_flux = training_set_flux
-
-inferred_labels = model.fit_labelled_set()
-v = model.vectorizer.get_label_vector(inferred_labels)
-inferred_flux = np.dot(v,model.theta.T)
-print(v.shape)
-
-
-
-# fit a b c for a single pixel/wave length
-
-# define a function for fitting
-def func(m, a, b, c):
-    (x,y,z) = m
-    return a * x + b * y + c * z
-
-# define the class for fitting spectrum by nearby spectrum
-class fit_neighborhood:
-
-    def __init__(self,n,i):
-        self.n = np.array(n)
-        self.i = np.array(i)
-
-
-    def fitting_spectrum_parameters(self,ivar):
-        nor = self.n
-        inf = self.i
-        n_pixel = nor[0, :].size
-        n_star = inf[:, 0].size
-        nor = norm_tr_flux
-        inf = inferred_flux
[…]

### 2016-10-21 paper/ms.tex
histogram_plot

@@
 The number of stellar and pixel each star are N and J.
-Here N=548 and J = 8575.
+Here N and J are the number of the stellar and the number of pixel each star.
 Write the objective function in the form of matrix can make it simpler.
@@
 
-By using (7) we can calculate a,b and c. b should be much bigger than both a and c. And a+b+c should be equal to 1.
-
-The result is \(a+b+c = 0.99990\).
-
-(a,b,c) = (-0.00215, 1.00462, -0.00258 ).
+By using (7) we can calculate a, b and c. b should be much bigger than both a and c. And a+b+c should be equal to 1.
 
@@
 
- Here a,b and c are the parameters obtained from spectrum optimization.
+ Here a,b and c are parameters obtained from spectrum optimization.
 Then we infer stellar labels by using $\theta_{j}^{opt}$ and generate optimized inferred labels.
@@
 
- Choose four stellar, which are not in the training set:
+ Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c.
+
+ The result is \(a+b+c = 0.999\).
+
+(a,b,c) = (0.078, 0.886, 0.035).
+
+The values of the objective function before and after are 177254 and 174031
+, which decreases by 2\%.
+
+The labels of the four stars are:
 
@@
  The red line "optimized" is \( y_{j,n}^{opt}\), which is generated by (3)
+
 \bigskip
@@
 Finally compare the chi-square for these four stars of the two methods:
- The optimized spectrum has a 1\% smaller chi-squared so our optimization works.
+The total chi-squared of the four stars becomes 2\% smaller, which means our method works.
 
  \subsection{\label{sec:level2}Experiment 2}
- Optimize $\theta_j$ and generate optimized inferred labels. Then plot the inferred labels and the optimized inferred labels.
+ Plot the parameters a, b and c vs the number of the star. 
+ \bigskip
+
+In experiment 1, we use only four stars to obtain parameters a, b and c and the result is pretty good.
+What if we optimize more stars?
+We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
+The number of stars is 639.
+But now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 639 objective functions.
+And there will be 639 sets of a, b and c.
+Then we can plot a histogram of a, b and c to see the distribution of their values.
 \bigskip
@@
 %\includegraphics[width=170mm]{figure_3.png}
- \centerline{Fig.3 Inferred labels and the reference labels}
+
 \bigskip
 
- Finally compare the chi-square.
+Also.
+We plot a, b, c against the mean fiber number, which is the average fiber number of the spectrum we optimize.
+In APOGEE DR 10, the fiber number is between 1 and 640.
+The parameters we use are from $figure_3$
 
-The chi-squared becomes 1\% bigger after the optimization. We need to do bigger optimization before inferring the labels!
+%\includegraphics[width=170mm]{figure_4.png}
+\bigskip
+
+This figure gives us information about the relation between parameters a, b, c and fiber number, which can be used to establish a data-driven spectrum calibration model.
 

### 2016-10-21 1020_normalize_flux_aspcap_v2.py

@@ -1,0 +1,224 @@
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib
+
+
+# function
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+# read data
+all_set = Table.read("/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/allStar-v304.fits")
+all_set_spectrum_dir = "/Volumes/data-2T/Data/APOGEE_DR10_ASPCAP/"
+
+# data
+all_set_flux = []
+all_set_ivar = []
+all_set_error = []
+test_labels_all = []
+fail = 0
+
+# choose some of them
+choose = []
+a=0
+for i in range(0,800):
+    a += np.random.randint(1,10)
+    choose.append(a)
+
+choose = np.array(choose)
+all_set = all_set[choose]
+
+
+# save the chosen star
+output = open('choose_500.pkl', 'wb')
+pickle.dump(choose, output)
+output.close()
+
+
+N = len(all_set)
+keep = np.ones(N, dtype=bool)
+tr_ID = []
+FiberID = []
+
+
+for i, row in enumerate(all_set):
+    try:
+        image_path = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_ASPCAP/aspcapStar-" + row["APOGEE_ID"] + ".fits"
+        # For apstar
+
+        image_path_2 = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_Apstar/apStar-s3-" + row["APOGEE_ID"] + ".fits"
+
+        if not os.path.exists(image_path):
+            print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+            keep[i] = False
+            continue
+
+        print("{}/{}: {}".format(i + 1, N, image_path))
+        # Let's only use two extension of the data
+
+        image = fits.open(image_path, ignore_missing_end=True)
+        dat = Table.read(image_path_2)
+
+        flux = image[1].data
[…]

### 2016-10-21 1020_opt_1percent.py

@@ -1,0 +1,179 @@
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib
+from astropy.io.fits import getdata
+
+import AnniesLasso_2 as tc
+
+
+training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
+training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
+
+
+training_set = Table.read("reference_labels.csv")
+
+
+
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+
+N = len(training_set)
+keep = np.ones(N, dtype=bool)
+
+training_set_flux = []
+training_set_ivar = []
+training_set_error = []
+for i, row in enumerate(training_set):
+
+    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
+
+    if not os.path.exists(image_path):
+        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+        keep[i] = False
+        continue
+
+    print("{}/{}: {}".format(i + 1, N, image_path))
+
+    image = fits.open(image_path)
+
+    flux = image[1].data
+    flux_err = image[2].data
+
+    badpix = get_pixmask(flux, flux_err)
+    ivar = 1.0/flux_err**2
+    error = flux_err
+    # badpix is a array and the length is 8575
+    flux[badpix] = 1.0
+    ivar[badpix] = 0.0
+
+    training_set_flux.append(flux)
+    training_set_ivar.append(ivar)
+    training_set_error.append(error)
+
+training_set_flux = np.array(training_set_flux)
+training_set_ivar = np.array(training_set_ivar)
+training_set_error = np.array(training_set_error)
+
+
+assert all(keep)
+
+# Construct model.
[…]

### 2016-10-21 AnniesLasso_2/cannon.py

@@ -208,11 +208,11 @@ class CannonModel(model.BaseCannonModel):
 
     # By Jason Cao
     # Input normalized_flux and normalized)ivar
-    # return optimized_flux and optimized_theta
-    def fitting_spectrum_parameters(self,normalized_flux,normalized_ivar):
+    # return optimized_flux, optimized_theta parameters and the variation of the parameters vs star
+    # All of them are np.array
+    def fitting_spectrum_parameters(self,normalized_flux,normalized_ivar,inf_flux):
         nor = normalized_flux
-        inferred_labels = self.fit_labelled_set()
-        inf = np.dot(self.theta, self.vectorizer(inferred_labels).T).T
+        inf = inf_flux
         ivar = normalized_ivar
         n_pixel = nor[0, :].size
         n_star = inf[:, 0].size
@@ -239,6 +239,7 @@ class CannonModel(model.BaseCannonModel):
 
         left = np.zeros((3,3))
         right = np.zeros(3)
+        parameters_long = np.array([0,1,0])
 
         for p in range(0, n_star):
 
@@ -262,11 +263,10 @@ class CannonModel(model.BaseCannonModel):
             left += np.dot(np.dot(a.T, c), a)
             right += np.dot(np.dot(a.T,c), y)
 
-
-        parameters = np.dot(inv(left),right)
+        parameters = np.dot(inv(left), right)
+        print(parameters[0],parameters[1],parameters[2],parameters[0]+parameters[1]+parameters[2])
 
         opt_flux = (parameters[0]*x_data+parameters[1]*y_data+parameters[2]*z_data)
-        print(parameters[0],parameters[1],parameters[2],parameters[0]+parameters[1]+parameters[2])
         #save the optimized spectrum
 
         # optimize theta
@@ -296,7 +296,75 @@ class CannonModel(model.BaseCannonModel):
         theta_opt = parameters[0] * theta_x + parameters[1] * theta_y + parameters[2] * theta_z
         print(parameters)
         theta_opt = theta_opt.T
-        return opt_flux,theta_opt
+        return opt_flux,theta_opt,parameters
+
+    # return the parameters of each star.
+    def fitting_spectrum_parameters_single(self,normalized_flux,normalized_ivar,inf_flux):
+        nor = normalized_flux
+        inf = inf_flux
+        ivar = normalized_ivar
+        n_pixel = nor[0, :].size
+        n_star = inf[:, 0].size
[…]

### 2016-10-26 AnniesLasso_2/cannon.py
bug fix

@@ -239,7 +239,7 @@ class CannonModel(model.BaseCannonModel):
 
         left = np.zeros((3,3))
         right = np.zeros(3)
-        parameters_long = np.array([0,1,0])
+
 
         for p in range(0, n_star):
 
@@ -299,6 +299,11 @@ class CannonModel(model.BaseCannonModel):
         return opt_flux,theta_opt,parameters
 
     # return the parameters of each star.
+    # Now the uncertainty of parameters is also calculated
+    # The structure of the uncertainty is each row is aa,ab,ac ba....
+    # so the dimension is 3*3*N, which is a 3 dimension array
+    # use self.uncertainty to store
+
     def fitting_spectrum_parameters_single(self,normalized_flux,normalized_ivar,inf_flux):
         nor = normalized_flux
         inf = inf_flux
@@ -326,10 +331,12 @@ class CannonModel(model.BaseCannonModel):
         # fit
         # It's not good. let's do it one star each time.
 
+        left = np.zeros((3,3))
+        right = np.zeros(3)
+        un = np.zeros((3,3))
+        parameters=np.array([0,1,0])
+        opt_flux = np.ones(n_pixel)
 
-
-        parameters = []
-        opt_flux = []
 
         for p in range(0, n_star):
 
@@ -350,20 +357,57 @@ class CannonModel(model.BaseCannonModel):
 
             y = nor_p.ravel()
             a = np.c_[np.c_[x_data_p.ravel(), y_data_p.ravel()], z_data_p.ravel()]
-            left  = np.dot(np.dot(a.T, c), a)
+
+            left = np.dot(np.dot(a.T, c), a)
             right = np.dot(np.dot(a.T,c), y)
-            parameters_p = np.dot(inv(left), right)
-            print(parameters_p[0], parameters_p[1], parameters_p[2], parameters_p[0] + parameters_p[1] + parameters_p[2])
 
-            opt_flux_p = (parameters_p[0] * x_data + parameters_p[1] * y_data + parameters_p[2] * z_data)
+            un_p = inv(left)
 
-            parameters.append(parameters_p)
-            opt_flux.append(opt_flux_p)
+            parameters_p =np.dot(inv(left), right)
 
-        parameters = np.array(parameters)
-        opt_flux = np.array(opt_flux)
+            opt_flux = np.vstack((opt_flux,parameters_p[0]*x_data_p+parameters_p[1]*y_data_p+parameters_p[2]*z_data_p))
[…]

### 2016-10-26 paper/ms.tex
Add delta-chi-squared

@@
 
+In our experiment except calculating $\theta_{j}$, we calculate a, b and c independently for each star, which means N=1 in formula(4)(5)(6)(7).
+
 %If the optimization works, we will optimized \(\theta_{j}\) besides a, b and c, which will come soon.
@@
 
- Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c.
-
- The result is \(a+b+c = 0.999\).
-
-(a,b,c) = (0.078, 0.886, 0.035).
-
-The values of the objective function before and after are 177254 and 174031
-, which decreases by 2\%.
+ Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c for each stars.
 
@@
  Star D  $T_{eff} =5003$  log g =2.8 $\left[Fe/h\right] =-0.71$
+
+\begin{table}[ht]
+\caption{Fitting results for the four stars}
+\centering
+\begin{tabular}{c c c c c}
+\hline\hline
+Star Name & a & b & c & a+b+c \\ [0.5ex] % inserts table %heading
+\hline
+Star A & 0.121 & 0.824 & 0.052 & 0.998 \\
+Star B & 0.176 & 0.541 &  0.278 & 0.995 \\
+Star C & 0.003 & 1.004 &  -0.007 & 1.000 \\
+Star D & -0.009  & 1.029 & -0.020 & 1.000 \\ [1ex]
+\hline
+\end{tabular}
+\label{table:nonlin}
+\end{table}
 
@@
 %\includegraphics[width=170mm]{figure_3.png}
+\bigskip
+
+\centerline{Fig.3 Histogram for  a, b and c}
 
@@
 
+\centerline{Fig.4 a,b,c vs Mean Fiber Number}
+\bigskip
+
 This figure gives us information about the relation between parameters a, b, c and fiber number, which can be used to establish a data-driven spectrum calibration model.
+\bigskip
+
+We also plot delta-chi-squared vs Mean Fiber number, where delta-chi-squared is the difference between the chi-squared of the spectrum before our optimization and after. It should be bigger than 0.
+\bigskip
+
+%\includegraphics[width=170mm]{figure_5.png}
+\bigskip
+
+\centerline{Fig.5 Delta-chi-squared vs Mean Fiber Number}
+\bigskip
 

### 2016-10-26 AnniesLasso_2/cannon.py

@@ -207,102 +207,12 @@ class CannonModel(model.BaseCannonModel):
     @model.requires_training_wheels
 
     # By Jason Cao
-    # Input normalized_flux and normalized)ivar
-    # return optimized_flux, optimized_theta parameters and the variation of the parameters vs star
-    # All of them are np.array
-    def fitting_spectrum_parameters(self,normalized_flux,normalized_ivar,inf_flux):
-        nor = normalized_flux
-        inf = inf_flux
-        ivar = normalized_ivar
-        n_pixel = nor[0, :].size
-        n_star = inf[:, 0].size
-        one = np.ones(n_star)
-
-        for pixel in range(0, n_pixel):
-            print("Building matrix",pixel,"{:.2f}%".format(pixel/n_pixel*100))
-            if pixel ==0 :
-                x_data = one
-                y_data = inf[:,pixel]
-                z_data = inf[:,pixel+1]
-
-            elif pixel>0 and pixel < n_pixel-1:
-                x_data = np.c_[x_data,inf[:,pixel-1]]
-                y_data = np.c_[y_data,inf[:,pixel]]
-                z_data = np.c_[z_data,inf[:,pixel+1]]
-
-            elif pixel == n_pixel-1:
-                x_data = np.c_[x_data, inf[:, pixel - 1]]
-                y_data = np.c_[y_data, inf[:, pixel]]
-                z_data = np.c_[z_data, one]
-        # fit
-        # It's not good. let's do it one star each time.
-
-        left = np.zeros((3,3))
-        right = np.zeros(3)
-
-
-        for p in range(0, n_star):
-
-            x_data_p = x_data[p, :]
-            y_data_p = y_data[p, :]
-            z_data_p = z_data[p, :]
-            nor_p = nor[p, :]
-            ivar_p = ivar[p, :]
-
-            # construct
-            ivar_r = ivar_p.ravel()
-            ni = len(ivar_r)
-            print("calculating parameters",p,"{:.2f}%".format(p/n_star*100))
-            c = np.zeros((ni, ni))
-
-            for i in range(0, ni):
-                c[i, i] = ivar_r[i]
-
-            y = nor_p.ravel()
-            a = np.c_[np.c_[x_data_p.ravel(), y_data_p.ravel()], z_data_p.ravel()]
-            left += np.dot(np.dot(a.T, c), a)
-            right += np.dot(np.dot(a.T,c), y)
-
[…]

### 2016-11-06 paper/ms.tex
Analyse a, b and c

@@
 
-\title{Optimize the Cannon 2}
+\title{CannonRV: Measuring radial velocities with a data-driven spectral model}
 \author[1]{Jason Cao\thanks{jc6933@nyu.edu}}
 \author[2]{David W. hogg\thanks{david.hogg@nyu.edu}}
+\author[3]{Melissa Ness\thanks{ness@mpia-hd.mpg.de}}
 
@@
 Max-Planck-Institut fuer Astronomie }
+\affil[3]{
+Max-Planck-Institut Max-Planck-Institut fuer Astronomie 17, D-69117 Heidelberg, Germany
+}
 
@@
 The model we adopt
- \[y_{jn} = v(l_n) \cdot \theta_{j} + e_{jn} (1)\]
+
+\begin{equation}
+y_{jn} = v(l_n) \cdot \theta_{j} + e_{jn}
+\end{equation}
 
@@
 Infer spectrum by using:
- \[y_{jn}^{inf} = v(l_n^{inf}) \cdot \theta_{j}  (2)\]
+
+\begin{equation}
+y_{jn}^{inf} = v(l_n^{inf}) \cdot \theta_{j} 
+\end{equation}
 
@@
 The new spectrum, which is the optimized spectrum, is represented by:
-\[y_{j,n}^{opt}=a\cdot y_{j-1,n}^{inf}+b\cdot y_{j,n}^{inf}+c\cdot y_{j+1,n}^{inf}(3)\]
+
+\begin{equation}
+y_{j,n}^{opt}=a\cdot y_{j-1,n}^{inf}+b\cdot y_{j,n}^{inf}+c\cdot y_{j+1,n}^{inf}
+\end{equation}
 \bigskip
 
-We use the least chi-squared method. So our objective function is the chi-squared between the optimized spectrum and the spectrum data. 
+We use the least chi-squared method. So our objective function is the chi-squared between the optimized spectrum and the spectrum data. The objective function for star n is:
 \bigskip
 
-$F_{obj} (a,b,c)$= \[\sum_{n=1,j=1}^{n=N,j=J} {(y_{jn} - y_{jn}^{opt})^2 \over{\sigma_{jn}^2}} \]  (4)
-\bigskip
+\begin{equation}
+F^{obj}_n (a,b,c)= \sum_{j=1}^{j=J} {(y_{jn} - y_{jn}^{opt})^2 \over{\sigma_{jn}^2}}
+\end{equation}
 
@@
 Write the objective function in the form of matrix can make it simpler.
-So we introduce several matrix: Y, A, C and X, which are defined as followed:
+There will be N objective functions and N sets of a, b and c.
+So we introduce several matrix: $Y_n$, $A_n$, $C_n$ and $X_n$, which are defined as followed:
 
@@
 
-\[
-Y
-=
-\begin{bmatrix}
-    Y_1&Y_2 &\dots&Y_{N}\\
-
-\end{bmatrix}
-\]
-
-where
 \[
@@
 % A
-\[
-A
-=
-\begin{bmatrix}
-    A_1&A_2 &\dots&A_{N}\\
 
-\end{bmatrix}
-\]
-
-where
 \[
@@
 \[
-C
-=
-\begin{bmatrix}
-    C_1&C_2 &\dots&C_{N}\\
-
-\end{bmatrix}
-\]
-
-where
-\[
 C_n
@@
 
-\(X = 
+\begin{center}
+\(X_n = 
  \begin{bmatrix}
 
-    a\\
-    b \\
-    c \\
+    a_n\\
+    b_n \\
+    c_n \\
 
@@
 \)
-
-We cut matrix Y, A and C into N smaller matrix so the calculation speed is higher. 
-\bigskip
+\end{center}
 
 Now the objective function can be described as:
-$F_{obj} (a,b,c)$= \[\sum_{n=1}^{N} (Y_n-A_n X)^TC^{-1}(Y_n-A_n X) (5)\]  
-\bigskip
+
+\begin{equation}
+F^{obj}_n (a_n,b_n,c_n)= (Y_n-A_n X_n)^TC^{-1}(Y_n-A_n X_n)
+\end{equation}
 
@@
 
-J = $\partial F_{obj}\over \partial X$ \[=\sum_{n=1}^{n=N}2\cdot [(Y_n-A_nX)^TC^{-1}]\cdot (-A_n) (6)\]   
-\bigskip
+\begin{equation}
+J = {\partial F^{obj}_n\over \partial X_n } = 2\cdot [(Y_n-A_nX_n)^TC^{-1}]\cdot (-A_n)
+\end{equation}
 
@@
 
-\[X = [\sum_{n=1}^{n=N}A_n^TC_n^{-1}A]^{-1} \cdot [\sum_{n=1}^{n=N}A^TC_n^{-1}Y_n](7)\]
-\bigskip
+\begin{equation}
+X_n = [\sum_{n=1}^{n=N}A_n^TC_n^{-1}A]^{-1} \cdot [\sum_{n=1}^{n=N}A^TC_n^{-1}Y_n]
+\end{equation}
 
-By using (7) we can calculate a, b and c. b should be much bigger than both a and c. And a+b+c should be equal to 1.
+By using (7) we can calculate $a_n$, $b_n$ and $c_n$, which are parameters a, b and c for star n. 
+b should be much bigger than both a and c. And a+b+c should be equal to 1.
 
@@
 
-In our experiment except calculating $\theta_{j}$, we calculate a, b and c independently for each star, which means N=1 in formula(4)(5)(6)(7).
-
-%If the optimization works, we will optimized \(\theta_{j}\) besides a, b and c, which will come soon.
 %It works!
 
- \subsection{\label{sec:level2}Optimized $\theta_{j}$ and inferred labels}
- After optimizing the inferred spectrum, we can modify $\theta_{j}$ and get a better result.
-The method is to represent $\theta_j$ by using $\theta_{j-1}$ , $\theta_j$ and $\theta_{j+1}$.
-If $\theta_j$ is out of range, set it as zero.
-So the optimized $\theta$ is:
- \[\theta_{j}^{opt}=a\cdot \theta_{j-1}+b\cdot \theta_{j}+c\cdot \theta_{j+1}(8)\]
+\subsection{\label{sec:level2}Spectrum calibration}
+\bigskip
+After the optimization, we obtain many sets of a, b and c.
+In our theory b should be close to 1 and a, c is much smaller than b.
+But the fact is that sometimes b is close to -1.
+This is because of the spectral broadening in the measurement.
+The equipment is not perfect, so the resolution of the spectrum will become lower due to scattering, dispersion or other reasons.
+Then the spectrum will broaden and the real spectrum at pixel j is not what we obtain, it should be the spectrum at nearby pixels, which include pixel j-1 and j+1.
+Thus b will be close to -1 and at the same time a and c should be close to 1, which we will check in experiment 3.
 \bigskip
 
- Here a,b and c are parameters obtained from spectrum optimization.
-Then we infer stellar labels by using $\theta_{j}^{opt}$ and generate optimized inferred labels.
-The data we use is the training set, which includes 548 stellar with 8575 pixel each.
- Finally, compare the chi-squared to check whether the optimization works.
+Sometimes a or c will be close to 1.
+This is also because of the measurement.
+Even we ignore the spectral broadening, the measured spectrum may move one pixel left or one pixel right from the real spectrum.
+If the measured spectrum move one pixel left, then a should be close to 1 and it's similar for c.
+The measured spectrum moves left or right is because of the error in the measured velocity, so there will be error in measuring the Doppler effect, which leads to a spectrum moving.
+We will show this in experiment 4.
+\bigskip
+
+\subsection{\label{sec:level2}Optimize Teff , log g and [Fe/H] simultaneously with a, b, c}
+
+Working on it...
 
@@
 The labels of the four stars are:
+\begin{center}
 
@@
  Star D  $T_{eff} =5003$  log g =2.8 $\left[Fe/h\right] =-0.71$
+
+ \end{center}
 
@@
 
-%\includegraphics[width=170mm]{figure_1.png}
+\includegraphics[width=170mm]{figure_1.png}
  \centerline{Fig.1 The optimized spectrum and the data spectrum}
@@
 
-%\includegraphics[width=170mm]{figure_2.png}
+\includegraphics[width=170mm]{figure_2.png}
  \centerline{Fig.2 The inferred spectrum and the data spectrum}
@@
 We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
-The number of stars is 639.
-But now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 639 objective functions.
-And there will be 639 sets of a, b and c.
-Then we can plot a histogram of a, b and c to see the distribution of their values.
+The number of stars is 907.
+Now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 907 objective functions.
+And there will be 907 sets of a, b and c.
+
+We plot a, b, c against the mean fiber number, which is the average fiber number of the spectrum we optimize.
+In APOGEE DR 10, the fiber number is between 1 and 640.
+The parameters we use are from figure 3
+
+\includegraphics[width=170mm]{figure_3.png}
 \bigskip
 
-%\includegraphics[width=170mm]{figure_3.png}
-\bigskip
-
-\centerline{Fig.3 Histogram for  a, b and c}
-
-\bigskip
-
-Also.
-We plot a, b, c against the mean fiber number, which is the average fiber number of the spectrum we optimize.
-In APOGEE DR 10, the fiber number is between 1 and 640.
-The parameters we use are from $figure_3$
-
-%\includegraphics[width=170mm]{figure_4.png}
-\bigskip
-
-\centerline{Fig.4 a,b,c vs Mean Fiber Number}
+\centerline{Fig.3 a,b,c vs Mean Fiber Number}
 \bigskip
@@
 
-%\includegraphics[width=170mm]{figure_5.png}
+\includegraphics[width=170mm]{figure_4.png}
 \bigskip
 
-\centerline{Fig.5 Delta-chi-squared vs Mean Fiber Number}
+\centerline{Fig.4 Delta-chi-squared vs Mean Fiber Number}
+\bigskip
+
+\subsection{\label{sec:level2}Experiment 3}
+
+\bigskip
+Now choose some examples from the 907 stars and make some plots.
+
+First, plot the four stars with biggest delta-chi-squared and smallest delta-chi-squared:
+
+\includegraphics[width=170mm]{figure_5.png}
+\bigskip
+
+\centerline{Fig.5 Spectrum of the four stars with biggest delta-chi-squared}
+\bigskip
+
+\includegraphics[width=170mm]{figure_6.png}
+\bigskip
+
+\centerline{Fig.6 Spectrum of the four stars with smallest delta-chi-squared}
+\bigskip
+
+From figure 6 and 7, we find that the four stars with smallest delta-chi-squared have b closer to 1, but the four stars with biggest delta-chi-squared don't.
+
+Also, we want to look into the spectral broadening.
+Plot four stars with b closest to 1:
+\bigskip
+
+\includegraphics[width=170mm]{figure_7.png}
+\bigskip
+
+\centerline{Fig.7 Spectrum of the four stars with b closest to 1}
+\bigskip
+
+From the histogram of a, b and c, we also find that sometimes b becomes -1, which means the spectrum is broadened due to the measurement.
+The resolution of the spectrum becomes lower and this is what we want to calibrate.
+\bigskip
+Here is the plot of the four stars with b closest to -1:
+\bigskip
+
+\includegraphics[width=170mm]{figure_8.png}
+\bigskip
+
+\centerline{Fig.8 Spectrum of the four stars with b closest to -1}
+\bigskip
+
+\bigskip
+
+We found a and c are close to 1, which is in accordance with our theory. 
+Also, the optimized spectrum broaden when b =-1, which means the measured spectrum broaden due to the error in the measurement. This is what we need to calibrate.
+\bigskip
+
+To look deeper into the results, we also choose the four stars with biggest $a-c$ and biggest $c-a$. Then make another two plots:
+\bigskip
+
+\includegraphics[width=170mm]{figure_9.png}
+\bigskip
+
+\centerline{Fig.9 Spectrum of the four stars with biggest $a-c$}
+\bigskip
+
+\bigskip
+
+\includegraphics[width=170mm]{figure_10.png}
+\bigskip
+
+\centerline{Fig.10 Spectrum of the four stars with biggest $c-a$}
+\bigskip
+
+For spectrum with $a>c$, the optimized spectrum moves right a little bit, which means the real spectrum should move left a little. It's similar for $c>a$
+
+\subsection{\label{sec:level2}Experiment 4}
+
+\bigskip
+We also plot $Teff$ against log g. The color bar shows the mean inverse variance of these stars.
+
+\includegraphics[width=170mm]{figure_11.png}
+\bigskip
+
+\centerline{Fig.11 $Teff$ vs $log g$}
 \bigskip

### 2016-11-06 1106_normalize_flux_pure_aspcap_v1.py
bug fix

@@ -1,0 +1,293 @@
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib
+
+
+# function
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+# read data
+all_set = Table.read("/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/allStar-v304.fits")
+
+# data
+
+all_set_flux = np.zeros(8575)
+all_set_ivar = np.zeros(8575)
+all_set_error = np.zeros(8575)
+
+
+# choose some of them
+choose = []
+a=0
+for i in range(0,1600):
+    a += np.random.randint(1,30)
+    choose.append(a)
+
+choose = np.array(choose)
+all_set = all_set[choose]
+# Now all set only have 1600 stars
+
+
+# save the chosen star and the new all-set. Let's name it as testing set.
+output = open('n_choose_800.pkl', 'wb')
+pickle.dump(choose, output)
+output.close()
+
+
+
+
+N = len(all_set)
+test_labels_all = []
+tr_ID = []
+FiberID = []
+choose_800_final = []
+fail = 0
+star=0
+
+# choose some flux and normalize them first, then filter the mean inverse variance.
+
+
+for i, row in enumerate(all_set):
+    try:
+
+
+        image_path = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_Apstar/apStar-s3-" + row["APOGEE_ID"] + ".fits"
+
+        if not os.path.exists(image_path):
+            print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+            fail += 1
+            continue
+
+        print("{}/{}: {}".format(i + 1, N, image_path))
+        # Let's only use two extension of the data
+
+        image = fits.open(image_path, ignore_missing_end=True)
+        dat = Table.read(image_path)
+
+        flux = image[1].data[0]
+        flux_err = image[2].data[0]
+
+    except IOError:
[…]

### 2016-11-08 paper/ms.tex
fix bugs

@@
 In our theory b should be close to 1 and a, c is much smaller than b.
-But the fact is that sometimes b is close to -1.
+But the fact is that sometimes b is much smaller than and c.
 This is because of the spectral broadening in the measurement.
@@
 Then the spectrum will broaden and the real spectrum at pixel j is not what we obtain, it should be the spectrum at nearby pixels, which include pixel j-1 and j+1.
-Thus b will be close to -1 and at the same time a and c should be close to 1, which we will check in experiment 3.
+Thus b will be smaller than a+c, which we will discuss in the following experiment 3.
 \bigskip
 
-Sometimes a or c will be close to 1.
+Sometimes a or c will be much bigger than the other two parameters.
 This is also because of the measurement.
@@
 The measured spectrum moves left or right is because of the error in the measured velocity, so there will be error in measuring the Doppler effect, which leads to a spectrum moving.
-We will show this in experiment 4.
+We will show this in experiment 3.
 \bigskip
@@
 We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
-The number of stars is 907.
-Now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 907 objective functions.
-And there will be 907 sets of a, b and c.
+The number of stars is 614.
+Now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 614 objective functions.
+And there will be 614 sets of a, b and c.
 
@@
 \bigskip
-Now choose some examples from the 907 stars and make some plots.
+Now choose some examples from the 614 stars and make some plots.
 
@@
 
-\centerline{Fig.5 Spectrum of the four stars with biggest delta-chi-squared}
+\centerline{Fig.5 Spectrum of the four stars with biggest delta-chi-squared. }
+
+\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 \bigskip
@@
 
-\centerline{Fig.6 Spectrum of the four stars with smallest delta-chi-squared}
+\centerline{Fig.6 Spectrum of the four stars with smallest delta-chi-squared. }
+
+\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 \bigskip
@@
 
-\centerline{Fig.7 Spectrum of the four stars with b closest to 1}
+\centerline{Fig.7 Spectrum of the four stars with b closest to 1. }
+
+\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 \bigskip
 
-From the histogram of a, b and c, we also find that sometimes b becomes -1, which means the spectrum is broadened due to the measurement.
+From the histogram of a, b and c, we also find that sometimes b becomes much smaller than a+c, which means the spectrum is broadening due to the measurement.
 The resolution of the spectrum becomes lower and this is what we want to calibrate.
 \bigskip
-Here is the plot of the four stars with b closest to -1:
+Here is the plot of the four stars with biggest a+c-b:
 \bigskip
@@
 
-\centerline{Fig.8 Spectrum of the four stars with b closest to -1}
+\centerline{Fig.8 Spectrum of the four stars with biggest a+c-b. }
+
+\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 \bigskip
@@
 We found a and c are close to 1, which is in accordance with our theory. 
-Also, the optimized spectrum broaden when b =-1, which means the measured spectrum broaden due to the error in the measurement. This is what we need to calibrate.
+Also, the optimized spectrum broaden when a+c is much bigger than b, which means the measured spectrum broaden due to the error in the measurement. This is what we need to calibrate.
 \bigskip
@@
 
-\centerline{Fig.9 Spectrum of the four stars with biggest $a-c$}
+\centerline{Fig.9 Spectrum of the four stars with biggest $a-c$.}
+
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 \bigskip
@@
 
-\centerline{Fig.10 Spectrum of the four stars with biggest $c-a$}
+\centerline{Fig.10 Spectrum of the four stars with biggest $c-a$.}
+
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 \bigskip
@@
 
+  %% Fifth paragraph
+
+ \section{\label{sec:level1}Appendix}
+
+ Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
+
+\includegraphics[width=170mm]{d_figure_2.png}
+\bigskip
+
+\centerline{Fig.2 Histogram of a b c for apstar data (What we use now)}
+\bigskip
+
 \end{document}

### 2016-11-08 1106_normalize_flux_pure_aspcap_v1.py

@@ -16,11 +16,24 @@ def get_pixmask(flux, err):
     bad_pixels = bad_err | bad_flux
     return bad_pixels
 
+def get_error_mask(err):
+    bad_err = (~np.isfinite(err))
+    bad_pixels = bad_err
+    return bad_pixels
+
 # read data
 all_set = Table.read("/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/allStar-v304.fits")
 
 # data
 
+
+## 1. read the dat
+## 2. add a mask (bitmask)
+## 3. filter-mean inverse variance
+
+
+
+# Try to use numpy array to avoid memory overflow
 all_set_flux = np.zeros(8575)
 all_set_ivar = np.zeros(8575)
 all_set_error = np.zeros(8575)
@@ -29,8 +42,8 @@ all_set_error = np.zeros(8575)
 # choose some of them
 choose = []
 a=0
-for i in range(0,1600):
-    a += np.random.randint(1,30)
+for i in range(0,3200):
+    a += np.random.randint(1,11)
     choose.append(a)
 
 choose = np.array(choose)
@@ -99,6 +112,7 @@ for i, row in enumerate(all_set):
             all_set_error = np.vstack((all_set_error, error))
             test_labels_all_i = [row["TEFF"], row["LOGG"], row["METALS"]]
             test_labels_all.append(test_labels_all_i)
+            print(test_labels_all_i)
             choose_800_final.append(i)
 
 
@@ -186,8 +200,21 @@ keep = np.ones(star, dtype=bool)
 
 for i in range(0,star):
     ivar = norm_tr_ivar[i,:]
+    print(ivar)
     if np.mean(ivar) > 10000 and np.mean(ivar) < 40000:
-        keep[i]=1
+
+## If the labels are not obtained, APOGEE will set them as -10000
+##  So exclude these labels
+        teff = test_labels_all[i,0]
+        logg = test_labels_all[i,1]
+        metal = test_labels_all[i,2]
+        if teff>0 and logg> -15 and metal > -15:
+            keep[i] = 1
+        else:
+            keep[i] = 0
+            star -= 1
+            fail += 1
+
 
     else:
         keep[i] = 0
@@ -202,6 +229,13 @@ norm_ivar =norm_test_ivar[keep]
[…]

### 2016-11-08 1106_opt_1_percent.py

@@ -1,0 +1,172 @@
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib
+from astropy.io.fits import getdata
+from numpy.linalg import inv
+import AnniesLasso_2 as tc
+import time
+
+
+
+# get the time of the program
+start_time = time.time()
+
+
+training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
+training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
+
+
+training_set = Table.read("reference_labels.csv")
+
+
+
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+
+N = len(training_set)
+keep = np.ones(N, dtype=bool)
+
+training_set_flux = []
+training_set_ivar = []
+training_set_error = []
+
+for i, row in enumerate(training_set):
+    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
+    if not os.path.exists(image_path):
+        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+        keep[i] = False
+        continue
+    print("{}/{}: {}".format(i + 1, N, image_path))
+    image = fits.open(image_path)
+    flux = image[1].data
+    flux_err = image[2].data
+    badpix = get_pixmask(flux, flux_err)
+    ivar = 1.0/flux_err**2
+    error = flux_err
+    # badpix is a array and the length is 8575
+    flux[badpix] = 1.0
+    ivar[badpix] = 0.0
+    training_set_flux.append(flux)
+    training_set_ivar.append(ivar)
+    training_set_error.append(error)
+
+training_set_flux = np.array(training_set_flux)
+training_set_ivar = np.array(training_set_ivar)
+training_set_error = np.array(training_set_error)
+
+
+assert all(keep)
+
[…]

### 2016-11-08 1106_plot_choose_4_stars.py

@@ -1,0 +1,316 @@
+from numpy import genfromtxt
+import matplotlib.pyplot as plt
+import random
+import matplotlib
+import numpy as np
+import pickle
+from astropy.table import Table
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import AnniesLasso_2 as tc
+
+import plot_class_4_star_v2_1107
+
+
+
+
+
+
+
+
+# import data
+pkl_file = open('n_delta_chi_900.pkl', 'rb')
+delta_chi_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_parameters_900.pkl', 'rb')
+parameters_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_FiberID_900.pkl', 'rb')
+FiberID = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_tr_ID_900.pkl', 'rb')
+tr_ID_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_testing_labels_900.pkl', 'rb')
+test_labels = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("testing_set_900.pkl", 'rb')
+testing_set = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# flux,ivar and error
+
+pkl_file = open("n_testing_flux_900.pkl", 'rb')
+testing_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_ivar_900.pkl", 'rb')
+testing_ivar = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_error_900.pkl", 'rb')
+testing_error = pickle.load(pkl_file)
+pkl_file.close()
+
+
+## check error
+"""
+plt.plot(testing_error[1,:],"r")
+
+axes = plt.gca()
+
+axes.set_ylim([-0.01,0.01])
+
+
+plt.show()
+
+"""
+
+
+
+
+
+#print(choose_800_final.shape)
+#print(choose_800_final.shape,FiberID.shape)
+
+
+# check shape
+#print(parameters_500.shape,delta_chi_500.shape)
+
+#### find the biggest four delta-chi and smallest four
+N_star = len(delta_chi_500)
+
+
[…]

### 2016-11-08 paper/ms.tex
clarify the spectrum we use

@@
 
+%{\AA}
 Suppose we have a trained model.
@@
 They span the range of $3500K <T_{eff}< 5300K$, $0 <log$ $g< 5$ and $-2.5 <\left[Fe/H\right]< 0.45$.
+The spectrum we use in the training and testing step of the cannon is the combined spectrum from aspcap files.
 ]
@@
 
- Then plot the spectrum
+ Then plot the spectrum. The spectrum we use is the combined non-normalized spectrum from apstar files.
 
@@
 We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
-The number of stars is 614.
+The mean inverse variance of the stars is bigger than 10000 but smaller than 40000.
+We also exclude stars with undetermined labels.
+(The label is set to -10000 if it's not determined.)The number of stars is 614.
 Now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 614 objective functions.
 And there will be 614 sets of a, b and c.
+The spectrum we use is the combined non-normalized spectrum from apstar files.
+And soon we will use the individual visit non-normalized spectrum from apstar files.
+Before using these spectrum, normalization is needed.
+The normalization method we use is the same as the one in Ness et al 2015.
 
@@
 
+\includegraphics[width=170mm]{d_figure_1.png}
+\bigskip
+
+\centerline{Fig.1 Histogram of a b c for apstar data (What we use now)}
+\bigskip
+
+ \section{\label{sec:level1}Appendix}
+
+Plot log g vs teff for all the stars we use in the training step.
+
 \includegraphics[width=170mm]{d_figure_2.png}
@@
 
-\centerline{Fig.2 Histogram of a b c for apstar data (What we use now)}
+\centerline{Fig.2 Log g vs Teff for the training set}
 \bigskip

### 2016-11-09 1108_optimize_all_data.py
optimize all

@@ -1,0 +1,321 @@
+from numpy import genfromtxt
+import matplotlib.pyplot as plt
+import random
+import matplotlib
+import numpy as np
+import pickle
+from astropy.table import Table
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import AnniesLasso_2 as tc
+import time
+
+## training the cannon
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
+training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
+
+
+training_set = Table.read("reference_labels.csv")
+
+
+
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+
+N = len(training_set)
+keep = np.ones(N, dtype=bool)
+
+training_set_flux = []
+training_set_ivar = []
+training_set_error = []
+
+for i, row in enumerate(training_set):
+    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
+    if not os.path.exists(image_path):
+        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+        keep[i] = False
+        continue
+    print("{}/{}: {}".format(i + 1, N, image_path))
+    image = fits.open(image_path)
+    flux = image[1].data
+    flux_err = image[2].data
+    badpix = get_pixmask(flux, flux_err)
+    ivar = 1.0/flux_err**2
+    error = flux_err
+    # badpix is a array and the length is 8575
+    flux[badpix] = 1.0
+    ivar[badpix] = 0.0
+    training_set_flux.append(flux)
+    training_set_ivar.append(ivar)
+    training_set_error.append(error)
+
+training_set_flux = np.array(training_set_flux)
+training_set_ivar = np.array(training_set_ivar)
+training_set_error = np.array(training_set_error)
+
+
+assert all(keep)
+
+# Construct model.
+model = tc.L1RegularizedCannonModel(
[…]

### 2016-11-09 paper/ms.tex
bug fix

@@
 The spectrum we use in the training and testing step of the cannon is the combined spectrum from aspcap files.
-]
+The labels we use are from the Allstar visit file.
 
@@
 We will show this in experiment 3.
+
+We will do this optimization for each visit of every star in APOGEE DR10.
+The spectrum we use is in apstar file.
+We will re-analyze the velocities after the optimization and deliver back the velocities correction for the APOGEE data.
 \bigskip
@@
 
-Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c for each stars.
+Choose four stellar, which are not in the training set.
+Optimize the spectrum of these four stars and obtain a, b and c for each stars.
+The labels we use are from the Cannon, which means they are inferred labels.
 
@@
 The normalization method we use is the same as the one in Ness et al 2015.
+The labels we use are from the Cannon, which means they are inferred labels.
 

### 2016-11-10 plot_class_4_star_v2_1107.py
Add new plot

@@ -1,0 +1,523 @@
+import matplotlib.pyplot as plt
+import random
+import matplotlib
+import numpy as np
+import pickle
+from astropy.table import Table
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import AnniesLasso_2 as tc
+
+
+class plot_4:
+    def __init__(self):
+        n = 1
+
+    def train(self):
+
+        training_set = Table.read("reference_labels.csv")
+
+        pkl_file = open('training_set_flux.pkl', 'rb')
+        training_set_flux = pickle.load(pkl_file)
+        pkl_file.close()
+
+        # read table
+        pkl_file = open('training_set_ivar.pkl', 'rb')
+        training_set_ivar = pickle.load(pkl_file)
+        pkl_file.close()
+
+
+
+        # Construct model.
+        model = tc.L1RegularizedCannonModel(
+            training_set, training_set_flux, training_set_ivar, threads=8)
+        model.s2 = 0
+        model.regularization = 0
+        model.vectorizer = tc.vectorizer.NormalizedPolynomialVectorizer(training_set,
+                                                                  tc.vectorizer.polynomial.terminator((
+                                                                                                            "Teff_{corr}",
+                                                                                                            "logg_{corr}",
+                                                                                                            "[M/H]_{corr}"),
+                                                                                                            2))
+
+        model.train()
+        self.model =model
+
+    def plot(self,flux,ivar,error,star_name,test_label):
+
+        #import data
+
+        pkl_file = open('wl.pkl', 'rb')
+        wl = pickle.load(pkl_file)
+        pkl_file.close()
+
[…]

### 2016-11-10 paper/ms.tex
better plot

@@
 \includegraphics[width=170mm]{figure_1.png}
- \centerline{Fig.1 The optimized spectrum and the data spectrum}
+ \centerline{Fig.1 The spectrum of Star A, B, C and D}
+
+ \centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 \bigskip
-
-\includegraphics[width=170mm]{figure_2.png}
- \centerline{Fig.2 The inferred spectrum and the data spectrum}
 
@@
 
-\includegraphics[width=170mm]{figure_3.png}
+\includegraphics[width=170mm]{figure_2.png}
 \bigskip
 
-\centerline{Fig.3 a,b,c vs Mean Fiber Number}
+\centerline{Fig.2 a,b,c vs Mean Fiber Number}
 \bigskip
@@
 
-\includegraphics[width=170mm]{figure_4.png}
+\includegraphics[width=170mm]{figure_3.png}
 \bigskip
 
-\centerline{Fig.4 Delta-chi-squared vs Mean Fiber Number}
+\centerline{Fig.3 Delta-chi-squared vs Mean Fiber Number}
 \bigskip
@@
 
-\includegraphics[width=170mm]{figure_5.png}
+\includegraphics[width=170mm]{figure_4.png}
 \bigskip
 
-\centerline{Fig.5 Spectrum of the four stars with biggest delta-chi-squared. }
+\centerline{Fig.4 Spectrum of the four stars with biggest delta-chi-squared. }
 
@@
 
-\includegraphics[width=170mm]{figure_6.png}
+\includegraphics[width=170mm]{figure_5.png}
 \bigskip
 
-\centerline{Fig.6 Spectrum of the four stars with smallest delta-chi-squared. }
+\centerline{Fig.5 Spectrum of the four stars with smallest delta-chi-squared. }
 
@@
 
-\includegraphics[width=170mm]{figure_7.png}
+\includegraphics[width=170mm]{figure_6.png}
 \bigskip
 
-\centerline{Fig.7 Spectrum of the four stars with b closest to 1. }
+\centerline{Fig.6 Spectrum of the four stars with b closest to 1. }
 
@@
 
-\includegraphics[width=170mm]{figure_8.png}
+\includegraphics[width=170mm]{figure_7.png}
 \bigskip
 
-\centerline{Fig.8 Spectrum of the four stars with biggest a+c-b. }
+\centerline{Fig.7 Spectrum of the four stars with biggest a+c-b. }
 
@@
 
-\includegraphics[width=170mm]{figure_9.png}
+\includegraphics[width=170mm]{figure_8.png}
 \bigskip
 
-\centerline{Fig.9 Spectrum of the four stars with biggest $a-c$.}
+\centerline{Fig.8 Spectrum of the four stars with biggest $a-c$.}
 
@@
 
-\includegraphics[width=170mm]{figure_10.png}
+\includegraphics[width=170mm]{figure_9.png}
 \bigskip
 
-\centerline{Fig.10 Spectrum of the four stars with biggest $c-a$.}
+\centerline{Fig.9 Spectrum of the four stars with biggest $c-a$.}
 
@@
 
-\includegraphics[width=170mm]{figure_11.png}
+\includegraphics[width=170mm]{figure_10.png}
 \bigskip
 
-\centerline{Fig.11 $Teff$ vs $log g$}
+\centerline{Fig.10 $Teff$ vs $log g$}
 \bigskip

### 2016-11-15 paper/ms.tex
Bug fixed

@@
 Working on it...
+I think one possible way is to use the velocities correction for the APOGEE data obtained from the spectrum calibration section. Then the optimized APOGEE spectrum can be represented as:
+You should look into the velocities and find a right way to describe them.
 
@@
 Optimize the spectrum of these four stars and obtain a, b and c for each stars.
-The labels we use are from the Cannon, which means they are inferred labels.
+The labels we use in the figures are from the Cannon, which means they are inferred labels.
 
@@
 \bigskip
-Now choose some examples from the 614 stars and make some plots.
+Now choose some examples from the 614 stars and make some plots.Sometimes the inferred spectrum doesn't look like the data, which is already described in Ness et al 2015.
+We don't use these stars in the plots.
 
@@
 
-For spectrum with $a>c$, the optimized spectrum moves right a little bit, which means the real spectrum should move left a little. It's similar for $c>a$
+For spectrum with $a>c$, the optimized spectrum moves left a little bit, which means the real spectrum should move right a little.
+It's similar for $c>a$.
+The c>a branch is not as obvious as the a>c branch.
 
@@
 \bigskip
-We also plot $Teff$ against log g. The color bar shows the mean inverse variance of these stars.
+We also plot the inferred labels $Teff$ against log g. The color bar shows the mean inverse variance of these stars.
 

### 2016-11-15 1106_plot_choose_4_stars.py

@@ -18,11 +18,6 @@ import plot_class_4_star_v2_1107
 
 
 
-
-
-
-
-
 # import data
 pkl_file = open('n_delta_chi_900.pkl', 'rb')
 delta_chi_500 = pickle.load(pkl_file)

### 2016-11-16 Diagnostic/plot_class_4_star_v2_1107.py
diagnostic for figure 10 in old version

@@ -1,0 +1,747 @@
+import matplotlib.pyplot as plt
+import random
+import matplotlib
+import numpy as np
+import pickle
+from astropy.table import Table
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import AnniesLasso_2 as tc
+
+
+class plot_4:
+    def __init__(self):
+        n = 1
+
+    def train(self):
+
+        training_set = Table.read("reference_labels.csv")
+
+        pkl_file = open('training_set_flux.pkl', 'rb')
+        training_set_flux = pickle.load(pkl_file)
+        pkl_file.close()
+
+        # read table
+        pkl_file = open('training_set_ivar.pkl', 'rb')
+        training_set_ivar = pickle.load(pkl_file)
+        pkl_file.close()
+
+
+
+        # Construct model.
+        model = tc.L1RegularizedCannonModel(
+            training_set, training_set_flux, training_set_ivar, threads=8)
+        model.s2 = 0
+        model.regularization = 0
+        model.vectorizer = tc.vectorizer.NormalizedPolynomialVectorizer(training_set,
+                                                                  tc.vectorizer.polynomial.terminator((
+                                                                                                            "Teff_{corr}",
+                                                                                                            "logg_{corr}",
+                                                                                                            "[M/H]_{corr}"),
+                                                                                                            2))
+
+        model.train()
+        self.model =model
+
+    def plot(self,flux,ivar,error,star_name,test_label):
+
+        #import data
+
+        pkl_file = open('wl.pkl', 'rb')
+        wl = pickle.load(pkl_file)
+        pkl_file.close()
+
[…]

### 2016-11-16 paper/ms.tex
Add figure 6 in Appendix for diagnostic step

@@
  Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
+ \bigskip
 
@@
 \bigskip
-
- \section{\label{sec:level1}Appendix}
 
@@
 
+Randomly choose four stars and manually set their a, b and c equal to parameters in figure 8, then plot the spectrum. The difference between a and c is about 0.3.
+
+\includegraphics[width=170mm]{d_figure_3.png}
+\bigskip
+
+\centerline{Fig.3 Comparison of the spectrum}
+
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized }
+\bigskip
+
+Randomly choose four stars and manually set a = 0.7 b = 0.2 c = 0.1, then plot the spectrum. The difference between a and c is 0.6.
+
+\includegraphics[width=170mm]{d_figure_4.png}
+\bigskip
+
+\centerline{Fig.4 Comparison of the spectrum}
+
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized }
+\bigskip
+
+Randomly choose four stars and manually set a = 2 b = -2 c = 1, then plot the spectrum. The difference between a and c is 1.
+
+\includegraphics[width=170mm]{d_figure_5.png}
+\bigskip
+
+\centerline{Fig.5 Comparison of the spectrum}
+
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized }
+\bigskip
+
+Diagnostic.
+The parameters showed in figure 6 are the parameters obtained from the optimization process using labels from the APOGEE team, which is not correct.
+But the parameters to generate optimized flux are from the optimization process using labels from the Cannon, which should be correct.
+
+\includegraphics[width=170mm]{d_figure_6.png}
+\bigskip
+
+\centerline{Fig.6 Comparison of the spectrum}
+
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized }
+\bigskip
+
 \end{document}

### 2016-11-16 Diagnostic/1108_opt_1_no_filter_inf_label.py
Add diagnostic plots 7,8

@@ -1,0 +1,172 @@
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib
+from astropy.io.fits import getdata
+from numpy.linalg import inv
+import AnniesLasso_2 as tc
+import time
+
+
+
+# get the time of the program
+start_time = time.time()
+
+
+training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
+training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
+
+
+training_set = Table.read("reference_labels.csv")
+
+
+
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+
+N = len(training_set)
+keep = np.ones(N, dtype=bool)
+
+training_set_flux = []
+training_set_ivar = []
+training_set_error = []
+
+for i, row in enumerate(training_set):
+    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
+    if not os.path.exists(image_path):
+        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+        keep[i] = False
+        continue
+    print("{}/{}: {}".format(i + 1, N, image_path))
+    image = fits.open(image_path)
+    flux = image[1].data
+    flux_err = image[2].data
+    badpix = get_pixmask(flux, flux_err)
+    ivar = 1.0/flux_err**2
+    error = flux_err
+    # badpix is a array and the length is 8575
+    flux[badpix] = 1.0
+    ivar[badpix] = 0.0
+    training_set_flux.append(flux)
+    training_set_ivar.append(ivar)
+    training_set_error.append(error)
+
+training_set_flux = np.array(training_set_flux)
+training_set_ivar = np.array(training_set_ivar)
+training_set_error = np.array(training_set_error)
+
+
[…]

### 2016-11-16 Diagnostic/1108_plot_4_star_diagnostic_inf_label_non_filter.py
add diagnostic plot

@@ -1,0 +1,636 @@
+from numpy import genfromtxt
+import matplotlib.pyplot as plt
+import random
+import matplotlib
+import numpy as np
+import pickle
+from astropy.table import Table
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import AnniesLasso_2 as tc
+
+import plot_class_4_star_v2_1107
+
+
+
+
+
+
+
+
+# import data
+pkl_file = open('n2_delta_chi_900.pkl', 'rb')
+delta_chi_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('error_4.pkl', 'rb')
+error = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n2_parameters_900.pkl', 'rb')
+parameters_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n2_FiberID_900.pkl', 'rb')
+FiberID = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n2_inf_flux_900.pkl', 'rb')
+inf_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+
+pkl_file = open('n2_tr_ID_900.pkl', 'rb')
+tr_ID_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n2_testing_labels_900.pkl', 'rb')
+test_labels = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n2_testing_set_900.pkl", 'rb')
+testing_set = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# flux,ivar and error
+
+pkl_file = open("n_testing_flux_900.pkl", 'rb')
+testing_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_ivar_900.pkl", 'rb')
+testing_ivar = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_error_900.pkl", 'rb')
+testing_error = pickle.load(pkl_file)
+pkl_file.close()
[…]

### 2016-11-17 Diagnostic/1106_plot_choose_4_stars.py
Diagnostic_for_nov_11

@@ -1,0 +1,386 @@
+from numpy import genfromtxt
+import matplotlib.pyplot as plt
+import random
+import matplotlib
+import numpy as np
+import pickle
+from astropy.table import Table
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import AnniesLasso_2 as tc
+
+import plot_class_4_star_v2_1107
+
+
+
+
+
+
+
+
+# import data
+pkl_file = open('n_delta_chi_900.pkl', 'rb')
+delta_chi_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+pkl_file = open('n_testing_labels_900.pkl', 'rb')
+test_labels_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_parameters_900.pkl', 'rb')
+parameters_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_FiberID_900.pkl', 'rb')
+FiberID = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_tr_ID_900.pkl', 'rb')
+tr_ID_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_inf_label_900.pkl', 'rb')
+test_labels = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("testing_set_900.pkl", 'rb')
+testing_set = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# flux,ivar and error
+
+pkl_file = open("n_testing_flux_900.pkl", 'rb')
+testing_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_ivar_900.pkl", 'rb')
+testing_ivar = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_error_900.pkl", 'rb')
+testing_error = pickle.load(pkl_file)
+pkl_file.close()
+
+
+## check error
+"""
+plt.plot(testing_error[1,:],"r")
+
+axes = plt.gca()
+
+axes.set_ylim([-0.01,0.01])
+
+
+plt.show()
+
+"""
+
+## replace test_label with inf_label
+
+
+
+
+
+
+#print(choose_800_final.shape)
+#print(choose_800_final.shape,FiberID.shape)
[…]

### 2016-11-17 Diagnostic/plot_class_4_star_v2_1107.py

@@ -48,266 +48,6 @@ class plot_4:
         model.train()
         self.model =model
 
-    def plot(self,flux,ivar,error,star_name,test_label):
-
-        #import data
-
-        pkl_file = open('wl.pkl', 'rb')
-        wl = pickle.load(pkl_file)
-        pkl_file.close()
-
-        all_set_flux = np.array(flux)
-        all_set_ivar = np.array(ivar)
-        all_set_error = np.array(error)
-        star_name = np.array(star_name)
-
-        inf_label = self.model.fit(all_set_flux, all_set_ivar)
-        v = self.model.vectorizer.get_label_vector(inf_label)
-        # v_500 = model.vectorizer.get_label_vector(test_label)
-
-        inf_flux = np.dot(v, self.model.theta.T)
-        # opt four star
-
-
-
-
-
-        # plot
-        nor = all_set_flux
-        inf_old = inf_flux
-
-        inf_opt, parameters_4 = self.model.fitting_spectrum_parameters_single(
-            all_set_flux, all_set_ivar, inf_old)
-
-        error = all_set_error
-
-        delta_chi = self.model.delta_chi_squared(all_set_flux, all_set_ivar, inf_flux)
-
-        # plot-opt
-        trans = 0.5
-        p1 = 0
-        p2 = 1
-        p3 = 2
-        p4 = 3
-
-        n1 = star_name[0]
-        n2 = star_name[1]
-        n3 = star_name[2]
-        n4 = star_name[3]
-        print(n1,n2,n3,n4)
-
-        # test label test_label
-
-        l1 = "Teff=%.3f Log g = %.3f" % (inf_label[0,0],inf_label[0,1])
-        l2 = "Teff=%.3f Log g = %.3f" % (inf_label[1, 0], inf_label[1, 1])
-        l3 = "Teff=%.3f Log g = %.3f" % (inf_label[2, 0], inf_label[2, 1])
-        l4 = "Teff=%.3f Log g = %.3f" % (inf_label[3, 0], inf_label[3, 1])
-
-        delta_para_1 = "delta-chi-squared=%f a=%.3f b=%.3f c=%.3f" % (
-        delta_chi[0], parameters_4[0, 0], parameters_4[0, 1], parameters_4[0, 2])
-
-        delta_para_2 = "delta-chi-squared=%f a=%.3f b=%.3f c=%.3f" % (
[…]

### 2016-11-17 paper/ms.tex
Add diagnostic plots 7,8
Add diagnostic figure 2,3,4

--- 2016-11-15 paper/ms.tex
@@
 
-\centerline{Fig.1 Histogram of a b c for apstar data (What we use now)}
+\centerline{Diagnostic Fig.1 Histogram of a b c for apstar data (What we use now)}
 \bigskip
 
- \section{\label{sec:level1}Appendix}
-
-Plot log g vs teff for all the stars we use in the training step.
+Comparison of the spectrum if we set the parameters showed in old figure 8. In old figure 8, the red line and the green line are on the top of each other
+ \bigskip
 
@@
 
-\centerline{Fig.2 Log g vs Teff for the training set}
+\centerline{Diagnostic Fig.2 Comparison of the spectrum if we set the parameters showed in old figure 8}
+\bigskip
+
+Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
+ \bigskip
+
+ Comparison of the spectrum if we set the parameters showed in old figure 9. In old figure 9, the difference between red line and the green line is too big if we consider their parameters.
+ \bigskip
+
+\includegraphics[width=170mm]{d_figure_3.png}
+\bigskip
+
+\centerline{Diagnostic Fig.3 Comparison of the spectrum if we set the parameters showed in old figure 9}
+\bigskip
+
+Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
+ \bigskip
+
+ If we want a plot like old figure 9, we can manually set a=0.5, b=1 and c= -0.5. Here a+b+c is not equal to 1 and this is the cause of the offset.
+ \bigskip
+
+\includegraphics[width=170mm]{d_figure_4.png}
+\bigskip
+
+\centerline{Diagnostic Fig.4 Comparison of the spectrum if we want a big difference between the red line and the green line}
+\bigskip
+
+Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
  \bigskip

### 2016-11-18 Diagnostic/1117_diagnostic_four_fake_stars.py
Add four fake stars to diagnose

@@ -1,0 +1,167 @@
+
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import AnniesLasso_2 as tc
+
+import plot_class_4_star_v2_1107
+
+
+
+
+
+
+
+
+# import data
+pkl_file = open('n_delta_chi_900.pkl', 'rb')
+delta_chi_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+pkl_file = open('n_testing_labels_900.pkl', 'rb')
+test_labels_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_parameters_900.pkl', 'rb')
+parameters_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_FiberID_900.pkl', 'rb')
+FiberID = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_tr_ID_900.pkl', 'rb')
+tr_ID_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_inf_label_900.pkl', 'rb')
+inf_labels = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("testing_set_900.pkl", 'rb')
+testing_set = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# flux,ivar and error
+
+pkl_file = open("n_testing_flux_900.pkl", 'rb')
+testing_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_ivar_900.pkl", 'rb')
+testing_ivar = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_error_900.pkl", 'rb')
+testing_error = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_inf_flux_900.pkl", 'rb')
+inf_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+big_a_c = (parameters_500[:,2]-parameters_500[:,0]).argsort()[0:4]
+big_a_c_set = testing_set[big_a_c]
+
+
+
+##################
+# plot:
+###################
+model = plot_class_4_star_v2_1107.plot_4()
+model.train()
+
+
+
[…]

### 2016-11-18 plot_class_4_star_v2_1107.py
Plot_v3 is the right versioj

@@ -48,266 +48,6 @@ class plot_4:
         model.train()
         self.model =model
 
-    def plot(self,flux,ivar,error,star_name,test_label):
-
-        #import data
-
-        pkl_file = open('wl.pkl', 'rb')
-        wl = pickle.load(pkl_file)
-        pkl_file.close()
-
-        all_set_flux = np.array(flux)
-        all_set_ivar = np.array(ivar)
-        all_set_error = np.array(error)
-        star_name = np.array(star_name)
-
-        inf_label = self.model.fit(all_set_flux, all_set_ivar)
-        v = self.model.vectorizer.get_label_vector(inf_label)
-        # v_500 = model.vectorizer.get_label_vector(test_label)
-
-        inf_flux = np.dot(v, self.model.theta.T)
-        # opt four star
-
-
-
-
-
-        # plot
-        nor = all_set_flux
-        inf_old = inf_flux
-
-        inf_opt, parameters_4 = self.model.fitting_spectrum_parameters_single(
-            all_set_flux, all_set_ivar, inf_old)
-
-        error = all_set_error
-
-        delta_chi = self.model.delta_chi_squared(all_set_flux, all_set_ivar, inf_flux)
-
-        # plot-opt
-        trans = 0.5
-        p1 = 0
-        p2 = 1
-        p3 = 2
-        p4 = 3
-
-        n1 = star_name[0]
-        n2 = star_name[1]
-        n3 = star_name[2]
-        n4 = star_name[3]
-        print(n1,n2,n3,n4)
-
-        # test label test_label
-
-        l1 = "Teff=%.3f Log g = %.3f" % (inf_label[0,0],inf_label[0,1])
-        l2 = "Teff=%.3f Log g = %.3f" % (inf_label[1, 0], inf_label[1, 1])
-        l3 = "Teff=%.3f Log g = %.3f" % (inf_label[2, 0], inf_label[2, 1])
-        l4 = "Teff=%.3f Log g = %.3f" % (inf_label[3, 0], inf_label[3, 1])
-
-        delta_para_1 = "delta-chi-squared=%f a=%.3f b=%.3f c=%.3f" % (
-        delta_chi[0], parameters_4[0, 0], parameters_4[0, 1], parameters_4[0, 2])
-
[…]

### 2016-11-18 paper/ms.tex
Add four fake stars to diagnose
Grammar fixed

@@
 
-Comparison of the spectrum if we set the parameters showed in old figure 8. In old figure 8, the red line and the green line are on the top of each other
+Comparison of the spectrum if we set the parameters shown in old figure 8. In old figure 8, the red line and the green line are on the top of each other
  \bigskip
@@
 
-\centerline{Diagnostic Fig.2 Comparison of the spectrum if we set the parameters showed in old figure 8}
+\centerline{Diagnostic Fig.2 Comparison of the spectrum if we set the parameters shown in old figure 8}
 \bigskip
 
-Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
- \bigskip
-
- Comparison of the spectrum if we set the parameters showed in old figure 9. In old figure 9, the difference between red line and the green line is too big if we consider their parameters.
+ Comparison of the spectrum if we set the parameters shown in old figure 9. In old figure 9, the difference between red line and the green line is too big if we consider their parameters.
  \bigskip
@@
 
-\centerline{Diagnostic Fig.3 Comparison of the spectrum if we set the parameters showed in old figure 9}
-\bigskip
-
-Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
+\centerline{Diagnostic Fig.3 Comparison of the spectrum if we set the parameters shown in old figure 9}
 \bigskip
@@
 
-Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
+In diagnostic plot 5, I use four fake stars.
+The data spectra of these four stars are generated by moving their inferred spectra one pixel left.
+If my new code is right, a, b and c will be [1,0,0].
+In diagnostic figure 5, a=1, b=0 and c=0.
+\bigskip
+
+\includegraphics[width=170mm]{d_figure_5.png}
+\bigskip
+
+\centerline{Diagnostic Fig.5 Comparison of the spectrum for the four fake stars}
 \bigskip

### 2016-11-20 1120_obtain_abc_for_training_set.py
Optimize labels by using a b and c

@@ -1,0 +1,208 @@
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib
+
+import AnniesLasso_2 as tc
+import time
+
+# Get training set data
+
+# get the time of the program
+start_time = time.time()
+
+
+training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
+training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
+
+
+training_set = Table.read("reference_labels.csv")
+
+
+
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+
+N = len(training_set)
+keep = np.ones(N, dtype=bool)
+
+training_set_flux = []
+training_set_ivar = []
+training_set_error = []
+
+for i, row in enumerate(training_set):
+    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
+    if not os.path.exists(image_path):
+        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+        keep[i] = False
+        continue
+    print("{}/{}: {}".format(i + 1, N, image_path))
+    image = fits.open(image_path)
+    flux = image[1].data
+    flux_err = image[2].data
+    badpix = get_pixmask(flux, flux_err)
+    ivar = 1.0/flux_err**2
+    error = flux_err
+    # badpix is a array and the length is 8575
+    flux[badpix] = 1.0
+    ivar[badpix] = 0.0
+    training_set_flux.append(flux)
+    training_set_ivar.append(ivar)
+    training_set_error.append(error)
+
+training_set_flux = np.array(training_set_flux)
+training_set_ivar = np.array(training_set_ivar)
+training_set_error = np.array(training_set_error)
+
+
+assert all(keep)
+
+# Construct model.
[…]

### 2016-11-20 1120_plot_check_training_abc.py

@@ -1,0 +1,87 @@
+import os
+import numpy as np
+from numpy import genfromtxt
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib
+
+import AnniesLasso_2 as tc
+import time
+
+
+# load data
+
+pkl_file = open('parameters_tr_inf.pkl', 'rb')
+parameters_tr_inf = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('parameters_tr.pkl', 'rb')
+parameters_tr = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# labels
+tr_label = genfromtxt("reference-3.csv",delimiter=",")
+tr_label = np.array(tr_label)
+
+
+pkl_file = open('inf_labels_tr_opt.pkl', 'rb')
+inf_labels_tr_opt = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('inf_labels_tr.pkl', 'rb')
+inf_labels_tr = pickle.load(pkl_file)
+pkl_file.close()
+
+#load n_900 data
+
+pkl_file = open('n_testing_labels_900.pkl', 'rb')
+ref_labels_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_inf_labels_900_opt.pkl', 'rb')
+inf_labels_900_opt = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_inf_label_900.pkl', 'rb')
+inf_labels_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+"""
+# chi squared
+
+xp=0
+
+old = np.sum((tr_label[:,xp]-inf_labels_tr[:,xp])**2)
+opt = np.sum((tr_label[:,xp]-inf_labels_tr_opt[:,xp])**2)
+
+print(old,opt)
+
+
+plt.plot(tr_label[:,xp],inf_labels_tr[:,xp],"ro")
+plt.plot(tr_label[:,xp],inf_labels_tr_opt[:,xp],"go")
+plt.show()
+
+
+
+"""
+
+# chi-squared:
+
+xp=0
+
+old = np.sum((ref_labels_900[:,xp]-inf_labels_900[:,xp])**2)
[…]

### 2016-11-20 paper/ms.tex
Add new feature
Optimize inferred labels by using six-label model (add a b and c to the
labels)

@@
 Working on it...
-I think one possible way is to use the velocities correction for the APOGEE data obtained from the spectrum calibration section. Then the optimized APOGEE spectrum can be represented as:
-You should look into the velocities and find a right way to describe them.
+
+To optimize the inferred labels, we can add a, b and c to the training set labels.
+First, calculate a, b and c for the 548 training set stars.
+Then, treat these a b and c as three new labels and re-train this new six-label model with these stars.
+After the training step, infer labels (Which we call optimized inferred labels) by using the new model and compare the results with the old inferred labels.
+The advantage of this change is that the model becomes better without adding new labels. This is a pure data-driven model.
+
+We will introduce this in Experiment 5.
 
@@
 
+\subsection{\label{sec:level2}Experiment 5}
+
+Optimize the inferred labels by using the new model, which include a, b and c in the training set.
+First, we obtain a b and c for the 548 stars in the training set, then treat them as three new labels.
+After that, we train this new six-label model with these 548 stars.
+\bigskip
+
+To check whether this change works, we infer labels for the 614 stars in Experiment 2 by using two methods.
+The first method is to infer labels with the old model, which has three labels $Teff$, $Log g $ and $Fe/H$.
+We call the inferred labels from the old model as $inf_{label}^{old}$.
+
+The second method is to generate labels by using the new six-label ($Teff$, $Log g $, $Fe/H$, $a$, $b$ and $c$) model and we call these inferred labels as $inf_{label}^{new}$.
+
+Finally, we plot the inferred labels against the reference label in figure 11,12 and 13.
+
+\includegraphics[width=170mm]{figure_11.png}
+\bigskip
+
+\centerline{Fig.11 1-1 plot of label $Teff$}
+\bigskip
+
+\includegraphics[width=170mm]{figure_12.png}
+\bigskip
+
+\centerline{Fig.12 1-1 plot of label $logg$}
+\bigskip
+
+\includegraphics[width=170mm]{figure_13.png}
+\bigskip
+
+\centerline{Fig.13 1-1 plot of label $Fe/H$}
+\bigskip
+
+From these plots, we can conclude that the chi-squared of the inferred labels is smaller if we use the new model.
+
+The training time of the new six-label mode is about 7 times longer.
+But infer labels from the spectrum by using the new model is very quick, which means it's possible for us to apply this model for all stars in the APOGEE DR10.
+
  %% Fourth paragraph

### 2016-11-20 1120_plot_check_training_abc.py
Better plot

@@ -7,6 +7,7 @@ import matplotlib.pyplot as plt
 import pickle
 import matplotlib.pyplot as plt
 import matplotlib
+import matplotlib as mpl
 
 import AnniesLasso_2 as tc
 import time
@@ -50,30 +51,19 @@ pkl_file = open('n_inf_label_900.pkl', 'rb')
 inf_labels_900 = pickle.load(pkl_file)
 pkl_file.close()
 
+pkl_file = open('n_testing_ivar_900.pkl', 'rb')
+testing_ivar_900 = pickle.load(pkl_file)
+pkl_file.close()
 
+ivar= np.mean(testing_ivar_900,axis=1)
+ivar = np.array(ivar)
 
-"""
-# chi squared
-
-xp=0
-
-old = np.sum((tr_label[:,xp]-inf_labels_tr[:,xp])**2)
-opt = np.sum((tr_label[:,xp]-inf_labels_tr_opt[:,xp])**2)
-
-print(old,opt)
-
-
-plt.plot(tr_label[:,xp],inf_labels_tr[:,xp],"ro")
-plt.plot(tr_label[:,xp],inf_labels_tr_opt[:,xp],"go")
-plt.show()
-
-
-
-"""
 
 # chi-squared:
 
-xp=0
+# chi squared
+
+xp=2
 
 old = np.sum((ref_labels_900[:,xp]-inf_labels_900[:,xp])**2)
 opt = np.sum((ref_labels_900[:,xp]-inf_labels_900_opt[:,xp])**2)
@@ -81,7 +71,38 @@ opt = np.sum((ref_labels_900[:,xp]-inf_labels_900_opt[:,xp])**2)
 print(old,opt)
 
 
-plt.plot(ref_labels_900[:,xp],inf_labels_900[:,xp],"ro")
-plt.plot(ref_labels_900[:,xp],inf_labels_900_opt[:,xp],"go")
+
+
+
+
+font = {'weight': 'bold','size': 20}
+mpl.rc('font', **font)
+fig = plt.figure()
+
+
+# ax1 = fig.add_axes([0.10, 0.1, 0.85, 1])
+
+plt.scatter(ref_labels_900[:,xp],inf_labels_900_opt[:,xp], marker='x',  c=ivar,
+                    vmin=10000, vmax=40000, alpha=0.5,label = "inf_label_opt chi-squared = %.f"%opt)
+
[…]

### 2016-11-25 plot_class_4_star_v2_1107.py
bug fixed(star names)

@@ -258,7 +258,7 @@ class plot_4:
 
         # Don't use this
         # plt.setp([a.get_xticklabels() for a in f.axes[:-1]], visible=False)
-        
+
         plt.show()
         #f.savefig(delta_para_1+".png",dpi=400,papertype = "a4")
 
@@ -626,6 +626,202 @@ class plot_4:
 
         # ax3
 
+        ax3.step(wl, nor[p2, :], "k", label=l2, alpha=1, linewidth=1.5)
+        ax3.errorbar(wl, nor[p2, :], ecolor='k', alpha=trans / 10, capthick=0.2, yerr=error[p1, :])
+        ax3.plot(wl, inf_opt[p2, :], "r", alpha=trans, linewidth=1.5)
+        ax3.plot(wl, inf_old[p2, :], "g", alpha=trans, linewidth=1.5)
+
+        ax3.legend(bbox_to_anchor=(0, 0.65), loc=3,
+                   ncol=1)
+        ax3.set_xlim([15660, 15780])
+        ax3.set_ylim([0.8, 1.2])
+        ax3.set_yticks(np.arange(0.8, 1.2, 0.1))
+
+        fig.suptitle('Comparison of the spectrum', fontsize=30, horizontalalignment="center")
+
+        # ax4
+
+        ax4.step(wl, nor[p2, :], "k", label=delta_para_2, alpha=1, linewidth=1.5)
+        ax4.errorbar(wl, nor[p2, :], ecolor='k', alpha=trans / 10, capthick=0.2, yerr=error[p1, :])
+        ax4.plot(wl, inf_opt[p2, :], "r", alpha=trans, linewidth=1.5)
+        ax4.plot(wl, inf_old[p2, :], "g", alpha=trans, linewidth=1.5)
+
+        ax4.legend(bbox_to_anchor=(0, 0.65), loc=3,
+                   ncol=1)
+        ax4.set_xlim([16160, 16280])
+        ax4.set_ylim([0.8, 1.2])
+        ax4.set_yticks(np.arange(0.8, 1.2, 0.1))
+
+        fig.suptitle('Comparison of the spectrum', fontsize=30, horizontalalignment="center")
+
+        # ax5
+
+        ax5.step(wl, nor[p3, :], "k", label=l3, alpha=1, linewidth=1.5)
+        ax5.errorbar(wl, nor[p3, :], ecolor='k', alpha=trans / 10, capthick=0.2, yerr=error[p1, :])
[…]

### 2016-11-25 1121_plot_choose_4_stars.py
plot the selected 4 stars

@@ -1,0 +1,396 @@
+from numpy import genfromtxt
+import matplotlib.pyplot as plt
+import random
+import matplotlib
+import numpy as np
+import pickle
+from astropy.table import Table
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import AnniesLasso_2 as tc
+
+import plot_class_4_star_v2_1107
+
+
+
+
+
+
+
+
+# import data
+pkl_file = open('n_delta_chi_900.pkl', 'rb')
+delta_chi_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+pkl_file = open('n_testing_labels_900.pkl', 'rb')
+test_labels_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_parameters_900.pkl', 'rb')
+parameters_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_FiberID_900.pkl', 'rb')
+FiberID = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_tr_ID_900.pkl', 'rb')
+tr_ID_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_inf_label_900.pkl', 'rb')
+inf_labels_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("testing_set_900.pkl", 'rb')
+testing_set = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# flux,ivar and error
+
+pkl_file = open("n_testing_flux_900.pkl", 'rb')
+testing_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_ivar_900.pkl", 'rb')
+testing_ivar = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_inf_flux_900.pkl", 'rb')
+inf_flux_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_error_900.pkl", 'rb')
+testing_error = pickle.load(pkl_file)
+pkl_file.close()
+
+
+## check error
+"""
+plt.plot(testing_error[1,:],"r")
+
+axes = plt.gca()
+
+axes.set_ylim([-0.01,0.01])
+
+
+plt.show()
+
+"""
+
[…]

### 2016-11-25 paper/ms.tex
interpret a, b c and check the validity of the normalization

--- 2016-11-18 paper/ms.tex
@@
 
+\subsection{\label{sec:level2} Interpret a, b, c in terms of radial velocity}
+
+%Can you interpret a, b, c in terms of radial velocity? If so, how?
+After we obtain a, b and c for these stars, we can calibrate the errors in the radial velocities of the combined spectra for these stars.
+These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit.
+The apStar files also include the individual visit spectra, resampled and shifted to rest wavelength.
+If we need to use the individual visits before resampling, apVisit files are needed.
+The velocity calibration information is also in apVisits files.
+In our experiment, we use the resampled spectrum of each visit in Apstar file.
+
+Consider Relativistic Doppler effect. the redshift factor is defined as z. The radial velocities of the stars are much smaller than c, so we have:
+
+\begin{equation}
+z = {{\lambda_0 - \lambda_s} \over \lambda_s} = \sqrt{{1+\beta} \over {1-\beta}} -1 \approx \beta
+\end{equation}
+Where $\beta ={ v \over c} $. $\lambda_0$ and $\lambda_s$ are the wave lengths measured at the observer and the source.
+
+The APOGEE team determine the radial velocities of the stars by two steps.
+\bigskip
+\\
+1. Estimate the radial velocity of each visit by cross-correlating the visit spectrum against a grid of synthetic spectra.
+\\
+2. Compare the spectrum of each visit with the combined spectrum and re-derive the radial velocity for each visit iteratively.
+
+After obtaining the velocity, we can use the de-Doppler wavelengths and resample the spectrum onto the final logarithmically-spaced wavelength scale using sinc interpolation.
+Finally, generate combined spectrum by using spectrum of different visits.
+The data spectrum we use in experiment 1 to 4 is the combined spectrum and we start to use spectrum of each visit in experiment 5.
+
+The radial velocity is related to parameter a, b and c.
+First, we need to assume that the inferred spectrum is set at rest, which means the radial velocity of it is zero.
+Second, we think the radial velocity of the data spectrum is equal to the radial velocity of the optimized spectrum.
+This is because the optimized spectrum is obtained by fitting to the data spectrum.
+First, we set the radial velocity to be positive if the star is leaving us.
+If a=1, b=0 and c=0, the optimized spectrum moves one pixel left from the inferred spectrum, which means the data spectrum should move one pixel right and the radial velocity of the data spectrum is not zero and it has a blue shift.
+Thus the radial velocity is negative and can be obtained by using (8).
+It's more convenient to use the logarithmic wavelength.
+\begin{equation}
+\log_{10}\lambda_0 - \log_{10}\lambda_s = \log_{10}(1+\beta)
+\end{equation}
+
+All spectrum in Apstar files are set to the same wavelength scale.
+The wavelength start at 15100.802 $\AA$ and the logarithmic wavelength grid spacing between two pixels is $6*10^{-6}$.
+By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if a=1 b= 0 and c=0, the radial velocity deviation in the APOGEE data is $-4144.68 m/s$
+
+Thus we can use a, b and c to determine the radial velocity correction for each visits of the APOGEE data.
+\begin{equation}
+v_{deviation} = (c-a)*v_{pixel}
+\end{equation}
+Where $v_{deviation}$ is the deviation of the APOGEE data and $v_{pixel}$ =  4144.68 m/s.
+
+Before we obtain a, b and c for each visit, we need to continuum-normalize the spectrum of each visit.
+The spectrum for each visit we use are in apstar files, which are already resampled to the sample wavelength scale with 8575 pixels.
+The method we use is the same as the one in Ness et al 2015.
+First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]].
+Then, do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance.
+Third, put a mask on the spectrum.
+Finally, fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.
+
+To check whether it works, we can infer labels by using these normalized visit. If the inferred labels from each visit are similar, the normalization works. 
+The details are in experiment 5.
+
+\subsection{\label{sec:level2} Obtain new information from the individual exposures}
+
+%How do you continuum-normalize the individual exposures, and can you demonstrate to me that your proposal of how to do that is working well?
+
 \subsection{\label{sec:level2}Optimize Teff , log g and [Fe/H] simultaneously with a, b, c}
@@
 Working on it...
-I think one possible way is to use the velocities correction for the APOGEE data obtained from the spectrum calibration section. Then the optimized APOGEE spectrum can be represented as:
-You should look into the velocities and find a right way to describe them.
 
@@
 
+\subsection{\label{sec:level2}Experiment 5}
+
+Here we choose the four stars with biggest a-c and obtain the radial velocity correction.
+The spectrum we use are the combined spectrum for these four stars.
+Then we derive their radial velocities correction and de-Doppler the wavelength.
+Use Sinc interpolation to resample them onto the same wavelength scale and obtain the calibrated spectrum.
+The wavelength scale is the same as the one in Apstar file.
+Finally, plot the data spectrum and the calibrated spectrum in figure 11.
+
+\includegraphics[width=170mm]{figure_11.png}
+\bigskip
+
+\centerline{Fig.11 Comparison of the calibrated spectrum and the data spectrum}
+\bigskip
+
+After that, we want to calibrate the spectrum for each visit.
+Choose the first star in figure 11 and normalize all visits for it.
+Then, plot them in figure 12.
+To check whether our normalization works, infer labels for each visit and compare them.
+If our normalization works, the inferred labels of each visit should be similar to each other.
+
+\includegraphics[width=170mm]{figure_12.png}
+\bigskip
+
+\centerline{Fig.12 Comparison of each visit for star XXR}
+\bigskip
+
+We also plot the histogram which shows the deviations of the inferred labels for each visits from the ones for combined spectrum.
+The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum.
+The data we use is the 614 stars in experiment 1 to 4.
+If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.
+
+\includegraphics[width=170mm]{figure_13.png}
+\bigskip
+
+\centerline{Fig.13 Histogram for the deviations of the inferred labels}
+\bigskip
+
+plot the correct radial velocity spetrum by using sinc interpolation
+plot the inferred labels plot the normalized spectrum for each apvisit and compare
+plot histogram of the deviation for inf labels for each visits.
+
  %% Fourth paragraph

### 2016-11-26 paper/ms.tex
Add validity of the normalization

@@
 
-To check whether it works, we can infer labels by using these normalized visit. If the inferred labels from each visit are similar, the normalization works. 
-The details are in experiment 5.
+To check whether it works, we can infer labels by using these normalized visit.
+If the inferred labels from each visit are similar, the normalization works.
+The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum and we define them as $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H.
+
+\begin{equation}
+\triangle Teff = Teff_{inf}^{vs} - Teff_{inf}^{cb}
+\end{equation}
+
+$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred labels for each visit and the combined spectrum.
+
+If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works. The details are in experiment 5.
 
@@
 
-\centerline{Fig.11 Comparison of the calibrated spectrum and the data spectrum}
+\centerline{Fig.11 Comparison of the calibrated spectrum and the data spectrum for the four stars with biggest a-c}
+
+\centerline{ The black line is the data spectrum. The green line is the inferred spectrum and the red line is the calibrated data spectrum}
 \bigskip
 
-After that, we want to calibrate the spectrum for each visit.
-Choose the first star in figure 11 and normalize all visits for it.
-Then, plot them in figure 12.
-To check whether our normalization works, infer labels for each visit and compare them.
-If our normalization works, the inferred labels of each visit should be similar to each other.
+We do the same thing four the four stars with biggest c-a.
 
@@
 
-\centerline{Fig.12 Comparison of each visit for star XXR}
+\centerline{Fig.12 Comparison of the calibrated spectrum and the data spectrum for the four stars with biggest c-a.}
+
+\centerline{ The black line is the data spectrum. The green line is the inferred spectrum and the red line is the calibrated data spectrum}
 \bigskip
 
-We also plot the histogram which shows the deviations of the inferred labels for each visits from the ones for combined spectrum.
-The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum.
+After that, we want to calibrate the spectrum for each visit.
+To begin with, we need to check whether our normalization works.
+The method is to infer labels for each visit and compare them.
+If our normalization works, the inferred labels from each visit for the same star should be similar to each other.
+We plot the histogram which shows the deviations of the inferred labels of each visits from the ones of combined spectrum for the same star.
+The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum and we define them as $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H.
 The data we use is the 614 stars in experiment 1 to 4.
@@
 
-\centerline{Fig.13 Histogram for the deviations of the inferred labels}
+\centerline{Fig.13 Histogram for Delta Teff}
 \bigskip
 
-plot the correct radial velocity spetrum by using sinc interpolation
-plot the inferred labels plot the normalized spectrum for each apvisit and compare
-plot histogram of the deviation for inf labels for each visits.
+\includegraphics[width=170mm]{figure_14.png}
+\bigskip
+
+\centerline{Fig.14 Histogram for Delta logg}
+
+\bigskip
+
+\includegraphics[width=170mm]{figure_15.png}
+\bigskip
+
+\centerline{Fig.15 Histogram for Delta Fe/H}
+\bigskip
+
+We can see that most of the deviations are close to 0, which means our normalization for each visit doesn't make the spectrum distort.
 
@@
 
-Comparison of the spectrum if we set the parameters shown in old figure 8. In old figure 8, the red line and the green line are on the top of each other
- \bigskip
-
-\includegraphics[width=170mm]{d_figure_2.png}
-\bigskip
-
-\centerline{Diagnostic Fig.2 Comparison of the spectrum if we set the parameters shown in old figure 8}
-\bigskip
-
- Comparison of the spectrum if we set the parameters shown in old figure 9. In old figure 9, the difference between red line and the green line is too big if we consider their parameters.
- \bigskip
-
-\includegraphics[width=170mm]{d_figure_3.png}
-\bigskip
-
-\centerline{Diagnostic Fig.3 Comparison of the spectrum if we set the parameters shown in old figure 9}
-\bigskip
-
- If we want a plot like old figure 9, we can manually set a=0.5, b=1 and c= -0.5. Here a+b+c is not equal to 1 and this is the cause of the offset.
- \bigskip
-
-\includegraphics[width=170mm]{d_figure_4.png}
-\bigskip
-
-\centerline{Diagnostic Fig.4 Comparison of the spectrum if we want a big difference between the red line and the green line}
-\bigskip
-
-In diagnostic plot 5, I use four fake stars.
-The data spectra of these four stars are generated by moving their inferred spectra one pixel left.
-If my new code is right, a, b and c will be [1,0,0].
-In diagnostic figure 5, a=1, b=0 and c=0.
-\bigskip
-
-\includegraphics[width=170mm]{d_figure_5.png}
-\bigskip
-
-\centerline{Diagnostic Fig.5 Comparison of the spectrum for the four fake stars}
-\bigskip
-
 \end{document}

### 2016-11-26 paper/ms.tex
interpret a, b and c

@@
 
-\subsection{\label{sec:level2} Interpret a, b, c in terms of radial velocity}
+\subsection{\label{sec:level2} Interpret a, b, c in term of radial velocity}
 
 %Can you interpret a, b, c in terms of radial velocity? If so, how?
-After we obtain a, b and c for these stars, we can calibrate the errors in the radial velocities of the combined spectra for these stars.
+After obtaining a, b and c for these stars, we can calibrate the errors in the radial velocities of the combined spectra for these stars.
 These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit.
@@
 If we need to use the individual visits before resampling, apVisit files are needed.
-The velocity calibration information is also in apVisits files.
-In our experiment, we use the resampled spectrum of each visit in Apstar file.
-
-Consider Relativistic Doppler effect. the redshift factor is defined as z. The radial velocities of the stars are much smaller than c, so we have:
-
-\begin{equation}
-z = {{\lambda_0 - \lambda_s} \over \lambda_s} = \sqrt{{1+\beta} \over {1-\beta}} -1 \approx \beta
-\end{equation}
-Where $\beta ={ v \over c} $. $\lambda_0$ and $\lambda_s$ are the wave lengths measured at the observer and the source.
-
+In our experiment, we use the resampled spectrum in Apstar file.
+The radial velocities of the spectrum in Apstar files should be 0, but in fact they are not.
+This is because of the errors in radial velocity measurement by the APOGEE team.
 The APOGEE team determine the radial velocities of the stars by two steps.
@@
 2. Compare the spectrum of each visit with the combined spectrum and re-derive the radial velocity for each visit iteratively. 
+\bigskip
 
-After obtaining the velocity, we can use the de-Doppler wavelengths and resample the spectrum onto the final logarithmically-spaced wavelength scale using sinc interpolation.
+After obtaining the velocities, the APOGEE team use the de-Doppler wavelengths and resample the spectrum onto the final logarithmically-spaced wavelength scale using sinc interpolation.
 Finally, generate combined spectrum by using spectrum of different visits.
+Both combined spectrum and each visit may have radial velocity errors because the synthetic spectra are not perfect.
+
+We will derive these radial velocity errors, then de-Doppler them and resample the fluxes onto a common, logarithmically-spaced wavelength scale, which is the same as the wavelength scale in Apstar and ASPCAP flies.
+
+Consider Relativistic Doppler effect. the redshift factor is defined as z. The velocity is positive if the star is leaving us. The radial velocities of the stars are much smaller than c, so we have:
+
+\begin{equation}
+z = {{\lambda_0 - \lambda_s} \over \lambda_s} = \sqrt{{1+\beta} \over {1-\beta}} -1 \approx \beta
+\end{equation}
+Where $\beta ={ v \over c} $. $v$ is the radial velocity. $\lambda_0$ and $\lambda_s$ are the wave lengths measured at the observer and the source.
+
 The data spectrum we use in experiment 1 to 4 is the combined spectrum and we start to use spectrum of each visit in experiment 5.
@@
 The radial velocity is related to parameter a, b and c.
-First, we need to assume that the inferred spectrum is set at rest, which means the radial velocity of it is zero.
+First, we need to assume that the inferred spectrum generated by the Cannon is set at rest, which means the radial velocity of it is zero.
 Second, we think the radial velocity of the data spectrum is equal to the radial velocity of the optimized spectrum.
-This is because the optimized spectrum is obtained by fitting to the data spectrum.
-First, we set the radial velocity to be positive if the star is leaving us.
+This is because the optimized spectrum is obtained by fitting the inferred spectrum to the data spectrum.
+\bigskip
+
+To begin with, we set the radial velocity to be positive if the star is leaving us.
 If a=1, b=0 and c=0, the optimized spectrum moves one pixel left from the inferred spectrum, which means the data spectrum should move one pixel right and the radial velocity of the data spectrum is not zero and it has a blue shift.
@@
 The wavelength start at 15100.802 $\AA$ and the logarithmic wavelength grid spacing between two pixels is $6*10^{-6}$.
-By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if a=1 b= 0 and c=0, the radial velocity deviation in the APOGEE data is $-4144.68 m/s$
+By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if a=1 b= 0 and c=0, the radial velocity error in the APOGEE data is $-4144.68 m/s$
 
-Thus we can use a, b and c to determine the radial velocity correction for each visits of the APOGEE data.
+Thus we can use a, b and c to determine the radial velocity correction for the combined spectrum and each visit of the APOGEE data.
 \begin{equation}
@@
 
-Before we obtain a, b and c for each visit, we need to continuum-normalize the spectrum of each visit.
-The spectrum for each visit we use are in apstar files, which are already resampled to the sample wavelength scale with 8575 pixels.
+%How do you continuum-normalize the individual exposures, and can you demonstrate to me that your proposal of how to do that is working well?
+
+Before deriving a, b and c for each visit, we need to continuum-normalize the spectrum of each visit.
+This is because the absolute value of each visit is different.
+Therefore, each visit spectrum needs to be roughly continuum normalized before they are combined.
+The APOGEE team use a median filter to continuum-normalize the spectrum of each visit.
+\bigskip
+
 The method we use is the same as the one in Ness et al 2015.
-First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]].
+The spectrum for each visit we use are in Apstar files, which are already resampled to the sample wavelength scale with 8575 pixels.
+First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum.
 Then, do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance.
@@
 Finally, fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.
+Our method is different from the one used by the APOGEE team and we will demonstrate it works.
 
-To check whether it works, we can infer labels by using these normalized visit.
+To check whether it works, we can infer labels by using the normalized flux of each visit.
 If the inferred labels from each visit are similar, the normalization works.
-The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum and we define them as $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H.
+We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:
 
 \begin{equation}
-\triangle Teff = Teff_{inf}^{vs} - Teff_{inf}^{cb}
+\triangle Teff = Teff_{inf}^{vs} - {Teff}_{inf}^{cb}
 \end{equation}
 
-$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred labels for each visit and the combined spectrum.
+\begin{equation}
+\triangle logg = logg_{inf}^{vs} - logg_{inf}^{cb}
+\end{equation}
 
-If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works. The details are in experiment 5.
+\begin{equation}
+\triangle Fe/H = Fe/H_{inf}^{vs} - Fe/H_{inf}^{cb}
+\end{equation}
+
+$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred Teff for each visit and the combined spectrum. It's similar for $logg$ and $Fe/H$
+
+If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.
+
+Also, we can look at the normalized spectrum of each visit. If the absolute value of normalized flux for each visit is similar to each other, the normalization works.
+
+The details are in experiment 5.
 
@@
 
-%How do you continuum-normalize the individual exposures, and can you demonstrate to me that your proposal of how to do that is working well?
+After calibrate the radial velocity, we can re-generate fluxes in Apstar files by using Apvisit files. The interpolation method we use is Sinc interpolation.
 
@@
 
-Here we choose the four stars with biggest a-c and obtain the radial velocity correction.
-The spectrum we use are the combined spectrum for these four stars.
-Then we derive their radial velocities correction and de-Doppler the wavelength.
+Here we choose the four stars with biggest a-c and obtain the radial velocity corrections for them.
+The spectrum we use are continuum-normalized combined spectrum for these four stars.
+Then we derive their radial velocity corrections and de-Doppler the wavelengths.
 Use Sinc interpolation to resample them onto the same wavelength scale and obtain the calibrated spectrum.
-The wavelength scale is the same as the one in Apstar file.
+The wavelength scale is the same as the one in Apstar file, which is described in the former section.
 Finally, plot the data spectrum and the calibrated spectrum in figure 11.
@@
 After that, we want to calibrate the spectrum for each visit.
-To begin with, we need to check whether our normalization works.
-The method is to infer labels for each visit and compare them.
-If our normalization works, the inferred labels from each visit for the same star should be similar to each other.
-We plot the histogram which shows the deviations of the inferred labels of each visits from the ones of combined spectrum for the same star.
-The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum and we define them as $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H.
+To begin with, we need to check whether our normalization works in each visit.
+The method is to infer labels for each visit and compare them with the ones from the combined spectrum.
+If our normalization works, the inferred labels from each visit for the same star should be similar to the ones from the combined spectrum.
+We plot the histogram which shows the deviations of the inferred labels of each visits from the ones generated by the combined spectrum for the same star.
 The data we use is the 614 stars in experiment 1 to 4.
@@
 
+In figure 16, we plot the continuum-normalized fluxes of all visits for the first star in figure 8.
+There are 9 individual visits.
+We can see that the absolute value of the flux for each visit is similar to each other, which means our normalization works.
+
+\includegraphics[width=170mm]{figure_16.png}
+\bigskip
+
+\centerline{Fig.16 Comparison of each visit for the first star in figure 8.}
+\bigskip
+
  %% Fourth paragraph

### 2016-11-26 paper/ms.tex
grammar check

@@
 %Can you interpret a, b, c in terms of radial velocity? If so, how?
-After obtaining a, b and c for these stars, we can calibrate the errors in the radial velocities of the combined spectra for these stars.
+After obtaining a, b and c for these stars, we can calibrate the errors in the radial velocities of the combined spectra of these stars.
 These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit.
@@
 If we need to use the individual visits before resampling, apVisit files are needed.
-In our experiment, we use the resampled spectrum in Apstar file.
+In our experiment, we use the resampled spectrum in Apstar files.
 The radial velocities of the spectrum in Apstar files should be 0, but in fact they are not.
 This is because of the errors in radial velocity measurement by the APOGEE team.
-The APOGEE team determine the radial velocities of the stars by two steps.
+The APOGEE team determines the radial velocities of the stars by two steps.
 \bigskip
@@
 
-After obtaining the velocities, the APOGEE team use the de-Doppler wavelengths and resample the spectrum onto the final logarithmically-spaced wavelength scale using sinc interpolation.
-Finally, generate combined spectrum by using spectrum of different visits.
+After obtaining the velocities, the APOGEE team uses the de-Doppler wavelengths and resample the spectrum onto the final logarithmically-spaced wavelength scale by using sinc interpolation.
+Finally, generate the combined spectrum by using the spectrums of different visits.
 Both combined spectrum and each visit may have radial velocity errors because the synthetic spectra are not perfect.
@@
 
-Consider Relativistic Doppler effect. the redshift factor is defined as z. The velocity is positive if the star is leaving us. The radial velocities of the stars are much smaller than c, so we have:
+Consider Relativistic Doppler effect. The redshift factor is defined as z. The radial velocity is positive if the star is leaving us.
 
@@
 
-The radial velocity is related to parameter a, b and c.
+The radial velocity is related to parameters a, b and c.
 First, we need to assume that the inferred spectrum generated by the Cannon is set at rest, which means the radial velocity of it is zero.
@@
 If a=1, b=0 and c=0, the optimized spectrum moves one pixel left from the inferred spectrum, which means the data spectrum should move one pixel right and the radial velocity of the data spectrum is not zero and it has a blue shift.
-Thus the radial velocity is negative and can be obtained by using (8).
+Thus the radial velocity correction is negative and can be obtained by using (8).
 It's more convenient to use the logarithmic wavelength.
@@
 
-All spectrum in Apstar files are set to the same wavelength scale.
+All spectrums in Apstar files are set to the same wavelength scale.
 The wavelength start at 15100.802 $\AA$ and the logarithmic wavelength grid spacing between two pixels is $6*10^{-6}$.
@@
 Therefore, each visit spectrum needs to be roughly continuum normalized before they are combined.
-The APOGEE team use a median filter to continuum-normalize the spectrum of each visit.
+The APOGEE team uses a median filter to continuum-normalize the spectrum of each visit.
 \bigskip
 
-The method we use is the same as the one in Ness et al 2015.
-The spectrum for each visit we use are in Apstar files, which are already resampled to the sample wavelength scale with 8575 pixels.
+Our method is the same as the one in Ness et al 2015.
+The spectrum for each visit is in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
 First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum.
@@
 
-To check whether it works, we can infer labels by using the normalized flux of each visit.
-If the inferred labels from each visit are similar, the normalization works.
+To check whether it works, we can look at the normalized spectrum of each visit. If the absolute value of the normalized flux for each visit is similar to each other, the normalization works.
+
+Also, we can infer labels by using the normalized flux of each visit.
+If the inferred labels from each visit are similar to the ones from the combined spectrum, the normalization works.
 We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:
@@
 If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.
-
-Also, we can look at the normalized spectrum of each visit. If the absolute value of normalized flux for each visit is similar to each other, the normalization works.
 
@@
 Here we choose the four stars with biggest a-c and obtain the radial velocity corrections for them.
-The spectrum we use are continuum-normalized combined spectrum for these four stars.
+The spectrum we use are continuum-normalized combined spectrum of these four stars.
 Then we derive their radial velocity corrections and de-Doppler the wavelengths.
@@
 If our normalization works, the inferred labels from each visit for the same star should be similar to the ones from the combined spectrum.
-We plot the histogram which shows the deviations of the inferred labels of each visits from the ones generated by the combined spectrum for the same star.
+We plot the histogram which shows the deviations of the inferred labels of each visit from the ones generated by the combined spectrum of the same star.
 The data we use is the 614 stars in experiment 1 to 4.

### 2016-11-26 1125_plot_4_calibrated_flux.py
spectrum calibration

@@ -1,0 +1,515 @@
+from numpy import genfromtxt
+import matplotlib.pyplot as plt
+import random
+import matplotlib
+import numpy as np
+import pickle
+from astropy.table import Table
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import AnniesLasso_2 as tc
+
+import plot_class_4_star_v2_1107
+
+
+
+
+
+
+
+
+# import data
+pkl_file = open('n_delta_chi_900.pkl', 'rb')
+delta_chi_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+pkl_file = open('n_testing_labels_900.pkl', 'rb')
+test_labels_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_parameters_900.pkl', 'rb')
+parameters_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_FiberID_900.pkl', 'rb')
+FiberID = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_tr_ID_900.pkl', 'rb')
+tr_ID_500 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('n_inf_label_900.pkl', 'rb')
+inf_labels_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("testing_set_900.pkl", 'rb')
+testing_set = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# flux,ivar and error
+
+pkl_file = open("n_testing_flux_900.pkl", 'rb')
+testing_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_ivar_900.pkl", 'rb')
+testing_ivar = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_inf_flux_900.pkl", 'rb')
+inf_flux_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open("n_testing_error_900.pkl", 'rb')
+testing_error = pickle.load(pkl_file)
+pkl_file.close()
+
+
+## check error
+"""
+plt.plot(testing_error[1,:],"r")
+
+axes = plt.gca()
+
+axes.set_ylim([-0.01,0.01])
+
+
[…]

### 2016-11-26 1125_plot_histogram_deviation_inf_labels.py

@@ -1,0 +1,72 @@
+import pickle
+import matplotlib
+import matplotlib.pyplot as plt
+
+
+# read data
+
+pkl_file = open('inf_labels_deviation_teff_900.pkl', 'rb')
+inf_labels_deviation_teff_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('inf_labels_deviation_logg_900.pkl', 'rb')
+inf_labels_deviation_logg_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('inf_labels_deviation_fe_900.pkl', 'rb')
+inf_labels_deviation_fe_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# plot histogram
+
+
+"""
+font = {'weight': 'bold','size': 30}
+matplotlib.rc('font', **font)
+fig = plt.figure()
+
+
+
+colors = ['b', 'g', 'r']
+name = ["Delta Teff","Delta logg","Delta Fe/H"]
+print(inf_labels_deviation_teff_900.shape,inf_labels_deviation_logg_900.shape,inf_labels_deviation_fe_900.shape)
+
+# Plot histogram
+fig = plt.figure()
+plt.hist(inf_labels_deviation_teff_900,bins=15,color=colors[0],label=name[0])
+plt.legend(prop={'size': 30})
+fig.suptitle('Histogram for the deviations of the inferred Teff',fontsize =30)
+plt.xlabel('values of Delta Teff', fontsize=30)
+plt.ylabel('Number of stars', fontsize=30)
+plt.show()
+
+
+colors = ['b', 'g', 'r']
+name = ["Delta Teff","Delta logg","Delta Fe/H"]
+
+# Plot histogram
+fig = plt.figure()
+plt.hist(inf_labels_deviation_logg_900,bins=15,color=colors[1],label=name[1])
+plt.legend(prop={'size': 30})
+fig.suptitle('Histogram for the deviations of the inferred logg',fontsize =30)
+plt.xlabel('values of Delta logg', fontsize=30)
+plt.ylabel('Number of stars', fontsize=30)
+plt.show()
+"""
+
+
+colors = ['b', 'g', 'r']
+name = ["Delta Teff","Delta logg","Delta Fe/H"]
+
+# Plot histogram
+fig = plt.figure()
+plt.hist(inf_labels_deviation_fe_900,bins=15,color=colors[2],label=name[2])
[…]

### 2016-11-26 1125_read_apstar_flux.py

@@ -1,0 +1,251 @@
+import TheCannon_2
+from TheCannon_2 import dataset,apogee
+from astropy.table import Table
+import numpy as np
+import os
+from astropy.io import fits
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib
+import AnniesLasso_2 as tc
+
+
+# function
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+def get_error_mask(err):
+    bad_err = (~np.isfinite(err))
+    bad_pixels = bad_err
+    return bad_pixels
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+# read data
+
+# open the choose file
+pkl_file = open('n_tr_ID_900.pkl', 'rb')
+tr_ID_900 = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+
+# train the model:
+
+training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
+training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
+
+
+training_set = Table.read("reference_labels.csv")
+
+
+
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+
+N = len(training_set)
+keep = np.ones(N, dtype=bool)
+
+training_set_flux = []
+training_set_ivar = []
+training_set_error = []
+
+for i, row in enumerate(training_set):
+    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
+    if not os.path.exists(image_path):
+        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+        keep[i] = False
+        continue
+    print("{}/{}: {}".format(i + 1, N, image_path))
+    image = fits.open(image_path)
+    flux = image[1].data
+    flux_err = image[2].data
[…]

### 2016-11-26 paper/ms.tex
structure change

@@
 
+\subsection{\label{sec:level2} Obtain information from the individual exposures}
+
 %How do you continuum-normalize the individual exposures, and can you demonstrate to me that your proposal of how to do that is working well?
@@
 The details are in experiment 5.
-
-\subsection{\label{sec:level2} Obtain new information from the individual exposures}
-
-After calibrate the radial velocity, we can re-generate fluxes in Apstar files by using Apvisit files. The interpolation method we use is Sinc interpolation.
 

### 2016-11-26 plot_class_4_star_v2_1107.py
sinc interpolation

@@ -12,7 +12,45 @@ import os
 from astropy.io import fits
 import pickle
 import AnniesLasso_2 as tc
+import math
 
+
+
+def log10(x):
+    return math.log10(x)
+
+# sinc interpolation
+
+# Distance between s is equal and they are your raw data
+# u is what you want. Then length of u is not equal to s.
+
+def sinc_interp(x, s, u):
+    """
+    Interpolates x, sampled at "s" instants
+    Output y is sampled at "u" instants ("u" for "upsampled")
+    """
+
+    # Your x is the raw flux
+    # Your s is the wave length of the raw flux. s should have equal distance
+
+    # Your u is the log wl, which has equal distance between the neighborhoods.
+    # The length of u is 8575 and you can use log wl
+
+    if len(x) != len(s):
+        print("len(x) should be equal to len(s")
+
+    # Find the period
+    # T_r = s[1] - s[0]
+
+    # I don't think these two methods have a big different.
+
+    # Can we use this?
+    N = len(s)
+    T = (s[N-1]-s[0])/N
+
+    sincM = np.tile(u, (len(s), 1)) - np.tile(s[:, np.newaxis], (1, len(u)))
+    y = np.dot(x, np.sinc(sincM / T))
+    return y
 
 class plot_4:
     def __init__(self):
@@ -736,6 +774,8 @@ class plot_4:
         wl = pickle.load(pkl_file)
         pkl_file.close()
 
+
+
         all_set_flux = np.array(flux)
         all_set_ivar = np.array(ivar)
         all_set_error = np.array(error)
@@ -743,6 +783,7 @@ class plot_4:
 
         # plot
         nor = all_set_flux
+
         inf_old = inf_flux
 
         inf_opt, parameters_4 = self.model.fitting_spectrum_parameters_single(
@@ -751,6 +792,39 @@ class plot_4:
         error = all_set_error
 
         delta_chi = self.model.delta_chi_squared(all_set_flux, all_set_ivar, inf_flux)
+
+        ###########################
+        # Now calibrate the nor flux by using a b and c
[…]

### 2016-12-04 paper/ms.tex
Compare two methods
Compare two formula for radial velocity shifts

@@
 There will be N objective functions and N sets of a, b and c.
-So we introduce several matrix: $Y_n$, $A_n$, $C_n$ and $X_n$, which are defined as followed:
+So we introduce several matrix: $Y_n$, $A_n$, $C_n$ and $X_n$ for star n, which are defined as followed:
 
@@
 \begin{equation}
-X_n = [\sum_{n=1}^{n=N}A_n^TC_n^{-1}A]^{-1} \cdot [\sum_{n=1}^{n=N}A^TC_n^{-1}Y_n]
+X_n = [A_n^TC_n^{-1}A_n]^{-1} \cdot [A_n^TC_n^{-1}Y_n]
 \end{equation}
@@
 The spectrum we use is in apstar file.
-We will re-analyze the velocities after the optimization and deliver back the velocities correction for the APOGEE data.
+We will re-analyze the velocities after the optimization and deliver back the velocities shift for the APOGEE data.
 \bigskip
@@
 If a=1, b=0 and c=0, the optimized spectrum moves one pixel left from the inferred spectrum, which means the data spectrum should move one pixel right and the radial velocity of the data spectrum is not zero and it has a blue shift.
-Thus the radial velocity correction is negative and can be obtained by using (8).
+Thus the radial velocity shift is negative and can be obtained by using (8).
 It's more convenient to use the logarithmic wavelength.
@@
 
-Thus we can use a, b and c to determine the radial velocity correction for the combined spectrum and each visit of the APOGEE data.
+Thus we can use a, b and c to determine the radial velocity shift for the combined spectrum and each visit of the APOGEE data.
 \begin{equation}
-v_{deviation} = (c-a)*v_{pixel}
+v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}
 \end{equation}
-Where $v_{deviation}$ is the deviation of the APOGEE data and $v_{pixel}$ =  4144.68 m/s.
+Where $v_{shift}$ is the shift of the radial velocity in APOGEE data and $v_{pixel}$ =  4144.68 m/s.
+\bigskip
 
@@
 \centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+
 \bigskip
@@
 
-Here we choose the four stars with biggest a-c and obtain the radial velocity corrections for them.
-The spectrum we use are continuum-normalized combined spectrum of these four stars.
-Then we derive their radial velocity corrections and de-Doppler the wavelengths.
-Use Sinc interpolation to resample them onto the same wavelength scale and obtain the calibrated spectrum.
-The wavelength scale is the same as the one in Apstar file, which is described in the former section.
-Finally, plot the data spectrum and the calibrated spectrum in figure 11.
+Here we plot the histogram of the radial velocity shifts in figure 11 and the radial velocity shifts in figure 12. The data we use is the combined spectrums of the 614 stars in the former experiment.
 
@@
 
-\centerline{Fig.11 Comparison of the calibrated spectrum and the data spectrum for the four stars with biggest a-c}
-
-\centerline{ The black line is the data spectrum. The green line is the inferred spectrum and the red line is the calibrated data spectrum}
+\centerline{Fig.11 Histogram of the radial velocity shifts in combined spectrums for the 614 stars. }
+\centerline{We exclude the outliers which have velocity shifts bigger than 2000 m/s}
+\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
 \bigskip
-
-We do the same thing four the four stars with biggest c-a.
 
@@
 
-\centerline{Fig.12 Comparison of the calibrated spectrum and the data spectrum for the four stars with biggest c-a.}
-
-\centerline{ The black line is the data spectrum. The green line is the inferred spectrum and the red line is the calibrated data spectrum}
+\centerline{Fig.12 Radial velocity shifts for combined spectrums of the 614 stars against mean fiber number}
+\centerline{We exclude the outliers which have velocity shifts bigger than 2000 m/s}
+\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
 \bigskip
 
-After that, we want to calibrate the spectrum for each visit.
+We also plot the four stars with biggest radial velocity shifts, which are in figure 13.
+
+\includegraphics[width=170mm]{figure_13.png}
+\bigskip
+
+\centerline{Fig.13 Spectrum of the four stars with biggest radial velocity shifts.}
+
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+
+\bigskip
+
+\bigskip
+
+After that, we want to calibrate the radial velocity for each visit.
 To begin with, we need to check whether our normalization works in each visit.
@@
 
-\includegraphics[width=170mm]{figure_13.png}
-\bigskip
-
-\centerline{Fig.13 Histogram for Delta Teff}
-\bigskip
-
 \includegraphics[width=170mm]{figure_14.png}
@@
 
-\centerline{Fig.14 Histogram for Delta logg}
-
+\centerline{Fig.14 Histogram for Delta Teff}
 \bigskip
@@
 
-\centerline{Fig.15 Histogram for Delta Fe/H}
+\centerline{Fig.15 Histogram for Delta logg}
+
+\bigskip
+
+\includegraphics[width=170mm]{figure_16.png}
+\bigskip
+
+\centerline{Fig.16 Histogram for Delta Fe/H}
 \bigskip
@@
 
-\includegraphics[width=170mm]{figure_16.png}
+\includegraphics[width=170mm]{figure_17.png}
 \bigskip
 
-\centerline{Fig.16 Comparison of each visit for the first star in figure 8.}
+\centerline{Fig.17 Comparison of each visit for the first star in figure 8.}
 \bigskip
@@
 
+I plot the histogram of radial velocity shifts derived by using $v_{shift} = (c-a)*v_{pixel}$ in diagnostic figure 2 and velocity shifts against mean fiber number in diagnostic figure 3.
+
+\bigskip
+
+\includegraphics[width=170mm]{d_figure_2.png}
+\bigskip
+
+\centerline{Diagnostic Fig.2 Histogram of radial velocity shifts}
+\centerline{The formula to derive velocity shifts is $v_{shift} = (c-a)*v_{pixel}$}
+\bigskip
+
+\bigskip
+
+\includegraphics[width=170mm]{d_figure_3.png}
+\bigskip
+
+\centerline{Diagnostic Fig.3 Radial velocity shifts against mean fiber number}
+\centerline{The formula to derive velocity shifts is $v_{shift} = (c-a)*v_{pixel}$}
+\bigskip
+
+We also plot the four stars with biggest radial velocity shifts, which are in figure 13. The formula I use is $v_{shift} = (c-a)*v_{pixel}$.
+
+\includegraphics[width=170mm]{d_figure_4.png}
+\bigskip
+
+\centerline{Diagnostic Fig.4 Spectrum of the four stars with biggest radial velocity shifts.}
+
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+
+\bigskip
+
+The original histogram of radial velocity shifts for figure 11.
+\bigskip
+
+\includegraphics[width=170mm]{d_figure_5.png}
+\bigskip
+
+\centerline{Diagnostic Fig.5 Histogram of radial velocity shifts}
+\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
+\bigskip
+
+\bigskip
+
+\includegraphics[width=170mm]{d_figure_6.png}
+\bigskip
+
+\centerline{Diagnostic Fig.6 Radial velocity shifts against mean fiber number}
+\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
+\bigskip
+
 \end{document}

### 2016-12-06 paper/ms.tex
Compare the two methods
Compare the two methods for obtaining radial velocity shifts

@@
 \end{equation}
-Where $\beta ={ v \over c} $. $v$ is the radial velocity. $\lambda_0$ and $\lambda_s$ are the wave lengths measured at the observer and the source.
+Where $\beta ={ v \over {v_{light}}} $. $v$ is the radial velocity. $\lambda_0$ and $\lambda_s$ are the wave lengths measured at the observer and the source.$v_{light}$ is the speed of light.
 
@@
 The wavelength start at 15100.802 $\AA$ and the logarithmic wavelength grid spacing between two pixels is $6*10^{-6}$.
-By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if a=1 b= 0 and c=0, the radial velocity error in the APOGEE data is $-4144.68 m/s$
+By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if the data spectrum moves one pixel left, the radial velocity shift in the APOGEE data is $-4144.68 m/s$.
+\\ In the following formulas, $v_{shift}$ is the shift of the radial velocity in APOGEE data and $v_{pixel}$ =  4144.68 m/s, which is the radial velocity related to one pixel.
+$v_{light}$ is the speed of light.
 
-Thus we can use a, b and c to determine the radial velocity shift for the combined spectrum and each visit of the APOGEE data.
+We can use a, b and c to determine the radial velocity shift for the combined spectrum and each visit of the APOGEE data.
+If the parameters are a, b and c, $a\over{a+b+c}$ of the spectrum moves one pixel left, $c\over{a+b+c}$ of the spectrum moves one pixel right and $b\over{a+b+c}$ of the spectrum doesn't move.
+The spectrum moves one pixel left has $v_{shift} = -v_{pixel}$ and the one moves one pixel right has $v_{shift} = v_{pixel}$.
+${a+c}\over2$ of the spectrum is broadening but it's included in the spectrum moves left and right.
+Thus the data spectrum moves ${c-a}\over{(a+b+c)}$ pixel right and we have
+
 \begin{equation}
-v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}
+\log_{10} (1+{v_{shift}}/v_{light}) = {{c-a}\over{(a+b+c)}}*\log_{10}(1+{v_{pixel}}/v_{light})
 \end{equation}
-Where $v_{shift}$ is the shift of the radial velocity in APOGEE data and $v_{pixel}$ =  4144.68 m/s.
+
+$v_{shift}/v_{light}$ and $v_{pixel}/v_{light}$ are small so we can use Taylor expansion. Then we have:
+
+\begin{equation}
+v_{shift} = {{(c-a)*v_{pixel}}\over{a+b+c}}
+\end{equation}
+
 \bigskip
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_1.png}
+\end{center}
  \centerline{Fig.1 The spectrum of Star A, B, C and D}
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_2.png}
-\bigskip
+\end{center}
 
@@
 We also plot delta-chi-squared vs Mean Fiber number, where delta-chi-squared is the difference between the chi-squared of the spectrum before our optimization and after. It should be bigger than 0.
-\bigskip
 
+\begin{center}
 \includegraphics[width=170mm]{figure_3.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_4.png}
-\bigskip
+\end{center}
 
@@
 \centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-\bigskip
 
+\begin{center}
 \includegraphics[width=170mm]{figure_5.png}
-\bigskip
+\end{center}
 
@@
 Plot four stars with b closest to 1:
-\bigskip
 
+\begin{center}
 \includegraphics[width=170mm]{figure_6.png}
-\bigskip
+\end{center}
 
@@
 Here is the plot of the four stars with biggest a+c-b:
-\bigskip
 
+\begin{center}
 \includegraphics[width=170mm]{figure_7.png}
-\bigskip
+\end{center}
 
@@
 To look deeper into the results, we also choose the four stars with biggest $a-c$ and biggest $c-a$. Then make another two plots:
-\bigskip
 
+\begin{center}
 \includegraphics[width=170mm]{figure_8.png}
-\bigskip
+\end{center}
 
@@
 
-\bigskip
-
+\begin{center}
 \includegraphics[width=170mm]{figure_9.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_10.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_11.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_12.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_13.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_14.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_15.png}
-\bigskip
+\end{center}
 
@@
 
-\bigskip
-
+\begin{center}
 \includegraphics[width=170mm]{figure_16.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{figure_17.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{d_figure_1.png}
-\bigskip
+\end{center}
 
@@
 
-\bigskip
-
+\begin{center}
 \includegraphics[width=170mm]{d_figure_2.png}
-\bigskip
+\end{center}
 
@@
 
-\bigskip
-
+\begin{center}
 \includegraphics[width=170mm]{d_figure_3.png}
-\bigskip
+\end{center}
 
@@
 
+\begin{center}
 \includegraphics[width=170mm]{d_figure_4.png}
-\bigskip
+\end{center}
 
@@
 The original histogram of radial velocity shifts for figure 11.
-\bigskip
 
+\begin{center}
 \includegraphics[width=170mm]{d_figure_5.png}
-\bigskip
+\end{center}
 
@@
 
-\bigskip
-
+\begin{center}
 \includegraphics[width=170mm]{d_figure_6.png}
-\bigskip
+\end{center}
 
@@
 
+To check which method is better, we choose the four stars with smallest abs(a-c).
+These four stars have abs(a-c) smaller than 0.001 and we think their radial velocity shifts are 0.
+We call $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$ method A and $v_{shift} = (c-a)*v_{pixel}$ method B.
+
+First, move the data spectrum of the four stars one pixel left and the radial velocity shift should be $-v_{pixel}$= -4144.68$m/s$
+
+\begin{center}
+\includegraphics[width=170mm]{d_figure_7.png}
+\end{center}
+
+\centerline{Diagnostic Fig.7 Move the data spectrum one pixel left.}
+\centerline{the radial velocity shift should be $-v_{pixel}$= -4144.68$m/s$}
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+\bigskip
+
+\bigskip
+
+Then, move the data spectrum of the four stars one pixel right and the radial velocity shift should be $v_{pixel}$= 4144.68$m/s$
+
+\begin{center}
+\includegraphics[width=170mm]{d_figure_8.png}
+\end{center}
+
+\centerline{Diagnostic Fig.8 Move the data spectrum one pixel right.}
+\centerline{the radial velocity shift should be $v_{pixel}$= 4144.68$m/s$}
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+
+\bigskip
+
 \end{document}

### 2016-12-06 1206_diagnostic_choose_4_small_a_c_move_manually.py

@@ -1,0 +1,224 @@
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import AnniesLasso_2 as tc
+import matplotlib.pyplot as plt
+import pickle
+
+import plot_class_4_star_v2_1107
+
+# load path
+
+pkl_file = open('n_900_path_fits.pkl', 'rb')
+path_fits = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_900_path_flux.pkl', 'rb')
+path_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+N = len(path_fits)
+print(N)
+
+velocity = []
+mean_fiber_id = []
+mean_ivar = []
+parameters = []
+nor = []
+ivar=[]
+inf =[]
+inf_label= []
+
+for i in range(0,N):
+    print("loading star %d"%(i+1))
+    star_i = fits.open(path_fits[i])
+    velocity.append(star_i[10].data[0])
+    mean_fiber_id.append(np.mean(star_i[7].data))
+    mean_ivar.append(np.mean(star_i[1].data[0]))
+    parameters.append(star_i[4].data[0])
+
+    nor.append(star_i[0].data[0])
+    ivar.append(star_i[1].data[0])
+    inf.append(star_i[2].data[0])
+    inf_label.append(star_i[9].data[0])
+
+    print(star_i[4].data[0].shape)
+
+velocity =np.array(velocity)
+mean_fiber_id = np.array(mean_fiber_id)
+parameters = np.array(parameters)
+nor=np.array(nor)
+ivar = np.array(ivar)
+inf = np.array(inf)
+inf_label = np.array(inf_label)
+
+
+v_jason = (parameters[:,2]-parameters[:,0])*(4144.68)
+
+
+
+# find the four stars with biggest v
+
+
+"""
+# Jason
+
+N =len(path_fits)
+big_v_4 = (velocity*velocity).argsort()[N-4:N]
+big_v_jason = (v_jason*v_jason).argsort()[N-4:N]
+
+model = plot_class_4_star_v3_1201.plot_4()
+# model.plot_name_4(path_fits[big_v_4])
+
+model.plot_name_4(path_fits[big_v_jason])
+
+
+"""
+N =len(path_fits)
+big_v_4 = (velocity*velocity).argsort()[N-4:N]
+big_v_jason = (v_jason*v_jason).argsort()[N-4:N]
+
[…]

### 2016-12-10 paper/ms.tex
Compare the results
Compare the two formulas for radial velocity shifts.

@@
 
-I plot the histogram of radial velocity shifts derived by using $v_{shift} = (c-a)*v_{pixel}$ in diagnostic figure 2 and velocity shifts against mean fiber number in diagnostic figure 3.
-
 \begin{center}
@@
 
-\centerline{Diagnostic Fig.2 Histogram of radial velocity shifts}
-\centerline{The formula to derive velocity shifts is $v_{shift} = (c-a)*v_{pixel}$}
+\centerline{Diagnostic Fig.2 Four fake stars with Gaussian wave pack spectrums}
+\centerline{The green line is the template and the black line is the observation}
 \bigskip
@@
 
-\centerline{Diagnostic Fig.3 Radial velocity shifts against mean fiber number}
-\centerline{The formula to derive velocity shifts is $v_{shift} = (c-a)*v_{pixel}$}
+\centerline{Diagnostic Fig.3 Spectrum of the four stars with biggest c-a}
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
 \bigskip
-
-We also plot the four stars with biggest radial velocity shifts, which are in figure 13. The formula I use is $v_{shift} = (c-a)*v_{pixel}$.
 
@@
 
-\centerline{Diagnostic Fig.4 Spectrum of the four stars with biggest radial velocity shifts.}
-
+\centerline{Diagnostic Fig.4 Spectrum of the four stars with biggest a-c}
 \centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
@@
 \bigskip
-
-The original histogram of radial velocity shifts for figure 11.
 
@@
 
-\centerline{Diagnostic Fig.5 Histogram of radial velocity shifts}
-\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
+\centerline{Diagnostic Fig.5 Spectrum of the four stars with biggest a+c-2b}
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
 \bigskip
@@
 
-\centerline{Diagnostic Fig.6 Radial velocity shifts against mean fiber number}
-\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
+\centerline{Diagnostic Fig.6 Spectrum of the four stars with b closest to 1}
+\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
 \bigskip
-
-To check which method is better, we choose the four stars with smallest abs(a-c).
-These four stars have abs(a-c) smaller than 0.001 and we think their radial velocity shifts are 0.
-We call $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$ method A and $v_{shift} = (c-a)*v_{pixel}$ method B.
-
-First, move the data spectrum of the four stars one pixel left and the radial velocity shift should be $-v_{pixel}$= -4144.68$m/s$
 
@@
 
-\centerline{Diagnostic Fig.7 Move the data spectrum one pixel left.}
-\centerline{the radial velocity shift should be $-v_{pixel}$= -4144.68$m/s$}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+$v_cc$ is the velocity shift from the cross-correlation. $v_David$ is the velocity shift from David's formula. $v_Jason$ is the velocity shift from Jason's formula.
+
+\centerline{Diagnostic Fig.7 $v_cc$ vs$v_David$}
+
 \bigskip
@@
 \bigskip
-
-Then, move the data spectrum of the four stars one pixel right and the radial velocity shift should be $v_{pixel}$= 4144.68$m/s$
 
@@
 
-\centerline{Diagnostic Fig.8 Move the data spectrum one pixel right.}
-\centerline{the radial velocity shift should be $v_{pixel}$= 4144.68$m/s$}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+\centerline{Diagnostic Fig.8 $v_cc$ vs$v_Jason$}
+
+\bigskip
+
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{d_figure_9.png}
+\end{center}
+
+\centerline{Diagnostic Fig.9 $v_cc$ vs$v_David$}
+
+\bigskip
+
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{d_figure_10.png}
+\end{center}
+
+\centerline{Diagnostic Fig.10 $v_cc$ vs$v_Jason$}
 

### 2016-12-10 1208_compare_rv_single_file.py

@@ -1,0 +1,74 @@
+import pickle
+import PyAstronomy
+from PyAstronomy import pyasl
+import numpy as np
+from astropy.io import fits
+import matplotlib.pylab as plt
+import Cross_correlation_1207 as cc
+
+
+# load path
+
+pkl_file = open('n_900_path_fits.pkl', 'rb')
+path_fits = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_900_path_flux.pkl', 'rb')
+path_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+N = len(path_fits)
+print(N)
+
+velocity = []
+mean_fiber_id = []
+mean_ivar = []
+parameters = []
+nor = []
+ivar=[]
+inf =[]
+inf_label= []
+
+for i in range(0,N):
+    print("loading star %d"%(i+1))
+    star_i = fits.open(path_fits[i])
+    velocity.append(star_i[10].data[0])
+    mean_fiber_id.append(np.mean(star_i[7].data))
+    mean_ivar.append(np.mean(star_i[1].data[0]))
+    parameters.append(star_i[4].data[0])
+
+    nor.append(star_i[0].data[0])
+    ivar.append(star_i[1].data[0])
+    inf.append(star_i[2].data[0])
+    inf_label.append(star_i[9].data[0])
+
+    print(star_i[4].data[0].shape)
+
+velocity =np.array(velocity)
+mean_fiber_id = np.array(mean_fiber_id)
+parameters = np.array(parameters)
+nor=np.array(nor)
+ivar = np.array(ivar)
+inf = np.array(inf)
+inf_label = np.array(inf_label)
+
+# velocity compare  CFF,David,Jason
+#N =605
+a=0
+b=100
+
+for i in range(a,b):
+
+    print('\033[1;31mdoing star %d of %d\033[1;m' % (i+1,N))
+    # CC, David, Jason
+    v1,v2,v3 = cc.cross_correlation_velocity_v2(parameters[i,0],parameters[i,1],parameters[i,2])
+
+    velocity_i = np.array([v1,v2,v3])
+    name = "/Users/caojunzhi/Desktop/Data/velocity_900/"+"velocity"+str(i)+".pkl"
+
+    output = open(name, 'wb')
+    pickle.dump(velocity_i, output)
+    output.close()
+

### 2016-12-10 1208_cross_correlation_velocity.py

@@ -1,0 +1,157 @@
+from __future__ import print_function, division
+import math
+import pickle
+import PyAstronomy
+import matplotlib
+
+from PyAstronomy import pyasl
+import numpy as np
+import matplotlib.pylab as plt
+
+
+import plot_class_4_star_v2_1107
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+def log(x):
+    return math.log10(x)
+
+def power10(x):
+    return 10**x
+
+wl_log = list(map(log,wl))
+wl_log = np.array(wl_log)
+
+wl_log_long = np.linspace(wl_log[0],wl_log[-1],8575*50)
+#print(wl_log_long)
+
+# make a new wave length scale ws: 8575*10 points
+ws = 10**(wl_log_long)
+print("ws shape check")
+print(ws.shape)
+
+# divide
+
+# May use this
+"""
+wl_log_long = np.linspace(wl_log[0],wl_log[-1],8575*10)
+wl_log_long_s =np.linspace(wl_log[4000],wl_log[4575],8575*2)
+wl_long = list(map(power10,wl_log_long))
+wl_long = np.array(wl_log)
+
+wl_long_s = list(map(power10,wl_log_long_s))
+wl_long_s = np.array(wl_long_s)
+print(wl_long_s[0],wl_long_s[-1])
+"""
+
+
+
+# Create the template
+
+# gamma = 0.2086
+gamma = 0.199
+
+sigma =10
+
+#tw = wl
+tw =ws
+#tw = np.linspace(wl[0],wl[-1],8575*10)
+tf = np.exp(-(tw-16000.0)**2/(2.*sigma**2))+1
+
+# choose 20%
+choose = np.arange(0,1716)
+choose = choose*5-1
+
+# 0.07 -- 4.2
+
+
+# Create data, which are not that well sampled
+#dw = wl[choose]
+
+#dw = np.linspace(wl[0],wl[-1],8575*2)
+
+#dw = wl
+dw =ws
+
+# df = np.exp(-(dw-5004.007)**2/(2.*0.1**2))
+x = np.exp(-(dw-16000.0+1*gamma)**2/(2.*sigma**2))+1
+y = np.exp(-(dw-16000.0)**2/(2.*sigma**2))+1
+z = np.exp(-(dw-16000.0-1*gamma)**2/(2.*sigma**2))+1
+
+# remake-abc
+
+a = 0.13
[…]

### 2016-12-10 1208_read_rv_compare_single_file.py

@@ -1,0 +1,90 @@
+import pickle
+import PyAstronomy
+from PyAstronomy import pyasl
+import numpy as np
+from astropy.io import fits
+import matplotlib.pylab as plt
+import Cross_correlation_1207 as cc
+
+
+# load path
+
+pkl_file = open('n_900_path_fits.pkl', 'rb')
+path_fits = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_900_path_flux.pkl', 'rb')
+path_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+N = len(path_fits)
+print(N)
+
+velocity = []
+mean_fiber_id = []
+mean_ivar = []
+parameters = []
+nor = []
+ivar=[]
+inf =[]
+inf_label= []
+
+for i in range(0,N):
+    print("loading star %d"%(i+1))
+    star_i = fits.open(path_fits[i])
+    velocity.append(star_i[10].data[0])
+    mean_fiber_id.append(np.mean(star_i[7].data))
+    mean_ivar.append(np.mean(star_i[1].data[0]))
+    parameters.append(star_i[4].data[0])
+
+    nor.append(star_i[0].data[0])
+    ivar.append(star_i[1].data[0])
+    inf.append(star_i[2].data[0])
+    inf_label.append(star_i[9].data[0])
+
+    print(star_i[4].data[0].shape)
+
+velocity =np.array(velocity)
+mean_fiber_id = np.array(mean_fiber_id)
+parameters = np.array(parameters)
+nor=np.array(nor)
+ivar = np.array(ivar)
+inf = np.array(inf)
+inf_label = np.array(inf_label)
+
+
+velocity_compare = []
+
+N = len(path_fits)
+
+for i in range(0,N):
+    name = "/Users/caojunzhi/Desktop/Data/velocity_900/" + "velocity" + str(i) + ".pkl"
+
+    pkl_file = open(name, 'rb')
+    v_i = pickle.load(pkl_file)
+    pkl_file.close()
+
+    velocity_compare.append(v_i)
+
+velocity_compare = np.array(velocity_compare)
+print(velocity_compare.shape)
+
+plt.plot(velocity_compare[:,0],"ko",label="CCF")
+plt.plot(velocity_compare[:,1],"go",label ="David")
+plt.plot(velocity_compare[:,2],"ro",label="Jason")
+axes = plt.gca()
[…]

### 2016-12-10 1209_plot_rv_compare.py

@@ -1,0 +1,218 @@
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import numpy as np
+import math
+from astropy.io import fits
+import Plot_compare_velocity_1209 as pm
+
+def log(x):
+    return math.log10(x)
+
+def power10(x):
+    return 10**x
+
+# load
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('moments_900.pkl', 'rb')
+moment = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('parameters_900.pkl', 'rb')
+parameters = pickle.load(pkl_file)
+pkl_file.close()
+
+pkl_file = open('velocity_compare_900.pkl', 'rb')
+velocity_compare = pickle.load(pkl_file)
+pkl_file.close()
+
+"""
+# load path
+
+pkl_file = open('n_900_path_fits.pkl', 'rb')
+path_fits = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_900_path_flux.pkl', 'rb')
+path_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+N = len(path_fits)
+print(N)
+
+velocity = []
+mean_fiber_id = []
+mean_ivar = []
+parameters = []
+nor = []
+ivar=[]
+inf =[]
+inf_label= []
+
+for i in range(0,N):
+    print("loading star %d"%(i+1))
+    star_i = fits.open(path_fits[i])
+    velocity.append(star_i[10].data[0])
+    mean_fiber_id.append(np.mean(star_i[7].data))
+    mean_ivar.append(np.mean(star_i[1].data[0]))
+    parameters.append(star_i[4].data[0])
+
+    nor.append(star_i[0].data[0])
+    ivar.append(star_i[1].data[0])
+    inf.append(star_i[2].data[0])
+    inf_label.append(star_i[9].data[0])
+
+    print(star_i[4].data[0].shape)
+
+velocity =np.array(velocity)
+mean_fiber_id = np.array(mean_fiber_id)
+parameters = np.array(parameters)
+nor=np.array(nor)
+ivar = np.array(ivar)
+inf = np.array(inf)
+inf_label = np.array(inf_label)
+
+
+
+
+
[…]

### 2016-12-10 Cross_correlation_1207.py

@@ -138,9 +138,20 @@ def cross_correlation_velocity_v2(a,b,c):
     # remake-abc
 
     df = a * x + b * y + c * z
+
+    """
     print(a, b, c)
     print(4.144 * (c - a) / ((a ** 2 + b ** 2 + c ** 2) ** 0.5))
-    print(4.144 * (c - a) / ((a + c - 2 * b) * 4))
+    print(4.144 * (a-c) / ((a + c - 2 * b) * 2))
+
+    """
+
+    # use simple
+    simple = 4.144 * (c - a) / (a + b + c)
+    jason = 4.144 * (c - a) / ((a ** 2 + b ** 2 + c ** 2) ** 0.5)
+    david = 4.144 * (a - c) / ((a + c - 2 * b) * 2)
+    print(a,b,c)
+    print(simple,david)
 
     """
     # Plot template and data
@@ -168,5 +179,4 @@ def cross_correlation_velocity_v2(a,b,c):
         print("  A blue-shift with respect to the template")
 
     # CCF, David, Me
-    return 1000*rv[maxind],4140 * (c - a) / ((a + c - 2 * b) * 4),4.140 * (c - a) / ((a ** 2 + b ** 2 + c ** 2) ** 0.5)
-
+    return 1000*rv[maxind],1000*david,1000*simple

### 2016-12-15 paper/ms.tex
Explain the velocity

@@
 \begin{equation}
-y_{j,n}^{opt}=a\cdot y_{j-1,n}^{inf}+b\cdot y_{j,n}^{inf}+c\cdot y_{j+1,n}^{inf}
+y_{j,n}^{opt}=a\cdot y_{j+1,n}^{inf}+b\cdot y_{j,n}^{inf}+c\cdot y_{j-1,n}^{inf}
 \end{equation}
@@
 
-    1 & y_{1,n} ^{inf} & y_{2,n} ^{inf}\\
-    y_{1,n}^{inf}&y_{2,n}^{inf}& y_{3,n}^{inf}  \\
+    y_{1,n}^{inf} & y_{1,n} ^{inf} & 1\\
+    y_{2,n}^{inf}&y_{2,n}^{inf}& y_{2,n}^{inf}  \\
     \vdots & \vdots & \vdots \\
-    y_{J-1,n}^{inf}&y_{J,n}^{inf}& 1  \\
+    1 &y_{J,n}^{inf}&  y_{J-1,n}^{inf} \\
 
@@
 This is because the optimized spectrum is obtained by fitting the inferred spectrum to the data spectrum.
+We set the radial velocity to be positive if the star is leaving us.
 \bigskip
 
-To begin with, we set the radial velocity to be positive if the star is leaving us.
-If a=1, b=0 and c=0, the optimized spectrum moves one pixel left from the inferred spectrum, which means the data spectrum should move one pixel right and the radial velocity of the data spectrum is not zero and it has a blue shift.
-Thus the radial velocity shift is negative and can be obtained by using (8).
-It's more convenient to use the logarithmic wavelength.
+The radial velocity is related to the pixels. We can obtain the velocity shift by calculating the centroid shift.
+
 \begin{equation}
-\log_{10}\lambda_0 - \log_{10}\lambda_s = \log_{10}(1+\beta)
+pixel_c = {\sum_{j=1}^{j=J} {j*y_{jn}}\over\sum_{j=1}^{j=J} {y_{jn}}}
 \end{equation}
 
-All spectrums in Apstar files are set to the same wavelength scale.
-The wavelength start at 15100.802 $\AA$ and the logarithmic wavelength grid spacing between two pixels is $6*10^{-6}$.
-By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if the data spectrum moves one pixel left, the radial velocity shift in the APOGEE data is $-4144.68 m/s$.
-\\ In the following formulas, $v_{shift}$ is the shift of the radial velocity in APOGEE data and $v_{pixel}$ =  4144.68 m/s, which is the radial velocity related to one pixel.
-$v_{light}$ is the speed of light.
+Where j is the pixel j, $y_{jn}$ is the flux at pixel j for star n. $pixel_c$ is the spectral centroid in pixel.
 
-We can use a, b and c to determine the radial velocity shift for the combined spectrum and each visit of the APOGEE data.
-If the parameters are a, b and c, $a\over{a+b+c}$ of the spectrum moves one pixel left, $c\over{a+b+c}$ of the spectrum moves one pixel right and $b\over{a+b+c}$ of the spectrum doesn't move.
-The spectrum moves one pixel left has $v_{shift} = -v_{pixel}$ and the one moves one pixel right has $v_{shift} = v_{pixel}$.
-${a+c}\over2$ of the spectrum is broadening but it's included in the spectrum moves left and right.
-Thus the data spectrum moves ${c-a}\over{(a+b+c)}$ pixel right and we have
+If the parameters are a, b and c. Then the centroid of the spectrum in frequency is:
+\begin{equation}
+pixel_c = {\sum_{j=1}^{j=J} {j*(a*y_{j+1,n}+b*y_{j,n}+c*y_{j-1,n})}\over\sum_{j=1}^{j=J} {(a*y_{j+1,n}+b*y_{j,n}+c*y_{j-1,n})}}
+\end{equation}
+
+We have $\sum_{j=1}^{j=J}{y_{j-1,n}}$ = $\sum_{j=1}^{j=J}{y_{j,n}}$ =$\sum_{j=1}^{j=J}{y_{j+1,n}}$ and $\sum_{j=1}^{j=J}{(j-1)*y_{j-1,n}}$ = $\sum_{j=1}^{j=J}{j*y_{j,n}}$ =$\sum_{j=1}^{j=J}{(j+1)*y_{j+1,n}}$.
+So the formula can be expressed as:
 
 \begin{equation}
-\log_{10} (1+{v_{shift}}/v_{light}) = {{c-a}\over{(a+b+c)}}*\log_{10}(1+{v_{pixel}}/v_{light})
+pixel_c = {\sum_{j=1}^{j=J} {j*(a*y_{j,n}+b*y_{j,n}+c*y_{j,n})}\over\sum_{j=1}^{j=J} {(a*y_{j,n}+b*y_{j,n}+c*y_{j,n})}} + {\sum_{j=1}^{j=J} {(c-a)*y_{j,n}}\over\sum_{j=1}^{j=J} {(a*y_{j,n}+b*y_{j,n}+c*y_{j,n})}}
 \end{equation}
 
-$v_{shift}/v_{light}$ and $v_{pixel}/v_{light}$ are small so we can use Taylor expansion. Then we have:
+The first term is the centroid of the inferred flux. The second term is the shift of the centroid, which is:
 
 \begin{equation}
-v_{shift} = {{(c-a)*v_{pixel}}\over{a+b+c}}
+pixel_c^{shift} = {{c-a}\over{a+b+c}}
 \end{equation}
 
-\bigskip
+Thus we have:
+
+\begin{equation}
+RV_{shift} = pixel_c^{shift}\cdot v_{pixel}
+\end{equation}
+Where $RV_{shift} $ is the radial velocity shift and $pixel_c^{shift}$ is the pixel centroid shift between the two spectrum.
+
+But if 2b<a+c, which means the magnitude of the spectrum moves one pixel left or right is big, the approximation will expire because the influence of the pixels two pixel left or right can't be ignored.
+When this happen, we will use five parameters, which are:
 
@@
 
-\begin{center}
-\includegraphics[width=170mm]{d_figure_7.png}
-\end{center}
-
-$v_cc$ is the velocity shift from the cross-correlation. $v_David$ is the velocity shift from David's formula. $v_Jason$ is the velocity shift from Jason's formula.
-
-\centerline{Diagnostic Fig.7 $v_cc$ vs$v_David$}
-
-\bigskip
-
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_8.png}
-\end{center}
-
-\centerline{Diagnostic Fig.8 $v_cc$ vs$v_Jason$}
-
-\bigskip
-
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_9.png}
-\end{center}
-
-\centerline{Diagnostic Fig.9 $v_cc$ vs$v_David$}
-
-\bigskip
-
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_10.png}
-\end{center}
-
-\centerline{Diagnostic Fig.10 $v_cc$ vs$v_Jason$}
-
-\bigskip
-
 \end{document}

### 2017-01-15 paper/ms.tex
Demonstrate our normalization method works

@@
 \usepackage{authblk}
+
+\usepackage{amsmath}
 
@@
 
-The radial velocity is related to the pixels. We can obtain the velocity shift by calculating the centroid shift.
+The radial velocity is related to the pixels. We can obtain the velocity shift by calculating the centroid shift. The centroid in pixel can be expressed as:
 
@@
 
-But if 2b<a+c, which means the magnitude of the spectrum moves one pixel left or right is big, the approximation will expire because the influence of the pixels two pixel left or right can't be ignored.
-When this happen, we will use five parameters, which are:
+But if 2b<a+c, which means the magnitude of the spectrum moves one pixel left or right is big, the approximation will expire because the influence of the pixels two pixels left or right can't be ignored.
+When this happens, we will use five parameters, which are:
+$a_1$, $a_2$, $a_3$, $a_4$, $a_5$. Now the optimized spectrum is:
+
+\begin{equation}
+y_{j,n}^{opt}=a_1\cdot y_{j+2,n}^{inf}+a_2\cdot y_{j+1,n}^{inf}+a_3\cdot y_{j,n}^{inf}+a_4\cdot y_{j-1,n}^{inf}+a_5\cdot y_{j-2,n}^{inf}
+\end{equation}
+This means we move the inferred spectrum two pixels left, one pixel left, zero pixel, one pixel right and two pixels right and generate five new spectrums.
+The parameters for them are $a_1$, $a_2$, $a_3$, $a_4$, $a_5$.
+We only use five parameters to calculate the radial velocity shift when $2b<a+c$, where the influence of the spectrum moves two pixels left and right can't be ignore.
+
+So the velocity shift is
+
+\begin{equation}
+RV_{shift} = v_{pixel} \cdot {{c-a}\over{a+b+c}}\qquad2b>a+c
+\end{equation}
+
+\begin{equation}
+RV_{shift} = v_{pixel} \cdot {{2a_5 +a_4 - a_2 - 2a_1}\over{a_1+a_2+a_3+a_4+a_5}}\qquad2b<a+c     
+\end{equation}
+
+We will plot the histogram for the five parameters in our experiment.
 
@@
 
-In figure 16, we plot the continuum-normalized fluxes of all visits for the first star in figure 8.
-There are 9 individual visits.
+In figure 17 and 18, we plot the continuum-normalized fluxes of all visits for the first star in figure 8.
+There are 6 individual visits and 2 combined spectrums.
+So in figure 17 and 18, there are 8 fluxes.
+The bottom two are the combined spectrum and the other 6 are individual visits.
 We can see that the absolute value of the flux for each visit is similar to each other, which means our normalization works.
@@
 \centerline{Fig.17 Comparison of each visit for the first star in figure 8.}
+\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{figure_18.png}
+\end{center}
+
+\centerline{Fig.18 Comparison of each visit for the first star in figure 8.}
+\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
 \bigskip
@@
 
+\begin{center}
+\includegraphics[width=170mm]{d_figure_7.png}
+\end{center}
+
+\centerline{Diagnostic Fig.7 Radial velocity shifts}
+\centerline{ $v_3$ is the RV shift obtained from a, b and c. $v_5$ is from the five parameters. $v$ is from a, b and c if $2b>a+c$ and $v$ = $v_5$ if $2b<a+c$}
+\bigskip
+
 \end{document}

### 2017-01-26 paper/ms2.tex
re-construct the document
Re-construct the document and make a few new plots for individual
visits.

--- 2017-01-15 paper/ms.tex
@@
 \usepackage{amsmath}
+
+\bibliographystyle{abbrv}
 
@@
 
-\section{\label{sec:level1}Introduction}
+\section{\label{sec:level1}Abstract}
 
-Coming soon...
+The Cannon is a powerful tool which can predict the stellar labels from fluxes, which is a data-driven machine learning model.
+Also, it can infer fluxes from the stellar labels.
+Here we use the Cannon as a tool to calibrate the radial velocities(RV) in APOGEE DR 10 by fitting the inferred fluxes with the data fluxes.
+Then we compare our RV shift result with the APOGEE team and conclude our method is better.
+The most important thing of this work is that we can calibrate the velocity by using a new method-use data-driven model to calibrate physical parameters without using physical model.
+This is quicker than better than traditional methods.
 
@@
  \section{\label{sec:level1}Assumption and method}
- \subsection{\label{sec:level2}Optimize the spectrum}
+
+ \subsection{\label{sec:level2}Continuum normalization}
+Since the Cannon need the spectrums to be normalized.
+The first thing we should do is to continuum normalize the combined spectrums and individual visits.
+The data we use is the Apstar files in APOGEE DR10, which include two combined spectrums and several individual visits and they are set to the same wavelength scale after removing the radial velocities derived by APOGEE team.
+There are 8575 pixels and the wave length is equally logarithmically-spaced.
+The wavelength starts at 1.514 $\mu m$ and ends at 1.696 $\mu m$.
+\bigskip
+
+Our method is the same as the one in Ness et al 2015.
+The spectrum for each visit is in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
+First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum.
+Then, do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance.
+Third, put a mask on the spectrum.
+Finally, fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.
+Our method is different from the one used by the APOGEE team and we will demonstrate it works.
+\bigskip
+
+To check whether our normalization methods works, we will:
+
+\begin{description}
+  \item[1] Plot the continuum pixels for combined spectrum and individual visits, then check whether they are roughly cover the spectrum evenly.
+  \item[2] Plot individual visits and compare them with the combined spectrum, they should have similar shape.
+  \item[3] Infer stellar labels from the individual visits by using the Cannon and the inferred labels should be similar from the ones from the combined spectrum for the very same star.
+\end{description}
+
+For point 3
+If the inferred labels from each visit are similar to the ones from the combined spectrum, the normalization works. We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:
+
+\begin{equation}
+\triangle Teff = Teff_{inf}^{vs} - {Teff}_{inf}^{cb}
+\end{equation}
+
+\begin{equation}
+\triangle logg = logg_{inf}^{vs} - logg_{inf}^{cb}
+\end{equation}
+
+\begin{equation}
+\triangle Fe/H = Fe/H_{inf}^{vs} - Fe/H_{inf}^{cb}
+\end{equation}
+
+$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred Teff for each visit and the combined spectrum. It's similar for $logg$ and $Fe/H$
+
+If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works. The details are in Experiment 1.
+
+\subsection{\label{sec:level2}Calibrate the spectrums}
 
 %{\AA}
-Suppose we have a trained model.
+In this part we will introduce the Cannon 2, and then use a linear method to optimize the inferred spectrum. Finally calibrate both the combined spectrum and individual visits.
+\bigskip
+
+The very first thing we use is the Cannon 2.
+Suppose we have a trained Cannon model.
 The training set contains 548 stellar and each stellar spectrum has 8575 pixels.
@@
 They span the range of $3500K <T_{eff}< 5300K$, $0 <log$ $g< 5$ and $-2.5 <\left[Fe/H\right]< 0.45$.
-The spectrum we use in the training and testing step of the cannon is the combined spectrum from aspcap files.
-The labels we use are from the Allstar visit file.
-
+In the training step, we only use the first combined spectrum for these 548 stars to train the model.
 The model we adopt
@@
 \end{equation}
+
+\begin{equation}
+y_{jn}^{inf} = v(l_n^{inf}) \cdot \theta_{j} 
+\end{equation}
+\bigskip
 
@@
 \( e_{jn}\) is a noise draw or residual at pixel j for star n.
+$l_n$ and $l_n^{inf}$ are stellar labels and inferred stellar labels for star n.
+$y_{jn}^{inf}$ is the inferred spectrum for star n at wavelength pixel j.
 
-\(l_n^{inf}\) and \( \theta_{j}\) are available after the training step.
-Infer spectrum by using:
+If we have a trained Cannon 2 model, $\theta_{j}$ is available.
+The labels we use are Teff, Log g and Fe/H.
+We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
+The mean inverse variance of the stars is bigger than 10000 but smaller than 40000.
+We also exclude stars with undetermined labels.
+(The label is set to -10000 if it's not determined.)The number of stars is 614.
+Apply the Cannon 2 on these stars and obtain the inferred labels and inferred fluxes for them.
+
+From the normalized combined spectrum and fluxes of individual visits for the very same star, several sets of inferred labels $l_n^{inf}$ are obtained.
+Then put the inferred labels $l_n^{inf}$ back into formula (5), the inferred combined spectrum and inferred fluxes of individual visits for star n is available.
+The data spectrum we use are in Apstar files.
+There are two combined spectrum and several individual visits in the Apstar files.
+Put all of these spectrum into the trained Cannon 2 and obtain several sets of inferred labels for each star.
+After that, put the inferred labels back into the model and calculate the inferred combined spectrum(There should be two) and inferred fluxes of individual visits.
+\bigskip
+
+In the following step, we deal with the combined spectrum and individual visits with the same method.
+$y_{j,n}$ represents one spectrum of star n at pixel j.
+It can be either combined spectrum or individual visit.
+\bigskip
+
+The APOGEE team set the combined spectrum and fluxes of individual visits at rest by removing the radial velocities.
+However, since the derived radial velocities from the APOGEE team is not 100 \% correct, these fluxes are not at rest.
+There are radial velocity shifts between the radial velocities from the APOGEE team and the correct radial velocities.
+But we can assume the shifts of radial velocities are Gaussian distributed, so the inferred fluxes generated by the Cannon 2 are at rest.
+This means we can use inferred fluxes to calibrate the radial velocities derived by the APOGEE team.
+\bigskip
 
 \begin{equation}
-y_{jn}^{inf} = v(l_n^{inf}) \cdot \theta_{j} 
+RV_{cor} = RV_{apo} + RV_{shift}
 \end{equation}
 
- This is how to obtain the synthesized spectrum by using the Cannon 2. We also call it inferred flux(spectrum).
-
-The Cannon 2 can predict the spectrum pretty well. But we can still improve it.
+Where $RV_{cor}$, $RV_{apo}$ and $RV_{shift}$ are the correct radial velocity, radial velocity from the APOGEE team and the radial velocity shift.
 \bigskip
 
-From the inferred spectrum \(y_{jn}^{inf}\), we optimize it and generate a better synthesized spectrum, which we call \(y_{jn}^{opt}\).
-\bigskip
-
-The method we use is to represent the spectrum at pixel j by using the inferred spectrum at pixel j-1,pixel j and pixel j+1.(If the pixel is out of range, set the flux as 1).
-The data we use is the same as the training step.
-\bigskip
-
-The new spectrum, which is the optimized spectrum, is represented by:
+First, we define a spectrum called optimized spectrum.
 
@@
 
-We use the least chi-squared method. So our objective function is the chi-squared between the optimized spectrum and the spectrum data. The objective function for star n is:
+Where $y_{j,n}^{opt}$ is the optimized spectrum for star n at wavelength pixel j.
+We move the inferred spectrums one pixel left, 0 pixel and one pixel right to simulate the radial velocity shift of the data spectrum.
+
+Then we fit the optimized spectrum to the data spectrum by using the least chi-squared method.
+After fitting the optimized spectrum to the data spectrum, we think the optimized spectrum has the very same radial velocity shift as the data spectrum.
+And we can derive the correct radial velocity of the spectrum by removing the radial velocity shift.
+So our objective function is the chi-squared between the optimized spectrum and the spectrum data.
+The objective function for star n is:
 \bigskip
@@
 Write the objective function in the form of matrix can make it simpler.
-There will be N objective functions and N sets of a, b and c.
-So we introduce several matrix: $Y_n$, $A_n$, $C_n$ and $X_n$ for star n, which are defined as followed:
 
@@
 
-By using (7) we can calculate $a_n$, $b_n$ and $c_n$, which are parameters a, b and c for star n. 
-b should be much bigger than both a and c. And a+b+c should be equal to 1.
+By using (8) we can calculate $a_n$, $b_n$ and $c_n$, which are parameters a, b and c for one spectrum of star n.
 
-Calculate the optimized spectrum \( y_{j,n}^{opt}\) by using (3). The Experiment 1 shows that the optimization works.
+% shall we put this part in Appendix
+Calculate the optimized spectrum \( y_{j,n}^{opt}\) by using (4). The Experiment 2 shows that the optimization works.
 \bigskip
 
-%It works!
-
-\subsection{\label{sec:level2}Spectrum calibration}
-\bigskip
-After the optimization, we obtain many sets of a, b and c.
-In our theory b should be close to 1 and a, c is much smaller than b.
-But the fact is that sometimes b is much smaller than and c.
-This is because of the spectral broadening in the measurement.
-The equipment is not perfect, so the resolution of the spectrum will become lower due to scattering, dispersion or other reasons.
-Then the spectrum will broaden and the real spectrum at pixel j is not what we obtain, it should be the spectrum at nearby pixels, which include pixel j-1 and j+1.
-Thus b will be smaller than a+c, which we will discuss in the following experiment 3.
-\bigskip
-
-Sometimes a or c will be much bigger than the other two parameters.
-This is also because of the measurement.
-Even we ignore the spectral broadening, the measured spectrum may move one pixel left or one pixel right from the real spectrum.
-If the measured spectrum move one pixel left, then a should be close to 1 and it's similar for c.
-The measured spectrum moves left or right is because of the error in the measured velocity, so there will be error in measuring the Doppler effect, which leads to a spectrum moving.
-We will show this in experiment 3.
-
-We will do this optimization for each visit of every star in APOGEE DR10.
-The spectrum we use is in apstar file.
-We will re-analyze the velocities after the optimization and deliver back the velocities shift for the APOGEE data.
-\bigskip
-
-\subsection{\label{sec:level2} Interpret a, b, c in term of radial velocity}
-
 %Can you interpret a, b, c in terms of radial velocity? If so, how?
-After obtaining a, b and c for these stars, we can calibrate the errors in the radial velocities of the combined spectra of these stars.
+After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate the combined spectra of these stars.
 These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit.
-The apStar files also include the individual visit spectra, resampled and shifted to rest wavelength.
-If we need to use the individual visits before resampling, apVisit files are needed.
-In our experiment, we use the resampled spectrum in Apstar files.
-The radial velocities of the spectrum in Apstar files should be 0, but in fact they are not.
-This is because of the errors in radial velocity measurement by the APOGEE team.
-The APOGEE team determines the radial velocities of the stars by two steps.
-\bigskip
-\\
-1. Estimate the radial velocity of each visit by cross-correlating the visit spectrum against a grid of synthetic spectra.
-\\
-2. Compare the spectrum of each visit with the combined spectrum and re-derive the radial velocity for each visit iteratively. 
-\bigskip
-
-After obtaining the velocities, the APOGEE team uses the de-Doppler wavelengths and resample the spectrum onto the final logarithmically-spaced wavelength scale by using sinc interpolation.
-Finally, generate the combined spectrum by using the spectrums of different visits.
-Both combined spectrum and each visit may have radial velocity errors because the synthetic spectra are not perfect.
-
-We will derive these radial velocity errors, then de-Doppler them and resample the fluxes onto a common, logarithmically-spaced wavelength scale, which is the same as the wavelength scale in Apstar and ASPCAP flies.
+There are two combined spectrums for one star, which are obtained by different method.
+The radial velocities of the spectrums in Apstar files should be 0, but in fact they are not.
+This is because of the errors in the radial velocity measurement by the APOGEE team.
 
@@
 Where $\beta ={ v \over {v_{light}}} $. $v$ is the radial velocity. $\lambda_0$ and $\lambda_s$ are the wave lengths measured at the observer and the source.$v_{light}$ is the speed of light.
-
-The data spectrum we use in experiment 1 to 4 is the combined spectrum and we start to use spectrum of each visit in experiment 5.
 
@@
 
-We will plot the histogram for the five parameters in our experiment.
-
-\subsection{\label{sec:level2} Obtain information from the individual exposures}
-
-%How do you continuum-normalize the individual exposures, and can you demonstrate to me that your proposal of how to do that is working well?
-
-Before deriving a, b and c for each visit, we need to continuum-normalize the spectrum of each visit.
-This is because the absolute value of each visit is different.
-Therefore, each visit spectrum needs to be roughly continuum normalized before they are combined.
-The APOGEE team uses a median filter to continuum-normalize the spectrum of each visit.
-\bigskip
-
-Our method is the same as the one in Ness et al 2015.
-The spectrum for each visit is in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
-First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum.
-Then, do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance.
-Third, put a mask on the spectrum.
-Finally, fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.
-Our method is different from the one used by the APOGEE team and we will demonstrate it works.
-
-To check whether it works, we can look at the normalized spectrum of each visit. If the absolute value of the normalized flux for each visit is similar to each other, the normalization works.
-
-Also, we can infer labels by using the normalized flux of each visit.
-If the inferred labels from each visit are similar to the ones from the combined spectrum, the normalization works.
-We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:
-
-\begin{equation}
-\triangle Teff = Teff_{inf}^{vs} - {Teff}_{inf}^{cb}
-\end{equation}
-
-\begin{equation}
-\triangle logg = logg_{inf}^{vs} - logg_{inf}^{cb}
-\end{equation}
-
-\begin{equation}
-\triangle Fe/H = Fe/H_{inf}^{vs} - Fe/H_{inf}^{cb}
-\end{equation}
-
-$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred Teff for each visit and the combined spectrum. It's similar for $logg$ and $Fe/H$
-
-If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.
-
-The details are in experiment 5.
+We will plot the histogram for the five parameters in our experiment and demonstrate moving two pixels are good enough for these $2b<a+c$cases.
 
@@
  \section{\label{sec:level1}Experiment}
+
  \subsection{\label{sec:level2}Experiment 1}
+To demonstrate the continuum normalization works well for the combined spectrums and individual visits, we plot the continuum pixels for stars with different SNR(signal to noise ratio), Teff and Logg.
+Here we randomly choose 5 stars with different SNR, Teff and logg and plot them in figure 1 to 5.
 
-Choose four stellar, which are not in the training set.
-Optimize the spectrum of these four stars and obtain a, b and c for each stars.
-The labels we use in the figures are from the Cannon, which means they are inferred labels.
+% star A
+\bigskip
 
-The labels of the four stars are:
 \begin{center}
+\includegraphics[width=170mm]{CP_A.png}
 
- Star A  $T_{eff} =4750$  log g =3.0 $\left[Fe/h\right] =0.15$
-
- Star B  $T_{eff} =4849$  log g =2.2 $\left[Fe/h\right] =-1.0$
-
- Star C  $T_{eff} =3614$  log g =0.4 $\left[Fe/h\right] =-0.68$
-
- Star D  $T_{eff} =5003$  log g =2.8 $\left[Fe/h\right] =-0.71$
+\centerline{Fig.1 Comparison of each visit for Star A.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star A is 108. Teff = 4939K Logg =2.71 }
 
@@
 
-\begin{table}[ht]
-\caption{Fitting results for the four stars}
-\centering
-\begin{tabular}{c c c c c}
-\hline\hline
-Star Name & a & b & c & a+b+c \\ [0.5ex] % inserts table %heading
-\hline
-Star A & 0.121 & 0.824 & 0.052 & 0.998 \\
-Star B & 0.176 & 0.541 &  0.278 & 0.995 \\
-Star C & 0.003 & 1.004 &  -0.007 & 1.000 \\
-Star D & -0.009  & 1.029 & -0.020 & 1.000 \\ [1ex]
-\hline
-\end{tabular}
-\label{table:nonlin}
-\end{table}
+% Star B
+\bigskip
 
- Then plot the spectrum. The spectrum we use is the combined non-normalized spectrum from apstar files.
+\begin{center}
+\includegraphics[width=170mm]{CP_B.png}
 
- The black line "Observed" is the observed spectrum from the data  \(y_{jn}\).
- The green line "inferred" is \( y_{j,n}^{inf}\) , which is generated by the Cannon 2.
- The red line "optimized" is \( y_{j,n}^{opt}\), which is generated by (3)
+\centerline{Fig.2 Comparison of each visit for Star B.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 }
+
+\end{center}
+
+% Star C
 
@@
 \begin{center}
-\includegraphics[width=170mm]{figure_1.png}
-\end{center}
- \centerline{Fig.1 The spectrum of Star A, B, C and D}
+\includegraphics[width=170mm]{CP_C.png}
 
- \centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-\bigskip
+\centerline{Fig.3 Comparison of each visit for Star C.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 }
 
-Finally compare the chi-square for these four stars of the two methods:
-The total chi-squared of the four stars becomes 2\% smaller, which means our method works.
-
- \subsection{\label{sec:level2}Experiment 2}
- Plot the parameters a, b and c vs the number of the star. 
- \bigskip
-
-In experiment 1, we use only four stars to obtain parameters a, b and c and the result is pretty good.
-What if we optimize more stars?
-We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
-The mean inverse variance of the stars is bigger than 10000 but smaller than 40000.
-We also exclude stars with undetermined labels.
-(The label is set to -10000 if it's not determined.)The number of stars is 614.
-Now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 614 objective functions.
-And there will be 614 sets of a, b and c.
-The spectrum we use is the combined non-normalized spectrum from apstar files.
-And soon we will use the individual visit non-normalized spectrum from apstar files.
-Before using these spectrum, normalization is needed.
-The normalization method we use is the same as the one in Ness et al 2015.
-The labels we use are from the Cannon, which means they are inferred labels.
-
-We plot a, b, c against the mean fiber number, which is the average fiber number of the spectrum we optimize.
-In APOGEE DR 10, the fiber number is between 1 and 640.
-The parameters we use are from figure 3
-
-\begin{center}
-\includegraphics[width=170mm]{figure_2.png}
 \end{center}
 
-\centerline{Fig.2 a,b,c vs Mean Fiber Number}
-\bigskip
-
-This figure gives us information about the relation between parameters a, b, c and fiber number, which can be used to establish a data-driven spectrum calibration model.
-\bigskip
-
-We also plot delta-chi-squared vs Mean Fiber number, where delta-chi-squared is the difference between the chi-squared of the spectrum before our optimization and after. It should be bigger than 0.
-
-\begin{center}
-\includegraphics[width=170mm]{figure_3.png}
-\end{center}
-
-\centerline{Fig.3 Delta-chi-squared vs Mean Fiber Number}
-\bigskip
-
-\subsection{\label{sec:level2}Experiment 3}
-
-\bigskip
-Now choose some examples from the 614 stars and make some plots.Sometimes the inferred spectrum doesn't look like the data, which is already described in Ness et al 2015.
-We don't use these stars in the plots.
-
-First, plot the four stars with biggest delta-chi-squared and smallest delta-chi-squared:
-
-\begin{center}
-\includegraphics[width=170mm]{figure_4.png}
-\end{center}
-
-\centerline{Fig.4 Spectrum of the four stars with biggest delta-chi-squared. }
-
-\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-
-\begin{center}
-\includegraphics[width=170mm]{figure_5.png}
-\end{center}
-
-\centerline{Fig.5 Spectrum of the four stars with smallest delta-chi-squared. }
-
-\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-\bigskip
-
-From figure 6 and 7, we find that the four stars with smallest delta-chi-squared have b closer to 1, but the four stars with biggest delta-chi-squared don't.
-
-Also, we want to look into the spectral broadening.
-Plot four stars with b closest to 1:
-
-\begin{center}
-\includegraphics[width=170mm]{figure_6.png}
-\end{center}
-
-\centerline{Fig.6 Spectrum of the four stars with b closest to 1. }
-
-\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-\bigskip
-
-From the histogram of a, b and c, we also find that sometimes b becomes much smaller than a+c, which means the spectrum is broadening due to the measurement.
-The resolution of the spectrum becomes lower and this is what we want to calibrate.
-\bigskip
-Here is the plot of the four stars with biggest a+c-b:
-
-\begin{center}
-\includegraphics[width=170mm]{figure_7.png}
-\end{center}
-
-\centerline{Fig.7 Spectrum of the four stars with biggest a+c-b. }
-
-\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-\bigskip
+% Star D
 
@@
 
-We found a and c are close to 1, which is in accordance with our theory. 
-Also, the optimized spectrum broaden when a+c is much bigger than b, which means the measured spectrum broaden due to the error in the measurement. This is what we need to calibrate.
-\bigskip
+\begin{center}
+\includegraphics[width=170mm]{CP_D.png}
 
-To look deeper into the results, we also choose the four stars with biggest $a-c$ and biggest $c-a$. Then make another two plots:
+\centerline{Fig.4 Comparison of each visit for Star D.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star D is 150. Teff = 4534K Logg =2.24 }
 
-\begin{center}
-\includegraphics[width=170mm]{figure_8.png}
 \end{center}
 
-\centerline{Fig.8 Spectrum of the four stars with biggest $a-c$.}
+% Star E
 
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 \bigskip
@@
 \begin{center}
-\includegraphics[width=170mm]{figure_9.png}
+\includegraphics[width=170mm]{CP_E.png}
+
+\centerline{Fig.5 Comparison of each visit for Star E.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star E is 177. Teff = 4639K Logg =2.21 }
+
 \end{center}
-
-\centerline{Fig.9 Spectrum of the four stars with biggest $c-a$.}
-
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 
@@
 
-For spectrum with $a>c$, the optimized spectrum moves left a little bit, which means the real spectrum should move right a little.
-It's similar for $c>a$.
-The c>a branch is not as obvious as the a>c branch.
-
-\subsection{\label{sec:level2}Experiment 4}
-
-\bigskip
-We also plot the inferred labels $Teff$ against log g. The color bar shows the mean inverse variance of these stars.
+We can also demonstrate the continuum normalization works by infer stellar labels from individual visits and compare them with one from the combined spectrum.
+Here we use formula 1, 2 and 3 to obtain delta-stellar labels.
+If they are very small, the normalization works.
+They are plotted in figure 6, 7 and 8.
 
 \begin{center}
-\includegraphics[width=170mm]{figure_10.png}
+\includegraphics[width=170mm]{hist_d_teff.png}
 \end{center}
 
-\centerline{Fig.10 $Teff$ vs $log g$}
-\bigskip
-
-\subsection{\label{sec:level2}Experiment 5}
-
-Here we plot the histogram of the radial velocity shifts in figure 11 and the radial velocity shifts in figure 12. The data we use is the combined spectrums of the 614 stars in the former experiment.
-
-\begin{center}
-\includegraphics[width=170mm]{figure_11.png}
-\end{center}
-
-\centerline{Fig.11 Histogram of the radial velocity shifts in combined spectrums for the 614 stars. }
-\centerline{We exclude the outliers which have velocity shifts bigger than 2000 m/s}
-\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
+\centerline{Fig.6 Histogram of Delta Teff for individual visits}
 \bigskip
@@
 \begin{center}
-\includegraphics[width=170mm]{figure_12.png}
+\includegraphics[width=170mm]{hist_d_logg.png}
 \end{center}
 
-\centerline{Fig.12 Radial velocity shifts for combined spectrums of the 614 stars against mean fiber number}
-\centerline{We exclude the outliers which have velocity shifts bigger than 2000 m/s}
-\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
+\centerline{Fig.7 Histogram of Delta logg for individual visits}
+
+\begin{center}
+\includegraphics[width=170mm]{hist_d_fe.png}
+\end{center}
+
+\centerline{Fig.8 Histogram of Delta Fe/H for individual visits}
 \bigskip
 
-We also plot the four stars with biggest radial velocity shifts, which are in figure 13.
+We can see that these delta-stellar labels of individual visits are close to 0, which means the spectrums of individual visits don't change shape after the normalization.
+That's to say, the normalization works.
 
-\begin{center}
-\includegraphics[width=170mm]{figure_13.png}
-\end{center}
+ \subsection{\label{sec:level2}Experiment 2}
 
-\centerline{Fig.13 Spectrum of the four stars with biggest radial velocity shifts.}
-
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-
-\bigskip
-
-\bigskip
-
-After that, we want to calibrate the radial velocity for each visit.
-To begin with, we need to check whether our normalization works in each visit.
-The method is to infer labels for each visit and compare them with the ones from the combined spectrum.
-If our normalization works, the inferred labels from each visit for the same star should be similar to the ones from the combined spectrum.
-We plot the histogram which shows the deviations of the inferred labels of each visit from the ones generated by the combined spectrum of the same star.
-The data we use is the 614 stars in experiment 1 to 4.
-If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.
-
-\begin{center}
-\includegraphics[width=170mm]{figure_14.png}
-\end{center}
-
-\centerline{Fig.14 Histogram for Delta Teff}
+ In experiment 2, we will focus on the parameters fitting for individual visits. First, we plot the histograms of parameters abc and RV shifts for individual visits.
 \bigskip
@@
 \begin{center}
-\includegraphics[width=170mm]{figure_15.png}
+\includegraphics[width=170mm]{hist_abc_visits.png}
 \end{center}
 
-\centerline{Fig.15 Histogram for Delta logg}
-
-\begin{center}
-\includegraphics[width=170mm]{figure_16.png}
-\end{center}
-
-\centerline{Fig.16 Histogram for Delta Fe/H}
-\bigskip
-
-We can see that most of the deviations are close to 0, which means our normalization for each visit doesn't make the spectrum distort.
-
-In figure 17 and 18, we plot the continuum-normalized fluxes of all visits for the first star in figure 8.
-There are 6 individual visits and 2 combined spectrums.
-So in figure 17 and 18, there are 8 fluxes.
-The bottom two are the combined spectrum and the other 6 are individual visits.
-We can see that the absolute value of the flux for each visit is similar to each other, which means our normalization works.
-
-\begin{center}
-\includegraphics[width=170mm]{figure_17.png}
-\end{center}
-
-\centerline{Fig.17 Comparison of each visit for the first star in figure 8.}
-\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
+\centerline{Fig.9 Histogram of a,b,c for individual visits}
 \bigskip
@@
 \begin{center}
-\includegraphics[width=170mm]{figure_18.png}
+\includegraphics[width=170mm]{hist_ve_visits.png}
 \end{center}
 
-\centerline{Fig.18 Comparison of each visit for the first star in figure 8.}
-\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
+\centerline{Fig.10 Histogram of RV shifts for individual visits}
 \bigskip
+
+Then, we try to find some relation between out results and FiberID, MJD(Modified Julia Date), RA and DEC. Figures 11, 12, 13, 14 and 15 shows the relation.
+
+\begin{center}
+\includegraphics[width=170mm]{dchi_vs_all.png}
+\end{center}
+
+\centerline{Fig.11 Delta-chi-squared vs MJD, FiberID, RA and DEC for individual visitis}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{a_vs_all.png}
+\end{center}
+
+\centerline{Fig.12 a vs MJD, FiberID, RA and DEC for individual visitis}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{b_vs_all.png}
+\end{center}
+
+\centerline{Fig.13 b vs MJD, FiberID, RA and DEC for individual visitis}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{c_vs_all.png}
+\end{center}
+
+\centerline{Fig.14 c vs MJD, FiberID, RA and DEC for individual visitis}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{ve_vs_all.png}
+\end{center}
+
+\centerline{Fig.15 RV shifts vs MJD, FiberID, RA and DEC for individual visitis}
+\bigskip
+
+Finally, we shows our RV shifts results are better than results from the APOGEE team. The evidences are in the following zoom-in plots.
 
@@
 Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
- \bigskip
 
-\begin{center}
-\includegraphics[width=170mm]{d_figure_1.png}
-\end{center}
-
-\centerline{Diagnostic Fig.1 Histogram of a b c for apstar data (What we use now)}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_2.png}
-\end{center}
-
-\centerline{Diagnostic Fig.2 Four fake stars with Gaussian wave pack spectrums}
-\centerline{The green line is the template and the black line is the observation}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_3.png}
-\end{center}
-
-\centerline{Diagnostic Fig.3 Spectrum of the four stars with biggest c-a}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_4.png}
-\end{center}
-
-\centerline{Diagnostic Fig.4 Spectrum of the four stars with biggest a-c}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_5.png}
-\end{center}
-
-\centerline{Diagnostic Fig.5 Spectrum of the four stars with biggest a+c-2b}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_6.png}
-\end{center}
-
-\centerline{Diagnostic Fig.6 Spectrum of the four stars with b closest to 1}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_7.png}
-\end{center}
-
-\centerline{Diagnostic Fig.7 Radial velocity shifts}
-\centerline{ $v_3$ is the RV shift obtained from a, b and c. $v_5$ is from the five parameters. $v$ is from a, b and c if $2b>a+c$ and $v$ = $v_5$ if $2b<a+c$}
-\bigskip
+reference
+\bibliography{t_1,pubext}
 

### 2017-01-26 0124_plots.py

@@ -1,0 +1,946 @@
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import matplotlib
+import pickle
+
+from TheCannon_2 import dataset,apogee
+from TheCannon_2 import model
+
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# load path
+
+pkl_file = open('n_900_path_fits.pkl', 'rb')
+path_fits = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_900_path_flux.pkl', 'rb')
+path_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# mean_ivar
+
+pkl_file = open('n_900_mean_ivar.pkl', 'rb')
+mi = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+N = len(path_fits)
+print(N)
+
+velocity = []
+fiber_id = []
+mean_ivar = []
+parameters = []
+a = []
+b = []
+c= []
+
+nor = []
+ivar=[]
+inf =[]
+inf_label= []
+dchi = []
+
+MJD = []
+meanivar = []
+
+RA = []
+DEC = []
+SNR = []
+
+
+for i in range(0,N):
+    print("loading star %d"%(i+1))
+
+    star_i = fits.open(path_fits[i])
+
+
+    ni = len(star_i[4].data[:, 0])
+
+    #mean ivar
+    one = np.ones(ni-2)
+    meanivar = np.append(meanivar,one*mi[i])
+
+    dchi = np.append(dchi,star_i[6].data[2:ni])
+    # SNR RA DEC
+    SNR = np.append(SNR,(star_i[0].header["SNR"]*one))
+    RA = np.append(RA, (star_i[0].header["RA"] * one))
+    DEC = np.append(DEC, (star_i[0].header["DEC"] * one))
+
+
+
+    velocity = np.append(velocity,star_i[10].data[2:ni,0])
+    fiber_id = np.append(fiber_id,star_i[7].data)
+    mean_ivar.append(np.mean(star_i[1].data[0]))
+    parameters = np.append(parameters,star_i[4].data[2:ni,2])
+
+    a = np.append(a, star_i[4].data[2:ni, 0])
+    b = np.append(b, star_i[4].data[2:ni, 1])
+    c = np.append(c, star_i[4].data[2:ni, 2])
+
+
[…]

### 2017-01-26 0125_choose_1_percent_new_single_table.py
Make everything simple
Delete unuseful parts and re-write everything in two simple programs.
The first one is choose 1% stars and calibrate RVs, then save the
result of every star in separate fits file. The second one is all my
plots in the document.

@@ -109,8 +109,8 @@ all_set = Table.read("/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.2
 # choose some of them
 choose = []
 a=0
-for i in range(0,3200):
-    a += np.random.randint(1,15)
+for i in range(0,4000):
+    a += np.random.randint(1,14)
     choose.append(a)
 
 choose = np.array(choose)
@@ -148,9 +148,12 @@ start_time = time.time()
 
 # save the path of the flux fits and the path of the opt parameters fits
 
-path_flux = []
-path_fits = []
+path_flux = np.array(["start"])
+path_fits = np.array(["start"])
 
+
+# mean ivar
+mi = []
 
 
 for i, row in enumerate(all_set):
@@ -158,6 +161,11 @@ for i, row in enumerate(all_set):
 
 
         image_path = "/Volumes/Data_2TB/Data/APOGEE_DR10_Apstar/apStar-s3-" + row["APOGEE_ID"] + ".fits"
+
+
+        RA = row["RA"]
+        DEC = row["DEC"]
+        SNR = row["SNR"]
 
         if not os.path.exists(image_path):
             print("{}/{} could not be found: {}".format(i + 1, N, image_path))
@@ -209,6 +217,12 @@ for i, row in enumerate(all_set):
             FiberID = m
 
             tr_ID = image_path
+            # data
+            MJD = dat[0]["MJD"]
+
+            # APOGEE velocity
+
+            VHELIO = dat[0]["VHELIO"]
 
             ## This is the real successful ones.
 
@@ -220,11 +234,11 @@ for i, row in enumerate(all_set):
             # by jason
 
             try:
-                star = len(flux[:, 0])
+                ni = len(flux[:, 0])
                 one = np.ones(len(flux[0, :]))
 
             except IndexError:
-                star = 1
+                ni = 1
                 one = np.ones(len(flux))
 
             else:
@@ -265,6 +279,11 @@ for i, row in enumerate(all_set):
                 opt_flux, parameters = model.fitting_spectrum_parameters_single \
                     (norm_tr_flux, norm_tr_ivar, inf_flux)
 
+                opt_flux_5 , parameters_5 = model.fitting_spectrum_parameters_single_5(norm_tr_flux, norm_tr_ivar, inf_flux)
+
+                parameters = np.c_[parameters,parameters_5]
+
+
[…]

### 2017-01-26 1020_normalize_flux_aspcap_v2.py

@@ -1,221 +1,0 @@
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-
-
-# function
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-# read data
-all_set = Table.read("/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/allStar-v304.fits")
-
-# data
-all_set_flux = []
-all_set_ivar = []
-all_set_error = []
-test_labels_all = []
-
-# choose some of them
-choose = []
-a=0
-for i in range(0,800):
-    a += np.random.randint(1,70)
-    choose.append(a)
-
-choose = np.array(choose)
-all_set = all_set[choose]
-
-
-# save the chosen star
-output = open('choose_800.pkl', 'wb')
-pickle.dump(choose, output)
-output.close()
-
-
-N = len(all_set)
-keep = np.ones(N, dtype=bool)
-tr_ID = []
-FiberID = []
-
-
-for i, row in enumerate(all_set):
-    try:
-        image_path = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_ASPCAP/aspcapStar-" + row["APOGEE_ID"] + ".fits"
-        # For apstar
-
-        image_path_2 = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_Apstar/apStar-s3-" + row["APOGEE_ID"] + ".fits"
-
-        if not os.path.exists(image_path):
-            print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-            keep[i] = False
-            continue
-
-        print("{}/{}: {}".format(i + 1, N, image_path))
-        # Let's only use two extension of the data
-
-        image = fits.open(image_path, ignore_missing_end=True)
-        dat = Table.read(image_path_2)
-
-        flux = image[1].data
-        flux_err = image[2].data
-
-    except IOError:
-        print("opts. This one fail")
[…]

### 2017-01-26 1020_plot_histogram.py

@@ -1,65 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import MaxNLocator
-from copy import deepcopy
-
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-from astropy.io.fits import getdata
-
-import AnniesLasso_2 as tc
-
-
-# open data
-
-pkl_file = open('parameters_500.pkl', 'rb')
-parameters_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('FiberID.pkl', 'rb')
-FiberID = pickle.load(pkl_file)
-pkl_file.close()
-
-# delete 0,0,0, which are the zero order of
-print(parameters_500.shape,FiberID.shape)
-
-colors = ['b', 'g', 'r']
-name = ["a","b","c"]
-
-# Plot histogram
-fig = plt.figure()
-plt.hist(parameters_500,bins=15,color=colors,label=name)
-plt.legend(prop={'size': 30})
-fig.suptitle('Histogram of parameters a,b and c',fontsize =30)
-plt.xlabel('values of a, b and c', fontsize=30)
-plt.ylabel('Number of stars', fontsize=30)
-
-plt.show()
-
-
-print("Plot histogram")
-
-# plot the parameters vs metadata
-
-
-font = {'weight': 'bold','size': 30}
-matplotlib.rc('font', **font)
-fig = plt.figure()
-
-plt.plot(FiberID,parameters_500[:,0], "bo", label="a", linewidth=3.0)
-plt.plot(FiberID,parameters_500[:,1], "go", label="b", linewidth=3.0)
-plt.plot(FiberID,parameters_500[:,2], "ro", label="c", linewidth=3.0)
-
-plt.legend(loc="best")
-
-fig.suptitle('a, b, c against mean fiber number', fontsize=30)
-plt.xlabel('fiber number', fontsize=28)
-plt.ylabel('values of a, b, c', fontsize=26)
-plt.show()
-

### 2017-01-26 1020_read_fiber_id.py

@@ -1,11 +1,0 @@
-from astropy.table import Table
-from astropy.io.fits import getdata
-from astropy.io import fits
-
-image_path = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_Apstar/apStar-s3-2M00000068+5710233.fits"
-image = fits.open(image_path,ignore_missing_end=True)
-
-dat = Table.read(image_path)
-
-#print(dat[0]["FIBER"],sum(dat[0]["FIBER"])/len(dat[0]["FIBER"]))
-print(dat[0]["FIBER"])

### 2017-01-26 1021_all_in_one.py

@@ -1,342 +1,0 @@
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-from astropy.io.fits import getdata
-
-import AnniesLasso_2 as tc
-
-
-
-# function
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-# read data
-all_set = Table.read("/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/allStar-v304.fits")
-
-
-
-
-"""
-# choose some of them
-choose = []
-a=0
-for i in range(0,1000):
-    a += np.random.randint(1,55)
-    choose.append(a)
-
-choose = np.array(choose)
-all_set = all_set[choose]
-
-
-# save the chosen star
-output = open('choose_500.pkl', 'wb')
-pickle.dump(choose, output)
-output.close()
-
-"""
-# open the chosen star
-pkl_file = open('choose_500.pkl', 'rb')
-choose = pickle.load(pkl_file)
-pkl_file.close()
-
-all_set = all_set[choose]
-
-# data
-all_set_flux = []
-all_set_ivar = []
-all_set_error = []
-test_labels_all = []
-N = len(all_set)
-keep = np.ones(N, dtype=bool)
-tr_ID = []
-FiberID = []
-
-
-for i, row in enumerate(all_set):
-    try:
-        image_path = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_ASPCAP/aspcapStar-" + row["APOGEE_ID"] + ".fits"
-        # For apstar
-
-        image_path_2 = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_Apstar/apStar-s3-" + row["APOGEE_ID"] + ".fits"
-
-        if not os.path.exists(image_path):
-            print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-            keep[i] = False
-            continue
-
[…]

### 2017-01-26 1025_relate_fiber_parameters.py

@@ -1,116 +1,0 @@
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-from astropy.io.fits import getdata
-from numpy.linalg import inv
-import AnniesLasso_2 as tc
-
-
-training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
-training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
-
-
-training_set = Table.read("reference_labels.csv")
-
-
-
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-
-N = len(training_set)
-keep = np.ones(N, dtype=bool)
-
-training_set_flux = []
-training_set_ivar = []
-training_set_error = []
-for i, row in enumerate(training_set):
-
-    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
-
-    if not os.path.exists(image_path):
-        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-        keep[i] = False
-        continue
-
-    print("{}/{}: {}".format(i + 1, N, image_path))
-
-    image = fits.open(image_path)
-
-    flux = image[1].data
-    flux_err = image[2].data
-
-    badpix = get_pixmask(flux, flux_err)
-    ivar = 1.0/flux_err**2
-    error = flux_err
-    # badpix is a array and the length is 8575
-    flux[badpix] = 1.0
-    ivar[badpix] = 0.0
-
-    training_set_flux.append(flux)
-    training_set_ivar.append(ivar)
-    training_set_error.append(error)
-
-training_set_flux = np.array(training_set_flux)
-training_set_ivar = np.array(training_set_ivar)
-training_set_error = np.array(training_set_error)
-
-
-assert all(keep)
-
-# Construct model.
[…]

### 2017-01-26 1026_Plot_delta_chi_squared.py

@@ -1,30 +1,0 @@
-from numpy import genfromtxt
-import matplotlib.pyplot as plt
-import random
-import matplotlib
-import numpy as np
-import pickle
-
-# import data
-pkl_file = open('delta_chi_500.pkl', 'rb')
-delta_chi_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('FiberID.pkl', 'rb')
-FiberID = pickle.load(pkl_file)
-pkl_file.close()
-
-#Plot
-font = {'weight': 'bold','size': 25}
-matplotlib.rc('font', **font)
-fig = plt.figure()
-
-axes = plt.gca()
-axes.set_ylim([0,50000])
-
-plt.plot(FiberID,delta_chi_500,"ro")
-
-fig.suptitle('Delta-Chi-Squared', fontsize=30)
-plt.xlabel('Fiber ID', fontsize=30)
-plt.ylabel('Delta chi-squared', fontsize=30)
-plt.show()

### 2017-01-26 1026_opt_1percent.py

@@ -1,178 +1,0 @@
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-from astropy.io.fits import getdata
-from numpy.linalg import inv
-import AnniesLasso_2 as tc
-import time
-
-
-
-# get the time of the program
-start_time = time.time()
-
-
-training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
-training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
-
-
-training_set = Table.read("reference_labels.csv")
-
-
-
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-
-N = len(training_set)
-keep = np.ones(N, dtype=bool)
-
-training_set_flux = []
-training_set_ivar = []
-training_set_error = []
-for i, row in enumerate(training_set):
-
-    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
-
-    if not os.path.exists(image_path):
-        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-        keep[i] = False
-        continue
-
-    print("{}/{}: {}".format(i + 1, N, image_path))
-
-    image = fits.open(image_path)
-
-    flux = image[1].data
-    flux_err = image[2].data
-
-    badpix = get_pixmask(flux, flux_err)
-    ivar = 1.0/flux_err**2
-    error = flux_err
-    # badpix is a array and the length is 8575
-    flux[badpix] = 1.0
-    ivar[badpix] = 0.0
-
-    training_set_flux.append(flux)
-    training_set_ivar.append(ivar)
-    training_set_error.append(error)
-
-training_set_flux = np.array(training_set_flux)
-training_set_ivar = np.array(training_set_ivar)
[…]

### 2017-01-26 1103_normalized_flux_selected_v1.py

@@ -1,241 +1,0 @@
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-
-
-# function
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-# read data
-all_set = Table.read("/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/allStar-v304.fits")
-
-# data
-all_set_flux = []
-all_set_ivar = []
-all_set_error = []
-test_labels_all = []
-
-# choose some of them
-choose = []
-a=0
-for i in range(0,1600):
-    a += np.random.randint(1,30)
-    choose.append(a)
-
-choose = np.array(choose)
-all_set = all_set[choose]
-# Now all set only have 1600 stars
-
-
-# save the chosen star and the new all-set. Let's name it as testing set.
-output = open('choose_800.pkl', 'wb')
-pickle.dump(choose, output)
-output.close()
-
-
-
-
-N = len(all_set)
-tr_ID = []
-FiberID = []
-choose_800_final = []
-fail = 0
-
-for i, row in enumerate(all_set):
-    try:
-        image_path = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_ASPCAP/aspcapStar-" + row["APOGEE_ID"] + ".fits"
-        # For apstar
-
-        image_path_2 = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_Apstar/apStar-s3-" + row["APOGEE_ID"] + ".fits"
-
-        if not os.path.exists(image_path):
-            print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-            continue
-
-        print("{}/{}: {}".format(i + 1, N, image_path))
-        # Let's only use two extension of the data
-
-        image = fits.open(image_path, ignore_missing_end=True)
-        dat = Table.read(image_path_2)
-
-        flux = image[1].data
-        flux_err = image[2].data
-
-    except IOError:
-        print("opts. This one fail")
[…]

### 2017-01-26 1103_opt_5_parameters.py

@@ -1,169 +1,0 @@
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-from astropy.io.fits import getdata
-from numpy.linalg import inv
-import AnniesLasso_2 as tc
-import time
-
-
-
-# get the time of the program
-start_time = time.time()
-
-
-training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
-training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
-
-
-training_set = Table.read("reference_labels.csv")
-
-
-
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-
-N = len(training_set)
-keep = np.ones(N, dtype=bool)
-
-training_set_flux = []
-training_set_ivar = []
-training_set_error = []
-
-for i, row in enumerate(training_set):
-    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
-    if not os.path.exists(image_path):
-        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-        keep[i] = False
-        continue
-    print("{}/{}: {}".format(i + 1, N, image_path))
-    image = fits.open(image_path)
-    flux = image[1].data
-    flux_err = image[2].data
-    badpix = get_pixmask(flux, flux_err)
-    ivar = 1.0/flux_err**2
-    error = flux_err
-    # badpix is a array and the length is 8575
-    flux[badpix] = 1.0
-    ivar[badpix] = 0.0
-    training_set_flux.append(flux)
-    training_set_ivar.append(ivar)
-    training_set_error.append(error)
-
-training_set_flux = np.array(training_set_flux)
-training_set_ivar = np.array(training_set_ivar)
-training_set_error = np.array(training_set_error)
-
-
[…]

### 2017-01-26 1106_normalize_flux_pure_aspcap_v1.py

@@ -1,328 +1,0 @@
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-
-
-# function
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-def get_error_mask(err):
-    bad_err = (~np.isfinite(err))
-    bad_pixels = bad_err
-    return bad_pixels
-
-# read data
-all_set = Table.read("/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/allStar-v304.fits")
-
-# data
-
-
-## 1. read the dat
-## 2. add a mask (bitmask)
-## 3. filter-mean inverse variance
-
-
-
-# Try to use numpy array to avoid memory overflow
-all_set_flux = np.zeros(8575)
-all_set_ivar = np.zeros(8575)
-all_set_error = np.zeros(8575)
-
-
-# choose some of them
-choose = []
-a=0
-for i in range(0,3200):
-    a += np.random.randint(1,11)
-    choose.append(a)
-
-choose = np.array(choose)
-all_set = all_set[choose]
-# Now all set only have 1600 stars
-
-
-# save the chosen star and the new all-set. Let's name it as testing set.
-output = open('n_choose_800.pkl', 'wb')
-pickle.dump(choose, output)
-output.close()
-
-
-
-
-N = len(all_set)
-test_labels_all = []
-tr_ID = []
-FiberID = []
-choose_800_final = []
-fail = 0
-star=0
-
-# choose some flux and normalize them first, then filter the mean inverse variance.
-
-
-for i, row in enumerate(all_set):
-    try:
-
-
-        image_path = "/Users/caojunzhi/Desktop/Data/APOGEE_DR10_Apstar/apStar-s3-" + row["APOGEE_ID"] + ".fits"
-
-        if not os.path.exists(image_path):
-            print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-            fail += 1
-            continue
-
-        print("{}/{}: {}".format(i + 1, N, image_path))
[…]

### 2017-01-26 1106_opt_1_percent.py

@@ -1,172 +1,0 @@
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-from astropy.io.fits import getdata
-from numpy.linalg import inv
-import AnniesLasso_2 as tc
-import time
-
-
-
-# get the time of the program
-start_time = time.time()
-
-
-training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
-training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
-
-
-training_set = Table.read("reference_labels.csv")
-
-
-
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-
-N = len(training_set)
-keep = np.ones(N, dtype=bool)
-
-training_set_flux = []
-training_set_ivar = []
-training_set_error = []
-
-for i, row in enumerate(training_set):
-    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
-    if not os.path.exists(image_path):
-        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-        keep[i] = False
-        continue
-    print("{}/{}: {}".format(i + 1, N, image_path))
-    image = fits.open(image_path)
-    flux = image[1].data
-    flux_err = image[2].data
-    badpix = get_pixmask(flux, flux_err)
-    ivar = 1.0/flux_err**2
-    error = flux_err
-    # badpix is a array and the length is 8575
-    flux[badpix] = 1.0
-    ivar[badpix] = 0.0
-    training_set_flux.append(flux)
-    training_set_ivar.append(ivar)
-    training_set_error.append(error)
-
-training_set_flux = np.array(training_set_flux)
-training_set_ivar = np.array(training_set_ivar)
-training_set_error = np.array(training_set_error)
-
-
-assert all(keep)
-
[…]

### 2017-01-26 1106_plot_choose_4_stars.py

@@ -1,311 +1,0 @@
-from numpy import genfromtxt
-import matplotlib.pyplot as plt
-import random
-import matplotlib
-import numpy as np
-import pickle
-from astropy.table import Table
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import AnniesLasso_2 as tc
-
-import plot_class_4_star_v2_1107
-
-
-
-# import data
-pkl_file = open('n_delta_chi_900.pkl', 'rb')
-delta_chi_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_parameters_900.pkl', 'rb')
-parameters_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_FiberID_900.pkl', 'rb')
-FiberID = pickle.load(pkl_file)
-pkl_file.close()
-
-
-pkl_file = open('n_tr_ID_900.pkl', 'rb')
-tr_ID_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_testing_labels_900.pkl', 'rb')
-test_labels = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("testing_set_900.pkl", 'rb')
-testing_set = pickle.load(pkl_file)
-pkl_file.close()
-
-
-# flux,ivar and error
-
-pkl_file = open("n_testing_flux_900.pkl", 'rb')
-testing_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("n_testing_ivar_900.pkl", 'rb')
-testing_ivar = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("n_testing_error_900.pkl", 'rb')
-testing_error = pickle.load(pkl_file)
-pkl_file.close()
-
-
-## check error
-"""
-plt.plot(testing_error[1,:],"r")
-
-axes = plt.gca()
-
-axes.set_ylim([-0.01,0.01])
-
-
-plt.show()
-
-"""
-
-
-
-
-
-#print(choose_800_final.shape)
-#print(choose_800_final.shape,FiberID.shape)
-
-
-# check shape
-#print(parameters_500.shape,delta_chi_500.shape)
-
-#### find the biggest four delta-chi and smallest four
-N_star = len(delta_chi_500)
-
-
[…]

### 2017-01-26 1108_optimize_all_data.py

@@ -1,321 +1,0 @@
-from numpy import genfromtxt
-import matplotlib.pyplot as plt
-import random
-import matplotlib
-import numpy as np
-import pickle
-from astropy.table import Table
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import AnniesLasso_2 as tc
-import time
-
-## training the cannon
-
-pkl_file = open('wl.pkl', 'rb')
-wl = pickle.load(pkl_file)
-pkl_file.close()
-
-
-
-training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
-training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
-
-
-training_set = Table.read("reference_labels.csv")
-
-
-
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-
-N = len(training_set)
-keep = np.ones(N, dtype=bool)
-
-training_set_flux = []
-training_set_ivar = []
-training_set_error = []
-
-for i, row in enumerate(training_set):
-    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
-    if not os.path.exists(image_path):
-        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-        keep[i] = False
-        continue
-    print("{}/{}: {}".format(i + 1, N, image_path))
-    image = fits.open(image_path)
-    flux = image[1].data
-    flux_err = image[2].data
-    badpix = get_pixmask(flux, flux_err)
-    ivar = 1.0/flux_err**2
-    error = flux_err
-    # badpix is a array and the length is 8575
-    flux[badpix] = 1.0
-    ivar[badpix] = 0.0
-    training_set_flux.append(flux)
-    training_set_ivar.append(ivar)
-    training_set_error.append(error)
-
-training_set_flux = np.array(training_set_flux)
-training_set_ivar = np.array(training_set_ivar)
-training_set_error = np.array(training_set_error)
-
-
-assert all(keep)
-
-# Construct model.
-model = tc.L1RegularizedCannonModel(
[…]

### 2017-01-26 1120_obtain_abc_for_training_set.py

@@ -1,208 +1,0 @@
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-
-import AnniesLasso_2 as tc
-import time
-
-# Get training set data
-
-# get the time of the program
-start_time = time.time()
-
-
-training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
-training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
-
-
-training_set = Table.read("reference_labels.csv")
-
-
-
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-
-N = len(training_set)
-keep = np.ones(N, dtype=bool)
-
-training_set_flux = []
-training_set_ivar = []
-training_set_error = []
-
-for i, row in enumerate(training_set):
-    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
-    if not os.path.exists(image_path):
-        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-        keep[i] = False
-        continue
-    print("{}/{}: {}".format(i + 1, N, image_path))
-    image = fits.open(image_path)
-    flux = image[1].data
-    flux_err = image[2].data
-    badpix = get_pixmask(flux, flux_err)
-    ivar = 1.0/flux_err**2
-    error = flux_err
-    # badpix is a array and the length is 8575
-    flux[badpix] = 1.0
-    ivar[badpix] = 0.0
-    training_set_flux.append(flux)
-    training_set_ivar.append(ivar)
-    training_set_error.append(error)
-
-training_set_flux = np.array(training_set_flux)
-training_set_ivar = np.array(training_set_ivar)
-training_set_error = np.array(training_set_error)
-
-
-assert all(keep)
-
-# Construct model.
[…]

### 2017-01-26 1120_plot_check_training_abc.py

@@ -1,108 +1,0 @@
-import os
-import numpy as np
-from numpy import genfromtxt
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-import matplotlib as mpl
-
-import AnniesLasso_2 as tc
-import time
-
-
-# load data
-
-pkl_file = open('parameters_tr_inf.pkl', 'rb')
-parameters_tr_inf = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('parameters_tr.pkl', 'rb')
-parameters_tr = pickle.load(pkl_file)
-pkl_file.close()
-
-
-# labels
-tr_label = genfromtxt("reference-3.csv",delimiter=",")
-tr_label = np.array(tr_label)
-
-
-pkl_file = open('inf_labels_tr_opt.pkl', 'rb')
-inf_labels_tr_opt = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('inf_labels_tr.pkl', 'rb')
-inf_labels_tr = pickle.load(pkl_file)
-pkl_file.close()
-
-#load n_900 data
-
-pkl_file = open('n_testing_labels_900.pkl', 'rb')
-ref_labels_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_inf_labels_900_opt.pkl', 'rb')
-inf_labels_900_opt = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_inf_label_900.pkl', 'rb')
-inf_labels_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_testing_ivar_900.pkl', 'rb')
-testing_ivar_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-ivar= np.mean(testing_ivar_900,axis=1)
-ivar = np.array(ivar)
-
-
-# chi-squared:
-
-# chi squared
-
-xp=2
-
-old = np.sum((ref_labels_900[:,xp]-inf_labels_900[:,xp])**2)
-opt = np.sum((ref_labels_900[:,xp]-inf_labels_900_opt[:,xp])**2)
-
-print(old,opt)
-
-
-
-
-
-
-font = {'weight': 'bold','size': 20}
-mpl.rc('font', **font)
[…]

### 2017-01-26 1121_plot_choose_4_stars.py

@@ -1,396 +1,0 @@
-from numpy import genfromtxt
-import matplotlib.pyplot as plt
-import random
-import matplotlib
-import numpy as np
-import pickle
-from astropy.table import Table
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import AnniesLasso_2 as tc
-
-import plot_class_4_star_v2_1107
-
-
-
-
-
-
-
-
-# import data
-pkl_file = open('n_delta_chi_900.pkl', 'rb')
-delta_chi_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-
-
-pkl_file = open('n_testing_labels_900.pkl', 'rb')
-test_labels_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_parameters_900.pkl', 'rb')
-parameters_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_FiberID_900.pkl', 'rb')
-FiberID = pickle.load(pkl_file)
-pkl_file.close()
-
-
-pkl_file = open('n_tr_ID_900.pkl', 'rb')
-tr_ID_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_inf_label_900.pkl', 'rb')
-inf_labels_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("testing_set_900.pkl", 'rb')
-testing_set = pickle.load(pkl_file)
-pkl_file.close()
-
-
-# flux,ivar and error
-
-pkl_file = open("n_testing_flux_900.pkl", 'rb')
-testing_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("n_testing_ivar_900.pkl", 'rb')
-testing_ivar = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("n_inf_flux_900.pkl", 'rb')
-inf_flux_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("n_testing_error_900.pkl", 'rb')
-testing_error = pickle.load(pkl_file)
-pkl_file.close()
-
-
-## check error
-"""
-plt.plot(testing_error[1,:],"r")
-
-axes = plt.gca()
-
-axes.set_ylim([-0.01,0.01])
-
-
-plt.show()
-
-"""
-
[…]

### 2017-01-26 1125_plot_4_calibrated_flux.py

@@ -1,515 +1,0 @@
-from numpy import genfromtxt
-import matplotlib.pyplot as plt
-import random
-import matplotlib
-import numpy as np
-import pickle
-from astropy.table import Table
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import AnniesLasso_2 as tc
-
-import plot_class_4_star_v2_1107
-
-
-
-
-
-
-
-
-# import data
-pkl_file = open('n_delta_chi_900.pkl', 'rb')
-delta_chi_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-
-
-pkl_file = open('n_testing_labels_900.pkl', 'rb')
-test_labels_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_parameters_900.pkl', 'rb')
-parameters_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_FiberID_900.pkl', 'rb')
-FiberID = pickle.load(pkl_file)
-pkl_file.close()
-
-
-pkl_file = open('n_tr_ID_900.pkl', 'rb')
-tr_ID_500 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('n_inf_label_900.pkl', 'rb')
-inf_labels_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("testing_set_900.pkl", 'rb')
-testing_set = pickle.load(pkl_file)
-pkl_file.close()
-
-
-# flux,ivar and error
-
-pkl_file = open("n_testing_flux_900.pkl", 'rb')
-testing_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("n_testing_ivar_900.pkl", 'rb')
-testing_ivar = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("n_inf_flux_900.pkl", 'rb')
-inf_flux_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open("n_testing_error_900.pkl", 'rb')
-testing_error = pickle.load(pkl_file)
-pkl_file.close()
-
-
-## check error
-"""
-plt.plot(testing_error[1,:],"r")
-
-axes = plt.gca()
-
-axes.set_ylim([-0.01,0.01])
-
-
[…]

### 2017-01-26 1125_plot_histogram_deviation_inf_labels.py

@@ -1,72 +1,0 @@
-import pickle
-import matplotlib
-import matplotlib.pyplot as plt
-
-
-# read data
-
-pkl_file = open('inf_labels_deviation_teff_900.pkl', 'rb')
-inf_labels_deviation_teff_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('inf_labels_deviation_logg_900.pkl', 'rb')
-inf_labels_deviation_logg_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('inf_labels_deviation_fe_900.pkl', 'rb')
-inf_labels_deviation_fe_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-
-# plot histogram
-
-
-"""
-font = {'weight': 'bold','size': 30}
-matplotlib.rc('font', **font)
-fig = plt.figure()
-
-
-
-colors = ['b', 'g', 'r']
-name = ["Delta Teff","Delta logg","Delta Fe/H"]
-print(inf_labels_deviation_teff_900.shape,inf_labels_deviation_logg_900.shape,inf_labels_deviation_fe_900.shape)
-
-# Plot histogram
-fig = plt.figure()
-plt.hist(inf_labels_deviation_teff_900,bins=15,color=colors[0],label=name[0])
-plt.legend(prop={'size': 30})
-fig.suptitle('Histogram for the deviations of the inferred Teff',fontsize =30)
-plt.xlabel('values of Delta Teff', fontsize=30)
-plt.ylabel('Number of stars', fontsize=30)
-plt.show()
-
-
-colors = ['b', 'g', 'r']
-name = ["Delta Teff","Delta logg","Delta Fe/H"]
-
-# Plot histogram
-fig = plt.figure()
-plt.hist(inf_labels_deviation_logg_900,bins=15,color=colors[1],label=name[1])
-plt.legend(prop={'size': 30})
-fig.suptitle('Histogram for the deviations of the inferred logg',fontsize =30)
-plt.xlabel('values of Delta logg', fontsize=30)
-plt.ylabel('Number of stars', fontsize=30)
-plt.show()
-"""
-
-
-colors = ['b', 'g', 'r']
-name = ["Delta Teff","Delta logg","Delta Fe/H"]
-
-# Plot histogram
-fig = plt.figure()
-plt.hist(inf_labels_deviation_fe_900,bins=15,color=colors[2],label=name[2])
[…]

### 2017-01-26 1125_read_apstar_flux.py

@@ -1,251 +1,0 @@
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-import AnniesLasso_2 as tc
-
-
-# function
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-def get_error_mask(err):
-    bad_err = (~np.isfinite(err))
-    bad_pixels = bad_err
-    return bad_pixels
-
-pkl_file = open('wl.pkl', 'rb')
-wl = pickle.load(pkl_file)
-pkl_file.close()
-
-# read data
-
-# open the choose file
-pkl_file = open('n_tr_ID_900.pkl', 'rb')
-tr_ID_900 = pickle.load(pkl_file)
-pkl_file.close()
-
-
-
-
-# train the model:
-
-training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
-training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
-
-
-training_set = Table.read("reference_labels.csv")
-
-
-
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-
-N = len(training_set)
-keep = np.ones(N, dtype=bool)
-
-training_set_flux = []
-training_set_ivar = []
-training_set_error = []
-
-for i, row in enumerate(training_set):
-    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
-    if not os.path.exists(image_path):
-        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-        keep[i] = False
-        continue
-    print("{}/{}: {}".format(i + 1, N, image_path))
-    image = fits.open(image_path)
-    flux = image[1].data
-    flux_err = image[2].data
[…]

### 2017-01-26 1129_opt_1_and_calculate_radial_velocity.py

@@ -1,184 +1,0 @@
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib
-from astropy.io.fits import getdata
-from numpy.linalg import inv
-import AnniesLasso_2 as tc
-import time
-
-
-
-# get the time of the program
-start_time = time.time()
-
-
-training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
-training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
-
-
-training_set = Table.read("reference_labels.csv")
-
-
-
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-
-
-N = len(training_set)
-keep = np.ones(N, dtype=bool)
-
-training_set_flux = []
-training_set_ivar = []
-training_set_error = []
-
-for i, row in enumerate(training_set):
-    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
-    if not os.path.exists(image_path):
-        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-        keep[i] = False
-        continue
-    print("{}/{}: {}".format(i + 1, N, image_path))
-    image = fits.open(image_path)
-    flux = image[1].data
-    flux_err = image[2].data
-    badpix = get_pixmask(flux, flux_err)
-    ivar = 1.0/flux_err**2
-    error = flux_err
-    # badpix is a array and the length is 8575
-    flux[badpix] = 1.0
-    ivar[badpix] = 0.0
-    training_set_flux.append(flux)
-    training_set_ivar.append(ivar)
-    training_set_error.append(error)
-
-training_set_flux = np.array(training_set_flux)
-training_set_ivar = np.array(training_set_ivar)
-training_set_error = np.array(training_set_error)
-
-
-assert all(keep)
-
[…]

### 2017-01-26 1130_plot_load_para_choose_4_star.py

@@ -1,50 +1,0 @@
-
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-import plot_class_4_star_v2_1107
-
-# load path
-
-pkl_file = open('n_900_path_fits.pkl', 'rb')
-path_fits = pickle.load(pkl_file)
-pkl_file.close()
-
-
-pkl_file = open('n_900_path_flux.pkl', 'rb')
-path_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-
-N = len(path_fits)
-print(N)
-
-parameters = []
-
-
-for i in range(0,N):
-    print("loading star %d"%(i+1))
-    star_i = fits.open(path_fits[i])
-    parameters.append(star_i[4].data[0])
-    print(star_i[4].data[0].shape)
-
-parameters = np.array(parameters)
-
-parameters_500 = parameters
-
-big_a_c = (parameters_500[:,2]-parameters_500[:,0]).argsort()[0:4]
-
-big_c_a = (parameters_500[:,0]-parameters_500[:,2]).argsort()[0:4]
-
-
-print(parameters_500[big_a_c])
-
-
-# plot
-model = plot_class_4_star_v2_1107.plot_4()
-model.plot_name_4(path_fits[big_a_c])
-
-

### 2017-01-26 1206_diagnostic_choose_4_small_a_c_move_manually.py

@@ -1,224 +1,0 @@
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import AnniesLasso_2 as tc
-import matplotlib.pyplot as plt
-import pickle
-
-import plot_class_4_star_v2_1107
-
-# load path
-
-pkl_file = open('n_900_path_fits.pkl', 'rb')
-path_fits = pickle.load(pkl_file)
-pkl_file.close()
-
-
-pkl_file = open('n_900_path_flux.pkl', 'rb')
-path_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-
-N = len(path_fits)
-print(N)
-
-velocity = []
-mean_fiber_id = []
-mean_ivar = []
-parameters = []
-nor = []
-ivar=[]
-inf =[]
-inf_label= []
-
-for i in range(0,N):
-    print("loading star %d"%(i+1))
-    star_i = fits.open(path_fits[i])
-    velocity.append(star_i[10].data[0])
-    mean_fiber_id.append(np.mean(star_i[7].data))
-    mean_ivar.append(np.mean(star_i[1].data[0]))
-    parameters.append(star_i[4].data[0])
-
-    nor.append(star_i[0].data[0])
-    ivar.append(star_i[1].data[0])
-    inf.append(star_i[2].data[0])
-    inf_label.append(star_i[9].data[0])
-
-    print(star_i[4].data[0].shape)
-
-velocity =np.array(velocity)
-mean_fiber_id = np.array(mean_fiber_id)
-parameters = np.array(parameters)
-nor=np.array(nor)
-ivar = np.array(ivar)
-inf = np.array(inf)
-inf_label = np.array(inf_label)
-
-
-v_jason = (parameters[:,2]-parameters[:,0])*(4144.68)
-
-
-
-# find the four stars with biggest v
-
-
-"""
-# Jason
-
-N =len(path_fits)
-big_v_4 = (velocity*velocity).argsort()[N-4:N]
-big_v_jason = (v_jason*v_jason).argsort()[N-4:N]
-
-model = plot_class_4_star_v3_1201.plot_4()
-# model.plot_name_4(path_fits[big_v_4])
-
-model.plot_name_4(path_fits[big_v_jason])
-
-
-"""
-N =len(path_fits)
-big_v_4 = (velocity*velocity).argsort()[N-4:N]
-big_v_jason = (v_jason*v_jason).argsort()[N-4:N]
-
[…]

### 2017-01-26 1208_compare_rv_single_file.py

@@ -1,74 +1,0 @@
-import pickle
-import PyAstronomy
-from PyAstronomy import pyasl
-import numpy as np
-from astropy.io import fits
-import matplotlib.pylab as plt
-import Cross_correlation_1207 as cc
-
-
-# load path
-
-pkl_file = open('n_900_path_fits.pkl', 'rb')
-path_fits = pickle.load(pkl_file)
-pkl_file.close()
-
-
-pkl_file = open('n_900_path_flux.pkl', 'rb')
-path_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-
-N = len(path_fits)
-print(N)
-
-velocity = []
-mean_fiber_id = []
-mean_ivar = []
-parameters = []
-nor = []
-ivar=[]
-inf =[]
-inf_label= []
-
-for i in range(0,N):
-    print("loading star %d"%(i+1))
-    star_i = fits.open(path_fits[i])
-    velocity.append(star_i[10].data[0])
-    mean_fiber_id.append(np.mean(star_i[7].data))
-    mean_ivar.append(np.mean(star_i[1].data[0]))
-    parameters.append(star_i[4].data[0])
-
-    nor.append(star_i[0].data[0])
-    ivar.append(star_i[1].data[0])
-    inf.append(star_i[2].data[0])
-    inf_label.append(star_i[9].data[0])
-
-    print(star_i[4].data[0].shape)
-
-velocity =np.array(velocity)
-mean_fiber_id = np.array(mean_fiber_id)
-parameters = np.array(parameters)
-nor=np.array(nor)
-ivar = np.array(ivar)
-inf = np.array(inf)
-inf_label = np.array(inf_label)
-
-# velocity compare  CFF,David,Jason
-#N =605
-a=0
-b=100
-
-for i in range(a,b):
-
-    print('\033[1;31mdoing star %d of %d\033[1;m' % (i+1,N))
-    # CC, David, Jason
-    v1,v2,v3 = cc.cross_correlation_velocity_v2(parameters[i,0],parameters[i,1],parameters[i,2])
-
-    velocity_i = np.array([v1,v2,v3])
-    name = "/Users/caojunzhi/Desktop/Data/velocity_900/"+"velocity"+str(i)+".pkl"
-
-    output = open(name, 'wb')
-    pickle.dump(velocity_i, output)
-    output.close()
-

### 2017-01-26 1208_cross_correlation_velocity.py

@@ -1,157 +1,0 @@
-from __future__ import print_function, division
-import math
-import pickle
-import PyAstronomy
-import matplotlib
-
-from PyAstronomy import pyasl
-import numpy as np
-import matplotlib.pylab as plt
-
-
-import plot_class_4_star_v2_1107
-
-pkl_file = open('wl.pkl', 'rb')
-wl = pickle.load(pkl_file)
-pkl_file.close()
-
-def log(x):
-    return math.log10(x)
-
-def power10(x):
-    return 10**x
-
-wl_log = list(map(log,wl))
-wl_log = np.array(wl_log)
-
-wl_log_long = np.linspace(wl_log[0],wl_log[-1],8575*50)
-#print(wl_log_long)
-
-# make a new wave length scale ws: 8575*10 points
-ws = 10**(wl_log_long)
-print("ws shape check")
-print(ws.shape)
-
-# divide
-
-# May use this
-"""
-wl_log_long = np.linspace(wl_log[0],wl_log[-1],8575*10)
-wl_log_long_s =np.linspace(wl_log[4000],wl_log[4575],8575*2)
-wl_long = list(map(power10,wl_log_long))
-wl_long = np.array(wl_log)
-
-wl_long_s = list(map(power10,wl_log_long_s))
-wl_long_s = np.array(wl_long_s)
-print(wl_long_s[0],wl_long_s[-1])
-"""
-
-
-
-# Create the template
-
-# gamma = 0.2086
-gamma = 0.199
-
-sigma =10
-
-#tw = wl
-tw =ws
-#tw = np.linspace(wl[0],wl[-1],8575*10)
-tf = np.exp(-(tw-16000.0)**2/(2.*sigma**2))+1
-
-# choose 20%
-choose = np.arange(0,1716)
-choose = choose*5-1
-
-# 0.07 -- 4.2
-
-
-# Create data, which are not that well sampled
-#dw = wl[choose]
-
-#dw = np.linspace(wl[0],wl[-1],8575*2)
-
-#dw = wl
-dw =ws
-
-# df = np.exp(-(dw-5004.007)**2/(2.*0.1**2))
-x = np.exp(-(dw-16000.0+1*gamma)**2/(2.*sigma**2))+1
-y = np.exp(-(dw-16000.0)**2/(2.*sigma**2))+1
-z = np.exp(-(dw-16000.0-1*gamma)**2/(2.*sigma**2))+1
-
-# remake-abc
-
-a = 0.13
[…]

### 2017-01-26 1208_read_rv_compare_single_file.py

@@ -1,90 +1,0 @@
-import pickle
-import PyAstronomy
-from PyAstronomy import pyasl
-import numpy as np
-from astropy.io import fits
-import matplotlib.pylab as plt
-import Cross_correlation_1207 as cc
-
-
-# load path
-
-pkl_file = open('n_900_path_fits.pkl', 'rb')
-path_fits = pickle.load(pkl_file)
-pkl_file.close()
-
-
-pkl_file = open('n_900_path_flux.pkl', 'rb')
-path_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-
-N = len(path_fits)
-print(N)
-
-velocity = []
-mean_fiber_id = []
-mean_ivar = []
-parameters = []
-nor = []
-ivar=[]
-inf =[]
-inf_label= []
-
-for i in range(0,N):
-    print("loading star %d"%(i+1))
-    star_i = fits.open(path_fits[i])
-    velocity.append(star_i[10].data[0])
-    mean_fiber_id.append(np.mean(star_i[7].data))
-    mean_ivar.append(np.mean(star_i[1].data[0]))
-    parameters.append(star_i[4].data[0])
-
-    nor.append(star_i[0].data[0])
-    ivar.append(star_i[1].data[0])
-    inf.append(star_i[2].data[0])
-    inf_label.append(star_i[9].data[0])
-
-    print(star_i[4].data[0].shape)
-
-velocity =np.array(velocity)
-mean_fiber_id = np.array(mean_fiber_id)
-parameters = np.array(parameters)
-nor=np.array(nor)
-ivar = np.array(ivar)
-inf = np.array(inf)
-inf_label = np.array(inf_label)
-
-
-velocity_compare = []
-
-N = len(path_fits)
-
-for i in range(0,N):
-    name = "/Users/caojunzhi/Desktop/Data/velocity_900/" + "velocity" + str(i) + ".pkl"
-
-    pkl_file = open(name, 'rb')
-    v_i = pickle.load(pkl_file)
-    pkl_file.close()
-
-    velocity_compare.append(v_i)
-
-velocity_compare = np.array(velocity_compare)
-print(velocity_compare.shape)
-
-plt.plot(velocity_compare[:,0],"ko",label="CCF")
-plt.plot(velocity_compare[:,1],"go",label ="David")
-plt.plot(velocity_compare[:,2],"ro",label="Jason")
-axes = plt.gca()
[…]

### 2017-01-26 1209_plot_rv_compare.py

@@ -1,218 +1,0 @@
-import pickle
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-import numpy as np
-import math
-from astropy.io import fits
-import Plot_compare_velocity_1209 as pm
-
-def log(x):
-    return math.log10(x)
-
-def power10(x):
-    return 10**x
-
-# load
-pkl_file = open('wl.pkl', 'rb')
-wl = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('moments_900.pkl', 'rb')
-moment = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('parameters_900.pkl', 'rb')
-parameters = pickle.load(pkl_file)
-pkl_file.close()
-
-pkl_file = open('velocity_compare_900.pkl', 'rb')
-velocity_compare = pickle.load(pkl_file)
-pkl_file.close()
-
-"""
-# load path
-
-pkl_file = open('n_900_path_fits.pkl', 'rb')
-path_fits = pickle.load(pkl_file)
-pkl_file.close()
-
-
-pkl_file = open('n_900_path_flux.pkl', 'rb')
-path_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-
-N = len(path_fits)
-print(N)
-
-velocity = []
-mean_fiber_id = []
-mean_ivar = []
-parameters = []
-nor = []
-ivar=[]
-inf =[]
-inf_label= []
-
-for i in range(0,N):
-    print("loading star %d"%(i+1))
-    star_i = fits.open(path_fits[i])
-    velocity.append(star_i[10].data[0])
-    mean_fiber_id.append(np.mean(star_i[7].data))
-    mean_ivar.append(np.mean(star_i[1].data[0]))
-    parameters.append(star_i[4].data[0])
-
-    nor.append(star_i[0].data[0])
-    ivar.append(star_i[1].data[0])
-    inf.append(star_i[2].data[0])
-    inf_label.append(star_i[9].data[0])
-
-    print(star_i[4].data[0].shape)
-
-velocity =np.array(velocity)
-mean_fiber_id = np.array(mean_fiber_id)
-parameters = np.array(parameters)
-nor=np.array(nor)
-ivar = np.array(ivar)
-inf = np.array(inf)
-inf_label = np.array(inf_label)
-
-
-
-
-
[…]

### 2017-01-26 Cross_correlation_1207.py

@@ -1,182 +1,0 @@
-from __future__ import print_function, division
-import math
-import pickle
-import PyAstronomy
-from PyAstronomy import pyasl
-import numpy as np
-import matplotlib.pylab as plt
-
-
-def log(x):
-    return math.log10(x)
-
-
-def power10(x):
-    return 10 ** x
-
-
-def cross_correlation_velocity(a,b,c):
-
-    pkl_file = open('wl.pkl', 'rb')
-    wl = pickle.load(pkl_file)
-    pkl_file.close()
-
-    # Create the template
-    # tw = wl
-    tw = np.linspace(wl[0], wl[-1], 8575*10)
-    tf = np.exp(-(tw - 16000.0) ** 2 / (2. * 20 ** 2))
-
-    # choose 20%
-    choose = np.arange(0, 1716)
-    choose = choose * 5 - 1
-
-    # 0.07 -- 4.2
-
-    # gamma = 0.2086
-    gamma = 0.199
-    # Create data, which are not that well sampled
-    # dw = wl[choose]
-    dw = np.linspace(wl[0], wl[-1], 8575*2)
-
-    # df = np.exp(-(dw-5004.007)**2/(2.*0.1**2))
-    x = np.exp(-(dw - 16000.0 + gamma) ** 2 / (2. * 20 ** 2))
-    y = np.exp(-(dw - 16000.0) ** 2 / (2. * 20 ** 2))
-    z = np.exp(-(dw - 16000.0 - gamma) ** 2 / (2. * 20 ** 2))
-
-    df = a * x + b * y + c * z
-    print(a, b, c)
-    print(4.144 * (c - a) / ((a ** 2 + b ** 2 + c ** 2) ** 0.5))
-    print(4.144 * (c - a) / ((a + c - 2 * b) * 4))
-
-    """
-    # Plot template and data
-    plt.title("Template (blue) and data (red)")
-    plt.plot(tw, tf, 'b.-')
-    plt.plot(dw, df, 'r.-')
-    plt.show()
-    """
-
-    # Carry out the cross-correlation.
-    # The RV-range is -30 - +30 km/s in steps of 0.6 km/s.
-    # The first and last 20 points of the data are skipped.
-    print("Doing cross-correlation")
-    rv, cc = pyasl.crosscorrRV(dw, df, tw, tf, -5, 5, 5. / 5000., skipedge=20)
-
-    # Find the index of maximum cross-correlation function
-    maxind = np.argmax(cc)
-
[…]

### 2017-01-26 example.py

@@ -1,147 +1,0 @@
-
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import pickle
-
-import AnniesLasso_2 as tc
-
-
-training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
-training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
-
-
-training_set = Table.read("reference_labels.csv")
-
-def get_pixmask(flux, err):
-    bad_flux = ~np.isfinite(flux)
-    bad_err = (~np.isfinite(err)) | (err <= 0)
-    bad_pixels = bad_err | bad_flux
-    return bad_pixels
-N = len(training_set)
-keep = np.ones(N, dtype=bool)
-
-training_set_flux = []
-training_set_ivar = []
-training_set_error = []
-for i, row in enumerate(training_set):
-
-    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
-    if not os.path.exists(image_path):
-        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
-        keep[i] = False
-        continue
-
-    print("{}/{}: {}".format(i + 1, N, image_path))
-
-    image = fits.open(image_path)
-
-    flux = image[1].data
-    flux_err = image[2].data
-
-    badpix = get_pixmask(flux, flux_err)
-    ivar = 1.0/flux_err**2
-    error = flux_err
-    # badpix is a array and the length is 8575
-    flux[badpix] = 1.0
-    ivar[badpix] = 0.0
-
-    training_set_flux.append(flux)
-    training_set_ivar.append(ivar)
-    training_set_error.append(error)
-
-training_set_flux = np.array(training_set_flux)
-training_set_ivar = np.array(training_set_ivar)
-training_set_error = np.array(training_set_error)
-
-# save training_set_flux, ivar and error
-"""
-output = open('training_set_flux.pkl', 'wb')
-pickle.dump(training_set_flux, output)
-output.close()
-
-output = open('training_set_ivar.pkl', 'wb')
-pickle.dump(training_set_ivar, output)
-output.close()
-
[…]

### 2017-01-26 plot_class_4_star_v2_1107.py

@@ -1,266 +1,0 @@
-import matplotlib.pyplot as plt
-import random
-import matplotlib
-import numpy as np
-import pickle
-from astropy.table import Table
-import TheCannon_2
-from TheCannon_2 import dataset,apogee
-from astropy.table import Table
-import numpy as np
-import os
-from astropy.io import fits
-import pickle
-import AnniesLasso_2 as tc
-import math
-import re
-
-
-
-def log10(x):
-    return math.log10(x)
-
-# sinc interpolation
-
-# Distance between s is equal and they are your raw data
-# u is what you want. Then length of u is not equal to s.
-
-
-
-class plot_4:
-    def __init__(self):
-        n = 1
-
-    def plot_name_4(self, path_array):
-
-        # import data
-
-        pkl_file = open('wl.pkl', 'rb')
-        wl = pickle.load(pkl_file)
-        pkl_file.close()
-
-        all_set_flux = []
-        all_set_ivar = []
-        star_name = []
-        inf_old = []
-        inf_opt = []
-        inf_label = []
-        parameters_4 = []
-        delta_chi = []
-
-        n_star = len(path_array)
-        for i in range(0,n_star):
-
-            star = fits.open(path_array[i])
-            all_set_flux.append(star[0].data[0])
-            all_set_ivar.append(star[1].data[0])
-            star_name_i = path_array[i]
-            star_name_i = re.sub('/Users/caojunzhi/Desktop/Data/n_900/', '', star_name_i)
-
-            star_name_i = re.sub('\.fits', '',star_name_i)
-            star_name.append(star_name_i)
-
-            inf_old.append(star[2].data[0])
-            inf_opt.append(star[3].data[0])
-            inf_label.append(star[9].data[0])
-            parameters_4.append(star[4].data[0])
-            delta_chi.append(star[6].data[0])
-
-        all_set_flux = np.array(all_set_flux)
-        all_set_ivar = np.array(all_set_ivar)
-        star_name = np.array(star_name)
[…]

### 2017-01-27 paper/ms2.tex
Add why our RVs are better

@@
 \bigskip
+
+In a word, the method we use to calibrate the radial velocities of the combined spectra and individual visits is:
+
+\begin{description}
+ \item[1] Infer labels from the fluxes of the combined spectra and individual visits. 
+ \item[2] Input these labels into the Cannon and generate inferred fluxes for the combined spectra and individual visits. Use these inferred fluxes as templates to calibrate radial velocities.
+ \item[3] Generate optimized fluxes and obtain parameters a, b and c. These parameters show the radial velocity shifts between the data fluxes and the inferred fluxes.
+ \item[4] By assuming these inferred fluxes are at rest, derive the radial velocity shifts of these combined spectra and individual visits.
+\end{description}
 
@@
 %Can you interpret a, b, c in terms of radial velocity? If so, how?
-After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate the combined spectra of these stars.
-These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit.
+After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate both the combined spectra and individual visits of these stars.
+These spectra are stored in Apstar files, which are regenerated onto a common, logarithmically-spaced wavelength scale after removing derived radial velocities of each visit.
 There are two combined spectrums for one star, which are obtained by different method.
@@
 
+\subsection{\label{sec:level2}Why our method is better}
+% In EXP 3
+
+The APOGEE team derive the radial velocities of individual visits by two steps.
+First, derive the relative radial velocity between each visit and the combined spectrum iteratively.
+Second, absolute radial velocity determination of the combined spectrum against a grid of synthetic spectra spanning a large range of stellar parameters.
+All radial velocities in these two steps are determined by cross-correlating a spectrum against a template spectrum.
+This mean the result is very sensitive to the normalization method since the result of cross-correlation is influenced by normalization prominently.
+Also, the traditional synthesized spectrum in the second step is not very reliable, which means the absolute velocity is not very accurate.
+From these two points, there is still much to be improved in APOGEE team's RV results.
+\bigskip
+
+In experiment 3, firstly we will show the RVs for individual visits from the APOGEE team is not very reliable.
+Then, plot our results and compare it with the ones by the APOGEE team.
+Finally, conclude our method gives a better RV measurement for individual visits.
+
 \subsection{\label{sec:level2}Optimize Teff , log g and [Fe/H] simultaneously with a, b, c}
@@
 \centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
-\centerline{SNR of Star A is 108. Teff = 4939K Logg =2.71 }
+\centerline{SNR of Star A is 108. Teff = 4939K Logg =2.71 Fe/H =-5.368}
 
@@
 \centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
-\centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 }
+\centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 Fe/H =3.486}
 
@@
 \centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
-\centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 }
+\centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 Fe/H =6.577}
 
@@
 \centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
-\centerline{SNR of Star D is 150. Teff = 4534K Logg =2.24 }
+\centerline{SNR of Star D is 140. Teff = 5094K Logg =3.088 Fe/H = -3.679 }
 
@@
 \centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
-\centerline{SNR of Star E is 177. Teff = 4639K Logg =2.21 }
+\centerline{SNR of Star E is 208. Teff = 4869K Logg =1.903 Fe/H = -1.691 }
 
@@
 
-Finally, we shows our RV shifts results are better than results from the APOGEE team. The evidences are in the following zoom-in plots.
+We will show our results are better than APOGEE's in the nect experiment.
+
+\subsection{\label{sec:level2}Experiment 3}
+
+Finally, we shows our RV shifts results are better than results from the APOGEE team. We demonstrate it by two steps:
+
+\begin{description}
+  \item[1] Use inferred fluxes as templates are reliable. These inferred fluxes are at rest.
+  \item[2] Our method for deriving the relative radial velocities between inferred fluxes and data spectra is good.
+
+\end{description}
+
+First, we show that use inferred fluxes as templates are reliable. Here we randomly choose 5 stars with different SNR, Teff, logg and Fe/H. Then plot the fluxes from the APOGEE team and the Cannon.
+
+% star 1
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{Peak_1.png}
+
+\centerline{Fig.16 Comparison of each visit for Star 1.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 1 is 206. Teff = 4208K Logg =1.347 Fe/H =-1.018}
+
+\end{center}
+
+% Star 2
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{Peak_2.png}
+
+\centerline{Fig.17 Comparison of each visit for Star 2.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 2 is 197. Teff = 4641K Logg =2.201 Fe/H =-5.873}
+
+\end{center}
+
+% Star 3
+
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{Peak_3.png}
+
+\centerline{Fig.18 Comparison of each visit for Star 3.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 3 is 117. Teff = 4902K Logg =2.639 Fe/H =-1.863}
+
+\end{center}
+
+% Star 4
+
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{Peak_4.png}
+
+\centerline{Fig.19 Comparison of each visit for Star 4.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 4 is 122. Teff = 4813K Logg =2.736 Fe/H = -1.832 }
+
+\end{center}
+
+% Star 5
+
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{Peak_5.png}
+
+\centerline{Fig.20 Comparison of each visit for Star 5.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 5 is 113. Teff = 4513K Logg =2.662 Fe/H = -5.215 }
+
+\end{center}
+
+\bigskip
+
+From these plots, we can see that the peak locations of fluxes from the APOGEE team shift, which should not happen because these fluxes are set at rest by the APOGEE team and there shouldn't be shifts between each fluxes.
+This means the radial velocities from the APOGEE team have some errors.
+When we look at the fluxes generated from the Cannon, the peaks from individual visits have the same positions.
+That's to say, we can use inferred fluxes from the Cannon as templates for calibration.
+\bigskip
+
+Then, we argue that our method for deriving the relative radial velocities between inferred fluxes and data spectra is good.
 

### 2017-01-27 0124_plot.py

@@ -865,10 +865,10 @@ class plot_continuum_pixel():
             # plt.errorbar(wl,flux[i] + 0.3 * i, ecolor='k', alpha=0.02, capthick=0.2, yerr=ivar[i]**(-0.5))
 
         axes = plt.gca()
-        # axes.set_xlim([15660, 15780])
+        axes.set_xlim([15660, 15780])
 
 
-        # axes.set_xlim([16160,16280])
+        axes.set_xlim([16160,16280])
         axes.set_ylim([0.5, 1 + 0.5 * N])
         # axes.set_yticks(np.arange(0.8,1.21,0.1))
 
@@ -878,6 +878,127 @@ class plot_continuum_pixel():
 
         plt.show()
 
+
+    def find_peak(self,flux):
+
+        # return the index of peak location
+
+        N = len(flux)
+
+        peak = []
+        for i in range(50,N-50):
+
+            m = flux[i]
+            l1 = flux[i-1]
+            l2 = flux[i-2]
+            l3 = flux[i-10]
+
+
+            r1 = flux[i+1]
+            r2 = flux[i + 2]
+            r3 = flux[i + 10]
+
+
+            if m<min(l1,l2,l3) and m<min(r1,r2,r3):
+                peak.append(i)
+            elif m>max(l1,l2,l3) and m>max(r1,r2,r3):
+                peak.append(i)
+
+        peak = np.array(peak)
+        return peak
+
+    def plot_peak_single_star(self,flux, inf_flux):
+
+
+
+        N = len(flux[:, 0])
+
+        name = ["combined spectrum", "combined spectrum"]
+        for j in range(0, N - 2):
+            name.append("individual visit")
+
+        plt.figure(1)
+
+        plt.subplot(2,1,1)
+
+
+        for i in range(N):
+            plt.plot(wl, flux[i] + 0.5 * i, label=name[i])
+
+
+            # plt.errorbar(wl,flux[i] + 0.3 * i, ecolor='k', alpha=0.02, capthick=0.2, yerr=ivar[i]**(-0.5))
+
+
+
+
+        ### Add vertical lines
+
+        peak_i = self.find_peak(flux[0,:])
+
+        n_p = len(peak_i)
+
+        for i in range(0,n_p):
+            index = peak_i[i]
+
[…]

### 2017-01-27 paper/ms2.tex
Grammar check

@@
 
-The Cannon is a powerful tool which can predict the stellar labels from fluxes, which is a data-driven machine learning model.
+The Cannon, which is a data-driven machine learning model \cite{ness2015cannon}, is a powerful tool that can predict stellar labels from spectra.
 Also, it can infer fluxes from the stellar labels.
-Here we use the Cannon as a tool to calibrate the radial velocities(RV) in APOGEE DR 10 by fitting the inferred fluxes with the data fluxes.
-Then we compare our RV shift result with the APOGEE team and conclude our method is better.
-The most important thing of this work is that we can calibrate the velocity by using a new method-use data-driven model to calibrate physical parameters without using physical model.
+Here we use the Cannon as a tool to calibrate radial velocities(RV) in APOGEE DR10 by fitting the inferred fluxes with the data fluxes.
+Then we compare our RV shift results with the ones from APOGEE team and conclude our method is better.
+The most important thing about this work is that we can calibrate the velocity by using a new data-driven model to calibrate physical parameters without using any physical model.
 This is quicker than better than traditional methods.
@@
  \subsection{\label{sec:level2}Continuum normalization}
-Since the Cannon need the spectrums to be normalized.
-The first thing we should do is to continuum normalize the combined spectrums and individual visits.
-The data we use is the Apstar files in APOGEE DR10, which include two combined spectrums and several individual visits and they are set to the same wavelength scale after removing the radial velocities derived by APOGEE team.
-There are 8575 pixels and the wave length is equally logarithmically-spaced.
+Since the Cannon needs the spectrums to be normalized.
+The first thing we should do is to continuum-normalize the combined spectrums and individual visits.
+The data we use is in Apstar files from APOGEE DR10, which include two combined spectrums and several individual visits for one star.
+They are set to the same rest wavelength scale after removing the radial velocities derived by APOGEE team.
+There are 8575 pixels and the wavelength is equally logarithmically-spaced.
 The wavelength starts at 1.514 $\mu m$ and ends at 1.696 $\mu m$.
@@
 
-Our method is the same as the one in Ness et al 2015.
-The spectrum for each visit is in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
-First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum.
-Then, do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance.
-Third, put a mask on the spectrum.
-Finally, fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.
-Our method is different from the one used by the APOGEE team and we will demonstrate it works.
+Our method is the same as the one in Ness et al 2015 \cite{ness2015cannon}.
+The spectrums are in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
+There are four steps for the normalization:
+
+\begin{description}
+ \item[1] Cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum.
+ \item[2] Do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance.
+ \item[3] Put a mask on the spectrum.
+ \item[4] Fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.
+\end{description}
+
+This normalization method is different from the one used by the APOGEE team and we will prove it works.
 \bigskip
 
-To check whether our normalization methods works, we will:
+To check whether our normalization method works, we will:
 
 \begin{description}
-  \item[1] Plot the continuum pixels for combined spectrum and individual visits, then check whether they are roughly cover the spectrum evenly.
-  \item[2] Plot individual visits and compare them with the combined spectrum, they should have similar shape.
-  \item[3] Infer stellar labels from the individual visits by using the Cannon and the inferred labels should be similar from the ones from the combined spectrum for the very same star.
+  \item[1] Plot continuum pixels for combined spectrums and individual visits, then check whether they roughly cover the spectrum evenly.
+  \item[2] Plot individual visits and compare them with the combined spectrum, they should have similar shapes.
+  \item[3] Infer stellar labels from individual visits by using the Cannon and these inferred labels should be similar to the ones from the combined spectrum of the very same star.
 \end{description}
@@
 %{\AA}
-In this part we will introduce the Cannon 2, and then use a linear method to optimize the inferred spectrum. Finally calibrate both the combined spectrum and individual visits.
-\bigskip
-
+In this part we will introduce the Cannon 2 \cite{casey2016cannon}, and then use a linear method to optimize the inferred spectrum.
+Finally calibrate both the combined spectrum and individual visits.
 In a word, the method we use to calibrate the radial velocities of the combined spectra and individual visits is:
@@
 \begin{description}
- \item[1] Infer labels from the fluxes of the combined spectra and individual visits. 
+ \item[1] Infer labels from combined spectra and individual visits. 
  \item[2] Input these labels into the Cannon and generate inferred fluxes for the combined spectra and individual visits. Use these inferred fluxes as templates to calibrate radial velocities.
  \item[3] Generate optimized fluxes and obtain parameters a, b and c. These parameters show the radial velocity shifts between the data fluxes and the inferred fluxes.
- \item[4] By assuming these inferred fluxes are at rest, derive the radial velocity shifts of these combined spectra and individual visits.
+ \item[4] By assuming these inferred fluxes are at rest, derive the radial velocity shifts of these combined spectra and individual visits. Finally, obtain the radial velocities of individual visits.
 \end{description}
 
-The very first thing we use is the Cannon 2.
+The very first thing we shall use is the Cannon 2.
 Suppose we have a trained Cannon model.
 The training set contains 548 stellar and each stellar spectrum has 8575 pixels.
-Every pixel is related to a specific wave length.
+Every pixel is related to a specific wavelength.
 It belongs to APOGEE data release 10 and has a good quality.
@@
 The labels we use are Teff, Log g and Fe/H.
-We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
+Randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
 The mean inverse variance of the stars is bigger than 10000 but smaller than 40000.
 We also exclude stars with undetermined labels.
-(The label is set to -10000 if it's not determined.)The number of stars is 614.
-Apply the Cannon 2 on these stars and obtain the inferred labels and inferred fluxes for them.
+(The label is set to -10000 if it's not determined.)The number of stars is 654.
+Apply the Cannon 2 on these stars and obtain inferred labels and inferred fluxes of them.
 
-From the normalized combined spectrum and fluxes of individual visits for the very same star, several sets of inferred labels $l_n^{inf}$ are obtained.
-Then put the inferred labels $l_n^{inf}$ back into formula (5), the inferred combined spectrum and inferred fluxes of individual visits for star n is available.
+From the normalized combined spectrum and fluxes of individual visits of the very same star, several sets of inferred labels $l_n^{inf}$ are obtained.
+Then put the inferred labels $l_n^{inf}$ back into formula (5), the inferred combined spectrum and inferred fluxes of individual visits are available.
 The data spectrum we use are in Apstar files.
-There are two combined spectrum and several individual visits in the Apstar files.
-Put all of these spectrum into the trained Cannon 2 and obtain several sets of inferred labels for each star.
+There are two combined spectrums and several individual visits in the Apstar files.
+Put all these spectrums into the trained Cannon 2 and obtain several sets of inferred labels for each star.
 After that, put the inferred labels back into the model and calculate the inferred combined spectrum(There should be two) and inferred fluxes of individual visits.
@@
 
-The APOGEE team set the combined spectrum and fluxes of individual visits at rest by removing the radial velocities.
-However, since the derived radial velocities from the APOGEE team is not 100 \% correct, these fluxes are not at rest.
+The APOGEE team sets the combined spectrum and fluxes of individual visits at rest by removing the radial velocities.
+However, since the derived radial velocities from the APOGEE team are not 100 \% correct, these fluxes are not at rest.
 There are radial velocity shifts between the radial velocities from the APOGEE team and the correct radial velocities.
 But we can assume the shifts of radial velocities are Gaussian distributed, so the inferred fluxes generated by the Cannon 2 are at rest.
-This means we can use inferred fluxes to calibrate the radial velocities derived by the APOGEE team.
+This means we can use inferred fluxes as templates to calibrate radial velocities derived by the APOGEE team.
+\cite{holtzman2013calibrations}
 \bigskip
@@
 
-Where $RV_{cor}$, $RV_{apo}$ and $RV_{shift}$ are the correct radial velocity, radial velocity from the APOGEE team and the radial velocity shift.
+Where $RV_{cor}$, $RV_{apo}$ and $RV_{shift}$ are the correct radial velocity, radial velocity from the APOGEE team and the radial velocity shift. In our experiment, we will derive the $RV_{shift}$.
 \bigskip
@@
 Then we fit the optimized spectrum to the data spectrum by using the least chi-squared method.
-After fitting the optimized spectrum to the data spectrum, we think the optimized spectrum has the very same radial velocity shift as the data spectrum.
-And we can derive the correct radial velocity of the spectrum by removing the radial velocity shift.
-So our objective function is the chi-squared between the optimized spectrum and the spectrum data.
-The objective function for star n is:
+After that, we think the optimized spectrum has the very same radial velocity shift as the data spectrum.
+And we can derive the correct radial velocity of the spectrum by removing the radial velocity shift in formula 6.
+The objective function is the chi-squared between the optimized spectrum and the spectrum data.
+The objective function for one flux of star n is:
 \bigskip
@@
 Write the objective function in the form of matrix can make it simpler.
+\cite{hogg2010data}
 
@@
 
-The dimension of the Jacobian Matrix is 1*3. To minimize the objective function, let the Jacobian Matrix be 0 and we have:
+The dimension of the Jacobian Matrix is (1,3). To minimize the objective function, let the Jacobian Matrix be 0 and we have:
 
@@
 After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate both the combined spectra and individual visits of these stars.
-These spectra are stored in Apstar files, which are regenerated onto a common, logarithmically-spaced wavelength scale after removing derived radial velocities of each visit.
-There are two combined spectrums for one star, which are obtained by different method.
-The radial velocities of the spectrums in Apstar files should be 0, but in fact they are not.
-This is because of the errors in the radial velocity measurement by the APOGEE team.
-
-Consider Relativistic Doppler effect. The redshift factor is defined as z. The radial velocity is positive if the star is leaving us.
+Consider Relativistic Doppler effect.
+The redshift factor is defined as z.
+The radial velocity is positive if the star is leaving us.
 
@@
 
-The radial velocity is related to the pixels. We can obtain the velocity shift by calculating the centroid shift. The centroid in pixel can be expressed as:
+The radial velocity is related to pixels. We can obtain the velocity shift by calculating the centroid shift. The centroid in pixel can be expressed as:
 
@@
 
-We will plot the histogram for the five parameters in our experiment and demonstrate moving two pixels are good enough for these $2b<a+c$cases.
+We will plot the histogram for the five parameters in our experiment and demonstrate moving two pixels are good enough for these $2b<a+c$ cases.
 
@@
 All radial velocities in these two steps are determined by cross-correlating a spectrum against a template spectrum.
-This mean the result is very sensitive to the normalization method since the result of cross-correlation is influenced by normalization prominently.
+This means the result is very sensitive to the normalization method since the result of cross-correlation is influenced by normalization prominently.
 Also, the traditional synthesized spectrum in the second step is not very reliable, which means the absolute velocity is not very accurate.
@@
 
-In experiment 3, firstly we will show the RVs for individual visits from the APOGEE team is not very reliable.
-Then, plot our results and compare it with the ones by the APOGEE team.
-Finally, conclude our method gives a better RV measurement for individual visits.
+In experiment 3, first, we will show the RVs for individual visits from the APOGEE team is not very reliable.
+Then, plot our results.
+Finally, argue our method gives a better RV measurement for individual visits.
 
@@
  \subsection{\label{sec:level2}Experiment 1}
-To demonstrate the continuum normalization works well for the combined spectrums and individual visits, we plot the continuum pixels for stars with different SNR(signal to noise ratio), Teff and Logg.
+To demonstrate the continuum normalization works well for combined spectrums and individual visits, we plot continuum pixels for stars with different SNR(signal to noise ratio), Teff and Logg.
 Here we randomly choose 5 stars with different SNR, Teff and logg and plot them in figure 1 to 5.
+If continuum pixels roughly cover the spectrums evenly, the normalization works well.
 
@@
 
+These continuum pixels roughly cover the spectrums evenly, which means the normalization works well.
+
 \bigskip
 
-We can also demonstrate the continuum normalization works by infer stellar labels from individual visits and compare them with one from the combined spectrum.
+We can also demonstrate the continuum normalization works by inferring stellar labels from individual visits and compare them with the ones from combined spectrums.
 Here we use formula 1, 2 and 3 to obtain delta-stellar labels.
@@
 
- In experiment 2, we will focus on the parameters fitting for individual visits. First, we plot the histograms of parameters abc and RV shifts for individual visits.
+ In experiment 2, we will focus on the parameters fitting of individual visits. First, we plot the histograms of parameters abc and RV shifts of individual visits.
 \bigskip
@@
 
-Then, we try to find some relation between out results and FiberID, MJD(Modified Julia Date), RA and DEC. Figures 11, 12, 13, 14 and 15 shows the relation.
+Then, we try to find some relation between our results and FiberID, MJD(Modified Julia Date), RA and DEC. Figures 11, 12, 13, 14 and 15 shows the relation.
 
@@
 
-We will show our results are better than APOGEE's in the nect experiment.
+We will show our results are better than APOGEE's in the next experiment.
 
@@
 
-Finally, we shows our RV shifts results are better than results from the APOGEE team. We demonstrate it by two steps:
-
-\begin{description}
-  \item[1] Use inferred fluxes as templates are reliable. These inferred fluxes are at rest.
-  \item[2] Our method for deriving the relative radial velocities between inferred fluxes and data spectra is good.
-
-\end{description}
-
-First, we show that use inferred fluxes as templates are reliable. Here we randomly choose 5 stars with different SNR, Teff, logg and Fe/H. Then plot the fluxes from the APOGEE team and the Cannon.
+Finally, we show our results are better than the results from the APOGEE team.
+We demonstrate it by randomly choosing 5 stars with different SNR, Teff, logg and Fe/H.
+Then plot the fluxes from the APOGEE team and the Cannon.
+We will show the inferred fluxes are at rest and our formula gives correct RV shifts.
 
@@
 
-From these plots, we can see that the peak locations of fluxes from the APOGEE team shift, which should not happen because these fluxes are set at rest by the APOGEE team and there shouldn't be shifts between each fluxes.
-This means the radial velocities from the APOGEE team have some errors.
+From these plots, we can see that the peaks of fluxes from the APOGEE team have shifts from each other, which should not happen because these fluxes are set at rest by the APOGEE team and there shouldn't be shifts between them.
+This means radial velocities from the APOGEE team are not very accurate.
 When we look at the fluxes generated from the Cannon, the peaks from individual visits have the same positions.
+These spectrums are at rest.
 That's to say, we can use inferred fluxes from the Cannon as templates for calibration.
@@
 
-Then, we argue that our method for deriving the relative radial velocities between inferred fluxes and data spectra is good.
+Then, we argue that our method for deriving the relative radial velocities(RV shifts) between inferred fluxes and data spectra is good.
+The APOGEE team use Cross-correlation to derive RV shifts, which is very sensitive to the normalization method.
+Also, Cross-correlation means we need to interpolate the data, which may cause the broadening of the spectrum.
+Here most of the RV shifts are smaller than one pixel(Figure 10) and this means the cross-correlation may not be very reliable.
+
+Our method is to move the inferred fluxes one pixel left and right.
+It uses two adjacent pixels and the pixel itself to calibrate each pixel.
+The prerequisite of this method is that the middle pixel accounts for a bigger proportion than the other two.
+This means considering three pixels is good enough.
+In figure 9, we can see that most b are close to 1 and most a, c are close to 0.
+This means our method works good for most of these cases.
+Even for the case that 2b<a+c, which means we need to consider at least 5 pixels.
+Our formula 20 gives a good expression.
+Since all the RV shifts in figure10 is smaller than 2 pixels, we don't need to consider 7 or more pixels.
+
+In conclusion, the method we use to determine the RV shifts is good. It gives more accurate radial velocities than the APOGEE team.
 
@@
 reference
-\bibliography{t_1,pubext}
+\bibliography{citation,pubext}
 

### 2017-01-27 0124_plot.py
Bug fixed

@@ -695,7 +695,7 @@ class plot():
         ax2.set_title('delta-chi-squared vs RA', fontsize=24,y=0.90)
 
         ax2.set_xlabel('RA', fontsize=30)
-        ax2.set_ylabel('delta-chi-squared', fontsize=30)
+        #ax2.set_ylabel('delta-chi-squared', fontsize=30)
 
         #ax2.set_position([0.5, 0.6, 0.4, 0.4])
 
@@ -727,7 +727,7 @@ class plot():
         ax4.set_title('delta-chi-squared vs FiberID', fontsize=24,y=0.90)
 
         ax4.set_xlabel('FIberID', fontsize=30)
-        ax4.set_ylabel('delta-chi-squared', fontsize=30)
+        #ax4.set_ylabel('delta-chi-squared', fontsize=30)
 
 
         #ax4.set_position([0.5,0, 0.4, 0.4])
@@ -1020,6 +1020,7 @@ model = plot()
 
 #model.c_subplot_4(c=parameters,MJD=MJD,Fiber=fiber_id,RA=RA,DEC=DEC,mean_ivar=meanivar)
 
+model.dchi_subplot_4(dchi=dchi,MJD=MJD,Fiber=fiber_id,RA=RA,DEC=DEC,mean_ivar=meanivar)
 
 """
 plt.plot(MJD,parameters,"ro")
@@ -1046,6 +1047,8 @@ plt.show()
 
 
 
+"""
+
 
 p = 628
 
@@ -1069,3 +1072,6 @@ model3 = plot_continuum_pixel()
 
 model3.plot_peak_single_star(flux = nor_i,inf_flux=inf_i)
 
+
+
+"""

### 2017-01-31 paper/ms.tex
Update my codes for the new matplotlib

@@
 
-\section{\label{sec:level1}Introduction}
+\section{\label{sec:level1}Abstract}
 
-Coming soon...
+The calculation of stellar radial velocities plays an important role in stellar spectroscopy.
+However, the traditional method of obtaining radial velocities is not perfect.
+Here we introduce a new data-driven method based on the Cannon, which is a data-driven machine learning model \cite{ness2015cannon}.
+The radial velocity shifts are derived by comparing the data flux with the template flux, which is generated by the Cannon.
+Then, apply it to APOGEE DR10 and compare our results with the ones from the APOGEE team.
+Finally, we argue that our method is better than the one from the APOGEE team.
+The most important thing about this work is that we can calibrate the radial velocities by a new data-driven model without using any physical model.
+This is quicker and better than the traditional method.
 
@@
  \section{\label{sec:level1}Assumption and method}
- \subsection{\label{sec:level2}Optimize the spectrum}
+
+ \subsection{\label{sec:level2}Continuum normalization}
+Since the Cannon needs the spectrums to be normalized.
+The first thing we should do is to continuum-normalize the combined spectrums and individual visits.
+The data we use is in Apstar files from APOGEE DR10, which include two combined spectrums and several individual visits for one star.
+They are set to the same rest wavelength scale after removing the radial velocities derived by APOGEE team.
+There are 8575 pixels and the wavelength is equally logarithmically-spaced.
+The wavelength starts at 1.514 $\mu m$ and ends at 1.696 $\mu m$.
+\bigskip
+
+Our method is the same as the one in Ness et al 2015 \cite{ness2015cannon}.
+The spectrums are in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
+There are four steps for the normalization:
+
+\begin{description}
+ \item[1] Cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum.
+ \item[2] Do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance.
+ \item[3] Put a mask on the spectrum.
+ \item[4] Fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.
+\end{description}
+
+This normalization method is different from the one used by the APOGEE team and we will prove it works.
+\bigskip
+
+To check whether our normalization method works, we will:
+
+\begin{description}
+  \item[1] Plot continuum pixels for combined spectrums and individual visits, then check whether they roughly cover the spectrum evenly.
+  \item[2] Plot individual visits and compare them with the combined spectrum, they should have similar shapes.
+  \item[3] Infer stellar labels from individual visits by using the Cannon and these inferred labels should be similar to the ones from the combined spectrum of the very same star.
+\end{description}
+
+For point 3
+If the inferred labels from each visit are similar to the ones from the combined spectrum, the normalization works. We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:
+
+\begin{equation}
+\triangle Teff = Teff_{inf}^{vs} - {Teff}_{inf}^{cb}
+\end{equation}
+
+\begin{equation}
+\triangle logg = logg_{inf}^{vs} - logg_{inf}^{cb}
+\end{equation}
+
+\begin{equation}
+\triangle Fe/H = Fe/H_{inf}^{vs} - Fe/H_{inf}^{cb}
+\end{equation}
+
+$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred Teff for each visit and the combined spectrum. It's similar for $logg$ and $Fe/H$
+
+If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works. The details are in Experiment 1.
+
+\subsection{\label{sec:level2}Calibrate the spectrums}
 
 %{\AA}
-Suppose we have a trained model.
+In this part we will introduce the Cannon 2 \cite{casey2016cannon}, and then use a linear method to optimize the inferred spectrum.
+Finally calibrate both the combined spectrum and individual visits.
+In a word, the method we use to calibrate the radial velocities of the combined spectra and individual visits is:
+
+\begin{description}
+ \item[1] Infer labels from combined spectra and individual visits. 
+ \item[2] Input these labels into the Cannon and generate inferred fluxes for the combined spectra and individual visits. Use these inferred fluxes as templates to calibrate radial velocities.
+ \item[3] Generate optimized fluxes and obtain parameters a, b and c. These parameters show the radial velocity shifts between the data fluxes and the inferred fluxes.
+ \item[4] By assuming these inferred fluxes are at rest, derive the radial velocity shifts of these combined spectra and individual visits. Finally, obtain the radial velocities of individual visits.
+\end{description}
+
+The very first thing we shall use is the Cannon 2.
+Suppose we have a trained Cannon model.
 The training set contains 548 stellar and each stellar spectrum has 8575 pixels.
-Every pixel is related to a specific wave length.
+Every pixel is related to a specific wavelength.
 It belongs to APOGEE data release 10 and has a good quality.
@@
 \( e_{jn}\) is a noise draw or residual at pixel j for star n.
+$l_n$ and $l_n^{inf}$ are stellar labels and inferred stellar labels for star n.
+$y_{jn}^{inf}$ is the inferred spectrum for star n at wavelength pixel j.
 
-\(l_n^{inf}\) and \( \theta_{j}\) are available after the training step.
-Infer spectrum by using:
+If we have a trained Cannon 2 model, $\theta_{j}$ is available.
+The labels we use are Teff, Log g and Fe/H.
+Randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
+The mean inverse variance of the stars is bigger than 10000 but smaller than 40000.
+We also exclude stars with undetermined labels.
+(The label is set to -10000 if it's not determined.)The number of stars is 654.
+Apply the Cannon 2 on these stars and obtain inferred labels and inferred fluxes of them.
+
+From the normalized combined spectrum and fluxes of individual visits of the very same star, several sets of inferred labels $l_n^{inf}$ are obtained.
+Then put the inferred labels $l_n^{inf}$ back into formula (5), the inferred combined spectrum and inferred fluxes of individual visits are available.
+The data spectrum we use are in Apstar files.
+There are two combined spectrums and several individual visits in the Apstar files.
+Put all these spectrums into the trained Cannon 2 and obtain several sets of inferred labels for each star.
+After that, put the inferred labels back into the model and calculate the inferred combined spectrum(There should be two) and inferred fluxes of individual visits.
+\bigskip
+
+In the following step, we deal with the combined spectrum and individual visits with the same method.
+$y_{j,n}$ represents one spectrum of star n at pixel j.
+It can be either combined spectrum or individual visit.
+\bigskip
+
+The APOGEE team sets the combined spectrum and fluxes of individual visits at rest by removing the radial velocities.
+However, since the derived radial velocities from the APOGEE team are not 100 \% correct, these fluxes are not at rest.
+There are radial velocity shifts between the radial velocities from the APOGEE team and the correct radial velocities.
+But we can assume the shifts of radial velocities are Gaussian distributed, so the inferred fluxes generated by the Cannon 2 are at rest.
+This means we can use inferred fluxes as templates to calibrate radial velocities derived by the APOGEE team.
+\cite{holtzman2013calibrations}
+\bigskip
 
 \begin{equation}
-y_{jn}^{inf} = v(l_n^{inf}) \cdot \theta_{j} 
+RV_{cor} = RV_{apo} + RV_{shift}
 \end{equation}
 
- This is how to obtain the synthesized spectrum by using the Cannon 2. We also call it inferred flux(spectrum).
-
-The Cannon 2 can predict the spectrum pretty well. But we can still improve it.
+Where $RV_{cor}$, $RV_{apo}$ and $RV_{shift}$ are the correct radial velocity, radial velocity from the APOGEE team and the radial velocity shift. In our experiment, we will derive the $RV_{shift}$.
 \bigskip
 
-From the inferred spectrum \(y_{jn}^{inf}\), we optimize it and generate a better synthesized spectrum, which we call \(y_{jn}^{opt}\).
-\bigskip
-
-The method we use is to represent the spectrum at pixel j by using the inferred spectrum at pixel j-1,pixel j and pixel j+1.(If the pixel is out of range, set the flux as 1).
-The data we use is the same as the training step.
-\bigskip
-
-The new spectrum, which is the optimized spectrum, is represented by:
+First, we define a spectrum called optimized spectrum.
 
@@
 
-We use the least chi-squared method. So our objective function is the chi-squared between the optimized spectrum and the spectrum data. The objective function for star n is:
+Where $y_{j,n}^{opt}$ is the optimized spectrum for star n at wavelength pixel j.
+We move the inferred spectrums one pixel left, 0 pixel and one pixel right to simulate the radial velocity shift of the data spectrum.
+
+Then we fit the optimized spectrum to the data spectrum by using the least chi-squared method.
+After that, we think the optimized spectrum has the very same radial velocity shift as the data spectrum.
+And we can derive the correct radial velocity of the spectrum by removing the radial velocity shift in formula 6.
+The objective function is the chi-squared between the optimized spectrum and the spectrum data.
+The objective function for one flux of star n is:
 \bigskip
@@
 Write the objective function in the form of matrix can make it simpler.
-There will be N objective functions and N sets of a, b and c.
-So we introduce several matrix: $Y_n$, $A_n$, $C_n$ and $X_n$ for star n, which are defined as followed:
+\cite{hogg2010data}
 
@@
 
-By using (7) we can calculate $a_n$, $b_n$ and $c_n$, which are parameters a, b and c for star n. 
-b should be much bigger than both a and c. And a+b+c should be equal to 1.
+By using (8) we can calculate $a_n$, $b_n$ and $c_n$, which are parameters a, b and c for one spectrum of star n.
 
-Calculate the optimized spectrum \( y_{j,n}^{opt}\) by using (3). The Experiment 1 shows that the optimization works.
+% shall we put this part in Appendix
+Calculate the optimized spectrum \( y_{j,n}^{opt}\) by using (4). The Experiment 2 shows that the optimization works.
 \bigskip
 
-%It works!
-
-\subsection{\label{sec:level2}Spectrum calibration}
-\bigskip
-After the optimization, we obtain many sets of a, b and c.
-In our theory b should be close to 1 and a, c is much smaller than b.
-But the fact is that sometimes b is much smaller than and c.
-This is because of the spectral broadening in the measurement.
-The equipment is not perfect, so the resolution of the spectrum will become lower due to scattering, dispersion or other reasons.
-Then the spectrum will broaden and the real spectrum at pixel j is not what we obtain, it should be the spectrum at nearby pixels, which include pixel j-1 and j+1.
-Thus b will be smaller than a+c, which we will discuss in the following experiment 3.
-\bigskip
-
-Sometimes a or c will be much bigger than the other two parameters.
-This is also because of the measurement.
-Even we ignore the spectral broadening, the measured spectrum may move one pixel left or one pixel right from the real spectrum.
-If the measured spectrum move one pixel left, then a should be close to 1 and it's similar for c.
-The measured spectrum moves left or right is because of the error in the measured velocity, so there will be error in measuring the Doppler effect, which leads to a spectrum moving.
-We will show this in experiment 3.
-
-We will do this optimization for each visit of every star in APOGEE DR10.
-The spectrum we use is in apstar file.
-We will re-analyze the velocities after the optimization and deliver back the velocities shift for the APOGEE data.
-\bigskip
-
-\subsection{\label{sec:level2} Interpret a, b, c in term of radial velocity}
-
 %Can you interpret a, b, c in terms of radial velocity? If so, how?
-After obtaining a, b and c for these stars, we can calibrate the errors in the radial velocities of the combined spectra of these stars.
-These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit.
-The apStar files also include the individual visit spectra, resampled and shifted to rest wavelength.
-If we need to use the individual visits before resampling, apVisit files are needed.
-In our experiment, we use the resampled spectrum in Apstar files.
-The radial velocities of the spectrum in Apstar files should be 0, but in fact they are not.
-This is because of the errors in radial velocity measurement by the APOGEE team.
-The APOGEE team determines the radial velocities of the stars by two steps.
-\bigskip
-\\
-1. Estimate the radial velocity of each visit by cross-correlating the visit spectrum against a grid of synthetic spectra.
-\\
-2. Compare the spectrum of each visit with the combined spectrum and re-derive the radial velocity for each visit iteratively. 
-\bigskip
-
-After obtaining the velocities, the APOGEE team uses the de-Doppler wavelengths and resample the spectrum onto the final logarithmically-spaced wavelength scale by using sinc interpolation.
-Finally, generate the combined spectrum by using the spectrums of different visits.
-Both combined spectrum and each visit may have radial velocity errors because the synthetic spectra are not perfect.
-
-We will derive these radial velocity errors, then de-Doppler them and resample the fluxes onto a common, logarithmically-spaced wavelength scale, which is the same as the wavelength scale in Apstar and ASPCAP flies.
-
-Consider Relativistic Doppler effect. The redshift factor is defined as z. The radial velocity is positive if the star is leaving us.
+After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate both the combined spectra and individual visits of these stars.
+Consider Relativistic Doppler effect.
+The redshift factor is defined as z.
+The radial velocity is positive if the star is leaving us.
 
@@
 
-We will plot the histogram for the five parameters in our experiment.
+We will plot the histogram for the five parameters in our experiment and demonstrate moving two pixels are good enough for these $2b<a+c$ cases.
 
-\subsection{\label{sec:level2} Obtain information from the individual exposures}
+\subsection{\label{sec:level2}Why our method is better}
+% In EXP 3
 
-%How do you continuum-normalize the individual exposures, and can you demonstrate to me that your proposal of how to do that is working well?
-
-Before deriving a, b and c for each visit, we need to continuum-normalize the spectrum of each visit.
-This is because the absolute value of each visit is different.
-Therefore, each visit spectrum needs to be roughly continuum normalized before they are combined.
-The APOGEE team uses a median filter to continuum-normalize the spectrum of each visit.
+The APOGEE team derive the radial velocities of individual visits by two steps.
+First, derive the relative radial velocity between each visit and the combined spectrum iteratively.
+Second, absolute radial velocity determination of the combined spectrum against a grid of synthetic spectra spanning a large range of stellar parameters.
+All radial velocities in these two steps are determined by cross-correlating a spectrum against a template spectrum.
+This means the result is very sensitive to the normalization method since the result of cross-correlation is influenced by normalization prominently.
+Also, the traditional synthesized spectrum in the second step is not very reliable, which means the absolute velocity is not very accurate.
+From these two points, there is still much to be improved in APOGEE team's RV results.
 \bigskip
 
-Our method is the same as the one in Ness et al 2015.
-The spectrum for each visit is in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
-First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum.
-Then, do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance.
-Third, put a mask on the spectrum.
-Finally, fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.
-Our method is different from the one used by the APOGEE team and we will demonstrate it works.
-
-To check whether it works, we can look at the normalized spectrum of each visit. If the absolute value of the normalized flux for each visit is similar to each other, the normalization works.
-
-Also, we can infer labels by using the normalized flux of each visit.
-If the inferred labels from each visit are similar to the ones from the combined spectrum, the normalization works.
-We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:
-
-\begin{equation}
-\triangle Teff = Teff_{inf}^{vs} - {Teff}_{inf}^{cb}
-\end{equation}
-
-\begin{equation}
-\triangle logg = logg_{inf}^{vs} - logg_{inf}^{cb}
-\end{equation}
-
-\begin{equation}
-\triangle Fe/H = Fe/H_{inf}^{vs} - Fe/H_{inf}^{cb}
-\end{equation}
-
-$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred Teff for each visit and the combined spectrum. It's similar for $logg$ and $Fe/H$
-
-If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.
-
-The details are in experiment 5.
+In experiment 3, first, we will show the RVs for individual visits from the APOGEE team is not very reliable.
+Then, plot our results.
+Finally, argue our method gives a better RV measurement for individual visits.
 
@@
  \section{\label{sec:level1}Experiment}
+
  \subsection{\label{sec:level2}Experiment 1}
+To demonstrate the continuum normalization works well for combined spectrums and individual visits, we plot continuum pixels for stars with different SNR(signal to noise ratio), Teff and Logg.
+Here we randomly choose 5 stars with different SNR, Teff and logg and plot them in figure 1 to 5.
+If continuum pixels roughly cover the spectrums evenly, the normalization works well.
 
-Choose four stellar, which are not in the training set.
-Optimize the spectrum of these four stars and obtain a, b and c for each stars.
-The labels we use in the figures are from the Cannon, which means they are inferred labels.
+% star A
+\bigskip
 
-The labels of the four stars are:
 \begin{center}
+\includegraphics[width=170mm]{CP_A.png}
 
- Star A  $T_{eff} =4750$  log g =3.0 $\left[Fe/h\right] =0.15$
-
- Star B  $T_{eff} =4849$  log g =2.2 $\left[Fe/h\right] =-1.0$
-
- Star C  $T_{eff} =3614$  log g =0.4 $\left[Fe/h\right] =-0.68$
-
- Star D  $T_{eff} =5003$  log g =2.8 $\left[Fe/h\right] =-0.71$
+\centerline{Fig.1 Comparison of each visit for Star A.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star A is 108. Teff = 4939K Logg =2.71 Fe/H =-5.368}
 
@@
 
-\begin{table}[ht]
-\caption{Fitting results for the four stars}
-\centering
-\begin{tabular}{c c c c c}
-\hline\hline
-Star Name & a & b & c & a+b+c \\ [0.5ex] % inserts table %heading
-\hline
-Star A & 0.121 & 0.824 & 0.052 & 0.998 \\
-Star B & 0.176 & 0.541 &  0.278 & 0.995 \\
-Star C & 0.003 & 1.004 &  -0.007 & 1.000 \\
-Star D & -0.009  & 1.029 & -0.020 & 1.000 \\ [1ex]
-\hline
-\end{tabular}
-\label{table:nonlin}
-\end{table}
+% Star B
+\bigskip
 
- Then plot the spectrum. The spectrum we use is the combined non-normalized spectrum from apstar files.
+\begin{center}
+\includegraphics[width=170mm]{CP_B.png}
 
- The black line "Observed" is the observed spectrum from the data  \(y_{jn}\).
- The green line "inferred" is \( y_{j,n}^{inf}\) , which is generated by the Cannon 2.
- The red line "optimized" is \( y_{j,n}^{opt}\), which is generated by (3)
+\centerline{Fig.2 Comparison of each visit for Star B.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 Fe/H =3.486}
+
+\end{center}
+
+% Star C
 
@@
 \begin{center}
-\includegraphics[width=170mm]{figure_1.png}
+\includegraphics[width=170mm]{CP_C.png}
+
+\centerline{Fig.3 Comparison of each visit for Star C.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 Fe/H =6.577}
+
 \end{center}
- \centerline{Fig.1 The spectrum of Star A, B, C and D}
 
- \centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+% Star D
+
 \bigskip
 
-Finally compare the chi-square for these four stars of the two methods:
-The total chi-squared of the four stars becomes 2\% smaller, which means our method works.
+\begin{center}
+\includegraphics[width=170mm]{CP_D.png}
+
+\centerline{Fig.4 Comparison of each visit for Star D.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star D is 140. Teff = 5094K Logg =3.088 Fe/H = -3.679 }
+
+\end{center}
+
+% Star E
+
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{CP_E.png}
+
+\centerline{Fig.5 Comparison of each visit for Star E.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star E is 208. Teff = 4869K Logg =1.903 Fe/H = -1.691 }
+
+\end{center}
+
+These continuum pixels roughly cover the spectrums evenly, which means the normalization works well.
+
+\bigskip
+
+We can also demonstrate the continuum normalization works by inferring stellar labels from individual visits and compare them with the ones from combined spectrums.
+Here we use formula 1, 2 and 3 to obtain delta-stellar labels.
+If they are very small, the normalization works.
+They are plotted in figure 6, 7 and 8.
+
+\begin{center}
+\includegraphics[width=170mm]{hist_d_teff.png}
+\end{center}
+
+\centerline{Fig.6 Histogram of Delta Teff for individual visits}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{hist_d_logg.png}
+\end{center}
+
+\centerline{Fig.7 Histogram of Delta logg for individual visits}
+
+\begin{center}
+\includegraphics[width=170mm]{hist_d_fe.png}
+\end{center}
+
+\centerline{Fig.8 Histogram of Delta Fe/H for individual visits}
+\bigskip
+
+We can see that these delta-stellar labels of individual visits are close to 0, which means the spectrums of individual visits don't change shape after the normalization.
+That's to say, the normalization works.
 
  \subsection{\label{sec:level2}Experiment 2}
- Plot the parameters a, b and c vs the number of the star. 
+
+ In experiment 2, we will focus on the parameters fitting of individual visits. First, we plot the histograms of parameters abc and RV shifts of individual visits.
 \bigskip
 
-In experiment 1, we use only four stars to obtain parameters a, b and c and the result is pretty good.
-What if we optimize more stars?
-We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
-The mean inverse variance of the stars is bigger than 10000 but smaller than 40000.
-We also exclude stars with undetermined labels.
-(The label is set to -10000 if it's not determined.)The number of stars is 614.
-Now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 614 objective functions.
-And there will be 614 sets of a, b and c.
-The spectrum we use is the combined non-normalized spectrum from apstar files.
-And soon we will use the individual visit non-normalized spectrum from apstar files.
-Before using these spectrum, normalization is needed.
-The normalization method we use is the same as the one in Ness et al 2015.
-The labels we use are from the Cannon, which means they are inferred labels.
+\begin{center}
+\includegraphics[width=170mm]{hist_abc_visits.png}
+\end{center}
 
-We plot a, b, c against the mean fiber number, which is the average fiber number of the spectrum we optimize.
-In APOGEE DR 10, the fiber number is between 1 and 640.
-The parameters we use are from figure 3
+\centerline{Fig.9 Histogram of a,b,c for individual visits}
+\bigskip
 
 \begin{center}
-\includegraphics[width=170mm]{figure_2.png}
+\includegraphics[width=170mm]{hist_ve_visits.png}
 \end{center}
 
-\centerline{Fig.2 a,b,c vs Mean Fiber Number}
+\centerline{Fig.10 Histogram of RV shifts for individual visits}
 \bigskip
 
-This figure gives us information about the relation between parameters a, b, c and fiber number, which can be used to establish a data-driven spectrum calibration model.
+Then, we try to find some relation between our results and FiberID, MJD(Modified Julia Date), RA and DEC. Figures 11, 12, 13, 14 and 15 shows the relation.
+
+\begin{center}
+\includegraphics[width=170mm]{dchi_vs_all.png}
+\end{center}
+
+\centerline{Fig.11 Delta-chi-squared vs MJD, FiberID, RA and DEC for individual visitis}
 \bigskip
 
-We also plot delta-chi-squared vs Mean Fiber number, where delta-chi-squared is the difference between the chi-squared of the spectrum before our optimization and after. It should be bigger than 0.
+\begin{center}
+\includegraphics[width=170mm]{a_vs_all.png}
+\end{center}
+
+\centerline{Fig.12 a vs MJD, FiberID, RA and DEC for individual visitis}
+\bigskip
 
 \begin{center}
-\includegraphics[width=170mm]{figure_3.png}
+\includegraphics[width=170mm]{b_vs_all.png}
 \end{center}
 
-\centerline{Fig.3 Delta-chi-squared vs Mean Fiber Number}
+\centerline{Fig.13 b vs MJD, FiberID, RA and DEC for individual visitis}
 \bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{c_vs_all.png}
+\end{center}
+
+\centerline{Fig.14 c vs MJD, FiberID, RA and DEC for individual visitis}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{ve_vs_all.png}
+\end{center}
+
+\centerline{Fig.15 RV shifts vs MJD, FiberID, RA and DEC for individual visitis}
+\bigskip
+
+We will show our results are better than APOGEE's in the next experiment.
 
@@
 
+Finally, we show our results are better than the results from the APOGEE team.
+We demonstrate it by randomly choosing 5 stars with different SNR, Teff, logg and Fe/H.
+Then plot the fluxes from the APOGEE team and the Cannon.
+We will show the inferred fluxes are at rest and our formula gives correct RV shifts.
+
+% star 1
 \bigskip
-Now choose some examples from the 614 stars and make some plots.Sometimes the inferred spectrum doesn't look like the data, which is already described in Ness et al 2015.
-We don't use these stars in the plots.
-
-First, plot the four stars with biggest delta-chi-squared and smallest delta-chi-squared:
 
 \begin{center}
-\includegraphics[width=170mm]{figure_4.png}
+\includegraphics[width=170mm]{Peak_1.png}
+
+\centerline{Fig.16 Comparison of each visit for Star 1.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 1 is 206. Teff = 4208K Logg =1.347 Fe/H =-1.018}
+
 \end{center}
 
-\centerline{Fig.4 Spectrum of the four stars with biggest delta-chi-squared. }
-
-\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+% Star 2
+\bigskip
 
 \begin{center}
-\includegraphics[width=170mm]{figure_5.png}
+\includegraphics[width=170mm]{Peak_2.png}
+
+\centerline{Fig.17 Comparison of each visit for Star 2.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 2 is 197. Teff = 4641K Logg =2.201 Fe/H =-5.873}
+
 \end{center}
 
-\centerline{Fig.5 Spectrum of the four stars with smallest delta-chi-squared. }
-
-\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-\bigskip
-
-From figure 6 and 7, we find that the four stars with smallest delta-chi-squared have b closer to 1, but the four stars with biggest delta-chi-squared don't.
-
-Also, we want to look into the spectral broadening.
-Plot four stars with b closest to 1:
-
-\begin{center}
-\includegraphics[width=170mm]{figure_6.png}
-\end{center}
-
-\centerline{Fig.6 Spectrum of the four stars with b closest to 1. }
-
-\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-\bigskip
-
-From the histogram of a, b and c, we also find that sometimes b becomes much smaller than a+c, which means the spectrum is broadening due to the measurement.
-The resolution of the spectrum becomes lower and this is what we want to calibrate.
-\bigskip
-Here is the plot of the four stars with biggest a+c-b:
-
-\begin{center}
-\includegraphics[width=170mm]{figure_7.png}
-\end{center}
-
-\centerline{Fig.7 Spectrum of the four stars with biggest a+c-b. }
-
-\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-\bigskip
+% Star 3
 
@@
 
-We found a and c are close to 1, which is in accordance with our theory. 
-Also, the optimized spectrum broaden when a+c is much bigger than b, which means the measured spectrum broaden due to the error in the measurement. This is what we need to calibrate.
-\bigskip
+\begin{center}
+\includegraphics[width=170mm]{Peak_3.png}
 
-To look deeper into the results, we also choose the four stars with biggest $a-c$ and biggest $c-a$. Then make another two plots:
+\centerline{Fig.18 Comparison of each visit for Star 3.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 3 is 117. Teff = 4902K Logg =2.639 Fe/H =-1.863}
 
-\begin{center}
-\includegraphics[width=170mm]{figure_8.png}
 \end{center}
 
-\centerline{Fig.8 Spectrum of the four stars with biggest $a-c$.}
+% Star 4
 
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 \bigskip
@@
 \begin{center}
-\includegraphics[width=170mm]{figure_9.png}
+\includegraphics[width=170mm]{Peak_4.png}
+
+\centerline{Fig.19 Comparison of each visit for Star 4.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 4 is 122. Teff = 4813K Logg =2.736 Fe/H = -1.832 }
+
 \end{center}
 
-\centerline{Fig.9 Spectrum of the four stars with biggest $c-a$.}
-
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
+% Star 5
 
@@
 
-For spectrum with $a>c$, the optimized spectrum moves left a little bit, which means the real spectrum should move right a little.
-It's similar for $c>a$.
-The c>a branch is not as obvious as the a>c branch.
+\begin{center}
+\includegraphics[width=170mm]{Peak_5.png}
 
-\subsection{\label{sec:level2}Experiment 4}
+\centerline{Fig.20 Comparison of each visit for Star 5.}
+\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
+\centerline{The black lines show the centers of the peaks in these fluxes}
+\centerline{SNR of Star 5 is 113. Teff = 4513K Logg =2.662 Fe/H = -5.215 }
 
-\bigskip
-We also plot the inferred labels $Teff$ against log g. The color bar shows the mean inverse variance of these stars.
-
-\begin{center}
-\includegraphics[width=170mm]{figure_10.png}
 \end{center}
-
-\centerline{Fig.10 $Teff$ vs $log g$}
-\bigskip
-
-\subsection{\label{sec:level2}Experiment 5}
-
-Here we plot the histogram of the radial velocity shifts in figure 11 and the radial velocity shifts in figure 12. The data we use is the combined spectrums of the 614 stars in the former experiment.
-
-\begin{center}
-\includegraphics[width=170mm]{figure_11.png}
-\end{center}
-
-\centerline{Fig.11 Histogram of the radial velocity shifts in combined spectrums for the 614 stars. }
-\centerline{We exclude the outliers which have velocity shifts bigger than 2000 m/s}
-\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{figure_12.png}
-\end{center}
-
-\centerline{Fig.12 Radial velocity shifts for combined spectrums of the 614 stars against mean fiber number}
-\centerline{We exclude the outliers which have velocity shifts bigger than 2000 m/s}
-\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
-\bigskip
-
-We also plot the four stars with biggest radial velocity shifts, which are in figure 13.
-
-\begin{center}
-\includegraphics[width=170mm]{figure_13.png}
-\end{center}
-
-\centerline{Fig.13 Spectrum of the four stars with biggest radial velocity shifts.}
-
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
 
@@
 
+From these plots, we can see that the peaks of fluxes from the APOGEE team have shifts from each other, which should not happen because these fluxes are set at rest by the APOGEE team and there shouldn't be shifts between them.
+This means radial velocities from the APOGEE team are not very accurate.
+When we look at the fluxes generated from the Cannon, the peaks from individual visits have the same positions.
+These spectrums are at rest.
+That's to say, we can use inferred fluxes from the Cannon as templates for calibration.
 \bigskip
 
-After that, we want to calibrate the radial velocity for each visit.
-To begin with, we need to check whether our normalization works in each visit.
-The method is to infer labels for each visit and compare them with the ones from the combined spectrum.
-If our normalization works, the inferred labels from each visit for the same star should be similar to the ones from the combined spectrum.
-We plot the histogram which shows the deviations of the inferred labels of each visit from the ones generated by the combined spectrum of the same star.
-The data we use is the 614 stars in experiment 1 to 4.
-If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.
+Then, we argue that our method for deriving the relative radial velocities(RV shifts) between inferred fluxes and data spectra is good.
+The APOGEE team use Cross-correlation to derive RV shifts, which is very sensitive to the normalization method.
+Also, Cross-correlation means we need to interpolate the data, which may cause the broadening of the spectrum.
+Here most of the RV shifts are smaller than one pixel(Figure 10) and this means the cross-correlation may not be very reliable.
 
-\begin{center}
-\includegraphics[width=170mm]{figure_14.png}
-\end{center}
+Our method is to move the inferred fluxes one pixel left and right.
+It uses two adjacent pixels and the pixel itself to calibrate each pixel.
+The prerequisite of this method is that the middle pixel accounts for a bigger proportion than the other two.
+This means considering three pixels is good enough.
+In figure 9, we can see that most b are close to 1 and most a, c are close to 0.
+This means our method works good for most of these cases.
+Even for the case that 2b<a+c, which means we need to consider at least 5 pixels.
+Our formula 20 gives a good expression.
+Since all the RV shifts in figure10 is smaller than 2 pixels, we don't need to consider 7 or more pixels.
 
-\centerline{Fig.14 Histogram for Delta Teff}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{figure_15.png}
-\end{center}
-
-\centerline{Fig.15 Histogram for Delta logg}
-
-\begin{center}
-\includegraphics[width=170mm]{figure_16.png}
-\end{center}
-
-\centerline{Fig.16 Histogram for Delta Fe/H}
-\bigskip
-
-We can see that most of the deviations are close to 0, which means our normalization for each visit doesn't make the spectrum distort.
-
-In figure 17 and 18, we plot the continuum-normalized fluxes of all visits for the first star in figure 8.
-There are 6 individual visits and 2 combined spectrums.
-So in figure 17 and 18, there are 8 fluxes.
-The bottom two are the combined spectrum and the other 6 are individual visits.
-We can see that the absolute value of the flux for each visit is similar to each other, which means our normalization works.
-
-\begin{center}
-\includegraphics[width=170mm]{figure_17.png}
-\end{center}
-
-\centerline{Fig.17 Comparison of each visit for the first star in figure 8.}
-\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{figure_18.png}
-\end{center}
-
-\centerline{Fig.18 Comparison of each visit for the first star in figure 8.}
-\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
-\bigskip
+In conclusion, the method we use to determine the RV shifts is good. It gives more accurate radial velocities than the APOGEE team.
 
@@
 Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
- \bigskip
 
-\begin{center}
-\includegraphics[width=170mm]{d_figure_1.png}
-\end{center}
-
-\centerline{Diagnostic Fig.1 Histogram of a b c for apstar data (What we use now)}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_2.png}
-\end{center}
-
-\centerline{Diagnostic Fig.2 Four fake stars with Gaussian wave pack spectrums}
-\centerline{The green line is the template and the black line is the observation}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_3.png}
-\end{center}
-
-\centerline{Diagnostic Fig.3 Spectrum of the four stars with biggest c-a}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_4.png}
-\end{center}
-
-\centerline{Diagnostic Fig.4 Spectrum of the four stars with biggest a-c}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
-
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_5.png}
-\end{center}
-
-\centerline{Diagnostic Fig.5 Spectrum of the four stars with biggest a+c-2b}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_6.png}
-\end{center}
-
-\centerline{Diagnostic Fig.6 Spectrum of the four stars with b closest to 1}
-\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{d_figure_7.png}
-\end{center}
-
-\centerline{Diagnostic Fig.7 Radial velocity shifts}
-\centerline{ $v_3$ is the RV shift obtained from a, b and c. $v_5$ is from the five parameters. $v$ is from a, b and c if $2b>a+c$ and $v$ = $v_5$ if $2b<a+c$}
-\bigskip
+reference
+\bibliography{citation,pubext}
 

### 2017-01-31 0124_plot.py

@@ -148,10 +148,10 @@ class plot():
         ax1.scatter(MJD, velocity, marker='x', c=mean_ivar,
                     vmin=10000, vmax=40000, alpha=1)
 
-        ax1.set_title('RV shifts vs MJD', fontsize=24,y=0.90)
+        ax1.set_title('RV shifts vs MJD', fontsize=24,y=0.85)
 
-        ax1.set_xlabel('MJD', fontsize=30)
-        ax1.set_ylabel('RV shifts $m/s$', fontsize=30)
+        ax1.set_xlabel('MJD', fontsize=20)
+        ax1.set_ylabel('RV shifts $m/s$', fontsize=20)
 
 
         ax1.set_ylim([-6000,8000])
@@ -165,10 +165,10 @@ class plot():
         ax2.scatter(RA, velocity, marker='x', c=mean_ivar,
                     vmin=10000, vmax=40000, alpha=1)
 
-        ax2.set_title('RV shifts vs RA', fontsize=24,y=0.90)
+        ax2.set_title('RV shifts vs RA', fontsize=24,y=0.85)
 
-        ax2.set_xlabel('RA', fontsize=30)
-        ax2.set_ylabel('RV shifts $m/s$', fontsize=30)
+        ax2.set_xlabel('RA', fontsize=20)
+        ax2.set_ylabel('RV shifts $m/s$', fontsize=20)
 
         #ax2.set_position([0.5, 0.6, 0.4, 0.4])
 
@@ -182,10 +182,10 @@ class plot():
         ax3.scatter(DEC, velocity, marker='x', c=mean_ivar,
                     vmin=10000, vmax=40000, alpha=1)
 
-        ax3.set_title('RV shifts vs DEC', fontsize=24,y=0.90)
+        ax3.set_title('RV shifts vs DEC', fontsize=24,y=0.85)
 
-        ax3.set_xlabel('DEC', fontsize=30)
-        ax3.set_ylabel('RV shifts $m/s$', fontsize=30)
+        ax3.set_xlabel('DEC', fontsize=20)
+        ax3.set_ylabel('RV shifts $m/s$', fontsize=20)
 
         ax3.set_ylim([-6000, 8000])
         ax3.set_yticks(np.arange(-6000, 8001, 3500))
@@ -199,10 +199,10 @@ class plot():
         ax4.scatter(Fiber, velocity, marker='x', c=mean_ivar,
                     vmin=10000, vmax=40000, alpha=1)
 
[…]

### 2017-02-19 paper/ms.tex
Fit the absorption line

@@
 \documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
-\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
+\usepackage{geometry}                		% See geometry.pdf to learn the layout mixions. There are lots.
 
@@
 However, the traditional method of obtaining radial velocities is not perfect.
-Here we introduce a new data-driven method based on the Cannon, which is a data-driven machine learning model \cite{ness2015cannon}.
-The radial velocity shifts are derived by comparing the data flux with the template flux, which is generated by the Cannon.
+Here we introduce a new data-driven method based on the Cannon, which is a machine learning model \cite{ness2015cannon}.
+The radial velocity shift is derived by comparing the data flux with the template flux, which is generated by the Cannon.
 Then, apply it to APOGEE DR10 and compare our results with the ones from the APOGEE team.
-Finally, we argue that our method is better than the one from the APOGEE team.
-The most important thing about this work is that we can calibrate the radial velocities by a new data-driven model without using any physical model.
-This is quicker and better than the traditional method.
+Finally, we argue that our method works better.
+The most important thing about this work is that we can calibrate the radial velocities by a new data-driven method without using any physical model.
+Also, the calibration step doesn't include any cross-correlation or interpolation, which is quicker and better than the traditional method.
 
@@
  \subsection{\label{sec:level2}Continuum normalization}
-Since the Cannon needs the spectrums to be normalized.
-The first thing we should do is to continuum-normalize the combined spectrums and individual visits.
-The data we use is in Apstar files from APOGEE DR10, which include two combined spectrums and several individual visits for one star.
-They are set to the same rest wavelength scale after removing the radial velocities derived by APOGEE team.
+Since the Cannon needs the spectrums to be normalized first.
+To start with, we should continuum-normalize the combined spectrums and individual visit spectrums.
+The data we use is in Apstar files from APOGEE DR10, which include two combined spectrums and several individual visit spectrums for one star.
+They are set to the same rest wavelength scale after removing the radial velocities derived by the APOGEE team.
 There are 8575 pixels and the wavelength is equally logarithmically-spaced.
@@
 The spectrums are in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
-There are four steps for the normalization:
+There are four steps in the normalization step:
 
@@
  \item[3] Put a mask on the spectrum.
- \item[4] Fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.
+ \item[4] Fit the continuum spectrum in these continuous regions by using a 3-order sinusoid function. Finally, obtain the continuum-normalized spectrum.
 \end{description}
@@
 
-If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works. The details are in Experiment 1.
+If most of the deviations are relatively small, the normalized spectrum for each visit doesn't lose shape, which means the normalization works. The details are in Experiment 1.
 
@@
 %{\AA}
-In this part we will introduce the Cannon 2 \cite{casey2016cannon}, and then use a linear method to optimize the inferred spectrum.
-Finally calibrate both the combined spectrum and individual visits.
-In a word, the method we use to calibrate the radial velocities of the combined spectra and individual visits is:
+In this part we will introduce the Cannon 2 \cite{casey2016cannon}, and then use a linear method to generate a mixture spectrum from the inferred spectrum.
+Finally calibrate both the combined spectrum and individual visit spectrums.
+The details are:
 
 \begin{description}
- \item[1] Infer labels from combined spectra and individual visits. 
- \item[2] Input these labels into the Cannon and generate inferred fluxes for the combined spectra and individual visits. Use these inferred fluxes as templates to calibrate radial velocities.
- \item[3] Generate optimized fluxes and obtain parameters a, b and c. These parameters show the radial velocity shifts between the data fluxes and the inferred fluxes.
- \item[4] By assuming these inferred fluxes are at rest, derive the radial velocity shifts of these combined spectra and individual visits. Finally, obtain the radial velocities of individual visits.
+ \item[1] Infer labels from combined spectrums and individual visit spectrums. 
+ \item[2] Input these labels back into the Cannon and generate inferred fluxes for the combined and individual visit spectrums. Use these inferred fluxes as templates to calibrate radial velocities.
+ \item[3] Generate mixture fluxes and obtain parameters a, b and c. These parameters can show the radial velocity shifts between the data fluxes and the inferred fluxes.
+ \item[4] By assuming inferred fluxes are at rest, derive the radial velocity shifts of individual visits. 
 \end{description}
 
-The very first thing we shall use is the Cannon 2.
+The very first thing is the Cannon 2.
 Suppose we have a trained Cannon model.
@@
 Each of them has at least nine stellar labels.
-But in the training step, we only use three of them $T_{eff}$, $log$ g  and $\left[Fe/H\right]$.
+But in the training step, we only use three of them: $T_{eff}$, $log$ g  and $\left[Fe/H\right]$.
 They span the range of $3500K <T_{eff}< 5300K$, $0 <log$ $g< 5$ and $-2.5 <\left[Fe/H\right]< 0.45$.
 In the training step, we only use the first combined spectrum for these 548 stars to train the model.
-The model we adopt
+The model we adopt is:
 
@@
 \(v(l_n)\) is the vectorizing function.
-The input \(l_n\) is the label list of length K for star n and the  output 
-\(v(l_n)\) is a vector of length D (D is bigger than K).
+The input \(l_n\) is the label list of length K for star n and the output \(v(l_n)\) is a vector of length D (D is bigger than K).
 \( \theta_{j}\) is a vector of length D of parameters which controlling the model at wavelength pixel j.
@@
 
-If we have a trained Cannon 2 model, $\theta_{j}$ is available.
-The labels we use are Teff, Log g and Fe/H.
-Randomly choose about 1\% of the APOGEE DR10 and make a histogram plot.
-The mean inverse variance of the stars is bigger than 10000 but smaller than 40000.
+After training the Cannon 2, randomly choose about 1\% of the APOGEE DR10.
+Only choose stars with mean inverse variance bigger than 10000 but smaller than 40000.
 We also exclude stars with undetermined labels.
@@
 
+Most stars have more than one visit.
 From the normalized combined spectrum and fluxes of individual visits of the very same star, several sets of inferred labels $l_n^{inf}$ are obtained.
@@
 
-In the following step, we deal with the combined spectrum and individual visits with the same method.
+In the following step, we deal with the combined spectrums and visit spectrums with the same method.
 $y_{j,n}$ represents one spectrum of star n at pixel j.
-It can be either combined spectrum or individual visit.
+It can be either the combined spectrum or the spectrum of one visit.
 \bigskip
@@
 The APOGEE team sets the combined spectrum and fluxes of individual visits at rest by removing the radial velocities.
-However, since the derived radial velocities from the APOGEE team are not 100 \% correct, these fluxes are not at rest.
+However, since the derived radial velocities from the APOGEE team are not 100 \% accurate, in fact these fluxes are not at rest.
 There are radial velocity shifts between the radial velocities from the APOGEE team and the correct radial velocities.
-But we can assume the shifts of radial velocities are Gaussian distributed, so the inferred fluxes generated by the Cannon 2 are at rest.
-This means we can use inferred fluxes as templates to calibrate radial velocities derived by the APOGEE team.
+But we can assume the radial velocity shifts are Gaussian distributed, so the inferred fluxes generated by the Cannon 2 are at rest.
+This means we can use the inferred fluxes as templates to calibrate the radial velocities derived by the APOGEE team.
 \cite{holtzman2013calibrations}
@@
 
-Where $RV_{cor}$, $RV_{apo}$ and $RV_{shift}$ are the correct radial velocity, radial velocity from the APOGEE team and the radial velocity shift. In our experiment, we will derive the $RV_{shift}$.
+Where $RV_{cor}$, $RV_{apo}$ and $RV_{shift}$ are the correct radial velocity, radial velocity from the APOGEE team and the radial velocity shift. In our experiment, we will derive $RV_{shift}$.
 \bigskip
 
-First, we define a spectrum called optimized spectrum.
+First, we define a spectrum called mixture spectrum.
 
 \begin{equation}
-y_{j,n}^{opt}=a\cdot y_{j+1,n}^{inf}+b\cdot y_{j,n}^{inf}+c\cdot y_{j-1,n}^{inf}
+y_{j,n}^{mix}=a\cdot y_{j+1,n}^{inf}+b\cdot y_{j,n}^{inf}+c\cdot y_{j-1,n}^{inf}
 \end{equation}
@@
 
-Where $y_{j,n}^{opt}$ is the optimized spectrum for star n at wavelength pixel j.
+Where $y_{j,n}^{mix}$ is the mixture spectrum for star n at wavelength pixel j.
 We move the inferred spectrums one pixel left, 0 pixel and one pixel right to simulate the radial velocity shift of the data spectrum.
 
-Then we fit the optimized spectrum to the data spectrum by using the least chi-squared method.
-After that, we think the optimized spectrum has the very same radial velocity shift as the data spectrum.
+Then, fit the mixture spectrum to the data spectrum by using the least chi-squared method.
+After that, we think the mixture spectrum has the very same radial velocity shift as the data spectrum.
 And we can derive the correct radial velocity of the spectrum by removing the radial velocity shift in formula 6.
-The objective function is the chi-squared between the optimized spectrum and the spectrum data.
-The objective function for one flux of star n is:
-\bigskip
+The objective function is the chi-squared between the mixture spectrum and the spectrum data, which is:
 
 \begin{equation}
-F^{obj}_n (a,b,c)= \sum_{j=1}^{j=J} {(y_{jn} - y_{jn}^{opt})^2 \over{\sigma_{jn}^2}}
+F^{obj}_n (a,b,c)= \sum_{j=1}^{j=J} {(y_{jn} - y_{jn}^{mix})^2 \over{\sigma_{jn}^2}}
 \end{equation}
 
-$\sigma_{jn}^2$ is the data uncertainty for star n at pixel j.
-The number of stellar and pixel each star are N and J.
-Here N and J are the number of the stellar and the number of pixel each star.
-Write the objective function in the form of matrix can make it simpler.
-\cite{hogg2010data}
+$\sigma_{jn}^2$ is the data uncertainty for star n at pixel j. Write the objective function in the form of matrix can make it simpler. \cite{hogg2010data}
 
@@
 % shall we put this part in Appendix
-Calculate the optimized spectrum \( y_{j,n}^{opt}\) by using (4). The Experiment 2 shows that the optimization works.
+% Calculate the mixture spectrum \( y_{j,n}^{mix}\) by using (4). The Experiment 2 shows that the method works.
 \bigskip
@@
 %Can you interpret a, b, c in terms of radial velocity? If so, how?
-After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate both the combined spectra and individual visits of these stars.
+After obtaining $a_n$, $b_n$ and $c_n$ for these stars, we can calibrate both the combined spectra and visit spectra of these stars.
 Consider Relativistic Doppler effect.
@@
 
-The radial velocity is related to parameters a, b and c.
-First, we need to assume that the inferred spectrum generated by the Cannon is set at rest, which means the radial velocity of it is zero.
-Second, we think the radial velocity of the data spectrum is equal to the radial velocity of the optimized spectrum.
-This is because the optimized spectrum is obtained by fitting the inferred spectrum to the data spectrum.
-We set the radial velocity to be positive if the star is leaving us.
-\bigskip
-
-The radial velocity is related to pixels. We can obtain the velocity shift by calculating the centroid shift. The centroid in pixel can be expressed as:
+By considering the shift of centroid, we can derive the radial velocity by using a, b and c.
+First, assume the inferred spectrum generated by the Cannon is at rest, which means the radial velocity of it is zero.
+Second, we think the radial velocity of the data spectrum is equal to the radial velocity of the mixture spectrum.
+This is because we fit the mixture spectrum to the data spectrum by using least chi-squared method.
+So the formula is:
 
@@
 
-If the parameters are a, b and c. Then the centroid of the spectrum in frequency is:
+If the parameters are a, b and c. Then the centroid of the spectrum is:
 \begin{equation}
@@
 
-Thus we have:
+The radial velocity shift can be calculated by using the shift of the mixture spectrum centroid. Thus we have:
 
@@
 \end{equation}
-Where $RV_{shift} $ is the radial velocity shift and $pixel_c^{shift}$ is the pixel centroid shift between the two spectrum.
+Where $RV_{shift} $ is the radial velocity shift and $pixel_c^{shift}$ is the pixel centroid shift between the two spectrums.
+\bigskip
+Also, the lower bound of the $RV_{shift}$ uncertainty can be estimated by using Cramer Rao method, which can be expressed as:
+\begin{equation}
+Un_{RV}^{shift} \geqslant v_{pixel}*\sqrt{J_1*I*J_1^T}
+\end{equation}
+$Un_{RV}^{shift}$ is the uncertainty of $RV_{shift}$.
+The minimum variance unbiased estimator(MVUE) for $pixel_c^{shift}$ is $T(a,b,c) = {{c-a}\over{a+b+c}}$.
+$J_1$ and $I$ are the Jacobian Matrix and the Fisher Matrix of T(a,b,c).
+$J_1 = [{{-b-2c}\over{(a+b+c)^2}} , {{a-c}\over{(a+b+c)^2}}, {{2a+b}\over{(a+b+c)^2}}]$ and $I = [A_n^TC_n^{-1}A_n]^{-1} $.
+\bigskip
 
 But if 2b<a+c, which means the magnitude of the spectrum moves one pixel left or right is big, the approximation will expire because the influence of the pixels two pixels left or right can't be ignored.
-When this happens, we will use five parameters, which are:
-$a_1$, $a_2$, $a_3$, $a_4$, $a_5$. Now the optimized spectrum is:
+When this happens, our formula won't work good.
+We are still trying to find a new formula for this case.
 
-\begin{equation}
-y_{j,n}^{opt}=a_1\cdot y_{j+2,n}^{inf}+a_2\cdot y_{j+1,n}^{inf}+a_3\cdot y_{j,n}^{inf}+a_4\cdot y_{j-1,n}^{inf}+a_5\cdot y_{j-2,n}^{inf}
-\end{equation}
-This means we move the inferred spectrum two pixels left, one pixel left, zero pixel, one pixel right and two pixels right and generate five new spectrums.
-The parameters for them are $a_1$, $a_2$, $a_3$, $a_4$, $a_5$.
-We only use five parameters to calculate the radial velocity shift when $2b<a+c$, where the influence of the spectrum moves two pixels left and right can't be ignore.
+\subsection{\label{sec:level2}Calibrate RVs by using absorption lines}
 
-So the velocity shift is
+Since the continuum fitting may mix with the RV calibration, we want to only use the absorption lines of the spectrum.
+Choose some very clear absorption lines and fit them by using the formulas above.
+The line list can be found in the document about ASPCAP pipeline \cite{shetrone2015sdss}.
+However, there are few clear absorption lines in the APOGEE data release.
+Also, for different types of stars the clear absorption lines are different.
+Thus, it's important that we find an effective way to find out clear lines for different stars.
+\bigskip
 
-\begin{equation}
-RV_{shift} = v_{pixel} \cdot {{c-a}\over{a+b+c}}\qquad2b>a+c
-\end{equation}
+Pick up the absorption lines by using the Gaussian fit in the data spectrum.
+Set the half-width of the gap to be 8 pixels or less.
+Also, remove the valleys which has a value bigger than 1.
+So, we obtain a set of absorption lines which satisfy the restriction.
+Only use pixels at these absorption lines by setting the inverse variance of the other pixels to be 0.
+Calculate the parameters for individual visits, then the radial velocity shifts.
+We will show this part in experiment 3.
 
-\begin{equation}
-RV_{shift} = v_{pixel} \cdot {{2a_5 +a_4 - a_2 - 2a_1}\over{a_1+a_2+a_3+a_4+a_5}}\qquad2b<a+c     
-\end{equation}
-
-We will plot the histogram for the five parameters in our experiment and demonstrate moving two pixels are good enough for these $2b<a+c$ cases.
+% ?? How to choose lines
+We also compare the results between the old method(fit the whole spectrum) and the new method(only fit the clear absorption line) in experiment 3.
 
@@
 From these two points, there is still much to be improved in APOGEE team's RV results.
+Meanwhile, the APOGEE team uses the whole spectrum to determine the radial velocity, which means the continuum-fitting may mix with the velocity fit.
+But in our experiment, we try to only use the absorption lines of the spectrum.
 \bigskip
 
-In experiment 3, first, we will show the RVs for individual visits from the APOGEE team is not very reliable.
-Then, plot our results.
-Finally, argue our method gives a better RV measurement for individual visits.
-
-\subsection{\label{sec:level2}Optimize Teff , log g and [Fe/H] simultaneously with a, b, c}
+\subsection{\label{sec:level2}optimize Teff , log g and [Fe/H] simultaneously with a, b, c}
 
@@
 To demonstrate the continuum normalization works well for combined spectrums and individual visits, we plot continuum pixels for stars with different SNR(signal to noise ratio), Teff and Logg.
-Here we randomly choose 5 stars with different SNR, Teff and logg and plot them in figure 1 to 5.
+Here we randomly choose 5 stars with different SNR, Teff and logg and plot them in.
 If continuum pixels roughly cover the spectrums evenly, the normalization works well.
+Here we only show on star.
+The plots of the other four stars can be found in appendix.
 
@@
 \centerline{Fig.1 Comparison of each visit for Star A.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The red dots are continuum pixels}
 \centerline{SNR of Star A is 108. Teff = 4939K Logg =2.71 Fe/H =-5.368}
@@
 
-% Star B
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{CP_B.png}
-
-\centerline{Fig.2 Comparison of each visit for Star B.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
-\centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 Fe/H =3.486}
-
-\end{center}
-
-% Star C
-
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{CP_C.png}
-
-\centerline{Fig.3 Comparison of each visit for Star C.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
-\centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 Fe/H =6.577}
-
-\end{center}
-
-% Star D
-
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{CP_D.png}
-
-\centerline{Fig.4 Comparison of each visit for Star D.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
-\centerline{SNR of Star D is 140. Teff = 5094K Logg =3.088 Fe/H = -3.679 }
-
-\end{center}
-
-% Star E
-
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{CP_E.png}
-
-\centerline{Fig.5 Comparison of each visit for Star E.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
-\centerline{SNR of Star E is 208. Teff = 4869K Logg =1.903 Fe/H = -1.691 }
-
-\end{center}
-
-These continuum pixels roughly cover the spectrums evenly, which means the normalization works well.
+The other four stars are in appendix figure 1-4. These continuum pixels roughly cover the spectrums evenly, which means the normalization works well.
 
@@
 If they are very small, the normalization works.
-They are plotted in figure 6, 7 and 8.
+They are plotted in figure 2, 3 and 4.
 
@@
 
-\centerline{Fig.6 Histogram of Delta Teff for individual visits}
+\centerline{Fig.2 Histogram of Delta Teff for individual visits}
 \bigskip
@@
 
-\centerline{Fig.7 Histogram of Delta logg for individual visits}
+\centerline{Fig.3 Histogram of Delta logg for individual visits}
 
@@
 
-\centerline{Fig.8 Histogram of Delta Fe/H for individual visits}
+\centerline{Fig.4 Histogram of Delta Fe/H for individual visits}
 \bigskip
@@
 \begin{center}
-\includegraphics[width=170mm]{hist_abc_visits.png}
+
+\includegraphics[width=170mm]{hist_rv_abc.png}
+
+\centerline{Fig.5 Histogram of RV shifts, a, b and c of individual visits}
+\centerline{Here we fit the whole spectrum}
 \end{center}
 
-\centerline{Fig.9 Histogram of a,b,c for individual visits}
 \bigskip
 
-\begin{center}
-\includegraphics[width=170mm]{hist_ve_visits.png}
-\end{center}
-
-\centerline{Fig.10 Histogram of RV shifts for individual visits}
-\bigskip
-
-Then, we try to find some relation between our results and FiberID, MJD(Modified Julia Date), RA and DEC. Figures 11, 12, 13, 14 and 15 shows the relation.
-
-\begin{center}
-\includegraphics[width=170mm]{dchi_vs_all.png}
-\end{center}
-
-\centerline{Fig.11 Delta-chi-squared vs MJD, FiberID, RA and DEC for individual visitis}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{a_vs_all.png}
-\end{center}
-
-\centerline{Fig.12 a vs MJD, FiberID, RA and DEC for individual visitis}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{b_vs_all.png}
-\end{center}
-
-\centerline{Fig.13 b vs MJD, FiberID, RA and DEC for individual visitis}
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{c_vs_all.png}
-\end{center}
-
-\centerline{Fig.14 c vs MJD, FiberID, RA and DEC for individual visitis}
-\bigskip
+Then, we try to find some relation between our results and FiberID, HJD(HELIO Julia Date), RA, DEC, AirMass and SNR, which is in Figure 6. The result for parameter a, b and c are in appendix.
 
@@
 
-\centerline{Fig.15 RV shifts vs MJD, FiberID, RA and DEC for individual visitis}
+\centerline{Fig.6 RV shifts of individual visits VS HJD, RA, DEC, FiberID, AirMass and SNR}
+\centerline{Here we fit the whole spectrum}
 \bigskip
@@
 \subsection{\label{sec:level2}Experiment 3}
+It's reasonable that we only use the absorption lines in the spectra since the continuum fitting may max with the RV fitting. In figure 7, we show the results by using the absorption lines.
 
-Finally, we show our results are better than the results from the APOGEE team.
-We demonstrate it by randomly choosing 5 stars with different SNR, Teff, logg and Fe/H.
-Then plot the fluxes from the APOGEE team and the Cannon.
-We will show the inferred fluxes are at rest and our formula gives correct RV shifts.
+\begin{center}
+\includegraphics[width=170mm]{hist_rv_abc_new.png}
+\end{center}
 
-% star 1
+\centerline{Fig.7 Histogram of RV shifts, a, b and c of individual visits}
+\centerline{Here we only fit the absorption lines}
 \bigskip
@@
 \begin{center}
-\includegraphics[width=170mm]{Peak_1.png}
+\includegraphics[width=170mm]{ve_vs_all_new.png}
 
-\centerline{Fig.16 Comparison of each visit for Star 1.}
-\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
-\centerline{The black lines show the centers of the peaks in these fluxes}
-\centerline{SNR of Star 1 is 206. Teff = 4208K Logg =1.347 Fe/H =-1.018}
+\centerline{Fig.8 RV shifts of individual visits VS HJD, RA, DEC, FiberID, AirMass and SNR}
+\centerline{Here we only fit the absorption lines}
+
+\end{center}
+\bigskip
+After that, we compare the results from the two method.
+
+\begin{center}
+\includegraphics[width=170mm]{old_vs_new.png}
+
+\centerline{Fig.9 Comparison of the two methods in individual visits}
+\centerline{Here we only fit the absorption lines}
 
@@
 
-% Star 2
-\bigskip
+The results of the two methods are similar to each other.
+However, there are very big difference at some visits.
+Now we choose the four visits with the biggest difference in delta RV shifts, which is defined as the absolute value of the RV shift difference between the two methods.
+The four visits are shown in figure 10.
 
 \begin{center}
-\includegraphics[width=170mm]{Peak_2.png}
+\includegraphics[width=170mm]{big_delta_4_visit.png}
 
-\centerline{Fig.17 Comparison of each visit for Star 2.}
-\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
-\centerline{The black lines show the centers of the peaks in these fluxes}
-\centerline{SNR of Star 2 is 197. Teff = 4641K Logg =2.201 Fe/H =-5.873}
+\centerline{Fig.10 The four stars with biggest delta RV shifts}
+\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
 
@@
 
-% Star 3
-
-\bigskip
+We also shows the four visits with the biggest RV shifts from the new method, which is in figure 11.
 
 \begin{center}
-\includegraphics[width=170mm]{Peak_3.png}
+\includegraphics[width=170mm]{big_4_visit.png}
 
-\centerline{Fig.18 Comparison of each visit for Star 3.}
-\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
-\centerline{The black lines show the centers of the peaks in these fluxes}
-\centerline{SNR of Star 3 is 117. Teff = 4902K Logg =2.639 Fe/H =-1.863}
+\centerline{Fig.11 The four stars with biggest RV shifts from the new method.}
+\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
 
@@
 
-% Star 4
+In figure 10 and 11, we can see that the new method can explain the RV shift between the inferred flux and the data flux better.
+For example, the second visit in figure 10 seems to have a very small RV shift.
+But, the old method gives a big RV shift, while the new method gives a small one, which is more persuasive.
 
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{Peak_4.png}
-
-\centerline{Fig.19 Comparison of each visit for Star 4.}
-\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
-\centerline{The black lines show the centers of the peaks in these fluxes}
-\centerline{SNR of Star 4 is 122. Teff = 4813K Logg =2.736 Fe/H = -1.832 }
-
-\end{center}
-
-% Star 5
-
-\bigskip
-
-\begin{center}
-\includegraphics[width=170mm]{Peak_5.png}
-
-\centerline{Fig.20 Comparison of each visit for Star 5.}
-\centerline{The bottom two in each subplot are the combined spectrum and the others are individual visits.}
-\centerline{The black lines show the centers of the peaks in these fluxes}
-\centerline{SNR of Star 5 is 113. Teff = 4513K Logg =2.662 Fe/H = -5.215 }
-
-\end{center}
-
-\bigskip
-
-From these plots, we can see that the peaks of fluxes from the APOGEE team have shifts from each other, which should not happen because these fluxes are set at rest by the APOGEE team and there shouldn't be shifts between them.
-This means radial velocities from the APOGEE team are not very accurate.
-When we look at the fluxes generated from the Cannon, the peaks from individual visits have the same positions.
-These spectrums are at rest.
-That's to say, we can use inferred fluxes from the Cannon as templates for calibration.
 \bigskip
@@
 This means considering three pixels is good enough.
-In figure 9, we can see that most b are close to 1 and most a, c are close to 0.
-This means our method works good for most of these cases.
-Even for the case that 2b<a+c, which means we need to consider at least 5 pixels.
-Our formula 20 gives a good expression.
-Since all the RV shifts in figure10 is smaller than 2 pixels, we don't need to consider 7 or more pixels.
+Our method still need to be improved for 2b<a+c.
+
+Also, the APOGEE team fit the whole spectrum to derive the radial velocity.
+The fitting may mix with the continuum fitting, which is not good.
+But we only use the absorption lines in the spectrum and the result should be better.
 
 In conclusion, the method we use to determine the RV shifts is good. It gives more accurate radial velocities than the APOGEE team.
+
+ \subsection{\label{sec:level2}Experiment 4}
+ We try our fitting method on the three suspect stars from APOGEE DR12, which are plotted in figure 12, 13 and 14.
+
+\begin{center}
+\includegraphics[width=170mm]{s3_A_para.png}
+
+\centerline{Fig.12 The individual visits of suspect Star 1}
+\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
+
+\end{center}
+
+\begin{center}
+\includegraphics[width=170mm]{s3_B_para.png}
+
+\centerline{Fig.13 The individual visits of suspect Star 2}
+\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
+
+\end{center}
+
+\begin{center}
+\includegraphics[width=170mm]{s3_C_para.png}
+
+\centerline{Fig.14 The individual visits of suspect Star 3}
+\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
+
+\end{center}
 
@@
 
+% d_1
+
+% Star B
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{CP_B.png}
+
+\centerline{Fig.1 Comparison of each visit for Star B.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 Fe/H =3.486}
+
+\end{center}
+
+% d_2
+% Star C
+
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{CP_C.png}
+
+\centerline{Fig.2 Comparison of each visit for Star C.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 Fe/H =6.577}
+
+\end{center}
+
+% d_3
+% Star D
+
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{CP_D.png}
+
+\centerline{Fig.3 Comparison of each visit for Star D.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star D is 140. Teff = 5094K Logg =3.088 Fe/H = -3.679 }
+
+\end{center}
+
+% d_4
+% Star E
+
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{CP_E.png}
+
+\centerline{Fig.4 Comparison of each visit for Star E.}
+\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{SNR of Star E is 208. Teff = 4869K Logg =1.903 Fe/H = -1.691 }
+
+\end{center}
+
 Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.

### 2017-02-19 0124_plot.py

@@ -1,1105 +1,0 @@
-import os
-import numpy as np
-from astropy.table import Table
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import matplotlib
-import pickle
-
-from TheCannon_2 import dataset,apogee
-from TheCannon_2 import model
-
-
-pkl_file = open('wl.pkl', 'rb')
-wl = pickle.load(pkl_file)
-pkl_file.close()
-
-
-# load path
-
-pkl_file = open('n_900_path_fits.pkl', 'rb')
-path_fits = pickle.load(pkl_file)
-pkl_file.close()
-
-
-pkl_file = open('n_900_path_flux.pkl', 'rb')
-path_flux = pickle.load(pkl_file)
-pkl_file.close()
-
-
-# mean_ivar
-
-pkl_file = open('n_900_mean_ivar.pkl', 'rb')
-mi = pickle.load(pkl_file)
-pkl_file.close()
-
-
-
-N = len(path_fits)
-print(N)
-
-velocity = []
-fiber_id = []
-mean_ivar = []
-parameters = []
-a = []
-b = []
-c= []
-
-nor = []
-ivar=[]
-inf =[]
-inf_label= []
-dchi = []
-
-MJD = []
-meanivar = []
-
-RA = []
-DEC = []
-SNR = []
-
-
-for i in range(0,N):
-    print("loading star %d"%(i+1))
-
-    star_i = fits.open(path_fits[i])
-
-
-    ni = len(star_i[4].data[:, 0])
-
-    #mean ivar
-    one = np.ones(ni-2)
-    meanivar = np.append(meanivar,one*mi[i])
-
-    dchi = np.append(dchi,star_i[6].data[2:ni])
-    # SNR RA DEC
-    SNR = np.append(SNR,(star_i[0].header["SNR"]*one))
-    RA = np.append(RA, (star_i[0].header["RA"] * one))
-    DEC = np.append(DEC, (star_i[0].header["DEC"] * one))
-
-
-
-    velocity = np.append(velocity,star_i[10].data[2:ni,0])
-    fiber_id = np.append(fiber_id,star_i[7].data)
-    mean_ivar.append(np.mean(star_i[1].data[0]))
-    parameters = np.append(parameters,star_i[4].data[2:ni,2])
-
-    a = np.append(a, star_i[4].data[2:ni, 0])
-    b = np.append(b, star_i[4].data[2:ni, 1])
-    c = np.append(c, star_i[4].data[2:ni, 2])
-
-
[…]

### 2017-02-19 0215_fitting_absorption_lines.py

@@ -1,0 +1,690 @@
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import matplotlib
+import pickle
+
+import astropy.io.fits as ts
+import AnniesLasso_2 as tc
+
+
+import math
+
+from astropy.time import Time
+from astropy import units as u
+from astropy.coordinates import SkyCoord
+from math import sin, asin, cos, acos, pi
+
+# calculate altaz from radectime
+
+
+def radec_to_azalt(time, ra,dec):
+
+    lon = -105.820417
+    lat = 32.780361
+
+    c = SkyCoord(ra=ra*u.degree, dec=dec*u.degree, frame='icrs')
+
+    # in degree
+    ra = c.ra.hour/24*360
+
+    ha = time.sidereal_time("mean").hour/24*360 - ra;
+    print(ra,time.sidereal_time("mean").hour/24*360,ha)
+
+    if (ha < 0):
+        ha = ha + 360
+
+
+        #    print "ha:", ha
+        # convert degrees to radians
+    ha = ha * pi / 180
+    dec = dec * pi / 180
+    lat = lat * pi / 180
+
+    # compute altitude in radians
+    sin_alt = sin(dec) * sin(lat) + cos(dec) * cos(lat) * cos(ha);
+    alt = asin(sin_alt)
+
+    # compute azimuth in radians
+    # divide by zero error at poles or if alt = 90 deg
+    cos_az = (sin(dec) - sin(alt) * sin(lat)) / (cos(alt) * cos(lat))
+    az = acos(cos_az)
+
+    # convert radians to degrees
+    hrz_altitude = alt * 180 / pi;
+    hrz_azimuth = az * 180 / pi;
+
+    # choose hemisphere
+    if (sin(ha) > 0):
+        hrz_azimuth = 360 - hrz_azimuth
+
+    hrz_azimuth = hrz_azimuth * 24.0 / 360.0
+
+    # return alt and az
+    return hrz_altitude ,hrz_azimuth
+
+
+def alt2airmass(alt):
+
+    zenithAngle = 90.0 - alt
+    za_radians = zenithAngle/180.0*math.pi
+    airmass = 1.0/math.cos(za_radians)
+
+    return airmass
+
+
+
+class airmass():
+
+    def cal_airmass(self,ra,dec,time):
+
[…]

### 2017-02-19 0217_plot_all_in_paper.py

@@ -1,0 +1,2146 @@
+
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import matplotlib
+import pickle
+
+from TheCannon_2 import dataset,apogee
+from TheCannon_2 import model
+
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# load path
+
+pkl_file = open('n_900_path_fits.pkl', 'rb')
+path_fits = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_900_path_flux.pkl', 'rb')
+path_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# mean_ivar
+
+pkl_file = open('n_900_mean_ivar.pkl', 'rb')
+mi = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+
+
+N = len(path_fits)
+print(N)
+
+
+class plot():
+
+    def read_data(self):
+
+        N = len(path_fits)
+        print(N)
+
+        velocity = []
+        velocity_new = []
+        fiber_id = []
+        mean_ivar = []
+        parameters = np.array([0,1,0])
+        parameters_new = np.array([0,1,0])
+
+
+        inf_label = []
+        dchi = []
+
+        MJD = []
+        HJD = []
+        meanivar = []
+
+        RA = []
+        DEC = []
+        SNR = []
+
+        airmass = []
+
+        # star name and the number of visit
+        # dimension N*2
+        star_visit = []
+        star_name = []
+
+
+
+        for i in range(0, N):
+            print("loading star %d" % (i + 1))
+
+            star_name_i = path_fits[i]
+
+            star_i = fits.open(path_fits[i])
+
+            ni = len(star_i[4].data[:, 0])
+
+
+
+            # mean ivar
+            one = np.ones(ni - 2)
+            for si in range(0,ni-2):
+                star_name = np.append(star_name, star_name_i)
+                star_visit.append(si)
+
+            meanivar = np.append(meanivar, one * mi[i])
+
+
+
+            dchi = np.append(dchi, star_i[6].data[2:ni])
+            # SNR RA DEC
+            SNR = np.append(SNR, (star_i[0].header["SNR"] * one))
[…]

### 2017-02-19 0218_plot_three_suspect_star.py

@@ -1,0 +1,2088 @@
+
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import matplotlib
+import pickle
+
+from TheCannon_2 import dataset,apogee
+from TheCannon_2 import model
+
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# load path
+
+pkl_file = open('n_900_path_fits.pkl', 'rb')
+path_fits = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_900_path_flux.pkl', 'rb')
+path_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# mean_ivar
+
+pkl_file = open('n_900_mean_ivar.pkl', 'rb')
+mi = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+
+
+N = len(path_fits)
+print(N)
+
+
+class plot():
+
+    def read_data(self):
+
+        N = len(path_fits)
+        print(N)
+
+        velocity = []
+        velocity_new = []
+        fiber_id = []
+        mean_ivar = []
+        parameters = np.array([0,1,0])
+        parameters_new = np.array([0,1,0])
+
+
+        inf_label = []
+        dchi = []
+
+        MJD = []
+        HJD = []
+        meanivar = []
+
+        RA = []
+        DEC = []
+        SNR = []
+
+        airmass = []
+
+        # star name and the number of visit
+        # dimension N*2
+        star_visit = []
+        star_name = []
+
+
+
+        for i in range(0, N):
+            print("loading star %d" % (i + 1))
+
+            star_name_i = path_fits[i]
+
+            star_i = fits.open(path_fits[i])
+
+            ni = len(star_i[4].data[:, 0])
+
+
+
+            # mean ivar
+            one = np.ones(ni - 2)
+            for si in range(0,ni-2):
+                star_name = np.append(star_name, star_name_i)
+                star_visit.append(si)
+
+            meanivar = np.append(meanivar, one * mi[i])
+
+
+
+            dchi = np.append(dchi, star_i[6].data[2:ni])
+            # SNR RA DEC
+            SNR = np.append(SNR, (star_i[0].header["SNR"] * one))
[…]

### 2017-02-19 0218_three_suspect_star_new_code.py

@@ -1,0 +1,566 @@
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import matplotlib
+import pickle
+
+import astropy.io.fits as ts
+import AnniesLasso_2 as tc
+
+
+import math
+
+from astropy.time import Time
+from astropy import units as u
+from astropy.coordinates import SkyCoord
+from math import sin, asin, cos, acos, pi
+
+# calculate altaz from radectime
+
+
+def radec_to_azalt(time, ra,dec):
+
+    lon = -105.820417
+    lat = 32.780361
+
+    c = SkyCoord(ra=ra*u.degree, dec=dec*u.degree, frame='icrs')
+
+    # in degree
+    ra = c.ra.hour/24*360
+
+    ha = time.sidereal_time("mean").hour/24*360 - ra;
+    print(ra,time.sidereal_time("mean").hour/24*360,ha)
+
+    if (ha < 0):
+        ha = ha + 360
+
+
+        #    print "ha:", ha
+        # convert degrees to radians
+    ha = ha * pi / 180
+    dec = dec * pi / 180
+    lat = lat * pi / 180
+
+    # compute altitude in radians
+    sin_alt = sin(dec) * sin(lat) + cos(dec) * cos(lat) * cos(ha);
+    alt = asin(sin_alt)
+
+    # compute azimuth in radians
+    # divide by zero error at poles or if alt = 90 deg
+    cos_az = (sin(dec) - sin(alt) * sin(lat)) / (cos(alt) * cos(lat))
+    az = acos(cos_az)
+
+    # convert radians to degrees
+    hrz_altitude = alt * 180 / pi;
+    hrz_azimuth = az * 180 / pi;
+
+    # choose hemisphere
+    if (sin(ha) > 0):
+        hrz_azimuth = 360 - hrz_azimuth
+
+    hrz_azimuth = hrz_azimuth * 24.0 / 360.0
+
+    # return alt and az
+    return hrz_altitude ,hrz_azimuth
+
+
+def alt2airmass(alt):
+
+    zenithAngle = 90.0 - alt
+    za_radians = zenithAngle/180.0*math.pi
+    airmass = 1.0/math.cos(za_radians)
+
+    return airmass
+
+
+
+class airmass():
+
+    def cal_airmass(self,ra,dec,time):
+
[…]

### 2017-02-22 paper/ms.tex
Add 4 plots

@@
  \subsection{\label{sec:level2}Continuum normalization}
-Since the Cannon needs the spectrums to be normalized first.
-To start with, we should continuum-normalize the combined spectrums and individual visit spectrums.
-The data we use is in Apstar files from APOGEE DR10, which include two combined spectrums and several individual visit spectrums for one star.
+Since the Cannon needs the spectra to be normalized first.
+To start with, we should continuum-normalize the combined spectra and individual visit spectra.
+The data we use is in Apstar files from APOGEE DR10, which include two combined spectra and several individual visit spectra for one star.
 They are set to the same rest wavelength scale after removing the radial velocities derived by the APOGEE team.
@@
 Our method is the same as the one in Ness et al 2015 \cite{ness2015cannon}.
-The spectrums are in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
+The spectra are in Apstar files, which are already resampled onto the sample wavelength scale with 8575 pixels.
 There are four steps in the normalization step:
@@
 \begin{description}
- \item[1] Cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectrum.
+ \item[1] Cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]] to avoid gaps in the spectra.
  \item[2] Do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance.
- \item[3] Put a mask on the spectrum.
- \item[4] Fit the continuum spectrum in these continuous regions by using a 3-order sinusoid function. Finally, obtain the continuum-normalized spectrum.
+ \item[3] Put a mask on the spectra.
+ \item[4] Fit the continuum spectra in these continuous regions by using a 3-order sinusoid function. Finally, obtain the continuum-normalized spectra.
 \end{description}
@@
 \begin{description}
-  \item[1] Plot continuum pixels for combined spectrums and individual visits, then check whether they roughly cover the spectrum evenly.
-  \item[2] Plot individual visits and compare them with the combined spectrum, they should have similar shapes.
-  \item[3] Infer stellar labels from individual visits by using the Cannon and these inferred labels should be similar to the ones from the combined spectrum of the very same star.
+  \item[1] Plot continuum pixels for combined spectra and individual visits, then check whether they roughly cover the spectra evenly.
+  \item[2] Plot individual visits and compare them with the combined spectra, they should have similar shapes.
+  \item[3] Infer stellar labels from individual visits by using the Cannon and these inferred labels should be similar to the ones from the combined spectra of the very same star.
 \end{description}
@@
 For point 3
-If the inferred labels from each visit are similar to the ones from the combined spectrum, the normalization works. We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:
+If the inferred labels from each visit are similar to the ones from the combined spectra, the normalization works. We define $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H as:
 
@@
 
-$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred Teff for each visit and the combined spectrum. It's similar for $logg$ and $Fe/H$
+$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred Teff for each visit and the combined spectra. It's similar for $logg$ and $Fe/H$
 
-If most of the deviations are relatively small, the normalized spectrum for each visit doesn't lose shape, which means the normalization works. The details are in Experiment 1.
+If most of the deviations are relatively small, the normalized spectra for each visit doesn't lose shape, which means the normalization works. The details are in Experiment 1.
 
-\subsection{\label{sec:level2}Calibrate the spectrums}
+\subsection{\label{sec:level2}A new method to derive the radial velocity}
 
 %{\AA}
-In this part we will introduce the Cannon 2 \cite{casey2016cannon}, and then use a linear method to generate a mixture spectrum from the inferred spectrum.
-Finally calibrate both the combined spectrum and individual visit spectrums.
+In this part we will introduce the Cannon 2 \cite{casey2016cannon}, and then use a linear method to generate a mixture spectra from the inferred spectra.
+Finally calibrate both the combined spectra and individual visit spectra.
 The details are:
@@
 \begin{description}
- \item[1] Infer labels from combined spectrums and individual visit spectrums. 
- \item[2] Input these labels back into the Cannon and generate inferred fluxes for the combined and individual visit spectrums. Use these inferred fluxes as templates to calibrate radial velocities.
+ \item[1] Infer labels from combined spectra and individual visit spectra. 
+ \item[2] Input these labels back into the Cannon and generate inferred fluxes for the combined and individual visit spectra. Use these inferred fluxes as templates to calibrate radial velocities.
  \item[3] Generate mixture fluxes and obtain parameters a, b and c. These parameters can show the radial velocity shifts between the data fluxes and the inferred fluxes.
@@
 Suppose we have a trained Cannon model.
-The training set contains 548 stellar and each stellar spectrum has 8575 pixels.
+The training set contains 548 stellar and each stellar spectra has 8575 pixels.
 Every pixel is related to a specific wavelength.
@@
 They span the range of $3500K <T_{eff}< 5300K$, $0 <log$ $g< 5$ and $-2.5 <\left[Fe/H\right]< 0.45$.
-In the training step, we only use the first combined spectrum for these 548 stars to train the model.
+In the training step, we only use the first combined spectra for these 548 stars to train the model.
 The model we adopt is:
@@
 
-Where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j.
+Where \(y_{jn}\) is the spectra data for star n at wavelength pixel j.
 \(v(l_n)\) is the vectorizing function.
@@
 $l_n$ and $l_n^{inf}$ are stellar labels and inferred stellar labels for star n.
-$y_{jn}^{inf}$ is the inferred spectrum for star n at wavelength pixel j.
+$y_{jn}^{inf}$ is the inferred spectra for star n at wavelength pixel j.
 
@@
 Most stars have more than one visit.
-From the normalized combined spectrum and fluxes of individual visits of the very same star, several sets of inferred labels $l_n^{inf}$ are obtained.
-Then put the inferred labels $l_n^{inf}$ back into formula (5), the inferred combined spectrum and inferred fluxes of individual visits are available.
-The data spectrum we use are in Apstar files.
-There are two combined spectrums and several individual visits in the Apstar files.
-Put all these spectrums into the trained Cannon 2 and obtain several sets of inferred labels for each star.
-After that, put the inferred labels back into the model and calculate the inferred combined spectrum(There should be two) and inferred fluxes of individual visits.
+From the normalized combined spectra and fluxes of individual visits of the very same star, several sets of inferred labels $l_n^{inf}$ are obtained.
+Then put the inferred labels $l_n^{inf}$ back into formula (5), the inferred combined spectra and inferred fluxes of individual visits are available.
+The data spectra we use are in Apstar files.
+There are two combined spectra and several individual visits in the Apstar files.
+Put all these spectra into the trained Cannon 2 and obtain several sets of inferred labels for each star.
+After that, put the inferred labels back into the model and calculate the inferred combined spectra(There should be two) and inferred fluxes of individual visits.
 \bigskip
 
-In the following step, we deal with the combined spectrums and visit spectrums with the same method.
-$y_{j,n}$ represents one spectrum of star n at pixel j.
-It can be either the combined spectrum or the spectrum of one visit.
+In the following step, we deal with the combined spectra and visit spectra with the same method.
+$y_{j,n}$ represents one spectra of star n at pixel j.
+It can be either the combined spectra or the spectra of one visit.
 \bigskip
 
-The APOGEE team sets the combined spectrum and fluxes of individual visits at rest by removing the radial velocities.
+The APOGEE team sets the combined spectra and fluxes of individual visits at rest by removing the radial velocities.
 However, since the derived radial velocities from the APOGEE team are not 100 \% accurate, in fact these fluxes are not at rest.
@@
 
-First, we define a spectrum called mixture spectrum.
+First, we define a spectra called mixture spectra.
 
@@
 
-Where $y_{j,n}^{mix}$ is the mixture spectrum for star n at wavelength pixel j.
-We move the inferred spectrums one pixel left, 0 pixel and one pixel right to simulate the radial velocity shift of the data spectrum.
+Where $y_{j,n}^{mix}$ is the mixture spectra for star n at wavelength pixel j.
+We move the inferred spectra one pixel left, 0 pixel and one pixel right to simulate the radial velocity shift of the data spectra.
 
-Then, fit the mixture spectrum to the data spectrum by using the least chi-squared method.
-After that, we think the mixture spectrum has the very same radial velocity shift as the data spectrum.
-And we can derive the correct radial velocity of the spectrum by removing the radial velocity shift in formula 6.
-The objective function is the chi-squared between the mixture spectrum and the spectrum data, which is:
+Then, fit the mixture spectra to the data spectra by using the least chi-squared method.
+After that, we think the mixture spectra has the very same radial velocity shift as the data spectra.
+And we can derive the correct radial velocity of the spectra by removing the radial velocity shift in formula 6.
+The objective function is the chi-squared between the mixture spectra and the spectra data, which is:
 
@@
 
-By using (8) we can calculate $a_n$, $b_n$ and $c_n$, which are parameters a, b and c for one spectrum of star n.
+By using (8) we can calculate $a_n$, $b_n$ and $c_n$, which are parameters a, b and c for one spectra of star n.
 
 % shall we put this part in Appendix
-% Calculate the mixture spectrum \( y_{j,n}^{mix}\) by using (4). The Experiment 2 shows that the method works.
+% Calculate the mixture spectra \( y_{j,n}^{mix}\) by using (4). The Experiment 2 shows that the method works.
 \bigskip
@@
 By considering the shift of centroid, we can derive the radial velocity by using a, b and c.
-First, assume the inferred spectrum generated by the Cannon is at rest, which means the radial velocity of it is zero.
-Second, we think the radial velocity of the data spectrum is equal to the radial velocity of the mixture spectrum.
-This is because we fit the mixture spectrum to the data spectrum by using least chi-squared method.
+First, assume the inferred spectra generated by the Cannon is at rest, which means the radial velocity of it is zero.
+Second, we think the radial velocity of the data spectra is equal to the radial velocity of the mixture spectra.
+This is because we fit the mixture spectra to the data spectra by using least chi-squared method.
 So the formula is:
@@
 
-If the parameters are a, b and c. Then the centroid of the spectrum is:
+If the parameters are a, b and c. Then the centroid of the spectra is:
 \begin{equation}
@@
 
-The radial velocity shift can be calculated by using the shift of the mixture spectrum centroid. Thus we have:
+The radial velocity shift can be calculated by using the shift of the mixture spectra centroid. Thus we have:
 
@@
 \end{equation}
-Where $RV_{shift} $ is the radial velocity shift and $pixel_c^{shift}$ is the pixel centroid shift between the two spectrums.
+Where $RV_{shift} $ is the radial velocity shift and $pixel_c^{shift}$ is the pixel centroid shift between the two spectra.
 \bigskip
@@
 
-But if 2b<a+c, which means the magnitude of the spectrum moves one pixel left or right is big, the approximation will expire because the influence of the pixels two pixels left or right can't be ignored.
+But if 2b<a+c, which means the magnitude of the spectra moves one pixel left or right is big, the approximation will expire because the influence of the points two pixels left or right can't be ignored.
 When this happens, our formula won't work good.
@@
 
-Since the continuum fitting may mix with the RV calibration, we want to only use the absorption lines of the spectrum.
+Since the continuum fitting may mix with the RV calibration, we want to only use the absorption lines of the spectra.
 Choose some very clear absorption lines and fit them by using the formulas above.
-The line list can be found in the document about ASPCAP pipeline \cite{shetrone2015sdss}.
-However, there are few clear absorption lines in the APOGEE data release.
+The line list can be found in the document about ASPCAP pipeline However, there are few clear absorption lines in the APOGEE data release.
 Also, for different types of stars the clear absorption lines are different.
@@
 
-Pick up the absorption lines by using the Gaussian fit in the data spectrum.
+Pick up the absorption lines by using the Gaussian fit in the data spectra.
 Set the half-width of the gap to be 8 pixels or less.
@@
 % ?? How to choose lines
-We also compare the results between the old method(fit the whole spectrum) and the new method(only fit the clear absorption line) in experiment 3.
+We also compare the results between the old method(fit the whole spectra) and the new method(only fit the clear absorption line) in experiment 3.
 
@@
 The APOGEE team derive the radial velocities of individual visits by two steps.
-First, derive the relative radial velocity between each visit and the combined spectrum iteratively.
-Second, absolute radial velocity determination of the combined spectrum against a grid of synthetic spectra spanning a large range of stellar parameters.
-All radial velocities in these two steps are determined by cross-correlating a spectrum against a template spectrum.
+First, derive the relative radial velocity between each visit and the combined spectra iteratively.
+Second, absolute radial velocity determination of the combined spectra against a grid of synthetic spectra spanning a large range of stellar parameters.
+All radial velocities in these two steps are determined by cross-correlating a spectra against a template spectra.
 This means the result is very sensitive to the normalization method since the result of cross-correlation is influenced by normalization prominently.
-Also, the traditional synthesized spectrum in the second step is not very reliable, which means the absolute velocity is not very accurate.
+Also, the traditional synthesized spectra in the second step is not very reliable, which means the absolute velocity is not very accurate.
 From these two points, there is still much to be improved in APOGEE team's RV results.
-Meanwhile, the APOGEE team uses the whole spectrum to determine the radial velocity, which means the continuum-fitting may mix with the velocity fit.
-But in our experiment, we try to only use the absorption lines of the spectrum.
+Meanwhile, the APOGEE team uses the whole spectra to determine the radial velocity, which means the continuum-fitting may mix with the velocity fit.
+But in our experiment, we try to only use the absorption lines of the spectra.
 \bigskip
@@
  \subsection{\label{sec:level2}Experiment 1}
-To demonstrate the continuum normalization works well for combined spectrums and individual visits, we plot continuum pixels for stars with different SNR(signal to noise ratio), Teff and Logg.
+To demonstrate the continuum normalization works well for combined spectra and individual visits, we plot continuum pixels for stars with different SNR(signal to noise ratio), Teff and Log g.
 Here we randomly choose 5 stars with different SNR, Teff and logg and plot them in.
-If continuum pixels roughly cover the spectrums evenly, the normalization works well.
+If continuum pixels roughly cover the spectra evenly, the normalization works well.
 Here we only show on star.
@@
 \centerline{Fig.1 Comparison of each visit for Star A.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The red dots are continuum pixels}
+\centerline{The bottom two are the combined spectra and the others are individual visits. The red dots are continuum pixels}
 \centerline{SNR of Star A is 108. Teff = 4939K Logg =2.71 Fe/H =-5.368}
@@
 
-The other four stars are in appendix figure 1-4. These continuum pixels roughly cover the spectrums evenly, which means the normalization works well.
+The other four stars are in appendix figure 1-4. These continuum pixels roughly cover the spectra evenly, which means the normalization works well.
 
@@
 
-We can also demonstrate the continuum normalization works by inferring stellar labels from individual visits and compare them with the ones from combined spectrums.
+We can also demonstrate the continuum normalization works by inferring stellar labels from individual visits and compare them with the ones from combined spectra.
 Here we use formula 1, 2 and 3 to obtain delta-stellar labels.
@@
 
-We can see that these delta-stellar labels of individual visits are close to 0, which means the spectrums of individual visits don't change shape after the normalization.
+We can see that these delta-stellar labels of individual visits are close to 0, which means the spectra of individual visits don't change shape after the normalization.
 That's to say, the normalization works.
@@
 \centerline{Fig.5 Histogram of RV shifts, a, b and c of individual visits}
-\centerline{Here we fit the whole spectrum}
+\centerline{Here we fit the whole spectra}
 \end{center}
@@
 \centerline{Fig.6 RV shifts of individual visits VS HJD, RA, DEC, FiberID, AirMass and SNR}
-\centerline{Here we fit the whole spectrum}
+\centerline{Here we fit the whole spectra}
 \bigskip
@@
 
-\centerline{Fig.10 The four stars with biggest delta RV shifts}
-\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
+\centerline{Fig.10 The four visits with biggest delta RV shifts}
+\centerline{The red dots are the absorption lines we use}
+\centerline{The black lines and blue lines are data spectra and inferred spectra from the Cannon.}
 
@@
 
-\centerline{Fig.11 The four stars with biggest RV shifts from the new method.}
-\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
+\centerline{Fig.11 The four visits with biggest RV shifts from the new method.}
+\centerline{The red dots are the absorption lines we use}
+\centerline{The black lines and blue lines are data spectra and inferred spectra from the Cannon.}
 
@@
 The APOGEE team use Cross-correlation to derive RV shifts, which is very sensitive to the normalization method.
-Also, Cross-correlation means we need to interpolate the data, which may cause the broadening of the spectrum.
+Also, Cross-correlation means we need to interpolate the data, which may cause the broadening of the spectra.
 Here most of the RV shifts are smaller than one pixel(Figure 10) and this means the cross-correlation may not be very reliable.
@@
 
-Also, the APOGEE team fit the whole spectrum to derive the radial velocity.
+Also, the APOGEE team fit the whole spectra to derive the radial velocity.
 The fitting may mix with the continuum fitting, which is not good.
-But we only use the absorption lines in the spectrum and the result should be better.
+But we only use the absorption lines in the spectra and the result should be better.
 
@@
 \centerline{Fig.12 The individual visits of suspect Star 1}
-\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
+\centerline{The red dots are the absorption lines we use}
+\centerline{The black lines and blue lines are data spectra and inferred spectra from the Cannon.}
 
@@
 \centerline{Fig.13 The individual visits of suspect Star 2}
-\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
+\centerline{The red dots are the absorption lines we use}
+\centerline{The black lines and blue lines are data spectra and inferred spectra from the Cannon.}
 
@@
 \centerline{Fig.14 The individual visits of suspect Star 3}
-\centerline{The red dots are the absorption lines we use. The black lines and blue lines are data spectrums and inferred spectrums from the Cannon.}
+\centerline{The red dots are the absorption lines we use}
+\centerline{The black lines and blue lines are data spectra and inferred spectra from the Cannon.}
 
@@
 \centerline{Fig.1 Comparison of each visit for Star B.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{The bottom two are the combined spectra and the others are individual visits. The black dots are continuum pixels}
 \centerline{SNR of Star B is 139. Teff = 4872K Logg =2.91 Fe/H =3.486}
@@
 \centerline{Fig.2 Comparison of each visit for Star C.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{The bottom two are the combined spectra and the others are individual visits. The black dots are continuum pixels}
 \centerline{SNR of Star C is 108. Teff = 4833K Logg =2.86 Fe/H =6.577}
@@
 \centerline{Fig.3 Comparison of each visit for Star D.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{The bottom two are the combined spectra and the others are individual visits. The black dots are continuum pixels}
 \centerline{SNR of Star D is 140. Teff = 5094K Logg =3.088 Fe/H = -3.679 }
@@
 \centerline{Fig.4 Comparison of each visit for Star E.}
-\centerline{The bottom two are the combined spectrum and the others are individual visits. The black dots are continuum pixels}
+\centerline{The bottom two are the combined spectra and the others are individual visits. The black dots are continuum pixels}
 \centerline{SNR of Star E is 208. Teff = 4869K Logg =1.903 Fe/H = -1.691 }
@@
 
-Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
+Now we show the results of a, b and c from fitting the whole spectra.
+
+\begin{center}
+\includegraphics[width=170mm]{a_vs_all.png}
+\end{center}
+
+\centerline{Fig.5 a vs MJD, FiberID, RA and DEC for individual visitis}
+\centerline{Parameter a from fitting the whole spectra.}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{b_vs_all.png}
+\end{center}
+
+\centerline{Fig.6 b vs MJD, FiberID, RA and DEC for individual visitis}
+\centerline{Parameter b from fitting the whole spectra.}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{c_vs_all.png}
+\end{center}
+
+\centerline{Fig.7 c vs MJD, FiberID, RA and DEC for individual visitis}
+\centerline{Parameter c from fitting the whole spectra.}
+\bigskip
+
+After that, we show the results of a, b and c from fitting the absorption lines.
+
+\begin{center}
+\includegraphics[width=170mm]{a_vs_all_new.png}
+\end{center}
+
+\centerline{Fig.8 a vs MJD, FiberID, RA and DEC for individual visitis}
+\centerline{Parameter a from fitting the absorption lines.}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{b_vs_all_new.png}
+\end{center}
+
+\centerline{Fig.9 b vs MJD, FiberID, RA and DEC for individual visitis}
+\centerline{Parameter b from fitting the absorption lines.}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{c_vs_all_new.png}
+\end{center}
+
+\centerline{Fig.10 c vs MJD, FiberID, RA and DEC for individual visitis}
+\centerline{Parameter c from fitting the absorption lines.}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{Peak_1.png}
+\end{center}
+
+\centerline{Fig.11 The spectra of Star A}
+\centerline{SNR of Star A is 206. Teff = 4208K Logg =1.347 Fe/H =-1.018}
+\centerline{The red dots are the absorption lines we use}
+\centerline{The black lines and blue lines are data spectra and inferred spectra from the Cannon.}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{Peak_2.png}
+\end{center}
+
+\centerline{Fig.12 The spectra of Star B}
+\centerline{SNR of Star B is 197. Teff = 4641K Logg =2.201 Fe/H =-5.873}
+\centerline{The red dots are the absorption lines we use}
+\centerline{The black lines and blue lines are data spectra and inferred spectra from the Cannon.}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{Peak_3.png}
+\end{center}
+
+\centerline{Fig.13 The spectra of Star C}
+\centerline{SNR of Star C is 117. Teff = 4902K Logg =2.639 Fe/H =-1.863}
+\centerline{The red dots are the absorption lines we use}
+\centerline{The black lines and blue lines are data spectra and inferred spectra from the Cannon.}
+\bigskip
+
+\begin{center}
+\includegraphics[width=170mm]{Peak_4.png}
+\end{center}
+
+\centerline{Fig.14 The spectra of Star D}
+\centerline{SNR of Star D is 122. Teff = 4813K Logg =2.736 Fe/H = -1.832}
+\centerline{The red dots are the absorption lines we use}
+\centerline{The black lines and blue lines are data spectra and inferred spectra from the Cannon.}
+\bigskip
 

### 2017-02-28 paper/ms.tex
Fit labels and abc simultaneously

@@
 
+%% Let's do it in a simple way
+
 \subsection{\label{sec:level2}optimize Teff , log g and [Fe/H] simultaneously with a, b, c}
 
-Working on it...
+Suppose we have a trained Cannon model. To infer the labels from the fluxes, we need to minimize the objective function:
+
+\begin{equation}
+l_m \leftarrow \left[ \sum_{j=1}^{j=J}{({y_{j,n}-V(l_m)\cdot \theta_j)^2} \over {e^2_{j,n}}} \right]
+\end{equation}
+
+$l_m$ is the $m$ th label of star n. V is the vectorizer and ${e^2_{j,n}}$ is the error of star n at pixel j, which include scatter and variance.
+
+If we include parameters a, b and c, the objective function will be:
+
+\begin{equation}
+l_m, a, b, c \leftarrow \left[ \sum_{j=1}^{j=J}{({y_{j,n} - a*V(l_m)\cdot \theta_{j + 1} - b*V(l_m)\cdot \theta_{j} - c*V(l_m)\cdot \theta_{j-1})^2} \over {e^2_{j,n}}} \right]
+\end{equation}
+
+Now we can obtain inferred labels and a, b and c simultaneously. And the new inferred flux is:
+
+\begin{equation}
+y_{j,n}^{inf,sim} = a*V(l_m)\cdot \theta_{j + 1} - b*V(l_m)\cdot \theta_{j} - c*V(l_m)\cdot \theta_{j-1}
+\end{equation}
+
+$y_{j,n}^{inf,sim} $ is the inferred flux from the new method, which fits labels and abc simultaneously.
+
+The results from this method are in experiment 5
 
@@
 
+ \subsection{\label{sec:level2}Experiment 5}
+ In experiment 5, we will check whether our method works. The method is to plot the new inferred labels against reference labels. Here we use the 548 stars in the training set.
+
+ \begin{center}
+\includegraphics[width=170mm]{sim_diagnostic.png}
+
+\centerline{Fig.15 Inferred labels VS reference labels of the new method.}
+
+\end{center}
+
+From figure 15 we can see that the inferred labels are close to the reference labels, which means the method works.
+
+ After that, we show the histogram of parameters a, b and c.
+
+ \begin{center}
+\includegraphics[width=170mm]{hist_rv_abc_sim.png}
+
+\centerline{Fig.16 The histogram of the results from simultaneous fitting}
+
+\end{center}
+
+We also shows the results VS FiberID, RA, DEC, SNR, HJD and AirMass.
+
+ \begin{center}
+\includegraphics[width=170mm]{ve_vs_all_sim.png}
+
+\centerline{Fig.17 RV shifts from simultaneous fitting}
+
+\end{center}
+
+# We also compare the results from the whole spectrum(The original method) and fitting simultaneously.
+
+ \begin{center}
+\includegraphics[width=170mm]{old_vs_new_sim.png}
+
+\centerline{Fig.18 Comparison of the results from fitting the whole spectrum and fitting simultaneously}
+
+\end{center}
+
  %% Fourth paragraph

### 2017-02-28 0228_opt_simultaneously_1_data.py

@@ -1,0 +1,182 @@
+import os
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import matplotlib
+import pickle
+
+import astropy.io.fits as ts
+import AnniesLasso_2 as tc
+
+
+import math
+
+def get_pixmask(flux, err):
+    bad_flux = ~np.isfinite(flux)
+    bad_err = (~np.isfinite(err)) | (err <= 0)
+    bad_pixels = bad_err | bad_flux
+    return bad_pixels
+
+
+
+
+# train the cannon
+
+
+## training the cannon
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+training_set_path = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/reference_labels.csv"
+training_set_spectrum_dir = "/Users/caojunzhi/Desktop/NYU/Laboratory/task 2016.8.1-12.23/My codes/Cannon Experiment python 3.5/Data/"
+
+training_set = Table.read("reference_labels.csv")
+
+N = len(training_set)
+keep = np.ones(N, dtype=bool)
+
+training_set_flux = []
+training_set_ivar = []
+training_set_error = []
+
+for i, row in enumerate(training_set):
+    image_path = os.path.join(training_set_spectrum_dir, row["ID"])
+    if not os.path.exists(image_path):
+        print("{}/{} could not be found: {}".format(i + 1, N, image_path))
+        keep[i] = False
+        continue
+    print("{}/{}: {}".format(i + 1, N, image_path))
+    image = fits.open(image_path)
+    flux = image[1].data
+    flux_err = image[2].data
+    badpix = get_pixmask(flux, flux_err)
+    ivar = 1.0 / flux_err ** 2
+    error = flux_err
+    # badpix is a array and the length is 8575
+    flux[badpix] = 1.0
+    ivar[badpix] = 0.0
+    training_set_flux.append(flux)
+    training_set_ivar.append(ivar)
+    training_set_error.append(error)
+
+training_set_flux = np.array(training_set_flux)
+training_set_ivar = np.array(training_set_ivar)
+training_set_error = np.array(training_set_error)
+
+assert all(keep)
+
+# Construct model.
+model = tc.L1RegularizedCannonModel(
[…]

### 2017-02-28 0228_plot_simultaneously_labels.py

@@ -1,0 +1,1890 @@
+
+import numpy as np
+from astropy.table import Table
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import matplotlib
+import pickle
+
+from TheCannon_2 import dataset,apogee
+from TheCannon_2 import model
+
+
+pkl_file = open('wl.pkl', 'rb')
+wl = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# load path
+
+pkl_file = open('n_900_path_fits.pkl', 'rb')
+path_fits = pickle.load(pkl_file)
+pkl_file.close()
+
+
+pkl_file = open('n_900_path_flux.pkl', 'rb')
+path_flux = pickle.load(pkl_file)
+pkl_file.close()
+
+
+# mean_ivar
+
+pkl_file = open('n_900_mean_ivar.pkl', 'rb')
+mi = pickle.load(pkl_file)
+pkl_file.close()
+
+
+
+
+
+N = len(path_fits)
+print(N)
+
+
+# here parameter_sim represent the results from simultaneously fitting
+
+
+class plot():
+
+    def read_data(self):
+
+        N = len(path_fits)
+        print(N)
+
+        velocity = []
+        velocity_new = []
+        fiber_id = []
+        mean_ivar = []
+        parameters = np.array([0,1,0])
+        parameters_new = np.array([0,1,0])
+        parameters_sim = np.array([0,1,0])
+
+
+
+        inf_label = []
+        dchi = []
+
+        MJD = []
+        HJD = []
+        meanivar = []
+
+        RA = []
+        DEC = []
+        SNR = []
+
+        airmass = []
+
+        # star name and the number of visit
+        # dimension N*2
+        star_visit = []
+        star_name = []
+
+
+
+        for i in range(0, N):
+            print("loading star %d" % (i + 1))
+
+            star_name_i = path_fits[i]
+
+            star_i = fits.open(path_fits[i])
+
+            ni = len(star_i[4].data[:, 0])
+
+
+
+            # mean ivar
+            one = np.ones(ni - 2)
+            for si in range(0,ni-2):
+                star_name = np.append(star_name, star_name_i)
+                star_visit.append(si)
+
+            meanivar = np.append(meanivar, one * mi[i])
+
+
[…]

### 2017-03-01 paper/ms.tex
Add plot
Biggest delta_RV between the two methods

@@
 
-\subsection{\label{sec:level2}optimize Teff , log g and [Fe/H] simultaneously with a, b, c}
+\subsection{\label{sec:level2} Optimize Teff , log g and [Fe/H] simultaneously with a, b, c}
 
@@
 \begin{equation}
-l_m \leftarrow \left[ \sum_{j=1}^{j=J}{({y_{j,n}-V(l_m)\cdot \theta_j)^2} \over {e^2_{j,n}}} \right]
+l_m \leftarrow argmin \left[ \sum_{j=1}^{j=J}{({y_{j,n}-V(l_m)\cdot \theta_j)^2} \over {e^2_{j,n}}} \right]
 \end{equation}
@@
 \begin{equation}
-l_m, a, b, c \leftarrow \left[ \sum_{j=1}^{j=J}{({y_{j,n} - a*V(l_m)\cdot \theta_{j + 1} - b*V(l_m)\cdot \theta_{j} - c*V(l_m)\cdot \theta_{j-1})^2} \over {e^2_{j,n}}} \right]
+l_m, a, b, c \leftarrow argmin \left[ \sum_{j=1}^{j=J}{({y_{j,n} - a*V(l_m)\cdot \theta_{j + 1} - b*V(l_m)\cdot \theta_{j} - c*V(l_m)\cdot \theta_{j-1})^2} \over {e^2_{j,n}}} \right]
 \end{equation}
@@
 
- After that, we show the histogram of parameters a, b and c.
+After that, we show the histogram of parameters a, b and c, which are from individual visits of the 654 stars in the former experiment.
 
@@
 
-# We also compare the results from the whole spectrum(The original method) and fitting simultaneously.
+We also compare the results from the whole spectrum(The original method) and fitting simultaneously.
 
@@
 \centerline{Fig.18 Comparison of the results from fitting the whole spectrum and fitting simultaneously}
+
+\end{center}
+
+Finally, we choose the sixteen visits with biggest $delta_RV$, which is defined as the difference between the RV shifts from the whole spectrum(The original method) and simultaneous fitting.
+
+ \begin{center}
+\includegraphics[width=170mm]{big_delta_rv_sim.png}
+
+\centerline{Fig.18 The visits with biggest $delta_RV$ part 1}
+
+\end{center}
+
+ \begin{center}
+\includegraphics[width=170mm]{big_delta_rv_sim2.png}
+
+\centerline{Fig.19 The visits with biggest $delta_RV$ part 2}
+
+\end{center}
+
+ \begin{center}
+\includegraphics[width=170mm]{big_delta_rv_sim3.png}
+
+\centerline{Fig.20 The visits with biggest $delta_RV$ part 4}
+
+\end{center}
+
+ \begin{center}
+\includegraphics[width=170mm]{big_delta_rv_sim4.png}
+
+\centerline{Fig.21 The visits with biggest $delta_RV$ part 4}
 

### 2017-04-06 paper/document.tex
CannonRV

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout mixions. There are lots.

\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath, amsthm, amssymb, amsfonts}

\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}

\usepackage{amsmath}

\bibliographystyle{abbrv}

%SetFonts

%SetFonts

\title{CannonRV: Measuring radial velocities with a data-driven spectral model}
\author[1]{Jason Cao\thanks{jc6933@nyu.edu}}
\author[2]{David W. hogg\thanks{david.hogg@nyu.edu}}
\author[3]{Melissa Ness\thanks{ness@mpia-hd.mpg.de}}

\affil[1]{Department of Physics,  New York University}
\affil[2]{NYU Physics - Center for Cosmology and Particle Physics
NYU Center for Data Science
Max-Planck-Institut fuer Astronomie }
\affil[3]{
Max-Planck-Institut Max-Planck-Institut fuer Astronomie 17, D-69117 Heidelberg, Germany
}

\renewcommand\Authands{ and }

\date{\today}						% Activate to display a given date or no date

\begin{document}
\maketitle

%%Okay these look great. Can you write a title and abstract for a possible paper on this? Let's put the method aside for a bit and try to write down what we think we have done, why, and what we have learned, in the form of an abstract.

\section{\label{sec:level1}Abstract}

\begin{flushleft}
The calculation of spectra radial velocities(RV) plays an important role in stellar spectroscopy. By doing cross-correlation between the data spectra and the spectral template, radial velocity of each epoch can be derived with high precision and most of the stars have smaller than one pixel shift between individual visits \cite{perez2016aspcap}. As a result, the individual visits for one star do have small but not zero RV shifts between each other. Using the traditional cross-correlation to calibrate shifts smaller than one pixel always involves interpolation, which may smooth the spectra. Thus, people are in badly need of an effective tool for small RV shifts calibration. Here we introduce CannonRV, a new RV calibration tool for small shifts based on the synthesized spectra from the Cannon, which is a data driven spectral model that has been proven to work well in APOGEE DR10 and DR12 data\cite{ness2015cannon}\cite{casey2016cannon}. By assuming the synthesized spectra from the Cannon are at rest, we use these spectra as calibration templates for each visit of every star. CannonRV obtains the RV shifts between two spectra by calculating the shift of centroid with least chi-squared method\cite{hogg2010data}, which doesn't include any interpolation or cross-correlation. CannonRV also generates a new spectra, called mixed spectra, which is the linear combination of the Cannon synthesized spectra moving one pixel left, itself and one pixel right. The mixed spectra is closer to the data spectra than the original Cannon synthesized spectra in aspect of chi-squared. We apply CannonRV on part of the DR10 and all red clump stars in DR13 and it gives us some promising results, including the RV shifts between individual visits become smaller after the calibration . The RV calibration results for the red clump stars in DR13, as well as our source code for calculating small RV shift between two spectra are available online.
\end{flushleft}

\begin{flushleft}
{\large \bf Key words: The Cannon, least squared ,Centroid shift, small RV shifts, epoch level.}
\end{flushleft}

\begin{flushleft}
{\large \bf Supporting material: Source code and binary table of the RV calibration results for the red clump stars in DR13.}
\end{flushleft}

%% Both inferring stellar labels ($T_{eff}$, $log\ g$, $[M/H]$) from spectra and generating synthesized spectra from labels

 %% second paragraph

 \section{\label{sec:level1}Assumption and method}

503 Service Unavailable

% \subsection{\label{sec:level2}Continuum normalization}

%% Third paragraph

 \section{\label{sec:level1}Experiment}

503 Service Unavailable

% \subsection{\label{sec:level2}Experiment 1}

\bigskip

{\huge \bf

\begin{center}
reference
\end{center}
}

\bibliography{citation,pubext}

\end{document}

### 2017-04-06 paper/document.tex
Add spectral broadening part

@@
 By assuming the synthesized spectra from the Cannon are at rest, we use these spectra as calibration templates for each visit of every star.
-CannonRV obtains the RV shifts between two spectra by calculating the shift of centroid with least chi-squared method\cite{hogg2010data}, which doesn't include any interpolation or cross-correlation.
-CannonRV also generates a new spectra, called mixed spectra, which is the linear combination of the Cannon synthesized spectra moving one pixel left, itself and one pixel right.
+First, CannonRV introduces a new spectra, called mixed spectra, which is the linear combination of the Cannon synthesized spectra moving one pixel left, itself and one pixel right.
+By fitting the mixed spectra to the data spectra using least chi squared fitting\cite{hogg2010data}, CannonRV obtains the mixed spectra and the parameters for it.
 The mixed spectra is closer to the data spectra than the original Cannon synthesized spectra in aspect of chi-squared.
-We apply CannonRV on part of the DR10 and all red clump stars in DR13 and it gives us some promising results, including the RV shifts between individual visits become smaller after the calibration .
+Both the RV shifts and the broadening of the spectra can be derived from these mixed spectra parameters.
+We apply CannonRV on part of the DR10 and all red clump stars in DR13 and it gives us some promising results, including the RV shifts between individual visits become smaller after the calibration and the spectral broadening becomes bigger as the increase of Fiber ID.
 The RV calibration results for the red clump stars in DR13, as well as our source code for calculating small RV shift between two spectra are available online.
